### 2023-03-21 Cap2.tex
Main Resumen

\section{Circuits for Pauli Maps}

\begin{itemize}
\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many different one-qubit channels inside the tetrahedron.
\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state.
\end{itemize}

### 2023-03-21 Cap3.tex
Main Resumen

\section{OPR Circuits}
\begin{itemize}
\item How can we reduce the amount of parametrized rotations used?
\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
\item \textbf{Theorem about OPR circuits:} The theorem gives the general form that the operator of an OPR circuit can have. \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
\begin{align*}
U = (\vec{v}_0, \vec{v}_1, \cdots, \vec{v}_{2^n-1})
\end{align*}
\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
\end{itemize}

### 2023-03-21 Cap5.tex
Main Resumen

\section{Exponential maps $e^{iHt}$}
\begin{itemize}
\item We will apply the results about OPR circuit to another kind of operation.
\item Consider operations $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
\item \textbf{Theorem:} A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.
\item \textbf{Examples:} Every matrix $H$ for one qubit, any $n$-qubit pauli matrix, some sums of Pauli matrices, etc.
\end{itemize}

### 2023-03-21 Cosas-Escritas-Antes.tex
Main Resumen

\section{Resumen}
\begin{itemize}
\item In this work we study parametrized quantum circuits used to implement
quantum operations over qubit systems. 
\item Specifically, we study two types of operations: Pauli
dynamical maps and transformations of the form $e^{iHt}$ on $n$ qubits. 
\item We focus mainly on operations that can be implemented using a circuit 
with only one parametrized rotation gate (OPR Circuit). 
\item We get the conditions on these operations to be
applied with an OPR circuit:\\

\textbf{Theorem:} An OPR circuit with parameter $p$ on $n$ qubits always has an operator of the form:
\begin{eqnarray}
U  = (\vec{v}_0, \vec{v}_1, \cdots, \vec{v}_{2^n-1})
\end{eqnarray}
where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$. \\

\item We propose a circuit to simulate Pauli dynamical maps on $n$ qubits using $2n$ ancilla qubits. We find the conditions for channels that can be simulated by an OPR circuit and some examples that fulfill these conditions.

\item We find the conditions that a matrix $H$ must have for the operation $e^{iHt}$ to be implementable with an OPR circuits: \\

 \textbf{Theorem:} An $n-$qubits operator $U = e^{iHt}$ (with $H$ time-independent) can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda, 0, \lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are $2^j$ for some $j$ such that $0 \leq j <n$.
\item We find how to construct the OPR circuit that implements $e^{iHt}$ given the conditions of the theorem and see some examples.

\item Finally, we implement some of these
circuits on IBM's quantum computers and obtain their fidelities.
\end{itemize}
\newpage

\section{Partes más desarrolladas}
\subsection{Resumen}
In this work we study parametrized quantum circuits used to 
implement quantum operators over qubits systems on a quantum computer. 
Specifically, we study Pauli dynamical maps and unitary transformations of the form $e^{iHt}$.
 We focus mainly on operations that can be implemented using a circuit  with only one parametrized rotation gate (OPR circuit),
 and get the conditions these operations must satisfy for 
 being applicable on an OPR circuit.
Finally, we implemented some specific examples of these circuits on IBM's quantum computers
and obtain the fidelity of this implementation.

\subsection{Introduction}
\begin{itemize}
\item 
\end{itemize}

\subsection{OPR Circuits}

\textbf{Definition, Circuit with one parametrized Gate (OPR circuit):} A quantum circuit
 that contains only one gate that depends on a parameter $p$.
Furthermore, the parametrized gate is a one qubit rotation about any axis. \\

\textbf{Property 1:} \textit{An $n$-qubit OPR circuit can always be transformed into the form of circuit \ref{fig: OPR general}, where $A$ and $B$ are $n$-qubit gates that don't depend on the parameter
and $s = s(p)$ is a function of the parameter.}\\

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate[wires = 4,nwires=3]{B} & \ctrl{3} & \qw & \gate[wires=4,nwires=3]{A} & \qw \\
\lstick{$q_1$} & \qw &  & \ctrl{2} & \qw & & \qw \\
\vdots & \vdots & & & \vdots & \\
\lstick{$q_{n-1}$} & \qw & & \gate{R_{\sigma_3}(2s(p))} & \qw & & \qw
\end{quantikz}
\caption{Forma general de un circuito RP.}
\label{fig: OPR general}
\end{figure}

First of all, we notice that by definition an OPR
will always consist on some operation $B$ followed by the parametrized rotation 
and then some operation $A$, where $A$ and $B$ are not parametrized.

Then, we notice that it isn't necessary to consider rotations
about an arbitrary axis, since a rotation about $\hat{n}$ parametrized by $p$ can
be converted into a rotation about $\sigma_3$ without the need of introducing gates that depend on $p$.
To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ is some function of $p$ (the $2$ is added for convenience later on) and $\hat{n} = (n_1,n_2,n_3)$ is the rotation axis,
 which can be written as $(n_1,n_2,n_3) = (\sin \theta \cos \phi , \sin \theta\sin \phi, \cos \theta)$ for some fixed angles $\phi, \theta$ dependent on $\hat{n}$. 
 Then, the rotation can be rewritten as (ref 12 de la tesis):
\begin{eqnarray}
R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
\end{eqnarray}
Because angles $\theta, \phi$ don't depend on the parameter $p$, 
any OPR circuit can be converted into a circuit in which the parametrized rotation is around $\sigma_3$ instead of an arbitrary axis.

Furthermore, the qubit to which the rotation is applied can be selected to be the last one,
since otherwise  swap gates can be added before and after the rotation to make it act on the last qubit.

Therfore, an OPR circuit can be transformed in a way that the rotation is around $\sigma_3$ and applied on the last qubit 
(possibly controlled by other qubits), 
so that it has the form \ref{fig: OPR general}. $\blacksquare$ \\ \\

\textbf{Property 2:} \textit{An OPR circuit implements an operator with a matrix in the computational basis of the form:}
\begin{eqnarray}
U = (|\vec{v}_0|, |\vec{v}_1|, |\vec{v}_2|, \cdots, |\vec{v}_{2^n-1}|),
\end{eqnarray}
\textit{where the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$,
with $\vec{a}_j ,\vec{b}_j, \vec{c}_j$ orthogonal and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}\\

\textbf{Proof:} Because of property 1, we know that any OPR
circuit can be converted into the form \ref{fig: OPR general},
so that we only need to consider the operator for that circuit. 
The $j$-th column of the circuit's matrix will be the result of applying the 
circuit to the state $|j\rangle$. 
First, applying $B$ to that state results in $B_{0,j} |0\rangle |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
 which can be rewritten by separating the states to which the controlled 
rotation will be applied from those to which it won't as follows:
\begin{eqnarray}
\sum_{k \in Ctrl} \left(B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right) + \sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j}|k\rangle |1\rangle \right),
\end{eqnarray}
where $Ctrl$ is the set of all basis states of the first $n-1$ qubits
such that they fulfill the controls of the rotation gate and therefore the gate is applied.

After $B$ creates this state, we need to apply the rotation to the result. 
This rotation will only be applied for those states on the first sum (since the fulfill the control conditions)
and not to the others. Therefore, we apply the gate to the last qubit of these states, 
remembering that $R_z(2s)$ acts by just adding a phase $e^{-is}$ to the $|0\rangle$ state
and a phase $e^{is}$ to the $|1\rangle$ state, and the result is:
\begin{eqnarray}
& \fl e^{-is} \sum_{k \in Ctrl} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle + \sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
& \qquad := e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
\end{eqnarray}
where $\vec{a'} = \sum_{k \in Ctrl} B_{2k,j}|k\rangle|0\rangle \;,\; \vec{b'}_j = \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle \;,\; \vec{c'}_j =\sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right) := e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j$.
 These vectors are clearly orthogonal because they are each linear combinations of different orthogonal states of the computational basis. 
Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the norm of the $j-$th column of $B$.

Finally, after having applied the rotation, the circuit applies gate $A$, 
so that the result is given by:
\begin{eqnarray}
e^{-is} A \vec{a'}_j + e^{is} A \vec{b'}_j + A \vec{c'}_j := e^{-is} \vec{a}_j + e^{is} \vec{b}_j + \vec{c}_j := \vec{v}_j,
\end{eqnarray}
where $\vec{a}_j = A \vec{a'}_j , \vec{b}_j = A \vec{b'}_j , \vec{c}_j = A \vec{c'}_j$ are orthogonal
vectors that satisfy $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$ because $A$ is unitary. 
Therefore, we conclude that the circuit takes a state $|j\rangle$ and converts it
 into the state represented by the vector $\vec{v}_j$, which means that the matrix representation of the circuit's operation is
 $U = (|\vec{v}_0|, |\vec{v}_1|, \cdots, |\vec{v}_{2^n-1}|)$. \\
\subsection{Pauli Channels and maps}
\subsubsection{Basic Definitions}

\begin{itemize}
\item A system of n-qubits can be represented by a positive matrix $\rho$ of size $2^n \times 2^n$ called the density matrix.
\item  An important set of operators acting on these systems are the Pauli operators, which are defined as
\begin{eqnarray}
\sigma_{\vec{\alpha}} = \sigma_{\alpha_1} \otimes \sigma_{\alpha_2} \otimes \cdots \otimes \sigma_{\alpha_n},
\end{eqnarray}
where $\vec{\alpha} = (\alpha_0, \alpha_1, \cdots , \alpha_{n-1})$ , $\alpha_i \in \{0,1,2,3\}$ and $\sigma_{\alpha_i}$ is the $\alpha_i$-th one qubit Pauli operator. \\

\item Using these operators, we define a Pauli channel as a transformation of the density matrix given by
\begin{eqnarray}
\varepsilon(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}} \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}} ,
\end{eqnarray}
where $k_{\vec{\gamma}}$ are positive real numbers such that $\sum_{\vec{\gamma}} k_{\vec{\gamma}} = 1$ (necessary conditions for the channel $\varepsilon$ to be completely positive and trace preserving).\\
\end{itemize}

\subsubsection{Circuit for a Pauli Channel}

We are interested in finding a way to construct a quantum circuit that can implement an arbitrary Pauli channel on a system of $n$ qubits. To do it, it is important to realize that a Pauli channel $\varepsilon (\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}} \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}}$ can be interpreted as an statistical mixture of the Pauli operators $\sigma_{\vec{\gamma}}$ applied to the density matrix $\rho$  with  probabilities $k_{\vec{\gamma}}$. That is, it can be interpreted as a transformation that applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.

Given this interpretation of the channel, it is easy to construct a quantum circuit that implements it with the help of $2n$ ancilla qubits. The general idea is to first construct a state on the ancilla qubits and then use this state and controlled gates to  apply each Pauli operator $\sigma_{\vec{\gamma}}$ with probability $k_{\vec{\gamma}}$ on the principal qubits.

The circuit that does this is presented in figure \ref{fig: circuito}, where $|\vec{\gamma}\rangle$ is defined as the $2n$ qubits state $|\vec{\gamma} \rangle = \otimes_{i=0}^n |\gamma_i \; \text{in binary} \rangle$. For example, if $\vec{\gamma} = (0,3,1,\cdots)$, then this state is defined as $|\vec{\gamma} \rangle = |001101 \rangle$.

\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
 vectors $\vec{\gamma}$} \\
\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1}}} & \qw & & &\\
\lstick{ } & & & & & &\\
\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2n$ qubits state $\sum_{\vec{\gamma}} \sqrt{k_{\vec{\gamma}}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=2]{$|\gamma_0 \rangle$} &  & & &\\
\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & \rstick[wires=2]{$|\gamma_1 \rangle$} & & & &\\
\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
\lstick{$aq_{2n-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & \rstick[wires=2]{$|\gamma_{n-1} \rangle$}& & & & \\
\lstick{$aq_{2n-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
\end{quantikz}
\caption{Circuit for a n-qubit Pauli channel.}
\label{fig: circuito}
\end{figure}

Where

\begin{figure}[h!]
\centering
\begin{quantikz}
& \ctrl{1} & \qw \rstick[wires=2]{$|\gamma_i \rangle$} \\
& \control{} & \qw
\end{quantikz}
\end{figure}
indicates that the controlled gate is activated if these two qubits are in the state $|\gamma_i \rangle$. In particular, using the common notation for controlled gates, we have
\begin{figure}[h!]
\centering
\begin{quantikz}
& \octrl{1} & \qw \rstick[wires=2]{if $\gamma_i = 0$} \\
& \ocontrol{} & \qw
\end{quantikz} \begin{quantikz}
& \octrl{1} & \qw \rstick[wires=2]{if $\gamma_i = 1$} \\
& \control{} & \qw
\end{quantikz}  \begin{quantikz}
& \ctrl{1} & \qw \rstick[wires=2]{if $\gamma_i = 2$} \\
& \ocontrol{} & \qw
\end{quantikz}  \begin{quantikz}
& \ctrl{1} & \qw \rstick[wires=2]{if $\gamma_i = 3$} \\
& \control{} & \qw
\end{quantikz}
\end{figure}

To see why this circuit works, we note that after creating the state $\sum_{\vec{\gamma}} \sqrt{k}_{\gamma} \; |\vec{\gamma} \rangle$, the circuit applies each gate $\sigma_{\vec{\gamma}}$ to the principal qubits under the condition that the ancilla qubits are on the state $|\vec{\gamma}\rangle$. This  means that each gate $\sigma_{\vec{\gamma}}$ is applied on the principal qubits with a probability $\sqrt{k_{\vec{\gamma}}}$, just as we wanted.  \\

\subsubsection{Pauli Dynamical Maps}

A Pauli dynamical map is defined as a continuous parametrized curve drawn inside the set of Pauli channels and starting at the identity channel. Therefore, a Pauli dynamical map can be written as
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
where $p$ is a parameter belonging to an interval $[a,b]$ and $\varepsilon_p$ is a Pauli channel for every $p$, with $\varepsilon_a$ being the identity channel.

Dynamical maps can be implemented using the same method as in figure \ref{fig: circuito}, with the only difference that now the state to be created on the ancilla qubits depends on parameter $p$ and it is given by $\sum_{\vec{\gamma}} \sqrt{k_{\vec{\gamma}}(p)} |\vec{\gamma}\rangle$.  \\

\subsubsection{OPR Circuit for dynamical maps}

For OPR circuits, the ancilla state has to be created with only one parametrized curve. Then, the theorem for OPR circuits implies that a map
\begin{eqnarray}
\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
\end{eqnarray}
can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
\begin{eqnarray}
\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} \cos s + \vec{b} \sin s
\end{eqnarray}
where $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors in $\mathbb{C}^{2n}$ and $|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2= 1$.

\subsubsection{Examples on one qubit and implementation on IBM computers}

For the special case of a system consisting of only one qubit, a Pauli channel takes the form
\begin{eqnarray}
\varepsilon(\rho) = k_0 I \rho I + k_1 X \rho X + k_2 Y \rho Y + k_3 Z \rho Z,
\end{eqnarray}
and the circuit that can be used to implement it reduces to:
\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
\lstick{$aq_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
\lstick{$aq_1$} & \gateinput{$\sqrt{k_0} |0 \rangle |0 \rangle + \sqrt{k_1} |0 \rangle |1 \rangle + \sqrt{k_2} |1 \rangle |0 \rangle + \sqrt{k_3} |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
\end{quantikz}
\caption{ Circuit for a one qubit Pauli channel.}
\label{fig: canal-1qbit} 
\end{figure}

This circuit can be applied for any one-qubit Pauli channel. It is well known that these channels can be represented as points in a tetrahedron with corners $(1,1,1)$, $(1,-1,-1)$, $(-1,1,-1)$ and $(-1,-1,1)$. To put the circuit to test, we sampled $250$ points inside the tetrahedron and applied quantum process tomography to each one by using Qiskit's ibmq-lima quantum computer. The fidelity of the Choi matrix obtained by quantum process tomography with respect to the theoretical Choi matrix of each channel was calculated and is plotted in the next figure.

\begin{figure}[h!]
\centering
\includegraphics[width=0.45\textwidth]{fidelidad-puntos.png}\\
\caption{Fidelity of one qubit channels using Qiskit's ibmq-lima.}
\end{figure}

\paragraph{$\sigma_3$ parabolic map} $\;$ \\

We take as an example the Pauli dynamical map for one qubit defined as
\begin{eqnarray}
\epsilon(\rho) = \dfrac{1}{4} (1-p)^2 \sigma_0 \rho \sigma_0 + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
\end{eqnarray}
with $p \in [-1,1]$. \\

To implement this dynamical map using the circuit presented in figure \ref{fig: one-rot}, it is necessary to create the state
\begin{eqnarray}
\left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right)
\end{eqnarray}
on the $2$ ancilla qubits. Luckily, this state can be written in the form $\vec{c} + \vec{a} \cos s + \vec{b} \sin s$ as
\begin{eqnarray}
\begin{pmatrix}
1/2 \\
0 \\ 
0 \\
1/2
\end{pmatrix} + \begin{pmatrix}
0 \\
1/2 \\
1/2 \\
0
\end{pmatrix}  \cos s + \begin{pmatrix}
-1/2 \\
0 \\
0 \\
1/2
\end{pmatrix} \sin s
\end{eqnarray}
with $s = \arcsin p$. According to theorem 1, the fact that the state we need to create over the ancilla qubits can be written like this implies that the dynamical map can be simulated in a quantum computer using only one parametrized rotation. The circuit used will have the same form as that in figure \ref{fig: canal-1qbit}, where the part used to create the state on the ancilla qubits will be:
\begin{figure}[h!]
\centering
\begin{quantikz}
\lstick{$aq_0$} & \gate[wires=2]{B} & \ctrl{1} & \gate[wires=2]{A} & \qw \\
\lstick{$aq_{1}$} & & \gate{R_{\sigma_2}(2s)} & & \qw  \\
\end{quantikz}
\caption{Circuit to create 2-qubit state}
\end{figure}

where according to theorem 1, matrices $A$ and $B$ can be chosen as:
\begin{eqnarray}
A &= \begin{pmatrix}
*  & c_0 / \sqrt{1-r^2} & -b_0/r & a_0 /r \\
*  & c_1 / \sqrt{1-r^2} & -b_1/r & a_1 /r \\ 
* & c_2 / \sqrt{1-r^2} & -b_2/r & a_2/r \\
* & c_3 / \sqrt{1-r^2} & -b_3/r & a_3/r \\
\end{pmatrix} = \begin{pmatrix}
0 & 1/\sqrt{2} & -1/\sqrt{2} & 0 \\
-1/\sqrt{2} & 0 & 0 & 1/\sqrt{2} \\
1/\sqrt{2} & 0 & 0 & 1/\sqrt{2} \\
0 & 1/\sqrt{2} & 1/\sqrt{2} & 0
\end{pmatrix} \\
B& = \begin{pmatrix}
0 & 0 & 0 & 1 \\
0 & 1 & 0 & 0\\
0 & 0& 1 & 0 \\
1 & 0 & 0 & 0 
\end{pmatrix}
\end{eqnarray}

To put it to test, we selected $20$ equally spaced values of $p$ between $-0.9$  and $0.9$ and implemented the corresponding circuit using the ibmq-Lima quantum computer. For each point, we used quantum process tomography to obtain the Choi matrix for the channel. Then, we calculated the fidelity of this matrix with respect to the theoretical Choi matrix of the channel. The following figure shows the fidelity of the simulated circuit for each value of $p$.
\begin{figure}[h!]
\centering
\includegraphics[width=0.55\textwidth]{fidelity-parabolic.PNG} \\
\caption{Fidelity for the Parabolic channel.}
\end{figure}

\newpage
\subsection{Unitary evolution $U = e^{iHt}$}

We are now interested on what conditions must an $n$-qubit time independent Hamiltonian $H$
fulfill for the unitary operator $U = e^{iHt}$ to be
implementable with an OPR circuit of $n$ qubits. \\

\textbf{Lemma:} \textit{The $n$-qubit operator $U = e^{iHt}$ can be implemented with an OPR circuit of $n$ qubits
if and only if $D = diag(e^{i\lambda_0 t}, \cdots, e^{i\lambda_{2^n-1}t})$ can be implemented with an OPR circuit of $n$ qubits,
where $\lambda_j$ is the $j$-th eigenvalue of $H$}\\

\textbf{Proof:} The hamiltonian $H$ can be diagonalized as $QHQ^{-1} = diag(\lambda_0,\lambda_1, \cdots,\lambda_{2^n-1})$
 where $Q$ is the  change of  basis matrix and doesn't depend on the parameter $t$ 
 (because $H$ is time independent). Then, the unitary matrix $U = e^{iHt}$ can be diagonalized similarly as $D = QUQ^{-1}$ where $D = diag(e^{i\lambda_0 t}, \cdots, e^{i\lambda_{2^n-1}t})$.

Then, if we have an OPR circuit for $U = e^{iHt}$, adding $Q$ and $Q^{-1}$ before and after the circuit converts it into an OPR circuit that
implements $D$. On the other hand, given an OPR circuit for $D$, adding $Q^{-1}$ and $Q$ before and after
converts it into an OPR circuit for $U$. $\blacksquare$. \\

\textbf{Theorem:} \textit{A $n$-qubits operator of the form $U = e^{iHt}$ (where $H$ is time independent) can be implemented 
using an OPR circuit if and only if the eigenvalues of $H$
are $-\lambda, 0, \lambda$ (for $\lambda$ a real number) and the degeneracy of $\lambda$ and $-\lambda$ is $2^j$ for $0 \leq j < n$.} \\

\textbf{Proof:} According to the lemma, if $U = e^{iHt}$ is implementable using an $n$-qubit OPR circuit,
then the diagonal matrix $D = diag(e^{i\lambda_0 t}, \cdots, e^{i\lambda_{2^n-1}t})$ is implementable using an $n$-qubit OPR circuit too,
 where $\lambda_k$ are the eigenvalues of $H$.

Therefore, according to Property 2 of OPR circuits,
matrix $D$ must have the form $(|\vec{v}_0|, |\vec{v}_1|, \cdots , |\vec{v}_{2^n-1}|)$, 
but because $D$ is diagonal, this form reduces to:
\begin{eqnarray}
D = \begin{pmatrix}
c_{00} + a_{00} e^{is} + b_{00} e^{-is} & 0 & \cdots  \\
0& c_{11} + a_{11} e^{is} + b_{11} e^{-is} & \cdots  \\
 \cdots & \cdots & \ddots 
\end{pmatrix}.
\end{eqnarray}
Furthermore, the column vectors $\vec{a}_j, \vec{b}_j, \vec{c}_j$ must be orthogonal, but because each column has only one nonzero entry,
only one of the vectors can be nonzero, so each entry must be $c_{jj}$ or $a_{jj} e^{is}$ or $b_{jj} e^{-is}$. 
And because the vectors also satisfy $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$, it must be true that $|c_{jj}|^2 = 1 $
or $|a_{jj}|^2 = 1$ or $|b_{jj}|^2 =1$.
Therefore, the $j$-th entry in the diagonal matrix must be of the form $e^{i \theta_{j}}$ or
$e^{i \theta_{j}} e^{is}$ or $e^{i \theta_j} e^{-is}$. Consequently, we can define the following sets:
\begin{eqnarray}
\Lambda_c = \{\lambda_j  | e^{i\lambda_j t} = e^{i \theta_j}\} \; ,\;
\Lambda_a = \{\lambda_j  | e^{i\lambda_j t} = e^{i \theta_j + is}\} \;,\;
\Lambda_b = \{\lambda_j  | e^{i\lambda_j t} = e^{i \theta_j-is}\}.
\end{eqnarray}
Every eigenvalue must belong to one of these sets. We can prove the following properties of these sets:
\begin{itemize}
\item The only eigenvalues in $\Lambda_c$ are $\lambda_j = 0$: This is because  $e^{i \lambda_j t}  = e^{i \theta_j}$ for every $t$ implies that $\lambda_j = 0$.
\item All eigenvalues in $\Lambda_a$ ($\Lambda_b)$ have the same value:
Take $\lambda_k , \lambda_j \in \Lambda_a (\Lambda_b)$, then $e^{i\lambda_k t} = e^{i \theta_k \pm is} \; ,\; e^{i\lambda_j t} = e^{i\theta_j \pm is}$,
therefore $\lambda_k t = \theta_k \pm s + 2\pi n_k$ and $\lambda_j t = \theta_j \pm s + 2\pi n_j$ with $n_k, n_j$ integers.
 Subtracting these equations implies that $(\lambda_k - \lambda_j)t = \theta_k - \theta_j + 2\pi n_k - 2\pi n_j$. 
 Given that the right side doesn't depend on $t$, we conclude that $\lambda_k - \lambda_j= 0$, so the eigenvalues are the same.

\item Eigenvalues in $\Lambda_a$ and $\Lambda_b$ have the same magnitude but opposite sign: 
Take an eigenvalue $\lambda_j \in \Lambda_a$ and $\lambda_k \in \Lambda_b$, 
then just as in the last step, we conclude that $\lambda_jt =  \theta_j + s + 2\pi n_j$ and $\lambda_kt = \theta_k - s + 2\pi n_k$
and adding these equations we get $(\lambda_j+ \lambda_k)t = \theta_j + \theta_k + 2\pi (n_j + n_k)$. 
Given that the right side doesn't depend on $t$, we conclude that $\lambda_j + \lambda_k =0$, so that $\lambda_j$ and $\lambda_k$ have opposite signs but equal magnitude.
\end{itemize}
Therefore, we conclude that the eigenvalues can be chosen out of $H$ must be chosen 3 sets, 
those in $\Lambda_c$ are equal to $0$, those in $\Lambda_a$ are equal to a value we
will call $\lambda$ and those in $\Lambda_b$ are all equal to $-\lambda$.

Finally, we notice that the degeneracy of $\lambda$ and
$-\lambda$ are $2^j$ for some $j \in \{0, \cdots, n-1\}$.
 To see that, we remember that because it is an OPR circuit, 
Matrix $D$ is equal to $D = A R_{\sigma_3} (2s)B$, 
with $R_{\sigma}$ a rotation applied to the last qubit and controlled by set of the first qubits and $A,B$ 
matrices that don't depend on $s$.
Furthermore, the matrix $R_{\sigma_3}(2s)$ is diagonal and
it has $2^j$ entries equal to $e^{is}$, $2^j$ entries equal to $e^{-is}$ and the rest equal to $1$ 
(where $j+1$ is the number of  control qubits). 
Therefore, we can write $R_{\sigma_3}(2s) = M_1 + e^{is} M_+ + e^{-is} M_-$
 where $M_1, M_+, M_-$ are diagonal matrices with all non-zero entries equal to $1$ and 
$M_+, M_-$ has $2^j$ non-zero entries and $M_1$ has $2^n - 2^{j+1}$ non-zero entries.

Finally, $D = A(M_1 + e^{is} M_+ + e^{-is} M_-) B = AM_1 B + e^{is} AM_+ B + e^{-is} AM_- B$,
and because $D$ is diagonal, $AM_1B , e^{is} AM_+B, e^{-is} AM_- B$ are
diagonal too. Due to the $A$ and $B$ being full-rank matrices, $e^{is} AM_+B$ 
and $e^{-is} AM_-B$ have a rank of $2^j$ and $AM_1B$ has a rank of $2^n- 2^{j+1}$. 
Therefore, considering $D$ is full rank and diagonal, 
$2^j$ of its entries will be $e^{is}$, another $2^j$ will be $e^{-is}$
and the rest will be $1$. \\

\textbf{Constructing the 
Circuit:}  Given that $H$ has the form given in the theorem,
then $e^{iHt}$ can be diagonalized as $D = diag(e^{i\lambda_0 t}, \cdots , e^{i\lambda_{2^n-1}t})$,
where $2^j$ of the entries are $e^{i\lambda t}$, another $2^j$ are $e^{-i\lambda t}$ 
and the rest are $1$. 
Given a value of $j$, we construct a rotation $R_{\sigma_3}(2\lambda t)$ on the last qubit and with $n-1-j$ control qubits 
(whichever we choose, as long as they are $n-1-j$).
Therefore, the matrix representing this rotation is diagonal with $2^j$
entries being $e^{i\lambda t}$, another $2^j$ being $e^{-i\lambda t}$ and the rest being $1$.
This matrix can then be multiplied by matrices that don't depend on $t$
such that the eigenvalues are reordered and we get the matrix $D$.
That it, we can get matrix $D$ using only one rotation that depends on $t$. 
Then, because $U = Q^{-1} D Q$, we can add matrices $Q^{-1}$ and $Q$ to the circuit
to obtain the complete OPR circuit of $U$. $\blacksquare$ \\ \\

\textbf{Note:} If we don't care about adding a global phase to the circuit, the eigenvalues can be translated to $-\lambda+a, a, \lambda+a$ for some $a\in \mathbb{R}$.\\

\subsubsection{Example}
\begin{itemize}
\item  Every matrix $H$ of $n$ qubits obtained as the
tensor product of $n$ Pauli operators fulfills the conditions of the theorem, 
because in particular all eigenvalues of $H$ will
be $1$ or $-1$ with the same number of each. 
\item Every matrix $H$ of one qubit fulfills the theorem, since it has two eigenvalues, that can always be written as $-\lambda+a, \lambda+a$.
\item I tried numerically for sums of Pauli matrices. For $2,3$ and $4$ qubits, the sum of two Pauli matrices (formed by the tensor product of $2,3$ or $4$ one qubit Pauli matrices) satisfy the conditions of the theorem.\\
\end{itemize}

\textbf{Example:} Consider $H = \sigma_3 \otimes \sigma_2$ for two qubits. In this case, the hamiltonian matrix is
\begin{eqnarray}
H = \begin{pmatrix}
0 & -i & 0 & 0 \\
i & 0 & 0 & 0 \\
0 &0 & 0 & i \\
0 & 0 & -i & 0
\end{pmatrix}
\end{eqnarray}
that has eigenvalues $\{-1,-1,1,1\}$. This matrix can be diagonalized as
\begin{eqnarray}
Q \begin{pmatrix}
-1 & 0 &0 & 0 \\
0 & -1 &0 & 0 \\
0 & 0 & 1 & 0 \\
0 & 0 & 0 & 1
\end{pmatrix} Q^{\dagger} \;\; ,\;\; Q:= \begin{pmatrix}
-\sqrt{2}/2 & 0 & 0 & - \sqrt{2}/2 \\
\sqrt{2}/2 i & 0 & 0 & -\sqrt{2}/2 i \\
0 &-\sqrt{2}/2 & \sqrt{2}/2 & 0\\
0 &-\sqrt{2}/2 i & -\sqrt{2}/2i & 0
\end{pmatrix},
\end{eqnarray}
therefore, the exponential matrix is given by:
\begin{eqnarray}
U = e^{iHt} = Q \begin{pmatrix}
e^{-it} & 0 &0 & 0 \\
0 & e^{-it} &0 & 0 \\
0 & 0 & e^{it} & 0 \\
0 & 0 & 0 & e^{it}
\end{pmatrix} Q^{\dagger}
\end{eqnarray}
The diagonal matrix between $Q$ and $Q^{\dagger}$ is simply $R_{\sigma_3} (2s)$ applied to the first qubit and without control qubits, therefore
the OPR circuit for this operation is given by figure \ref{fig: 2x3}

\begin{figure}
\centering
\begin{quantikz}
\lstick{$q_0$} & \gate[wires=2]{Q^{\dagger}} & \swap{1} & \qw & \swap{1} & \gate[wires=2]{Q} & \qw \\
\lstick{$q_1$} & \qw & \targX{} & \gate{R_Z(2t)} & \targX{}  & \qw & \qw\\
\end{quantikz}
\caption{Circuito para $\sigma_2 \oplus \sigma_3$}
\label{fig: 2x3}
\end{figure}
I tried out this circuit on 
real quantum computers for values of $t$ between 
$0$ and $\pi$ and after applying QPT consistently got a fidelity of around $0.85$ for 
every value of $t$.\\

\subsection{Conclusions}
\begin{itemize}
\item
\end{itemize}

\end{document}

### 2023-03-21 main.tex
Main Resumen

 \documentclass[12pt]{template/iopart}

% allow loading amsmath
\expandafter\let\csname equation*\endcsname\relax
\expandafter\let\csname endequation*\endcsname\relax

\usepackage[english]{babel}
\usepackage{graphicx,helvet}
\usepackage{color}
\usepackage{url}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{graphicx,helvet}
\usepackage{color}
\usepackage[inline]{showlabels}
\usepackage{bbm,bm}
\usepackage{soul}
\usepackage{amsfonts}
\usepackage{iopams}
\usepackage{lipsum}

\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{quantikz}

\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\FXRegisterAuthor{cp}{acp}{\color{blue}CP}
\FXRegisterAuthor{tb}{ttb}{\color{OliveGreen}TB}

\newcommand\keywords[1]{Keywords: #1}

\begin{document}
\title[Title]{Title}

\author{Tomás Basile$^1$ and Carlos Pineda$^2$}

\address{$^1$ Facultad de Ciencias. Universidad Nacional Autónoma de México, Ciudad de México 01000, Mexico}
\address{$^2$ Instituto de Física, Universidad Nacional Autónoma de México, Ciudad de México 01000, México}
\ead{carlospgmat03@gmail.com}

\begin{abstract}
The abstract follows the addresses and
should give readers concise information about the content 
of the article and indicate the main results obtained and conclusions 
drawn. It should be self-contained---there should be no references to 
figures, tables, equations, bibliographic references etc.  It should be enclosed between \verb"\begin{abstract}"
and \verb"\end{abstract}" commands.  The abstract should normally be restricted 
to a single paragraph of around 200 words~\cite{bengtsson_zyczkowski_2017}.
\end{abstract}
\keywords{magnetic moment, solar neutrinos, astrophysics} \\
\submitto{\PS}
\maketitle

\input{Cap1}
\input{Cap2}
\input{Cap3}
\input{Cap4}
\input{Cap5}
\input{Cap6}

\newpage
\appendix
\input{Cosas-Escritas-Antes}

\textbf{Acknowledgments}

Support by projects CONACyT 285754, 254515 and UNAM-PAPIIT IG100518, IG101421 is
acknowledged.  \\

\textbf{References}
\bibliographystyle{unsrt.bst}
\bibliography{Bibliography}

\end{document}

### 2023-03-25 Cap2.tex
Actualización 2

@@
 \item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
-\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many different one-qubit channels inside the tetrahedron.
+\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
 \item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state.

### 2023-03-25 Cap3.tex
Actualización 2

@@
 \item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
-\item \textbf{Theorem about OPR circuits:} The theorem gives the general form that the operator of an OPR circuit can have.
-\textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
+\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
 \begin{align*}
-U = (\vec{v}_0, \vec{v}_1, \cdots, \vec{v}_{2^n-1})
+U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
 \end{align*}

### 2023-03-25 Cap5.tex
Actualización 2

@@
 \begin{itemize}
-\item We will apply the results about OPR circuit to another kind of operation.
-\item Consider operations $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
-\item \textbf{Theorem:} A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.
-\item \textbf{Examples:} Every matrix $H$ for one qubit, any $n$-qubit pauli matrix, some sums of Pauli matrices, etc.
+\item We will apply the results about OPR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
+\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
+\item \textbf{Examples.} Some examples are: Every matrix $H$ for one qubit, any $n$-qubit pauli matrix, some sums of Pauli matrices, etc.
 \end{itemize}

### 2023-03-30 Cap2.tex
Cap2 y puntos cap5

@@
 \section{Circuits for Pauli Maps}
+\label{sec: Circuits for Pauli Maps}
 
@@
 \item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
-\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state.
+\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
 \end{itemize}
+
+In this section we introduce the concept of Pauli channels and 
+Pauli dynamical maps, as well as proposal for a quantum circuit that simulates them on systems of $N$ qubits. 
+Furthermore, we show the results of implementing the circuit on a 
+quantum computer for the particular case of Pauli channels of one qubit.
+
+\subsection{Quantum Channels}
+\label{subsec: Quantum Channels}
+Quantum channels are the most general linear operations that a 
+quantum system (which is represented by a density matrix $\rho$) 
+can undergo independently of its past~\cite{zimansbook,cirac}. 
+These channels are constructed based on three fundamental properties: 
+linearity, trace preservation, and complete positivity.
+
+Linearity ensures that a quantum channel $\mathcal{E}$ maps any convex combination 
+of density matrices into a convex combination of their evolution. 
+The trace preserving property is given by $\tr \mathcal{E}[\rho] = \tr \rho = 1$ 
+and guarantees that the quantum channel occurs with a probability of 1. 
+The complete positivity condition ensures that the quantum channel preserves positive semidefiniteness. 
+A linear map $\mathcal{E}$ is considered positive if it maps density operators to density operators 
+($\mathcal{E}(\rho) \geq 0$  for all density matrices $\rho$). 
+If the extension of a positive map to include an ancilla results in another positive map, 
+the original map is said to be completely positive~\cite{geometry}. 
+This property is required for quantum channels to allow for the
+proper evolution of potentially entangled states with an ancilla.
+
+Jamiołkowski and Choi~\cite{choi,jamil} developed a simple algorithm to test for 
+complete positivity of a quantum channel. 
+The algorithm exploits the isomorphism between a channel $\mathcal{E}$ and the 
+state $\mathcal{D} = (\text{id} \otimes \mathcal{E}) [|\Omega \rangle \langle  \Omega|]$, 
+where $|\Omega\rangle$ is a maximally entangled state between the original system and an 
+ancilla and “id” is the identity channel. 
+Remarkably, the map $\mathcal{E}$ is completely positive if and 
+only if $\mathcal{D}$ (also known as the Choi or dynamical matrix of $\mathcal{E}$) is positive semidefinite.
+
+\subsection{Pauli Channels}
+\label{subsec: Pauli Channels}
+
+To define a Pauli channel, we start by exploring the single-qubit scenario and then the $N$-qubit one. 
+First of all, the most general single-qubit density matrix can be written as
+\begin{equation}
+\label{ec: Density Matrix}
+\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
+\end{equation}
+with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices. 
+Normalization requires that $r_0 = 1$ and the remaining $r_{1,2,3}$ form a Bloch vector. 
+A Pauli channel is defined as an operation
+that applies a convex combination of Pauli matrices to the density matrix in the following way:
+\begin{equation}
+\label{ec: Pauli channel 1 qbit}
+\mathcal{E}(\rho) = \sum_{\gamma=0}^3 k_{\gamma} \sigma_{\gamma} \rho \sigma_{\gamma},
+\end{equation}
+where $k_{\gamma}$ are non-negative real numbers such that 
+$\sum_{\gamma} k_{\gamma} = 1$ (these conditions are needed for the channel 
+to be completely positive and trace preserving).
+
+Having defined the one qubit case, 
+in order to present the $N-$qubit one, we 
+need to introduce the so-called \textit{Pauli strings}, defined as
+\begin{equation}
+\label{ec: Density matrix Nqbit}
+\sigma_{\vec{\alpha}} = \sigma_{\alpha_1} \otimes \sigma_{\alpha_2}\otimes \cdots \otimes \sigma_{\alpha_N},
+\end{equation}
+where $\vec{\alpha}$ denotes a multi-index $(\alpha_1, \cdots, \alpha_N)$
+ and $\alpha_i \in \{0,1,2,3\}$. 
+ These operators form an orthogonal basis in the space of operators acting on $N$ qubits. 
+ Similarly to the single-qubit case, the density matrix $\rho$ 
+of a system of $N$ qubits can be written using Pauli strings as:
+\begin{equation}
+\label{ec:cap2-1}
+\rho = \dfrac{1}{2^N} \sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
+\end{equation}
+Then, we define a Pauli channel as a transformation of the density 
+matrix given by
+\begin{equation}
+\label{ec: pauli channel N-qubt}
+\mathcal{E}(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}} \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
+\end{equation}
+where just as before, complete positivity and trace preservation requires
+that $k_{\vec{\gamma}}$ are positive real numbers such 
+that $\sum_{\vec{\gamma}} k_{\vec{\gamma}}=1$.
+
+\subsection{Circuit for a Pauli Channel}
+
+We are interested in constructing a quantum circuit that can implement an
+arbitrary Pauli channel on a system of $N$ qubits. 
+To do it, it is important to realize that a Pauli channel
+ as shown in equation \ref{ec: pauli channel N-qubt}  can 
+be interpreted as as a transformation that applies
+each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
+
+Given this interpretation of the channel, 
+it is easy to construct a quantum circuit that implements 
+it with the help of $2n$ ancilla qubits.
+The general idea is to first construct a state on the ancilla qubits
+and then use this state to control gates that 
+apply each Pauli operator $\sigma_{\vec{\gamma}}$ with probability $k_{\vec{\gamma}}$ 
+on the principal qubits.
+
+The circuit that does this is presented in figure 
+\ref{fig: circuit-pauli}. 
+The first step in the circuit is to create the state
+\begin{equation}
+\label{ec: state}
+\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle,
+\end{equation}
+where $b_{\vec{\gamma}}$ is in general a complex number such that 
+\begin{equation}
+|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}.
+\end{equation}
+Moreover $|\vec{\gamma}\rangle$ is defined as a $2n$ qubit state given by
+\begin{equation}
+|\vec{\gamma} \rangle = |\gamma_1\rangle |\gamma_2 \rangle \cdots |\gamma_N \rangle,
+\end{equation}
+where $|\gamma_i \rangle$ is the $2$ qubit state $|00\rangle, |01\rangle , |10\rangle$ or $|11\rangle$ when $\gamma_i = 0,1,2,3$ respectively. \\
+
+This means that when measured in the computational base, the state given in \ref{ec: state} 
+gives collapses to $|\vec{\gamma}\rangle$ with a 
+probability $|b_{\vec{\gamma}}|^2 = k_{\gamma}$. 
+The circuit \ref{fig: circuit-pauli} uses this fact
+to apply the operations $\sigma_{\vec{\gamma}}$ over the principal qubits
+with probabilities $k_{\gamma}$ by using controlled operations. 
+In figure \ref{fig: circuito}, the symbol of figure \ref{fig: control}
+\begin{figure}[h!]
+\label{fig: control}
+\centering
+\begin{quantikz}
+& \ctrl{1} & \qw \rstick[wires=2]{$|\gamma_i \rangle$} \\
+& \control{} & \qw
+\end{quantikz}
+\end{figure}
+indicates that the controlled gate is
+activated if these two qubits are in the state $|\gamma_i \rangle$. 
+\begin{figure}
+\centering
+\begin{quantikz}
+\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
+ vectors $\vec{\gamma}$} \\
+\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
+\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
+\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1}}} & \qw & & &\\
+\lstick{ } & & & & & &\\
+\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=2]{$|\gamma_0 \rangle$} &  & & &\\
+\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
+\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & \rstick[wires=2]{$|\gamma_1 \rangle$} & & & &\\
+\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
+\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
+\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & \rstick[wires=2]{$|\gamma_{n-1} \rangle$}& & & & \\
+\lstick{$aq_{2N-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
+\end{quantikz}
+\caption{\textbf{\tbnote{Obvio éstas no serían las figuras finales, 
+pero la forma en que hacen los circuitos cuánticos depende de la revista
+y entonces las rediseñaré después.}} Circuit to implement an $N$-qubit Pauli channel 
+on the qubits $q_0, q_1, \cdots, q_{n-1}$. 
+The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
+on $2N$ ancilla qubits and then uses them to apply
+all possible Pauli strings on the principal qubits
+with probabilities $k_{\vec{\gamma}}$.}
+\label{fig: circuit-pauli}
+\end{figure}
+
+To see why the circuit from figure \ref{fig: circuito}
+ works, 
+we note that after creating the state 
+$\sum_{\vec{\gamma}} b_{\gamma} \; |\vec{\gamma} \rangle$, 
+the circuit applies each gate $\sigma_{\vec{\gamma}}$ to the principal qubits 
+under the condition that the ancilla qubits are 
+on the state $|\vec{\gamma}\rangle$. 
+This  means that each gate $\sigma_{\vec{\gamma}}$ is applied 
+on the principal qubits with a probability $k_{\vec{\gamma}}$, 
+just as we wanted.  \\
+
+\subsubsection{Simulation for one-qubit Pauli channels}
+\label{subsec: Simulation for one-qubit Pauli channels}
+For the particular case of Pauli channel on one qubit, 
+the circuit that simulates it can be constructed as in figure 
+\ref{fig: citcuit-pauli-1}, which is a special case of figure \ref{fig: circuit-pauli}.
+
+\begin{figure}
+\centering
+\begin{quantikz}
+\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
+\lstick{$aq_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
+\lstick{$aq_1$} & \gateinput{$b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
+\end{quantikz}
+\caption{Circuit for a one-qubit Pauli channel, which is a particular case of figure \ref{fig: circuit-pauli}.}
+\label{fig: canal-1qbit-A} 
+\end{figure}
+Taking advantage of the quantum computers that IBM has available,
+we sampled $250$ one-qubit Pauli channels and simulated them using the 
+ibmq-lima quantum computer. 
+For each of these channels, the accuracy of the implementation in the quantum computer
+was quantified by calculating the
+ process fidelity of the Choi matrix obtained by performing
+quantum process tomography to the circuit
+with respect to the theoretical Choi matrix of
+the corresponding channel.
+Finally, using the well known fact that one-qubit Pauli channels can be represented
+as points in a tetrahedron with corners $(1,1,1), (1-1,-1), (-1,1,-1)$ and $(-1,-1,1)$, 
+in figure \ref{fig: fidelity one qubit}.
+\begin{figure}
+\centering
+\includegraphics[width=0.45\textwidth]{fidelidad-puntos.png}\\
+\caption{Fidelities of one-qubit Pauli channels implemented on IBM's ibmq-lima.}
+\label{fig: fidelity one qubit}
+\end{figure}
+\subsubsection{Pauli Dynamical Maps}
+\label{subsec: Pauli Dynamical Maps}
+
+A Pauli dynamical map is defined as a continuous parametrized 
+curve drawn inside the set of Pauli channels and starting at the identity channel. 
+Therefore, a Pauli dynamical map can be written as
+\begin{eqnarray}
+\mathcal{E}_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
+\end{eqnarray}
+where $p$ is a parameter in an interval $[a,b]$ 
+and $\mathcal{E}_p$ is a Pauli channel for every $p$, 
+with $\mathcal{E}_a$ being the identity channel.
+
+Dynamical maps can be implemented using the same method as 
+in figure \ref{fig: circuito}, with the only difference that now the state 
+to be created on the ancilla qubits depends on parameter $p$ 
+and therefore is given by 
+\begin{equation}
+\label{ec: parametrized state}
+\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle
+\end{equation}
+
+\newpage

### 2023-03-30 Cap5.tex
Cap2 y puntos cap5

@@
 \item We will apply the results about OPR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
+\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with an OPR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with an OPR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
+\item \textbf{Proof:}  Es b\'asicamente usar que $H = QDQ^{-1}$ para una matriz $Q$ que no depende de $t$ y por lo tanto no agrega compuertas parametrizadas al circuito. 
 \item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
-\item \textbf{Examples.} Some examples are: Every matrix $H$ for one qubit, any $n$-qubit pauli matrix, some sums of Pauli matrices, etc.
+\item \textbf{Proof:} Estoy buscando formas de simplificar la prueba, porque es medio larguita.
+Pero básicamente es usar el lema y entonces preocuparnos sólo por $D$.
+Luego  usar el teorema de la sección 3 y notar que sólo hay tres tipos de  $\lambda$s posibles y luego notar que deben de tener esas degeneraciones.
+\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito OPR que hace la operación a partir de una $H$ que cumpla la hipótesis.
+\item \textbf{Examples.} Mencionar que por el teorema, los ejemplos son sistemas con 3 energías separadas por la misma distancia y con las degeneraciones dadas en el teorema. 
+La verdad que no se me ocurren sistemas físicos comunes que cumplan eso.
+\begin{itemize}
+\item Cualquier matriz $H$ de un qubit cumple el teorema.
+\item Cualquier matriz de $n$ qubits que sea el producto tensorial de matrices de Pauli para cada partícula (o sea algo como $\sigma_{i_1} \otimes \sigma_{i_2} \otimes \cdots \otimes \sigma_{i_n}$) cumple el teorema.
+\item Estoy viendo para cadenas de espines si hay condiciones para las que cumplan las hipótesis del teorema, pero no he encontrado aún.
 \end{itemize}
+\item Hice explícitamente el circuito de 2 qubits para $H = \sigma_3 \otimes \sigma_2$ y lo simulé en las computadoras de IBM, obteniendo una fidelidad de $0.85$.
+
+\end{itemize}

### 2023-03-30 Cosas-Escritas-Antes.tex
Cap2 y puntos cap5

@@
 
-\textbf{Property 1:} \textit{An $n$-qubit OPR circuit can always be transformed into the form of circuit \ref{fig: OPR general}, where $A$ and $B$ are $n$-qubit gates that don't depend on the parameter
+\textbf{Property 1:} \textit{An $n$-qubit OPR circuit can always be transformed into the form of circuit \ref{fig: OPR general-A}, where $A$ and $B$ are $n$-qubit gates that don't depend on the parameter
 and $s = s(p)$ is a function of the parameter.}\\
@@
 \caption{Forma general de un circuito RP.}
-\label{fig: OPR general}
+\label{fig: OPR general-A}
 \end{figure}
@@
 (possibly controlled by other qubits), 
-so that it has the form \ref{fig: OPR general}. $\blacksquare$ \\ \\
+so that it has the form \ref{fig: OPR general-A}. $\blacksquare$ \\ \\
 
@@
 \textbf{Proof:} Because of property 1, we know that any OPR
-circuit can be converted into the form \ref{fig: OPR general},
+circuit can be converted into the form \ref{fig: OPR general-A},
 so that we only need to consider the operator for that circuit. 
@@
 
-The circuit that does this is presented in figure \ref{fig: circuito}, where $|\vec{\gamma}\rangle$ is defined as the $2n$ qubits state $|\vec{\gamma} \rangle = \otimes_{i=0}^n |\gamma_i \; \text{in binary} \rangle$.
+The circuit that does this is presented in figure \ref{fig: circuito-A}, where $|\vec{\gamma}\rangle$ is defined as the $2n$ qubits state $|\vec{\gamma} \rangle = \otimes_{i=0}^n |\gamma_i \; \text{in binary} \rangle$.
 For example, if $\vec{\gamma} = (0,3,1,\cdots)$, then this state is defined as $|\vec{\gamma} \rangle = |001101 \rangle$.
@@
 \caption{Circuit for a n-qubit Pauli channel.}
-\label{fig: circuito}
+\label{fig: circuito-A}
 \end{figure}
@@
 
-Dynamical maps can be implemented using the same method as in figure \ref{fig: circuito}, with the only difference that now the state to be created on the ancilla qubits depends on parameter $p$ and it is given by $\sum_{\vec{\gamma}} \sqrt{k_{\vec{\gamma}}(p)} |\vec{\gamma}\rangle$.
+Dynamical maps can be implemented using the same method as in figure \ref{fig: circuito-A}, with the only difference that now the state to be created on the ancilla qubits depends on parameter $p$ and it is given by $\sum_{\vec{\gamma}} \sqrt{k_{\vec{\gamma}}(p)} |\vec{\gamma}\rangle$.
 \\
@@
 \caption{ Circuit for a one qubit Pauli channel.}
-\label{fig: canal-1qbit} 
+\label{fig: canal-1qbit-A} 
 \end{figure}
@@
 
-To implement this dynamical map using the circuit presented in figure \ref{fig: one-rot}, it is necessary to create the state
+To implement this dynamical map using the circuit presented in figure \ref{fig: one-rot-A}, it is necessary to create the state
 \begin{eqnarray}
@@
 According to theorem 1, the fact that the state we need to create over the ancilla qubits can be written like this implies that the dynamical map can be simulated in a quantum computer using only one parametrized rotation.
-The circuit used will have the same form as that in figure \ref{fig: canal-1qbit}, where the part used to create the state on the ancilla qubits will be:
+The circuit used will have the same form as that in figure \ref{fig: canal-1qbit-A}, where the part used to create the state on the ancilla qubits will be:
 \begin{figure}[h!]
@@
 The diagonal matrix between $Q$ and $Q^{\dagger}$ is simply $R_{\sigma_3} (2s)$ applied to the first qubit and without control qubits, therefore
-the OPR circuit for this operation is given by figure \ref{fig: 2x3}
+the OPR circuit for this operation is given by figure \ref{fig: 2x3-A}
 
@@
 \caption{Circuito para $\sigma_2 \oplus \sigma_3$}
-\label{fig: 2x3}
+\label{fig: 2x3-A}
 \end{figure}
@@
 \end{itemize}
-
-\end{document}

### 2023-04-03 Cosas-Escritas-Antes.tex
Pequeña corrección
Plos one

@@
 (possibly controlled by other qubits), 
-so that it has the form \ref{fig: OPR general-A}. $\blacksquare$ \\ \\
+so that it has the form \ref{fig: OPR general-A}. $\blacksquare$ \\
 
@@
 \begin{eqnarray}
-& \fl e^{-is} \sum_{k \in Ctrl} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle + \sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
+& e^{-is} \sum_{k \in Ctrl} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle + \sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
 & \qquad := e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
@@
 \centering
-\includegraphics[width=0.45\textwidth]{fidelidad-puntos.png}\\
+\includegraphics[width=0.45\textwidth]{fidelity-points.png}\\
 \caption{Fidelity of one qubit channels using Qiskit's ibmq-lima.}
@@
 Then, because $U = Q^{-1} D Q$, we can add matrices $Q^{-1}$ and $Q$ to the circuit
-to obtain the complete OPR circuit of $U$. $\blacksquare$ \\ \\
+to obtain the complete OPR circuit of $U$. $\blacksquare$ \\
 

### 2023-04-03 main.tex
I had a cup of tea and now it's fixed
Cap2 y puntos cap5
Plos one

@@
- \documentclass[12pt]{template/iopart}
+% Template for PLoS
+% Version 3.6 Aug 2022
+%
+% % % % % % % % % % % % % % % % % % % % % %
+%
+% -- IMPORTANT NOTE
+%
+% This template contains comments intended 
+% to minimize problems and delays during our production 
+% process. Please follow the template instructions
+% whenever possible.
+%
+% % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Once your paper is accepted for publication, 
+% PLEASE REMOVE ALL TRACKED CHANGES in this file 
+% and leave only the final text of your manuscript. 
+% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
+% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
+%
+%
+% There are no restrictions on package use within the LaTeX files except that no packages listed in the template may be deleted.
+%
+% Please do not include colors or graphics in the text.
+%
+% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
+%
+% % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- FIGURES AND TABLES
+%
+% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
+%
+% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
+% - Figures should be uploaded separately from your manuscript file. 
+% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
+% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
+% For figure citations, please use "Fig" instead of "Figure".
+% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
+%
+% Tables should be cell-based and may not contain:
+% - spacing/line breaks within cells to alter layout or alignment
+% - do not nest tabular environments (no tabular environments within tabular environments)
+% - no graphics or colored text (cell background color/shading OK)
+% See http://journals.plos.org/plosone/s/tables for table guidelines.
+%
+% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
+%
+% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
+%
+% IMPORTANT
+% Below are a few tips to help format your equations and other special characters according to our specifications.
+For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
+%
+% For inline equations, please be sure to include all portions of an equation in the math environment.
+For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
+%
+% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
+%
+% Please add line breaks to long display equations when possible in order to fit size of the column. 
+%
+% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
+%
+% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
+%
+% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
+%
+% % % % % % % % % % % % % % % % % % % % % % % % 
+%
+% Please contact latex@plos.org with any questions.
+%
+% % % % % % % % % % % % % % % % % % % % % % % %
 
-% allow loading amsmath
-\expandafter\let\csname equation*\endcsname\relax
-\expandafter\let\csname endequation*\endcsname\relax
+\documentclass[10pt,letterpaper]{article}
+\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+
+% amsmath and amssymb packages, useful for mathematical formulas and symbols
+\usepackage{amsmath,amssymb}
+
+% Use adjustwidth environment to exceed column width (see example table in text)
+\usepackage{changepage}
+
+% textcomp package and marvosym package for additional characters
+\usepackage{textcomp,marvosym}
+
+% cite package, to clean up citations in the main text. Do not remove.
+\usepackage{cite}
+
+% Use nameref to cite supporting information files (see Supporting Information section for more info)
+\usepackage{nameref,hyperref}
+
+% line numbers
+\usepackage[right]{lineno}
+
+% ligatures disabled
+\usepackage[nopatch=eqnum]{microtype}
+\DisableLigatures[f]{encoding = *, family = * }
+
+% color can be used to apply background shading to table cells only
+\usepackage[table]{xcolor}
+
+% array package and thick rules for tables
+\usepackage{array}
+
+% create "+" rule type for thick vertical lines
+\newcolumntype{+}{!{\vrule width 2pt}}
+
+% create \thickcline for thick horizontal lines of variable length
+\newlength\savedwidth
+\newcommand\thickcline[1]{%
+  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+  \cline{#1}%
+  \noalign{\vskip\arrayrulewidth}%
+  \noalign{\global\arrayrulewidth\savedwidth}%
+}
+
+% \thickhline command for thick horizontal lines that span the table
+\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
+\hline
+\noalign{\global\arrayrulewidth\savedwidth}}
+
+% Remove comment for double spacing
+%\usepackage{setspace} 
+%\doublespacing
+
+% Text layout
+\raggedright
+\setlength{\parindent}{0.5cm}
+\textwidth 5.25in 
+\textheight 8.75in
+
+% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
+% Captions will be left justified
+\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
+\renewcommand{\figurename}{Fig}
+
+% Use the PLoS provided BiBTeX style
+\bibliographystyle{plos2015}
+
+% Remove brackets from numbering in List of References
+\makeatletter
+\renewcommand{\@biblabel}[1]{\quad#1.}
+\makeatother
+
+% Header and Footer with logo
+\usepackage{lastpage,fancyhdr,graphicx}
+\usepackage{epstopdf}
 
@@
 \usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
-\usepackage[T1]{fontenc}
 \usepackage{hyperref}
-\usepackage{graphicx,helvet}
-\usepackage{color}
 \usepackage[inline]{showlabels}
@@
 \usepackage{amsfonts}
-\usepackage{iopams}
-\usepackage{lipsum}
+\usepackage{showlabels}
 
@@
 \FXRegisterAuthor{cp}{acp}{\color{blue}CP}
-\FXRegisterAuthor{tb}{ttb}{\color{OliveGreen}TB}
+\FXRegisterAuthor{tb}{ttb}{\color{green}TB}
 
-\newcommand\keywords[1]{Keywords: #1}
+%\pagestyle{myheadings}
+\pagestyle{fancy}
+\fancyhf{}
+%\setlength{\headheight}{27.023pt}
+%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
+\rfoot{\thepage/\pageref{LastPage}}
+\renewcommand{\headrulewidth}{0pt}
+\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
+\fancyheadoffset[L]{2.25in}
+\fancyfootoffset[L]{2.25in}
+\lfoot{\today}
+
+%% Include all macros below
+
+\newcommand{\lorem}{{\bf LOREM}}
+\newcommand{\ipsum}{{\bf IPSUM}}
+\DeclareMathOperator{\tr}{tr}
+
+%% END MACROS SECTION
 
 \begin{document}
-\title[Title]{Title}
+\vspace*{0.2in}
 
-\author{Tomás Basile$^1$ and Carlos Pineda$^2$}
+% Title must be 250 characters or less.
 
-\address{$^1$ Facultad de Ciencias. Universidad Nacional Autónoma de México, Ciudad de México 01000, Mexico}
-\address{$^2$ Instituto de Física, Universidad Nacional Autónoma de México, Ciudad de México 01000, México}
-\ead{carlospgmat03@gmail.com}
+\begin{flushleft}
+{\Large
+\textbf\newline{Title of submission to PLOS journals} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+}
+\newline
+% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
+\\
+Tomás Basile\textsuperscript{1\Yinyang},
+Carlos Pineda\textsuperscript{2*\Yinyang},
+\\
+\bigskip
+\textbf{1} Facultad de Ciencias. Universidad Nacional Autónoma de México, Ciudad de México 01000, Mexico
+\\
+\textbf{2} Instituto de Física, Universidad Nacional Autónoma de México, Ciudad de México 01000, México
+\\
+\bigskip
 
-\begin{abstract}
-The abstract follows the addresses and
-should give readers concise information about the content 
-of the article and indicate the main results obtained and conclusions 
-drawn. It should be self-contained---there should be no references to 
-figures, tables, equations, bibliographic references etc.  It should be enclosed between \verb"\begin{abstract}"
-and \verb"\end{abstract}" commands.  The abstract should normally be restricted 
-to a single paragraph of around 200 words~\cite{bengtsson_zyczkowski_2017}.
-\end{abstract}
-\keywords{magnetic moment, solar neutrinos, astrophysics} \\
-\submitto{\PS}
-\maketitle
+% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
+% 
+% Remove or comment out the author notes below if they aren't used.
+%
+% Primary Equal Contribution Note
+\Yinyang These authors contributed equally to this work.
 
-\input{Cap1}
-\input{Cap2}
-\input{Cap3}
-\input{Cap4}
-\input{Cap5}
-\input{Cap6}
+% Additional Equal Contribution Note
+% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
+% \ddag These authors also contributed equally to this work.
+
+% Current address notes
+% \textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
+% \textcurrency b Insert second current address 
+% \textcurrency c Insert third current address
+
+% Deceased author note
+% \dag Deceased
+
+% Group/Consortium Author Note
+% \textpilcrow Membership list can be found in the Acknowledgments section.
+
+% Use the asterisk to denote corresponding authorship and provide email address in note below.
+* carlospgmat03@gmail.com
+
+\end{flushleft}
+% Please keep the abstract below 300 words
+\section*{Abstract}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Curabitur eget porta erat.
+Morbi consectetur est vel gravida pretium.
+Suspendisse ut dui eu ante cursus gravida non sed sem.
+Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
+Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
+Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
+Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
+Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+
+% Please keep the Author Summary between 150 and 200 words
+% Use first person. PLOS ONE authors please skip this step. 
+% Author Summary not valid for PLOS ONE submissions.   
+%\section*{Author summary}
+%Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Curabitur eget porta erat.
+Morbi consectetur est vel gravida pretium.
+Suspendisse ut dui eu ante cursus gravida non sed sem.
+Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
+Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
+Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
+Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
+Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+
+\linenumbers
+
+% Use "Eq" instead of "Equation" for equation citations.
+\section*{Introduction}
+%Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit.
+Curabitur eget porta erat.
+Morbi consectetur est vel gravida pretium.
+Suspendisse ut dui eu ante cursus gravida non sed sem.
+Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam.
+Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
+Nunc pellentesque pretium diam, quis maximus dolor faucibus id.%~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
+Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+
+\begin{eqnarray}
+\label{eq:schemeP}
+	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
+\end{eqnarray}
+
+\section*{Circuits for Pauli Maps}
+\label{sec: Circuits for Pauli Maps}
+
+\textbf{Lista de puntos:}
+\begin{itemize}
+\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
+\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
+\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
+\end{itemize}
+
+In this section we introduce the concept of Pauli channels and 
+Pauli dynamical maps, as well as proposal for a quantum circuit that simulates them on systems of $N$ qubits. 
+Furthermore, we show the results of implementing the circuit on a 
+quantum computer for the particular case of Pauli channels of one qubit.
+
+\subsection*{Quantum Channels}
+\label{subsec: Quantum Channels}
+Quantum channels are the most general linear operations that a 
+quantum system (which is represented by a density matrix $\rho$) 
+can undergo independently of its past~\cite{zimansbook,cirac}. 
+These channels are constructed based on three fundamental properties: 
+linearity, trace preservation, and complete positivity.
+
+Linearity ensures that a quantum channel $\mathcal{E}$ maps any convex combination 
+of density matrices into a convex combination of their evolution. 
+The trace preserving property is given by $\tr \mathcal{E}[\rho] = \tr \rho = 1$ 
+and guarantees that the quantum channel occurs with a probability of $1$. 
+The complete positivity condition ensures that the quantum channel preserves positive semidefiniteness. 
+A linear map $\mathcal{E}$ is considered positive if it maps density operators to density operators 
+($\mathcal{E}(\rho) \geq 0$  for all density matrices $\rho$). 
+If the extension of a positive map to include an ancilla results in another positive map, 
+the original map is said to be completely positive~\cite{geometry}. 
+This property is required for quantum channels to allow for the
+proper evolution of potentially entangled states with an ancilla.
+
+Jamiołkowski and Choi~\cite{choi,jamil} developed a simple algorithm to test for 
+complete positivity of a quantum channel. 
+The algorithm exploits the isomorphism between a channel $\mathcal{E}$ and the 
+state $\mathcal{D} = (\text{id} \otimes \mathcal{E}) [|\Omega \rangle \langle  \Omega|]$, 
+where $|\Omega\rangle$ is a maximally entangled state between the original system and an 
+ancilla and “id” is the identity channel. 
+Remarkably, the map $\mathcal{E}$ is completely positive if and 
+only if $\mathcal{D}$ (also known as the Choi or dynamical matrix of $\mathcal{E}$) is positive semidefinite.
+
+\subsection*{Pauli Channels}
+\label{subsec: Pauli Channels}
+
+To define a Pauli channel, we start by exploring the single-qubit scenario and then the $N$-qubit one. 
+First of all, the most general single-qubit density matrix can be written as
+\begin{eqnarray}
+\label{ec: Density Matrix}
+\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
+\end{eqnarray}
+with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices. 
+Normalization requires that $r_0 = 1$ and the remaining $r_{1,2,3}$ form a Bloch vector. 
+A Pauli channel is defined as an operation
+that applies a convex combination of Pauli matrices to the density matrix in the following way:
+\begin{eqnarray}
+\label{ec: Pauli channel 1 qbit}
+\mathcal{E}(\rho) = \sum_{\gamma=0}^3 k_{\gamma} \sigma_{\gamma} \rho \sigma_{\gamma},
+\end{eqnarray}
+where $k_{\gamma}$ are non-negative real numbers such that 
+$\sum_{\gamma} k_{\gamma} = 1$ (these conditions are needed for the channel 
+to be completely positive and trace preserving).
+
+Having defined the one qubit case, 
+in order to present the $N-$qubit one, we 
+need to introduce the so-called \textit{Pauli strings}, defined as
+\begin{eqnarray}
+\label{ec: Pauli string}
+\sigma_{\vec{\alpha}} = \sigma_{\alpha_1} \otimes \sigma_{\alpha_2}\otimes \cdots \otimes \sigma_{\alpha_N},
+\end{eqnarray}
+where $\vec{\alpha}$ denotes a multi-index $(\alpha_1, \cdots, \alpha_N)$
+ and $\alpha_i \in \{0,1,2,3\}$. 
+ These operators form an orthogonal basis in the space of operators acting on $N$ qubits. 
+ Similarly to the single-qubit case, the density matrix $\rho$ 
+of a system of $N$ qubits can be written using Pauli strings as:
+\begin{eqnarray}
+\label{ec:  Density matrix Nqbit}
+\rho = \dfrac{1}{2^N} \sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
+\end{eqnarray}
+Then, we define a Pauli channel as a transformation of the density 
+matrix given by
+\begin{eqnarray}
+\label{ec: pauli channel N-qubt}
+\mathcal{E}(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}} \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
+\end{eqnarray}
+where just as before, complete positivity and trace preservation requires
+that $k_{\vec{\gamma}}$ are positive real numbers such 
+that $\sum_{\vec{\gamma}} k_{\vec{\gamma}}=1$.
+
+\subsection*{Circuit for a Pauli Channel}
+\label{subsec: Circuit for a Pauli Channel}
+
+We are interested in constructing a quantum circuit that can implement an
+arbitrary Pauli channel on a system of $N$ qubits. 
+To do it, it is important to realize that a Pauli channel
+ as shown in Eq~(\ref{ec: pauli channel N-qubt})  can 
+be interpreted as a transformation that applies
+each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
+
+Given this interpretation of the channel, 
+it is easy to construct a quantum circuit that implements 
+it with the help of $2n$ ancilla qubits.
+The general idea is to first construct a state on the ancilla qubits
+and then use this state to control gates that 
+apply each Pauli operator $\sigma_{\vec{\gamma}}$ with probability $k_{\vec{\gamma}}$ 
+on the principal qubits.
+
+The circuit that does this is presented in Fig~(\ref{fig: circuit-pauli}). 
+The first step in the circuit is to create the state
+\begin{eqnarray}
+\label{ec: state}
+\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle,
+\end{eqnarray}
+where $b_{\vec{\gamma}}$ is in general a complex number such that 
+\begin{eqnarray}
+\label{ec: b}
+|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}.
+\end{eqnarray}
+Moreover $|\vec{\gamma}\rangle$ is defined as a $2n$ qubit state given by
+\begin{eqnarray}
+|\vec{\gamma} \rangle = |\gamma_1\rangle |\gamma_2 \rangle \cdots |\gamma_N \rangle,
+\end{eqnarray}
+where $|\gamma_i \rangle$ is the $2$ qubit state $|00\rangle, |01\rangle , |10\rangle$ or $|11\rangle$ when $\gamma_i = 0,1,2,3$ respectively. \\
+
+\begin{figure}[h!]
+\centering
+\begin{quantikz}
+\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
+ vectors $\vec{\gamma}$} \\
+\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
+\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
+\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1}}} & \qw & & &\\
+\lstick{ } & & & & & &\\
+\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=2]{$|\gamma_0 \rangle$} &  & & &\\
+\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
+\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & \rstick[wires=2]{$|\gamma_1 \rangle$} & & & &\\
+\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
+\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
+\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & \rstick[wires=2]{$|\gamma_{n-1} \rangle$}& & & & \\
+\lstick{$aq_{2N-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
+\end{quantikz}
+\caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS.
+Hay que dejar el figure solamente con la caption y label.}} \textbf{\tbnote{Obvio éstas no serían las figuras finales,
+he visto que hacen los circuitos de forma distinta en Plos One y no usando Quantikz.}} {\bf Circuit for an $N$-qubit Pauli channel.} Circuit to implement an $N$-qubit Pauli channel 
+on the qubits $q_0, q_1, \cdots, q_{n-1}$. 
+The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
+on $2N$ ancilla qubits and then uses them to apply
+all possible Pauli strings on the principal qubits
+with probabilities $k_{\vec{\gamma}}$.}
+\label{fig: circuit-pauli}
+\end{figure}
+
+This means that when measured in the computational base, the state given in Eq~(\ref{ec: state})
+collapses to $|\vec{\gamma}\rangle$ with a 
+probability $|b_{\vec{\gamma}}|^2 = k_{\gamma}$. 
+The circuit in Fig~(\ref{fig: circuit-pauli}) uses this fact
+to apply the operations $\sigma_{\vec{\gamma}}$ over the principal qubits
+with probabilities $k_{\gamma}$ by using controlled operations. 
+In Fig~(\ref{fig: circuit-pauli}), the symbol shown in Fig~(\ref{fig: control})
+indicates that the controlled gate is
+activated if these two qubits are in the state $|\gamma_i \rangle$. 
+\begin{figure}[h!]
+\centering
+\begin{quantikz}
+& \ctrl{1} & \qw \rstick[wires=2]{$|\gamma_i \rangle$} \\
+& \control{} & \qw
+\end{quantikz}
+\caption{{\bf Control qubits} \tbnote{Al igual que antes, esta imagen se tiene que quitar para la entrega final.} Control $|\gamma_i \rangle$ for two qubits.}
+\label{fig: control}
+\end{figure}
+
+To see why the circuit from Fig~(\ref{fig: circuit-pauli})
+ works, 
+we note that after creating the state 
+$\sum_{\vec{\gamma}} b_{\gamma} \; |\vec{\gamma} \rangle$, 
+the circuit applies each gate $\sigma_{\vec{\gamma}}$ to the principal qubits 
+under the condition that the ancilla qubits are 
+on the state $|\vec{\gamma}\rangle$. 
+This  means that each gate $\sigma_{\vec{\gamma}}$ is applied 
+on the principal qubits with a probability $k_{\vec{\gamma}}$, 
+just as we wanted.  \\
+
+\subsubsection*{Simulation for one-qubit Pauli channels}
+\label{subsec: Simulation for one-qubit Pauli channels}
+For the particular case of a Pauli channel on one qubit, 
+the circuit that simulates it can be constructed as in Fig~(\ref{fig: citcuit-pauli-1}),
+ which is a special case of figure \ref{fig: circuit-pauli}.
+
+\begin{figure}[h!]
+\centering
+\begin{quantikz}
+\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
+\lstick{$aq_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
+\lstick{$aq_1$} & \gateinput{$b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
+\end{quantikz}
+\caption{\tbnote{Al igual que antes, hay que adaptar esta figura y quitarla antes de entregar}.
+{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
+\label{fig: citcuit-pauli-1} 
+\end{figure}
+Taking advantage of the quantum computers that IBM has available,
+we sampled $250$ one-qubit Pauli channels and simulated them using the 
+ibmq-lima quantum computer. 
+For each of these channels, the accuracy of the implementation in the quantum computer
+was quantified by calculating the
+ process fidelity of the Choi matrix obtained by performing
+quantum process tomography to the circuit
+with respect to the theoretical Choi matrix of
+the corresponding channel.
+Finally, using the well known fact that one-qubit Pauli channels can be represented
+as points in a tetrahedron with corners $(1,1,1), (1-1,-1), (-1,1,-1)$ and $(-1,-1,1)$, 
+in Fig~(\ref{fig: fidelity one qubit}).
+\begin{figure}[h!]
+\centering
+\includegraphics[width=0.45\textwidth]{fidelity-points.png}\\
+\caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}.
+{\bf Fidelities one-qubit Pauli channel} Fidelities of one-qubit Pauli channels implemented on IBM's ibmq-lima.
+The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the fidelity of each channel's implementation using the circuit for a 1-qubit Pauli channel}
+\label{fig: fidelity one qubit}
+\end{figure}
+
+\subsubsection*{Pauli Dynamical Maps}
+\label{subsec: Pauli Dynamical Maps}
+
+A Pauli dynamical map is defined as a continuous parametrized 
+curve drawn inside the set of Pauli channels and starting at the identity channel. 
+Therefore, a Pauli dynamical map can be written as
+\begin{eqnarray}
+\label{ec: Pauli dynamical map}
+\mathcal{E}_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
+\end{eqnarray}
+where $p$ is a parameter in an interval $[a,b]$ 
+and $\mathcal{E}_p$ is a Pauli channel for every $p$, 
+with $\mathcal{E}_a$ being the identity channel.
+
+Dynamical maps can be implemented using the same method as 
+in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
+to be created on the ancilla qubits depends on parameter $p$ 
+and therefore is given by 
+\begin{eqnarray}
+\label{ec: parametrized state}
+\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle
+\end{eqnarray}
+
+\section*{OPR Circuits}
+\label{sec: OPR Circuits}
+\textbf{Puntos:}
+\begin{itemize}
+\item How can we reduce the amount of parametrized rotations used?
+\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
+\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
+\begin{eqnarray}
+U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
+\end{eqnarray}
+\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
+\end{itemize}
+
+\section*{OPR circuit for a Pauli map}
+\label{sec: OPR circuit for a Pauli map}
+\textbf{Puntos:}
+\begin{itemize}
+\item Use the last theorem to conclude which maps can be created using an OPR circuit.
+\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. and an example that doesn't satisfy the conditions.
+\item \textbf{Results:} Show results of simulating those maps on a quantum computer. 
+\end{itemize}
+
+\section*{Exponential maps $e^{iHt}$}
+\label{sec: Exponential maps}
+\textbf{Puntos:}
+
+\begin{itemize}
+\item We will apply the results about OPR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
+\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with an OPR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with an OPR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
+\item \textbf{Proof:}  Es b\'asicamente usar que $H = QDQ^{-1}$ para una matriz $Q$ que no depende de $t$ y por lo tanto no agrega compuertas parametrizadas al circuito. 
+\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
+\item \textbf{Proof:} Estoy buscando formas de simplificar la prueba, porque es medio larguita.
+Pero básicamente es usar el lema y entonces preocuparnos sólo por $D$.
+Luego  usar el teorema de la sección 3 y notar que sólo hay tres tipos de  $\lambda$s posibles y luego notar que deben de tener esas degeneraciones.
+\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito OPR que hace la operación a partir de una $H$ que cumpla la hipótesis.
+\item \textbf{Examples.} Mencionar que por el teorema, los ejemplos son sistemas con 3 energías separadas por la misma distancia y con las degeneraciones dadas en el teorema. 
+La verdad que no se me ocurren sistemas físicos comunes que cumplan eso.
+\begin{itemize}
+\item Cualquier matriz $H$ de un qubit cumple el teorema.
+\item Cualquier matriz de $n$ qubits que sea el producto tensorial de matrices de Pauli para cada partícula (o sea algo como $\sigma_{i_1} \otimes \sigma_{i_2} \otimes \cdots \otimes \sigma_{i_n}$) cumple el teorema.
+\item Estoy viendo para cadenas de espines si hay condiciones para las que cumplan las hipótesis del teorema, pero no he encontrado aún.
+\end{itemize}
+\item Hice explícitamente el circuito de 2 qubits para $H = \sigma_3 \otimes \sigma_2$ y lo simulé en las computadoras de IBM, obteniendo una fidelidad de $0.85$.
+\end{itemize}
+
+\section*{Conclusion}
+
+CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
+
+Sed non aliquet felis.
+Lorem ipsum dolor sit amet, consectetur adipiscing elit.
+Mauris commodo justo ac dui pretium imperdiet.
+Sed suscipit iaculis mi at feugiat.
+Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna.
+Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
+Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
+Nam condimentum sem eget mollis euismod.
+Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex.
+Nunc est dui, sodales sed mauris nec, auctor sagittis leo.
+Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor.
+For more information, see \nameref{S1_Appendix}.
+
+\section*{Supporting information}
+
+% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
+\paragraph*{S1 Fig.}
+\label{S1_Fig}
+{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
+
+\paragraph*{S2 Fig.}
+\label{S2_Fig}
+{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\paragraph*{S1 File.}
+\label{S1_File}
+{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\paragraph*{S1 Video.}
+\label{S1_Video}
+{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\paragraph*{S1 Appendix.}
+\label{S1_Appendix}
+{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\paragraph*{S1 Table.}
+\label{S1_Table}
+{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+Etiam eget sapien nibh.
+Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
+Curabitur fringilla pulvinar lectus consectetur pellentesque.
+
+\section*{Acknowledgments}
+Support by projects CONACyT 285754, 254515 and UNAM-PAPIIT IG100518, IG101421 is
+acknowledged.
+
+\nolinenumbers
+
+% Either type in your references using
+% \begin{thebibliography}{}
+% \bibitem{}
+% Text
+% \end{thebibliography}
+%
+% or
+%
+% Compile your BiBTeX database using our plos2015.bst
+% style file and paste the contents of your .bbl file
+% here. See http://journals.plos.org/plosone/s/latex for 
+% step-by-step instructions.
+% 
+%\begin{thebibliography}{10}
+%
+%\bibitem{bib1}
+%Conant GC, Wolfe KH.
+%\newblock {{T}urning a hobby into a job: how duplicated genes find new
+%  functions}.
+%\newblock Nat Rev Genet. 2008 Dec;9(12):938--950.
+
+%\bibitem{bib2}
+%Ohno S.
+%\newblock Evolution by gene duplication.
+%\newblock London: George Alien \& Unwin Ltd. Berlin, %Heidelberg and New York:
+%  Springer-Verlag.; 1970.
+
+%\bibitem{bib3}
+%Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
+%\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
+%  infection through a transposon insertion followed by a {D}uplication}.
+%\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
+%
+%\end{thebibliography}
+
+\tbnote{Poner la bibliografía como ellos dicen (copiarla toda aquí en lugar de ponerla en un archivo .bib)}
+\textbf{References}
+\bibliography{Bibliography}
 
@@
 
-\textbf{Acknowledgments}
-
-Support by projects CONACyT 285754, 254515 and UNAM-PAPIIT IG100518, IG101421 is
-acknowledged.  \\
-
-\textbf{References}
-\bibliographystyle{unsrt.bst}
-\bibliography{Bibliography}
-
 \end{document}

### 2023-04-04 main.tex
Update

@@
 it with the help of $2n$ ancilla qubits.
-The general idea is to first construct a state on the ancilla qubits
-and then use this state to control gates that 
-apply each Pauli operator $\sigma_{\vec{\gamma}}$ with probability $k_{\vec{\gamma}}$ 
-on the principal qubits.
-
-The circuit that does this is presented in Fig~(\ref{fig: circuit-pauli}). 
-The first step in the circuit is to create the state
+The circuit that does this is presented in Fig~(\ref{fig: circuit-pauli}) and its 
+first step in the circuit is to create the state
 \begin{eqnarray}
 \label{ec: state}
-\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle,
+\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
 \end{eqnarray}
+in the ancilla qubits, 
 where $b_{\vec{\gamma}}$ is in general a complex number such that 
@@
 \caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS.
-Hay que dejar el figure solamente con la caption y label.}} \textbf{\tbnote{Obvio éstas no serían las figuras finales,
-he visto que hacen los circuitos de forma distinta en Plos One y no usando Quantikz.}} {\bf Circuit for an $N$-qubit Pauli channel.} Circuit to implement an $N$-qubit Pauli channel 
+Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel.} Circuit to implement an $N$-qubit Pauli channel
 on the qubits $q_0, q_1, \cdots, q_{n-1}$. 
@@
 with probabilities $k_{\gamma}$ by using controlled operations. 
-In Fig~(\ref{fig: circuit-pauli}), the symbol shown in Fig~(\ref{fig: control})
+The symbol shown in Fig~(\ref{fig: control})
 indicates that the controlled gate is
@@
 the circuit that simulates it can be constructed as in Fig~(\ref{fig: citcuit-pauli-1}),
- which is a special case of figure \ref{fig: circuit-pauli}.
+ which is a special case of Fig(\ref{fig: circuit-pauli}).
 
@@
 
-Dynamical maps can be implemented using the same method as 
+Dynamical maps can be implemented using the same circuit as 
 in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
@@
 \label{ec: parametrized state}
-\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle
+\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
 \end{eqnarray}
@@
 \begin{itemize}
+\item As said before, to implement a Pauli dynamical map, 
+we need to create the parametrized $2n$-qubit state 
+$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
+\item However, creating this state will in general require many rotations parametrized by $p$. 
+For example, for the case of a Pauli dynamical map on 1 qubit, 
+the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
+In general, to create a parametrized state on $2n$ ancilla qubits will require
+$2n-1$ rotations parametrized by $p$.
 \item How can we reduce the amount of parametrized rotations used?
@@
 \textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
+\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
+aunque se puede y debe achicar bastante.
 \end{itemize}
@@
 \begin{itemize}
-\item Use the last theorem to conclude which maps can be created using an OPR circuit.
-\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. and an example that doesn't satisfy the conditions.
+\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
+\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
+and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
 \item \textbf{Results:} Show results of simulating those maps on a quantum computer. 
+Lo tengo para parabolic y para depolarizing.
 \end{itemize}

### 2023-04-12 main.tex
I'm guessing this may start causing us problems either soon or never.

@@
-% Template for PLoS
-% Version 3.6 Aug 2022
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended 
-% to minimize problems and delays during our production 
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file 
-% and leave only the final text of your manuscript. 
-% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
-% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
-%
-%
-% There are no restrictions on package use within the LaTeX files except that no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig" instead of "Figure".
-% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - spacing/line breaks within cells to alter layout or alignment
-% - do not nest tabular environments (no tabular environments within tabular environments)
-% - no graphics or colored text (cell background color/shading OK)
-% See http://journals.plos.org/plosone/s/tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
-%
-% For inline equations, please be sure to include all portions of an equation in the math environment.
-For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
-%
-% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column. 
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
-%
-% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
-%
-% % % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-
-\documentclass[10pt,letterpaper]{article}
+\documentclass[10pt,letterpaper]{article} % {{{
 \usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
 \usepackage{amsmath,amssymb}
-
 % Use adjustwidth environment to exceed column width (see example table in text)
@@
 
+% }}}
 \begin{document}
+% Titulo, afiliacion, abstract  {{{
 \vspace*{0.2in}
@@
 % Use "Eq" instead of "Equation" for equation citations.
-\section*{Introduction}
+% }}}
+\section*{Introduction} % {{{
 %Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit.
@@
 \end{eqnarray}
-
-\section*{Circuits for Pauli Maps}
-\label{sec: Circuits for Pauli Maps}
-
+% }}}
+\section{Circuits for Pauli Maps}  \label{sec: Circuits for Pauli Maps} % {{{
+% Intro  {{{
 \textbf{Lista de puntos:}
@@
 
-In this section we introduce the concept of Pauli channels and 
-Pauli dynamical maps, as well as proposal for a quantum circuit that simulates them on systems of $N$ qubits. 
-Furthermore, we show the results of implementing the circuit on a 
-quantum computer for the particular case of Pauli channels of one qubit.
+In this section \cpnote{ser coherente con las subsecciones que se tienen nota que no 
+hay mencion a los quantum channels. Menos
+cuadrado, quizá pasar por chatgpt. hacerlo al final cuanod se tenga el capitulo
+por lo menos leido y aprobado en principio de mi parte.} we introduce the
+concept of Pauli channels and Pauli dynamical
+maps, as well as proposal for a quantum circuit that simulates them on systems
+of $N$ qubits.  Furthermore, we show the results of implementing the circuit on
+a quantum computer for the particular case of Pauli channels of one qubit. 
+% }}}
+\subsection*{Quantum Channels} \label{subsec: Quantum Channels} % {{{
 
-\subsection*{Quantum Channels}
-\label{subsec: Quantum Channels}
+\cpnote{Creo que toca iterar, pensando un poco en nivel licenciatura. ver ejemplos }
+\cpnote{Tambien creo que no es coherente tener una subseccion para esto si 
+lo qeu se quiere decir en la seccion es otra cosa.}
+
 Quantum channels are the most general linear operations that a 
@@
 
-Linearity ensures that a quantum channel $\mathcal{E}$ maps any convex combination 
-of density matrices into a convex combination of their evolution. 
-The trace preserving property is given by $\tr \mathcal{E}[\rho] = \tr \rho = 1$ 
-and guarantees that the quantum channel occurs with a probability of $1$. 
-The complete positivity condition ensures that the quantum channel preserves positive semidefiniteness. 
-A linear map $\mathcal{E}$ is considered positive if it maps density operators to density operators 
-($\mathcal{E}(\rho) \geq 0$  for all density matrices $\rho$). 
-If the extension of a positive map to include an ancilla results in another positive map, 
-the original map is said to be completely positive~\cite{geometry}. 
-This property is required for quantum channels to allow for the
-proper evolution of potentially entangled states with an ancilla.
+Linearity ensures that a quantum channel $\mathcal{E}$ maps any convex
+combination of density matrices into a convex combination of their evolution.
+The trace preserving property is given by $\tr \mathcal{E}[\rho] = \tr \rho =
+1$ and guarantees that the quantum channel occurs with a probability of $1$.
+The complete positivity condition ensures that the quantum channel preserves
+positive semidefiniteness.  A linear map $\mathcal{E}$ is considered positive
+if it maps density operators to density operators ($\mathcal{E}(\rho) \geq 0$
+for all density matrices $\rho$).  If the extension of a positive map to
+include an ancilla results in another positive map, the original map is said to
+be completely positive~\cite{geometry}.  This property is required for quantum
+channels to allow for the proper evolution of potentially entangled states with
+an ancilla.
 
-Jamiołkowski and Choi~\cite{choi,jamil} developed a simple algorithm to test for 
-complete positivity of a quantum channel. 
-The algorithm exploits the isomorphism between a channel $\mathcal{E}$ and the 
-state $\mathcal{D} = (\text{id} \otimes \mathcal{E}) [|\Omega \rangle \langle  \Omega|]$, 
-where $|\Omega\rangle$ is a maximally entangled state between the original system and an 
-ancilla and “id” is the identity channel. 
-Remarkably, the map $\mathcal{E}$ is completely positive if and 
-only if $\mathcal{D}$ (also known as the Choi or dynamical matrix of $\mathcal{E}$) is positive semidefinite.
+Jamiołkowski and Choi~\cite{choi,jamil} developed a simple algorithm to test
+for complete positivity of a quantum channel.  The algorithm exploits the
+isomorphism between a channel $\mathcal{E}$ and the state $\mathcal{D} =
+(\text{id} \otimes \mathcal{E}) [|\Omega \rangle \langle  \Omega|]$, where
+$|\Omega\rangle$ is a maximally entangled state between the original system and
+an ancilla and “id” is the identity channel.  Remarkably, the map $\mathcal{E}$
+is completely positive if and only if $\mathcal{D}$ (also known as the Choi or
+dynamical matrix of $\mathcal{E}$) is positive semidefinite.
 
-\subsection*{Pauli Channels}
-\label{subsec: Pauli Channels}
+% }}}
+\subsection*{Pauli Channels} \label{subsec: Pauli Channels} % {{{
 
-To define a Pauli channel, we start by exploring the single-qubit scenario and then the $N$-qubit one. 
-First of all, the most general single-qubit density matrix can be written as
+To define a Pauli channel, we start by exploring the single-qubit scenario and
+then the $N$-qubit one.  First of all, the most general single-qubit density
+matrix can be written as
 \begin{eqnarray}
@@
 with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
-Normalization requires that $r_0 = 1$ and the remaining $r_{1,2,3}$ form a Bloch vector. 
+Normalization requires that $r_0 = 1$ and the remaining $r_{1,2,3}$ form a
+Bloch vector \cpnote{explicar un poco mejor. Me parece que para el publico vale 
+la pena ser un poco mas explicito. pero no estoy muy seguro. }. 
 A Pauli channel is defined as an operation
@@
 to be completely positive and trace preserving). 
+\cpnote{en todo hay que mejorar un poco la redaccion. Aca me gustaria que 
+se interpretara. Creo qe es mas que atenuacion de los componentes, o es solo atenuacion? 
+en todo caso ver mejor como va la cosa. }
 
@@
 
-\subsection*{Circuit for a Pauli Channel}
+\cpnote{Creo qeu toca motivar, conectar con cosas conocidas y en general no ser tan seco}
+% }}}
+\subsection*{Circuit for a Pauli Channel} % {{{
 \label{subsec: Circuit for a Pauli Channel}
+
+\cpnote{esto está un poco desordenado y a un ritmo creo qeu inapropiado por lo rapido}
 
@@
 
+\cpnote{paro aca de leer}
+
 \begin{figure}[h!]
@@
 \lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
-\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1}}} & \qw & & &\\
+\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1} }} & \qw & & &\\
 \lstick{ } & & & & & &\\
@@
 
-\subsubsection*{Simulation for one-qubit Pauli channels}
+\subsubsection*{Simulation for one-qubit Pauli channels} % {{{
 \label{subsec: Simulation for one-qubit Pauli channels}
@@
 \end{figure}
-
-\subsubsection*{Pauli Dynamical Maps}
+% }}}
+\subsubsection*{Pauli Dynamical Maps} % {{{
 \label{subsec: Pauli Dynamical Maps}
@@
 \end{eqnarray}
-
-\section*{OPR Circuits}
+% }}}
+% }}}
+% }}}
+\section*{OPR Circuits} % {{{
 \label{sec: OPR Circuits}
@@
 \end{itemize}
-
-\section*{OPR circuit for a Pauli map}
+% }}}
+\section*{OPR circuit for a Pauli map} % {{{
 \label{sec: OPR circuit for a Pauli map}
@@
 \end{itemize}
-
-\section*{Exponential maps $e^{iHt}$}
+% }}}
+\section*{Exponential maps $e^{iHt}$} % {{{
 \label{sec: Exponential maps}
@@
 \end{itemize}
-
-\section*{Conclusion}
+% }}}
+\section*{Conclusion} % {{{
 
@@
 For more information, see \nameref{S1_Appendix}.
-
-\section*{Supporting information}
+% }}}
+\section*{Supporting information} % {{{
 
@@
 Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\section*{Acknowledgments}
+% }}}
+\section*{Acknowledgments} % {{{
 Support by projects CONACyT 285754, 254515 and UNAM-PAPIIT IG100518, IG101421 is
@@
 
+% }}}
+% Biblbiografia {{{
 % Either type in your references using
@@
 %\end{thebibliography}
-
 \tbnote{Poner la bibliografía como ellos dicen (copiarla toda aquí en lugar de ponerla en un archivo .bib)}
@@
 
+% }}}
 \newpage

### 2023-04-16 main.tex
Algunos cambios

@@
 \section*{Introduction} % {{{
-%Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.%~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
 
-\begin{eqnarray}
-\label{eq:schemeP}
-	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
-\end{eqnarray}
 % }}}
-\section{Circuits for Pauli Maps}  \label{sec: Circuits for Pauli Maps} % {{{
+\section{Pauli Channels}  \label{sec: Pauli Channels} % {{{
 % Intro  {{{
@@
 por lo menos leido y aprobado en principio de mi parte.} we introduce the
-concept of Pauli channels and Pauli dynamical
-maps, as well as proposal for a quantum circuit that simulates them on systems
-of $N$ qubits.  Furthermore, we show the results of implementing the circuit on
-a quantum computer for the particular case of Pauli channels of one qubit. 
+concept of quantum channels, focusing on a specific type called Pauli channels.
+Finally, we consider Pauli dynamical maps, which
+are curves of Pauli channels parametrized by a variable.
+
+%Quitarrrr:
+Then, we propose a quantum circuit that simulates N-qubit Pauli channels
+and show the results of implementing the circuit for $N=1$ on
+a quantum computer. 
 % }}}
@@
 
-Quantum channels are the most general linear operations that a 
-quantum system (which is represented by a density matrix $\rho$) 
-can undergo independently of its past~\cite{zimansbook,cirac}. 
+In quantum mechanics, a closed system is represented by a state vector in a 
+Hilbert space $\mathcal{H}$. 
+The state's evolution is given by Schrodinger's
+equation and is always unitary.
+However, in real-world situations, 
+quantum systems are usually open and interact with their environment in various complicated ways. 
+For example, the system's state may become entangled with the environment,
+which can lead to loss of information of the system's state over time.
+
+Instead of vectors in the Hilbert space $\mathcal{H}$,
+open systems are described by matrices $\rho$ acting on $\mathcal{H}$
+called density matrices and they include information about 
+the system's interaction with the environment.
+To be physically valid, a density matrix $\rho$
+has to satisfy the two following conditions:
+1. $\tr(\rho) =1$ and 2. $\rho$ is positive semi-definite $(\rho \geq 0)$.
+
+Given that, we can finally define quantum channels, which
+describe the time evolution of open quantum systems.
+Quantum channels are the most general linear operations
+that a quantum system (which is represented 
+by a density matrix $\rho$) can undergo independently of its
+past~\cite{zimansbook,cirac}.
 These channels are constructed based on three fundamental properties: 
@@
 
-Linearity ensures that a quantum channel $\mathcal{E}$ maps any convex
-combination of density matrices into a convex combination of their evolution.
-The trace preserving property is given by $\tr \mathcal{E}[\rho] = \tr \rho =
-1$ and guarantees that the quantum channel occurs with a probability of $1$.
-The complete positivity condition ensures that the quantum channel preserves
-positive semidefiniteness.  A linear map $\mathcal{E}$ is considered positive
-if it maps density operators to density operators ($\mathcal{E}(\rho) \geq 0$
-for all density matrices $\rho$).  If the extension of a positive map to
-include an ancilla results in another positive map, the original map is said to
-be completely positive~\cite{geometry}.  This property is required for quantum
-channels to allow for the proper evolution of potentially entangled states with
-an ancilla.
+Linearity ensures that a quantum channel $\mathcal{E}$ maps any ensemble
+of density matrices into the corresponding ensemble of their evolution.
+The trace preserving property is given by $\tr (\mathcal{E}[\rho]) = \tr (\rho) =
+1$ and guarantees that the quantum channel does not change the condition that $\tr(\rho) = 1$.
+Finally, the channel should also preserve
+the condition $\rho \geq 0$, and a map that does this is called a positive map.
+However, positivity of $\mathcal{E}$ is not enough, 
+and we actually require the more restrictive condition of complete positivity.
+Complete positivity means that
+$\mathcal{E} \otimes \mathbb{I}_n$ is positive for
+any positive integer $n$ 
+(where $\mathbb{I}_n$ is the $n\times n$ identity matrix).
+This is required to ensure that even if $\rho$ is entangled with another system,
+applying $\mathcal{E}$ to $\rho$ while doing nothing to the
+ other system still results in  a positive semidefinite state.
 
-Jamiołkowski and Choi~\cite{choi,jamil} developed a simple algorithm to test
-for complete positivity of a quantum channel.  The algorithm exploits the
+Given a possible quantum channel $\mathcal{E}$, 
+the condition of trace preservation is straightforward to examine but complete positivity is not as simple.
+To test complete positivity of a quantum channel, 
+Jamiołkowski and Choi~\cite{choi,jamil} developed a simple algorithm.  
+The algorithm exploits the
 isomorphism between a channel $\mathcal{E}$ and the state $\mathcal{D} =
-(\text{id} \otimes \mathcal{E}) [|\Omega \rangle \langle  \Omega|]$, where
-$|\Omega\rangle$ is a maximally entangled state between the original system and
-an ancilla and “id” is the identity channel.  Remarkably, the map $\mathcal{E}$
+(\mathbb{I} \otimes \mathcal{E}) [|\Omega \rangle \langle  \Omega|]$, where
+$|\Omega\rangle = 1/\text{dim}(\mathcal{H}) \sum_{i}^{\text{dim}(\mathcal{H})} |i \rangle |i \rangle$ is a maximally entangled state between the original system and
+an ancilla.  Remarkably, the map $\mathcal{E}$
 is completely positive if and only if $\mathcal{D}$ (also known as the Choi or
@@
 
-To define a Pauli channel, we start by exploring the single-qubit scenario and
-then the $N$-qubit one.  First of all, the most general single-qubit density
+We have discussed the main features of quantum channels and 
+now we turn our attention to a specific 
+type of channel for $N$-qubit systems called Pauli channels.
+First we define a Pauli channel on a one-qubit system,
+whose most general single-qubit density
 matrix can be written as
@@
 with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
-Normalization requires that $r_0 = 1$ and the remaining $r_{1,2,3}$ form a
-Bloch vector \cpnote{explicar un poco mejor. Me parece que para el publico vale 
+The condition $\tr(\rho) = 1$ requires that $r_0 = 1$ while $\rho \geq 0$ 
+implies that the remaining $r_{1,2,3}$ form
+a vector $\vec{r}= (r_1,r_2,r_3)$ inside a unit sphere known as the Bloch sphere. \cpnote{explicar un poco mejor. Me parece que para el publico vale 
 la pena ser un poco mas explicito. pero no estoy muy seguro. }. 
-A Pauli channel is defined as an operation
-that applies a convex combination of Pauli matrices to the density matrix in the following way:
+A Pauli channel is defined as an operation that
+applies each Pauli matrix $\sigma_{\gamma}$ to
+the system with probabilities $k_{\gamma}$ with $\gamma = 0,1,2,3$. 
+Mathematically, the Pauli channel is written in the following way:
 \begin{eqnarray}
@@
 \end{eqnarray} 
-where $k_{\gamma}$ are non-negative real numbers such that 
-$\sum_{\gamma} k_{\gamma} = 1$ (these conditions are needed for the channel 
-to be completely positive and trace preserving). 
+where of course the probabilities $k_{\gamma}$ of applying $\sigma_{\gamma}$
+are non-negative real numbers such that 
+$\sum_{\gamma} k_{\gamma} = 1$ (these conditions also ensure that the channel is 
+trace preserving and completely positive). 
 \cpnote{en todo hay que mejorar un poco la redaccion. Aca me gustaria que 
@@
 en todo caso ver mejor como va la cosa. }
+
+Apart from this interpretation of Pauli channels,
+we can find another one by seeing how the channel acts on the 
+density matrix of eq. (\ref{ec: Density Matrix}).
+To do it, we substitute eq. (\ref{ec: Density Matrix}) in eq. (\ref{ec: Pauli channel 1 qbit}):
+\begin{equation}
+\mathcal{E}(\rho) = \dfrac{1}{2}\sum_{\gamma,\alpha=0}^3 k_{\gamma} r_{\alpha} \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}.
+\end{equation}
+This can be simplified by using the following property of Pauli matrices:
+\begin{equation}
+\label{ec: propiedad-pauli}
+\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A_{\alpha,\gamma} = \begin{pmatrix}
+1 & 1 & 1 & 1\\
+1 & 1 & -1 &-1 \\
+1 & -1 & 1 & -1 \\
+1 & -1 & -1 & 1
+\end{pmatrix},
+\end{equation}
+which leads to
+\begin{equation}
+\label{ec: rho-transformada}
+\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
+\end{equation}
+Equation \ref{ec: rho-transformada} gives us another interpretation of Pauli channels.
+Pauli channels take each component $r_{\alpha}$
+of the density matrix and multiply them
+by $\sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}$, 
+that is:
+\begin{equation}
+\label{ec: multipliers}
+r_{\alpha}  \xrightarrow[\text{Channel}]{\text{Pauli}}  \tau_{\alpha} r_{\alpha} ,\;\; \tau_{\alpha} := \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}.
+\end{equation}
+Furthermore, reverting the definition of $\tau_{\alpha}$ by using that $A^{-1} = \dfrac{1}{4} A$, 
+we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\gamma} A_{\gamma,\alpha} \tau_{\gamma}$.
+Then, using that $k_{\gamma} \geq 0$ and $\sum_{\gamma} k_{\gamma} = 1$,
+we get the following conditions on the multipliers:
+\begin{eqnarray}
+\label{eq: conditions-tetrahedron}
+1+\tau_i -\tau_j - \tau_k \geq 0, \\
+1+\tau_1 + \tau_2 + \tau_3 \geq 0.
+\end{eqnarray}
+These conditions imply that $(\tau_1,\tau_2,\tau_3)$
+has to be inside a tetrahedron with
+vertices $(1,1,1), (1,-1,-1),(-1,1,-1)$ and $(-1,-1,1)$. 
+Therefore, the $\tau_{1,2,3}$ are numbers between 
+$-1$ and $1$, which means that the components
+$r_{\alpha}$ of the density matrix are always 
+attenuated and possibly flipped sign.
+
+Pauli channels can be used to model noise....
 
@@
 \end{eqnarray}
-Then, we define a Pauli channel as a transformation of the density 
-matrix given by
+Then, just as before we define a Pauli channel as a transformation that applies 
+the operators $\sigma_{\vec{\gamma}}$ to $\rho$ with probabilities $k_{\vec{\gamma}}$
+and is described mathematically by:
 \begin{eqnarray}
@@
 where just as before, complete positivity and trace preservation requires
-that $k_{\vec{\gamma}}$ are positive real numbers such 
+that $k_{\vec{\gamma}}$ are non-negative real numbers such 
 that $\sum_{\vec{\gamma}} k_{\vec{\gamma}}=1$.
 
+\textbf{Interpretación de multiplicadores}
+
 \cpnote{Creo qeu toca motivar, conectar con cosas conocidas y en general no ser tan seco}
+
 % }}}
-\subsection*{Circuit for a Pauli Channel} % {{{
+\subsection*{Pauli Dynamical Maps} % {{{
+\label{subsec: Pauli Dynamical Maps}
+
+A Pauli dynamical map is defined as a continuous parametrized 
+curve drawn inside the set of Pauli channels and starting at the identity channel. 
+Therefore, a Pauli dynamical map can be written as
+\begin{eqnarray}
+\label{ec: Pauli dynamical map}
+\mathcal{E}_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
+\end{eqnarray}
+where $p$ is a parameter in an interval $[a,b]$ 
+and $\mathcal{E}_p$ is a Pauli channel for every $p$, 
+with $\mathcal{E}_a$ being the identity channel.
+
+% }}}
+% }}}
+\section{Circuit for a Pauli Channel} % {{{
 \label{subsec: Circuit for a Pauli Channel}
@@
 arbitrary Pauli channel on a system of $N$ qubits. 
-To do it, it is important to realize that a Pauli channel
- as shown in Eq~(\ref{ec: pauli channel N-qubt})  can 
-be interpreted as a transformation that applies
+To do it, we remember that a Pauli channel as in eq.~(\ref{ec: pauli channel N-qubt})
+is interpreted as a transformation that applies
 each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
@@
 it with the help of $2n$ ancilla qubits.
+The general idea is to create a state in the ancilla qubits that can then
+be used to apply the operators $\sigma_{\vec{\gamma}}$
+to the system.
 The circuit that does this is presented in Fig~(\ref{fig: circuit-pauli}) and its 
@@
 \lstick{ } & & & & & &\\
-\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=2]{$|\gamma_0 \rangle$} &  & & &\\
+\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=7]{$|\vec{\gamma} \rangle$} &  & & &\\
 \lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
-\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & \rstick[wires=2]{$|\gamma_1 \rangle$} & & & &\\
+\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & & & & &\\
 \lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
 \vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
-\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & \rstick[wires=2]{$|\gamma_{n-1} \rangle$}& & & & \\
+\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & & & & & \\
 \lstick{$aq_{2N-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
@@
 
-\subsubsection*{Simulation for one-qubit Pauli channels} % {{{
+\subsection*{Simulation for one-qubit Pauli channels} % {{{
 \label{subsec: Simulation for one-qubit Pauli channels}
@@
 \end{figure}
-% }}}
-\subsubsection*{Pauli Dynamical Maps} % {{{
-\label{subsec: Pauli Dynamical Maps}
-
-A Pauli dynamical map is defined as a continuous parametrized 
-curve drawn inside the set of Pauli channels and starting at the identity channel. 
-Therefore, a Pauli dynamical map can be written as
-\begin{eqnarray}
-\label{ec: Pauli dynamical map}
-\mathcal{E}_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
-\end{eqnarray}
-where $p$ is a parameter in an interval $[a,b]$ 
-and $\mathcal{E}_p$ is a Pauli channel for every $p$, 
-with $\mathcal{E}_a$ being the identity channel.
 
@@
 % }}}
-% }}}
+
 \section*{OPR Circuits} % {{{

### 2023-04-18 main.tex
Otros cambios

@@
 concept of quantum channels, focusing on a specific type called Pauli channels.
-Finally, we consider Pauli dynamical maps, which
+Furthermore, we define Pauli dynamical maps, which
 are curves of Pauli channels parametrized by a variable.
-
-%Quitarrrr:
-Then, we propose a quantum circuit that simulates N-qubit Pauli channels
-and show the results of implementing the circuit for $N=1$ on
-a quantum computer. 
 % }}}
@@
 
-In quantum mechanics, a closed system is represented by a state vector in a 
+In quantum mechanics, a closed system's state is represented by a vector in a 
 Hilbert space $\mathcal{H}$. 
-The state's evolution is given by Schrodinger's
-equation and is always unitary.
-However, in real-world situations, 
-quantum systems are usually open and interact with their environment in various complicated ways. 
-For example, the system's state may become entangled with the environment,
-which can lead to loss of information of the system's state over time.
+The state's evolution is unitary and given by Schrodinger's equation~\cite{Rieffel}.
+However, in real-world situations, quantum systems are usually open, 
+which means that they interact with their environment~\cite{Breuer}. 
+For instance, the system's state may become entangled with the environment,
+leading to a loss of information about the system's state over time.
 
-Instead of vectors in the Hilbert space $\mathcal{H}$,
-open systems are described by matrices $\rho$ acting on $\mathcal{H}$
-called density matrices and they include information about 
-the system's interaction with the environment.
-To be physically valid, a density matrix $\rho$
-has to satisfy the two following conditions:
-1. $\tr(\rho) =1$ and 2. $\rho$ is positive semi-definite $(\rho \geq 0)$.
+To describe open systems, instead of state vectors,
+we use matrices $\rho$ that act on $\mathcal{H}$.
+These matrices are called density matrices, and they include information about the system's interaction with its environment. 
+For a density matrix $\rho$ to be physically valid, 
+it must satisfy two conditions: $\tr(\rho) = 1$ and $\rho$ is positive semi-definite,
+which is denoted as $\rho \geq 0$~\cite{chuangbook}.
 
-Given that, we can finally define quantum channels, which
-describe the time evolution of open quantum systems.
+Knowing this, we can now define quantum channels.
+Quantum channels are operators $\mathcal{E}$ that
+describe the evolution of open quantum systems, such that $\rho \rightarrow \mathcal{E}(\rho)$.
 Quantum channels are the most general linear operations
-that a quantum system (which is represented 
-by a density matrix $\rho$) can undergo independently of its
+that a quantum system can undergo independently of its
 past~\cite{zimansbook,cirac}.
@@
 (where $\mathbb{I}_n$ is the $n\times n$ identity matrix).
-This is required to ensure that even if $\rho$ is entangled with another system,
-applying $\mathcal{E}$ to $\rho$ while doing nothing to the
- other system still results in  a positive semidefinite state.
+This ensures that even if the principal system is entangled with another system,
+applying $\mathcal{E}$ to the principal system while doing nothing to the
+ other one still results in  a positive semidefinite state for the principal system~\cite{chuangbook}.
 
-Given a possible quantum channel $\mathcal{E}$, 
-the condition of trace preservation is straightforward to examine but complete positivity is not as simple.
+Given a quantum channel $\mathcal{E}$, 
+the condition of trace preservation is straightforward to verify but complete positivity is not as simple.
 To test complete positivity of a quantum channel, 
-Jamiołkowski and Choi~\cite{choi,jamil} developed a simple algorithm.  
-The algorithm exploits the
+Jamiołkowski and Choi~\cite{choi,jamil} developed a simple algorithm that exploits the
 isomorphism between a channel $\mathcal{E}$ and the state $\mathcal{D} =
@@
 type of channel for $N$-qubit systems called Pauli channels.
-First we define a Pauli channel on a one-qubit system,
-whose most general single-qubit density
-matrix can be written as
-\begin{eqnarray}
-\label{ec: Density Matrix}
+First we will define these channels for single-qubit systems,
+whose most general density matrix can be written as~\cite{chuangbook}:
+\begin{equation}
+\label{eq: Density Matrix}
 \rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
-\end{eqnarray}
+\end{equation}
 with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
@@
 implies that the remaining $r_{1,2,3}$ form
-a vector $\vec{r}= (r_1,r_2,r_3)$ inside a unit sphere known as the Bloch sphere. \cpnote{explicar un poco mejor. Me parece que para el publico vale 
-la pena ser un poco mas explicito. pero no estoy muy seguro. }. 
-A Pauli channel is defined as an operation that
-applies each Pauli matrix $\sigma_{\gamma}$ to
-the system with probabilities $k_{\gamma}$ with $\gamma = 0,1,2,3$. 
+a vector $\vec{r}= (r_1,r_2,r_3)$ inside a unit sphere known as the Bloch sphere~\cite{Marinescu}.
+That is, every possible density matrix for a one-qubit
+system is uniquely associated with a point in a unit sphere. \cpnote{explicar un poco mejor. Me parece que para el publico vale 
+la pena ser un poco mas explicito. pero no estoy muy seguro.}
+
+Given a one-qubit system described by $\rho$, 
+a Pauli channel is defined as an operation that with probability $k_{\gamma}$
+applies the Pauli matrix $\sigma_{\gamma}$ to
+the system, for $\gamma = 0,1,2,3$~\cite{geometry}.
 Mathematically, the Pauli channel is written in the following way:
 \begin{eqnarray}
-\label{ec: Pauli channel 1 qbit}
+\label{eq: Pauli channel 1 qbit}
 \mathcal{E}(\rho) = \sum_{\gamma=0}^3 k_{\gamma} \sigma_{\gamma} \rho \sigma_{\gamma},
@@
 where of course the probabilities $k_{\gamma}$ of applying $\sigma_{\gamma}$
-are non-negative real numbers such that 
+have to be non-negative real numbers such that 
 $\sum_{\gamma} k_{\gamma} = 1$ (these conditions also ensure that the channel is 
 trace preserving and completely positive).
+
+Pauli channels are some of the 
+most fundamental noise models in quantum information science~\cite{Terhal}. 
+Some notable examples of Pauli channels are the following:
+\begin{itemize}
+\item \textbf{Bit Flip Channel:} This is a channel that with probability $1-p$ leaves the qubit as it is 
+and with probability $p$ it applies the $\sigma_1$ matrix 
+(which flips the basis states $|0\rangle$ and $|1\rangle$ of the qubit), and
+so it is given by:
+\begin{align*}
+\mathcal{E}(\rho) = (1-p) \rho + p \sigma_1 \rho \sigma_1.
+\end{align*}
+Analogous channels exist using $\sigma_3$ (called the bit flip channel,
+which has a probability $p$ of adding a relative phase $\pi$ to the state) or 
+using $\sigma_2$ (called the phase flip channel, 
+which has a probability $p$ of 
+flipping the base states and also add a relative phase $\pi$).
+\item \textbf{Depolarizing channel:} 
+This channel has a probability $1-p$
+of doing nothing to the qubit and a probability $p$ of converting it into the maximally mixed state $\dfrac{1}{2} \mathbb{I}$
+and it can be written as:
+\begin{equation}
+\mathcal{E}(\rho) = (1-p)\rho + p \dfrac{1}{2} \mathbb{I} = \left(1 - \dfrac{3p}{4} \right) \sigma + \dfrac{p}{4} \sigma_1 \rho \sigma_1 + \dfrac{p}{4} \sigma_2 \rho \sigma_2+ \dfrac{p}{4} \sigma_3 \rho \sigma_3.
+\end{equation} 
+\end{itemize}
+
 \cpnote{en todo hay que mejorar un poco la redaccion. Aca me gustaria que 
@@
 
-Apart from this interpretation of Pauli channels,
-we can find another one by seeing how the channel acts on the 
-density matrix of eq. (\ref{ec: Density Matrix}).
-To do it, we substitute eq. (\ref{ec: Density Matrix}) in eq. (\ref{ec: Pauli channel 1 qbit}):
+We can also see how an arbitrary Pauli channel acts on an arbitrary  
+density matrix.
+To do it, we substitute eq. (\ref{eq: Density Matrix}) 
+in eq. (\ref{eq: Pauli channel 1 qbit}):
 \begin{equation}
@@
 \begin{equation}
-\label{ec: propiedad-pauli}
+\label{eq: propiedad-pauli}
 \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A_{\alpha,\gamma} = \begin{pmatrix}
@@
 \begin{equation}
-\label{ec: rho-transformada}
+\label{eq: rho-transformada}
 \mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
 \end{equation}
-Equation \ref{ec: rho-transformada} gives us another interpretation of Pauli channels.
-Pauli channels take each component $r_{\alpha}$
-of the density matrix and multiply them
+Eq.~(\ref{eq: rho-transformada}) once again has the form of eq.~(\ref{eq: Density Matrix})
+but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
+This gives us another way of understanding Pauli channels
+as operations that take each component $r_{\alpha}$
+of the density matrix and multiplies them
 by $\sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}$, 
@@
 \begin{equation}
-\label{ec: multipliers}
+\label{eq: multipliers}
 r_{\alpha}  \xrightarrow[\text{Channel}]{\text{Pauli}}  \tau_{\alpha} r_{\alpha} ,\;\; \tau_{\alpha} := \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}.
 \end{equation}
+Notice that $\tau_0 = 1$, which is a consequence of $\sum_{\gamma}k_{\gamma}=1$
+and ensures that after the channel, the resulting density matrix still has trace one. 
 Furthermore, reverting the definition of $\tau_{\alpha}$ by using that $A^{-1} = \dfrac{1}{4} A$, 
-we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\gamma} A_{\gamma,\alpha} \tau_{\gamma}$.
-Then, using that $k_{\gamma} \geq 0$ and $\sum_{\gamma} k_{\gamma} = 1$,
-we get the following conditions on the multipliers:
+we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\alpha} A_{\alpha,\gamma} \tau_{\alpha}$.
+Then, using that $k_{\gamma} \geq 0$
+we get the following conditions on the multipliers $\tau_{\alpha}$:
 \begin{eqnarray}
 \label{eq: conditions-tetrahedron}
-1+\tau_i -\tau_j - \tau_k \geq 0, \\
-1+\tau_1 + \tau_2 + \tau_3 \geq 0.
+&1+\tau_i -\tau_j - \tau_k \geq 0,  \;\;\; \text{for $i,j,k$ different numbers in $\{1,2,3\}$}, \\
+&1+\tau_1 + \tau_2 + \tau_3 \geq 0.
 \end{eqnarray}
+
 These conditions imply that $(\tau_1,\tau_2,\tau_3)$
@@
 $r_{\alpha}$ of the density matrix are always 
-attenuated and possibly flipped sign.
+attenuated and possibly sign flipped.
 
-Pauli channels can be used to model noise....
-
-Having defined the one qubit case, 
-in order to present the $N-$qubit one, we 
-need to introduce the so-called \textit{Pauli strings}, defined as
+Having defined the one qubit case,  we can now generalize to $N$ qubits.
+In order to do it, we need to introduce the so-called \textit{Pauli strings}, defined as
 \begin{eqnarray}
-\label{ec: Pauli string}
+\label{eq: Pauli string}
 \sigma_{\vec{\alpha}} = \sigma_{\alpha_1} \otimes \sigma_{\alpha_2}\otimes \cdots \otimes \sigma_{\alpha_N},
@@
 of a system of $N$ qubits can be written using Pauli strings as:
-\begin{eqnarray}
-\label{ec:  Density matrix Nqbit}
+\begin{equation}
+\label{eq:  Density matrix Nqbit}
 \rho = \dfrac{1}{2^N} \sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
-\end{eqnarray}
-Then, just as before we define a Pauli channel as a transformation that applies 
-the operators $\sigma_{\vec{\gamma}}$ to $\rho$ with probabilities $k_{\vec{\gamma}}$
-and is described mathematically by:
-\begin{eqnarray}
-\label{ec: pauli channel N-qubt}
+\end{equation}
+Then, just as before, we define a Pauli channel as a transformation that applies 
+the operator $\sigma_{\vec{\gamma}}$ to $\rho$ with probability $k_{\vec{\gamma}}$
+and is therefore described mathematically by:
+\begin{equation}
+\label{eq: pauli channel N-qubit}
 \mathcal{E}(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}} \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
-\end{eqnarray}
-where just as before, complete positivity and trace preservation requires
-that $k_{\vec{\gamma}}$ are non-negative real numbers such 
+\end{equation}
+where just as before, $k_{\vec{\gamma}}$ are non-negative real numbers such 
 that $\sum_{\vec{\gamma}} k_{\vec{\gamma}}=1$.
 
-\textbf{Interpretación de multiplicadores}
-
+As in the one qubit case, Pauli channels for $N$ qubits 
+attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
+This can be seen by substituting eq. (\ref{eq:  Density matrix Nqbit}) in eq. (\ref{eq: pauli channel N-qubit})
+and using the property of eq. (\ref{eq: propiedad-pauli}):
+\begin{align*}
+\mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
+& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
+\end{align*}
+which means that applying the Pauli channel multiplies the 
+components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
 \cpnote{Creo qeu toca motivar, conectar con cosas conocidas y en general no ser tan seco}
@@
 
-A Pauli dynamical map is defined as a continuous parametrized 
+As seen in the last section, Pauli channels and in 
+general quantum channels are discrete maps
+that transform a density matrix $\rho$ into $\mathcal{E}(\rho)$.
+However, we could also define a continuous set of 
+channels $\varepsilon_p$ with $p$ a real parameter.
+
+For the special case of Pauli channels, we define 
+a Pauli dynamical map as a continuous parametrized 
 curve drawn inside the set of Pauli channels and starting at the identity channel. 
@@
 \begin{eqnarray}
-\label{ec: Pauli dynamical map}
+\label{eq: Pauli dynamical map}
 \mathcal{E}_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
@@
 
+In this section we propose a quantum circuit that 
+simulates N-qubit Pauli channels.
+Furthermore, we show the results of implementing the circuit for $N=1$ on
+a quantum computer. 
 \cpnote{esto está un poco desordenado y a un ritmo creo qeu inapropiado por lo rapido}
 
-We are interested in constructing a quantum circuit that can implement an
-arbitrary Pauli channel on a system of $N$ qubits. 
-To do it, we remember that a Pauli channel as in eq.~(\ref{ec: pauli channel N-qubt})
-is interpreted as a transformation that applies
-each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
-
-Given this interpretation of the channel, 
-it is easy to construct a quantum circuit that implements 
-it with the help of $2n$ ancilla qubits.
-The general idea is to create a state in the ancilla qubits that can then
-be used to apply the operators $\sigma_{\vec{\gamma}}$
-to the system.
-The circuit that does this is presented in Fig~(\ref{fig: circuit-pauli}) and its 
-first step in the circuit is to create the state
+To create the circuit, we remember that a Pauli channel as in eq.~(\ref{eq: pauli channel N-qubit})
+applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
+Given this, it is easy to construct a quantum circuit that implements 
+a Pauli channel with the help of $2N$ ancilla qubits,
+the circuit that does this is presented in fig. (\ref{fig: circuit-pauli}).
+The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
 \begin{eqnarray}
-\label{ec: state}
+\label{eq: state}
 \sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
@@
 in the ancilla qubits, 
-where $b_{\vec{\gamma}}$ is in general a complex number such that 
-\begin{eqnarray}
-\label{ec: b}
-|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}.
-\end{eqnarray}
-Moreover $|\vec{\gamma}\rangle$ is defined as a $2n$ qubit state given by
-\begin{eqnarray}
-|\vec{\gamma} \rangle = |\gamma_1\rangle |\gamma_2 \rangle \cdots |\gamma_N \rangle,
-\end{eqnarray}
-where $|\gamma_i \rangle$ is the $2$ qubit state $|00\rangle, |01\rangle , |10\rangle$ or $|11\rangle$ when $\gamma_i = 0,1,2,3$ respectively. \\
+where $b_{\vec{\gamma}}$ are numbers such that $
+|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}.$
+
+%Moreover $|\vec{\gamma}\rangle$ is defined as a $2n$ qubit state given by
+%\begin{eqnarray}
+%|\vec{\gamma} \rangle = |\gamma_1\rangle |\gamma_2 \rangle \cdots |\gamma_N \rangle,
+%\end{eqnarray}
+%where $|\gamma_i \rangle$ is the $2$ qubit state $|00\rangle, |01\rangle , |10\rangle$ or $|11\rangle$ when $\gamma_i = 0,1,2,3$ respectively. \\
 
@@
 
-This means that when measured in the computational base, the state given in Eq~(\ref{ec: state})
+This means that when measured in the computational basis, the state given in eq.~(\ref{eq: state})
 collapses to $|\vec{\gamma}\rangle$ with a 
 probability $|b_{\vec{\gamma}}|^2 = k_{\gamma}$. 
-The circuit in Fig~(\ref{fig: circuit-pauli}) uses this fact
-to apply the operations $\sigma_{\vec{\gamma}}$ over the principal qubits
-with probabilities $k_{\gamma}$ by using controlled operations. 
-The symbol shown in Fig~(\ref{fig: control})
-indicates that the controlled gate is
-activated if these two qubits are in the state $|\gamma_i \rangle$. 
-\begin{figure}[h!]
-\centering
-\begin{quantikz}
-& \ctrl{1} & \qw \rstick[wires=2]{$|\gamma_i \rangle$} \\
-& \control{} & \qw
-\end{quantikz}
-\caption{{\bf Control qubits} \tbnote{Al igual que antes, esta imagen se tiene que quitar para la entrega final.} Control $|\gamma_i \rangle$ for two qubits.}
-\label{fig: control}
-\end{figure}
-
-To see why the circuit from Fig~(\ref{fig: circuit-pauli})
- works, 
-we note that after creating the state 
-$\sum_{\vec{\gamma}} b_{\gamma} \; |\vec{\gamma} \rangle$, 
-the circuit applies each gate $\sigma_{\vec{\gamma}}$ to the principal qubits 
-under the condition that the ancilla qubits are 
-on the state $|\vec{\gamma}\rangle$. 
-This  means that each gate $\sigma_{\vec{\gamma}}$ is applied 
-on the principal qubits with a probability $k_{\vec{\gamma}}$, 
-just as we wanted.  \\
+The circuit in fig.~(\ref{fig: circuit-pauli}) uses this fact
+to operate $\sigma_{\vec{\gamma}}$ on the principal qubits
+with a probability $k_{\gamma}$ by using controlled operations 
+that apply $\sigma_{\vec{\gamma}}$ to the principal qubits
+only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
+Therefore, the circuit from fig.~(\ref{fig: circuit-pauli}) 
+applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
+with a probability $k_{\vec{\gamma}}$, 
+just as a Pauli channel is supposed to do.  \\
 
@@
 For the particular case of a Pauli channel on one qubit, 
-the circuit that simulates it can be constructed as in Fig~(\ref{fig: citcuit-pauli-1}),
- which is a special case of Fig(\ref{fig: circuit-pauli}).
+the circuit that simulates it can be constructed as in fig. (\ref{fig: citcuit-pauli-1}),
+ which is a special case of fig. (\ref{fig: circuit-pauli}).
 
@@
 \end{figure}
-Taking advantage of the quantum computers that IBM has available,
-we sampled $250$ one-qubit Pauli channels and simulated them using the 
+Taking advantage of the quantum computers that IBM has available~\cite{Qiskit},
+we sampled $249$ one-qubit Pauli channels and simulated them using the 
 ibmq-lima quantum computer. 
-For each of these channels, the accuracy of the implementation in the quantum computer
-was quantified by calculating the
- process fidelity of the Choi matrix obtained by performing
-quantum process tomography to the circuit
-with respect to the theoretical Choi matrix of
-the corresponding channel.
-Finally, using the well known fact that one-qubit Pauli channels can be represented
-as points in a tetrahedron with corners $(1,1,1), (1-1,-1), (-1,1,-1)$ and $(-1,-1,1)$, 
-in Fig~(\ref{fig: fidelity one qubit}).
+For each of these channels, we used quantum process tomography to obtain the
+Choi matrix corresponding to the implementation of the circuit~\cite{Chuang:1996}.
+Then, we compared this Choi matrix with the theoretical
+Choi matrix of the channel we were implementing by calculating the 
+process fidelity~\cite{Jozsa94,chuangbook} between them.
+Finally, using the representation of Pauli channels in a tetrahedron as
+in eq.~(\ref{eq: conditions-tetrahedron}),
+we show the fidelities for these channels in fig.~(\ref{fig: fidelity one qubit}).
 \begin{figure}[h!]
@@
 {\bf Fidelities one-qubit Pauli channel} Fidelities of one-qubit Pauli channels implemented on IBM's ibmq-lima.
-The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the fidelity of each channel's implementation using the circuit for a 1-qubit Pauli channel}
+The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the fidelity of each channel's implementation using the circuit for a 1-qubit Pauli channel.
+\tbnote{Puedo cambiar la fidelidad por otras distancias, como la diamond norm,
+pero estoy buscando cuál conviene más.}}w
 \label{fig: fidelity one qubit}
@@
 
+% }}}
+% }}}
+
+\newpage
+\section*{OPR Circuits} % {{{
+\label{sec: OPR Circuits}
 Dynamical maps can be implemented using the same circuit as 
@@
 \begin{eqnarray}
-\label{ec: parametrized state}
+\label{eq: parametrized state}
 \sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
 \end{eqnarray}
-% }}}
-% }}}
 
-\section*{OPR Circuits} % {{{
-\label{sec: OPR Circuits}
 \textbf{Puntos:}

### 2023-04-20 main.tex
last hope failed, maybe now

@@
 \section{Pauli Channels}  \label{sec: Pauli Channels} % {{{
+\cpnote{Es raro qeu la seccion y una subseccion se llamen igual. Por discutir con Tomas}
 % Intro  {{{
@@
 
-\cpnote{Creo que toca iterar, pensando un poco en nivel licenciatura. ver ejemplos }
-\cpnote{Tambien creo que no es coherente tener una subseccion para esto si 
-lo qeu se quiere decir en la seccion es otra cosa.}
+% \cpnote{Creo que toca iterar, pensando un poco en nivel licenciatura. ver ejemplos }
+% \cpnote{Tambien creo que no es coherente tener una subseccion para esto si 
+% lo qeu se quiere decir en la seccion es otra cosa.}
 
 In quantum mechanics, a closed system's state is represented by a vector in a
-Hilbert space $\mathcal{H}$. 
-The state's evolution is unitary and given by Schrodinger's equation~\cite{Rieffel}.
-However, in real-world situations, quantum systems are usually open, 
-which means that they interact with their environment~\cite{Breuer}. 
-For instance, the system's state may become entangled with the environment,
-leading to a loss of information about the system's state over time.
+Hilbert space $\mathcal{H}$.  The state's evolution is unitary and given by
+Schrodinger's equation~\cite{Rieffel}.  However, in real-world situations,
+quantum systems are usually open, which means that they interact with their
+environment~\cite{Breuer}.  For instance, the system's state may become
+entangled with the environment, leading to a loss of information about the
+system's state over time.
 
@@
 For a density matrix $\rho$ to be physically valid, 
-it must satisfy two conditions: $\tr(\rho) = 1$ and $\rho$ is positive semi-definite,
+it must satisfy two conditions: $\tr(\rho) = 1$ and it must be positive semi-definite,
 which is denoted as $\rho \geq 0$~\cite{chuangbook}.
@@
 Quantum channels are operators $\mathcal{E}$ that
-describe the evolution of open quantum systems, such that $\rho \rightarrow \mathcal{E}(\rho)$.
+can describe the evolution of open quantum systems, such that $\rho \rightarrow \mathcal{E}(\rho)$.
 Quantum channels are the most general linear operations
@@
 
+\cpnote{Le hice un par de cambios pequeños pero la veo bastante bien. }
 % }}}
@@
 now we turn our attention to a specific 
-type of channel for $N$-qubit systems called Pauli channels.
+type of channels for $N$-qubit systems called Pauli channels.
 First we will define these channels for single-qubit systems,
@@
 That is, every possible density matrix for a one-qubit
-system is uniquely associated with a point in a unit sphere. \cpnote{explicar un poco mejor. Me parece que para el publico vale 
-la pena ser un poco mas explicito. pero no estoy muy seguro.}
+system is uniquely associated with a point in a unit sphere. 
+% \cpnote{explicar un poco mejor. Me parece que para el publico vale 
+% la pena ser un poco mas explicito. pero no estoy muy seguro.}
 
@@
 \end{eqnarray} 
-where of course the probabilities $k_{\gamma}$ of applying $\sigma_{\gamma}$
-have to be non-negative real numbers such that 
+where the probabilities $k_{\gamma}$ of applying $\sigma_{\gamma}$
+are non-negative real numbers such that 
 $\sum_{\gamma} k_{\gamma} = 1$ (these conditions also ensure that the channel is 
@@
 \end{itemize}
-
-\cpnote{en todo hay que mejorar un poco la redaccion. Aca me gustaria que 
-se interpretara. Creo qe es mas que atenuacion de los componentes, o es solo atenuacion? 
-en todo caso ver mejor como va la cosa. }
 
@@
 components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
-\cpnote{Creo qeu toca motivar, conectar con cosas conocidas y en general no ser tan seco}
-
 % }}}
@@
 \label{subsec: Pauli Dynamical Maps}
+
+\cpnote{aca voy}
 
@@
 % }}}
-
-\newpage
 \section*{OPR Circuits} % {{{

### 2023-04-21 main.tex
Fix the fixes
Pipeline goes brrrrrrr
Cambios sec 1 y 2

@@
 % }}}
-\section*{Introduction} % {{{
+\section{Introduction} % {{{
 
 % }}}
-\section{Pauli Channels}  \label{sec: Pauli Channels} % {{{
+\section{Quantum Channels}  \label{sec: Pauli Channels} % {{{
 \cpnote{Es raro qeu la seccion y una subseccion se llamen igual. Por discutir con Tomas}
+\tbnote{Lo cambié}
+\cpnote{El texto esta bien, pero creo qeu la distribucino de subsecciones esta chistosna y 
+los titulo tambien. Platicar con Tomas a ver a que llegamos. }
+
 % Intro  {{{
@@
 % }}}
-\subsection*{Quantum Channels} \label{subsec: Quantum Channels} % {{{
+%\subsection*{Quantum Channels} \label{subsec: Quantum Channels} % {{{
 
@@
 \cpnote{Le hice un par de cambios pequeños pero la veo bastante bien. }
+\tbnote{Perfecto, gracias!}
 % }}}
-\subsection*{Pauli Channels} \label{subsec: Pauli Channels} % {{{
+\subsection{Pauli Channels} 
+\label{subsec: Pauli Channels} % {{{
 
@@
 % }}}
-\subsection*{Pauli Dynamical Maps} % {{{
+\subsection{Pauli Dynamical Maps} % {{{
 \label{subsec: Pauli Dynamical Maps}
-
-\cpnote{aca voy}
 
@@
 
-In this section we propose a quantum circuit that 
-simulates N-qubit Pauli channels.
-Furthermore, we show the results of implementing the circuit for $N=1$ on
-a quantum computer. 
-\cpnote{esto está un poco desordenado y a un ritmo creo qeu inapropiado por lo rapido}
+\cpnote{Acá voy}
 
-To create the circuit, we remember that a Pauli channel as in eq.~(\ref{eq: pauli channel N-qubit})
+In this section we propose a quantum circuit that simulates N-qubit Pauli
+channels.  Furthermore, we show the results of implementing the circuit for
+$N=1$ on a quantum computer.
+
+To create the circuit, we remember that a Pauli channel as the one in eq.~(\ref{eq: pauli channel N-qubit})
 applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
@@
 where $b_{\vec{\gamma}}$ are numbers such that $
-|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}.$
+|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
+The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined by $|\gamma_1 \rangle \cdots |\gamma_N\rangle$.
 
@@
 
-\cpnote{paro aca de leer}
-
 \begin{figure}[h!]
@@
 \begin{quantikz}
-\lstick{$q_0$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_0}} & \qw & & &  & & \rstick[wires=12]{Repeat for all \\
- vectors $\vec{\gamma}$} \\
-\lstick{$q_1$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_1}} & \qw & & & &\\
-\lstick{ } & \vdots & \vdots & \vdots & &  & & & &\\
-\lstick{$q_{n-1}$} & \qw & \qw & \qw & \gate{\sigma_{\gamma_{n-1} }} & \qw & & &\\
-\lstick{ } & & & & & &\\
-\lstick{$aq_0$} & \qw & \gate[wires=7,nwires=5]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \qw &  \ctrl{-5} & \qw & \rstick[wires=7]{$|\vec{\gamma} \rangle$} &  & & &\\
-\lstick{$aq_1$} & \qw & & \qw &  \ctrl{-6} &\qw & & & & & \\
-\lstick{$aq_2$} &\qw & & \qw &  \ctrl{-7} & \qw & & & & &\\
-\lstick{$aq_3$} &\qw & & \qw &  \ctrl{-8} & \qw & & & & &\\
-\vdots  &\vdots & & \vdots & &  \vdots & & & & &\\
-\lstick{$aq_{2N-2}$}& \qw &  &\qw  & \ctrl{-10} & \qw & & & & & \\
-\lstick{$aq_{2N-1}$}& \qw & & \qw  &  \ctrl{-11} & \qw & & & & &\\
+\lstick{$q:\; |0\rangle^{\otimes N}$} & \qw & \gate{\sigma_{\vec{\gamma}}} \gategroup[wires=2,steps
+=1,style={dashed, inner sep=4pt}]{Repeat for all $\vec{\gamma}$}
+\gategroup[wires=2,steps
+=1,style={dashed, inner sep=4pt}, label style = {label position = below, yshift = 0.15cm}]
+{$|\vec{\gamma}\rangle$} & \qw \\
+\lstick{$\tilde{q}:\; |0\rangle^{\otimes 2N}$} & \gate[wires=1]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \ctrl{-1} 
+% \gategroup[wires=1,steps
+%=1,style={color=white, inner sep=0pt}, label style= {label position=below}]{$|\vec{\gamma}\rangle$} 
+& \qw 
 \end{quantikz}
 \caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS.
-Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel.} Circuit to implement an $N$-qubit Pauli channel
-on the qubits $q_0, q_1, \cdots, q_{n-1}$. 
+Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel on $N$ qubits.}
 The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
-on $2N$ ancilla qubits and then uses them to apply
-all possible Pauli strings on the principal qubits
-with probabilities $k_{\vec{\gamma}}$.}
+on the $2N$ ancilla qubits denoted by $\tilde{q}$. 
+Then, for every vector $\vec{\gamma}$, it applies the operator $\sigma_{\vec{\gamma}}$ 
+if the ancilla qubits are in the state $\vec{\gamma}$.}
 \label{fig: circuit-pauli}
@@
 
-\subsection*{Simulation for one-qubit Pauli channels} % {{{
+\subsection{Simulation for one-qubit Pauli channels} % {{{
 \label{subsec: Simulation for one-qubit Pauli channels}
@@
 the circuit that simulates it can be constructed as in fig. (\ref{fig: citcuit-pauli-1}),
- which is a special case of fig. (\ref{fig: circuit-pauli}).
+ which is a special case of fig. (\ref{fig: circuit-pauli})
+ but with all qubits explicitly shown.
 
@@
 \lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
-\lstick{$aq_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
-\lstick{$aq_1$} & \gateinput{$b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
+\lstick{$\tilde{q}_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
+\lstick{$\tilde{q}_1$} & \gateinput{$\;\;\;\;\;b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
 \end{quantikz}
@@
 ibmq-lima quantum computer. 
-For each of these channels, we used quantum process tomography to obtain the
-Choi matrix corresponding to the implementation of the circuit~\cite{Chuang:1996}.
+For each of these channels, we used quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the
+Choi matrix corresponding to the implementation of the circuit $\mathcal{C}_{I}$.
 Then, we compared this Choi matrix with the theoretical
-Choi matrix of the channel we were implementing by calculating the 
-process fidelity~\cite{Jozsa94,chuangbook} between them.
+Choi matrix $\mathcal{C}_T$ of the channel we wanted to implement.
+
+To make this comparison, we used the diamond norm~\cite{Aharonov},
+which allows us to discriminate between quantum channels.
+Suppose an agent is given one of the channels $\mathcal{C}_I$, $\mathcal{C}_T$
+with probability $1/2$ for each,
+and tries to guess which channel they received
+by passing through it a state $\rho$ and measuring the result.
+Then, the maximal probability of success (out of all possible states $\rho$) that
+the agent guesses correctly is~\cite{Benenti}:
+\begin{equation}
+\label{eq: probability-success}
+p_{succ} = \dfrac{1}{2}+ \dfrac{1}{2} ||\mathcal{C}_I - \mathcal{C}_T ||_{\diamond},
+\end{equation}
+where $|| \cdot ||_{\diamond}$ is the diamond norm.
+Notice that $p_{succ}=1/2$ means that the channels
+are indistinguishable, while $p_{succ}=1$
+indicates that they are perfectly distinguishable.
+
 Finally, using the representation of Pauli channels in a tetrahedron as
 in eq.~(\ref{eq: conditions-tetrahedron}),
-we show the fidelities for these channels in fig.~(\ref{fig: fidelity one qubit}).
+we show in fig.~(\ref{fig: fidelity one qubit}) the maximal probabilities of success defined by eq. (\ref{eq: probability-success}) for the channels analyzed.
 \begin{figure}[h!]
 \centering
-\includegraphics[width=0.45\textwidth]{fidelity-points.png}\\
+\includegraphics[width=0.45\textwidth]{probabilities-points.png}\\
 \caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}.
-{\bf Fidelities one-qubit Pauli channel} Fidelities of one-qubit Pauli channels implemented on IBM's ibmq-lima.
-The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the fidelity of each channel's implementation using the circuit for a 1-qubit Pauli channel.
-\tbnote{Puedo cambiar la fidelidad por otras distancias, como la diamond norm,
-pero estoy buscando cuál conviene más.}}w
+{\bf Maximal probabilities of success for one-qubit Pauli channel} $p_{succ}$ of one-qubit Pauli channels implemented on IBM's ibmq-lima.
+The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the distinguishability of each channel's implementation using the circuit for a 1-qubit Pauli channel.}
 \label{fig: fidelity one qubit}
@@
 
+\newpage
 % }}}
 % }}}
-\section*{OPR Circuits} % {{{
+\section{OPR Circuits} % {{{
 \label{sec: OPR Circuits}
@@
 % }}}
-\section*{OPR circuit for a Pauli map} % {{{
+\section{OPR circuit for a Pauli map} % {{{
 \label{sec: OPR circuit for a Pauli map}
@@
 % }}}
-\section*{Exponential maps $e^{iHt}$} % {{{
+\section{Exponential maps $e^{iHt}$} % {{{
 \label{sec: Exponential maps}
@@
 % }}}
-\section*{Conclusion} % {{{
+\section{Conclusion} % {{{
 
@@
 % }}}
-\section*{Supporting information} % {{{
+\section{Supporting information} % {{{
 
@@
 % }}}
-\section*{Acknowledgments} % {{{
+\section{Acknowledgments} % {{{
 Support by projects CONACyT 285754, 254515 and UNAM-PAPIIT IG100518, IG101421 is

### 2023-05-03 main.tex
Corrección
Batman! (this commit has no parents)

@@
 
-In this section we propose a quantum circuit that simulates N-qubit Pauli
-channels.  Furthermore, we show the results of implementing the circuit for
-$N=1$ on a quantum computer.
+In this section we propose a quantum circuit that simulates $N$-qubit Pauli
+channels.  Moreover, we implement the circuit for $N=1$ on a quantum computer
+and analyze the results\cpnote{Quizá en una frase poner el resultado aca o ampliar
+tantito}.
 
-To create the circuit, we remember that a Pauli channel as the one in eq.~(\ref{eq: pauli channel N-qubit})
+\cpnote{Yo abriría este parrafo con una frase que de la idea muy general. Decir 
+algo asi como que vamos a crear un estado conque contenga a las $k$s 
+como coeficientes y leugo controlar la aplicación de los Pauli strings. Luego
+ya dar los detalles. Así incluso mas escueto de lo que pongo. Por ejemplo:
+To design the circiot that implements 13, we construct a state that incorportes
+probabilities $k$ and subsequently apply controlled operation. In particular... }
+\cpnote{No me gusta como está organizado este parrafo. Le puedes dar una iterada?}
+To design the circuit, we remember that a Pauli channel as the one in
+eq.~(\ref{eq: pauli channel N-qubit})
 applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
@@
 \centering
-\begin{quantikz}
-\lstick{$q:\; |0\rangle^{\otimes N}$} & \qw & \gate{\sigma_{\vec{\gamma}}} \gategroup[wires=2,steps
-=1,style={dashed, inner sep=4pt}]{Repeat for all $\vec{\gamma}$}
-\gategroup[wires=2,steps
-=1,style={dashed, inner sep=4pt}, label style = {label position = below, yshift = 0.15cm}]
-{$|\vec{\gamma}\rangle$} & \qw \\
-\lstick{$\tilde{q}:\; |0\rangle^{\otimes 2N}$} & \gate[wires=1]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \ctrl{-1} 
-% \gategroup[wires=1,steps
-%=1,style={color=white, inner sep=0pt}, label style= {label position=below}]{$|\vec{\gamma}\rangle$} 
-& \qw 
-\end{quantikz}
-\caption{\textbf{\tbnote{Hay que quitar esta imagen del texto al entregar el artículo y ponerla en un archivo a parte de tipo TIFF or EPS.
-Hay que dejar el figure solamente con la caption y label.}} {\bf Circuit for an $N$-qubit Pauli channel on $N$ qubits.}
+% \begin{quantikz}
+% \lstick{$q:\; |0\rangle^{\otimes N}$} & \qw & \gate{\sigma_{\vec{\gamma} }} \gategroup[wires=2,steps
+% =1,style={dashed, inner sep=4pt}]{Repeat for all $\vec{\gamma}$}
+% \gategroup[wires=2,steps
+% =1,style={dashed, inner sep=4pt}, label style = {label position = below, yshift = 0.15cm}]
+% {$|\vec{\gamma}\rangle$} & \qw \\
+% \lstick{$\tilde{q}:\; |0\rangle^{\otimes 2N}$} & \gate[wires=1]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \ctrl{-1} 
+% % \gategroup[wires=1,steps
+% %=1,style={color=white, inner sep=0pt}, label style= {label position=below}]{$|\vec{\gamma}\rangle$} 
+% & \qw 
+% \end{quantikz}
+\includegraphics{images/circuito_general.pdf}
+\caption{\cpnote{Revisa el archivo images/circuito\_general.pdf y el makefile correspondiente} {\bf Circuit for an $N$-qubit Pauli channel on $N$ qubits.}
 The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
@@
 
+\cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
+de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
+Itera (quizá solo quitando esas dos palabras)}
 This means that when measured in the computational basis, the state given in eq.~(\ref{eq: state})
 collapses to $|\vec{\gamma}\rangle$ with a 
-probability $|b_{\vec{\gamma}}|^2 = k_{\gamma}$. 
+probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
 The circuit in fig.~(\ref{fig: circuit-pauli}) uses this fact
 to operate $\sigma_{\vec{\gamma}}$ on the principal qubits
-with a probability $k_{\gamma}$ by using controlled operations 
+with a probability $k_{\vec\gamma}$ by using controlled operations 
 that apply $\sigma_{\vec{\gamma}}$ to the principal qubits
@@
 with a probability $k_{\vec{\gamma}}$, 
-just as a Pauli channel is supposed to do.  \\
+just as a Pauli channel is supposed to do.  
+\cpnote{Del circuito, parece ue las fases de las bs gammas no omportan mucho (o nada). 
+Esa libertad la hemos considerado? De alguna manera colapsan curvas de las que
+hemos visto?}
 
@@
 \label{subsec: Simulation for one-qubit Pauli channels}
-For the particular case of a Pauli channel on one qubit, 
-the circuit that simulates it can be constructed as in fig. (\ref{fig: citcuit-pauli-1}),
- which is a special case of fig. (\ref{fig: circuit-pauli})
- but with all qubits explicitly shown.
+\cpnote{Es raro tener una sola subseccion. De perdida dos, o ninguna. Charlemso a ver como 
+reorganizar las secciones (creo que el flujo si va bien hasta ahora)}
+
+For the particular case of a Pauli channel on one qubit, the circuit that
+simulates it can be constructed as in fig.~\ref{fig: citcuit-pauli-1},
+ which is a special case of fig. \ref{fig: circuit-pauli}
+ but with all qubits \cpnote{y compuertas , etc digamos que details} explicitly shown.
 
@@
 \end{quantikz}
-\caption{\tbnote{Al igual que antes, hay que adaptar esta figura y quitarla antes de entregar}.
-{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
+\caption{\cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho. 
+Otra cosa quizá para discutir. La creacion del estado especial de dos qubits no esta
+aca explicita. Eso creo que si lo podemos hacer en general, o no? Como sería eso? Lo discutimos
+a ver si lo pones?
+} {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
 \label{fig: citcuit-pauli-1} 
@@
 ibmq-lima quantum computer. 
-For each of these channels, we used quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the
-Choi matrix corresponding to the implementation of the circuit $\mathcal{C}_{I}$.
+For each of these channels, we used quantum process tomography~\cite{Qiskit,
+Chuang:1996} to obtain the Choi matrix corresponding to the implementation of
+the circuit $\mathcal{C}_{I}$ .
 Then, we compared this Choi matrix with the theoretical
-Choi matrix $\mathcal{C}_T$ of the channel we wanted to implement.
+Choi matrix $\mathcal{C}_T$ of the channel we wanted to implement\cpnote{Quizá
+referirnos mejor al canal? Lo discutimos}.
 
-To make this comparison, we used the diamond norm~\cite{Aharonov},
-which allows us to discriminate between quantum channels.
+To perform this comparison, we used the diamond norm~\cite{Aharonov},
+which allows us to discriminate \cpnote{creo qeu todas lasnormas nos
+permiten discriminar entre canales. itera} between quantum channels.
 Suppose an agent is given one of the channels $\mathcal{C}_I$, $\mathcal{C}_T$
-with probability $1/2$ for each,
+with probability $1/2$ for each \cpnote{que pasa para una probabilidad $p$?
+Otra cosa, los canales no se caracterizan por lo general po rla matriz 
+de choi, tonces por aca quizá hay problemas. Discutamos notacion.},
 and tries to guess which channel they received
@@
 \end{equation}
-where $|| \cdot ||_{\diamond}$ is the diamond norm.
-Notice that $p_{succ}=1/2$ means that the channels
-are indistinguishable, while $p_{succ}=1$
-indicates that they are perfectly distinguishable.
+where $|| \cdot ||_{\diamond}$ is the diamond norm.  Notice that $p_{succ}=1/2$
+means that the channels are the same \cpnote{qioza una frase explicando porque
+esto es razonable}, while $p_{succ}=1$ indicates that they are perfectly
+distinguishable \cpnote{hummm ejemplo al menos para nosotros.}.
 
@@
 in eq.~(\ref{eq: conditions-tetrahedron}),
-we show in fig.~(\ref{fig: fidelity one qubit}) the maximal probabilities of success defined by eq. (\ref{eq: probability-success}) for the channels analyzed.
+we show in fig.~(\ref{fig: fidelity one qubit}) the maximal probabilities of
+success defined by eq. (\ref{eq: probability-success}) for the channels
+analyzed. \cpnote{Falta analisis de los resultados. }
+
+\cpnote{Mejorar la figura, quizá dejando la tridimensional y ademas poniendo unos 6 cortes. Probar
+con diferentes colores.}
+
 \begin{figure}[h!]
@@
 
-\newpage
 % }}}

### 2023-05-05 main.tex
Fixed the build.
Cambios

@@
 \usepackage{textcomp,marvosym}
+\usepackage{subcaption}
 
@@
 cuadrado, quizá pasar por chatgpt. hacerlo al final cuanod se tenga el capitulo
-por lo menos leido y aprobado en principio de mi parte.} we introduce the
+por lo menos leido y aprobado en principio de mi parte.} \tbnote{Ya} we introduce the
 concept of quantum channels, focusing on a specific type called Pauli channels.
@@
 \section{Circuit for a Pauli Channel} % {{{
-\label{subsec: Circuit for a Pauli Channel}
-
+\label{sec: Circuit for a Pauli Channel}
 \cpnote{Acá voy}
@@
 channels.  Moreover, we implement the circuit for $N=1$ on a quantum computer
-and analyze the results\cpnote{Quizá en una frase poner el resultado aca o ampliar
-tantito}.
+and analyze the results using the diamond norm.
+\cpnote{Quizá en una frase poner el resultado aca o ampliar
+tantito} \tbnote{Va, agregué lo siguiente: 
+We conclude that the circuit performs optimally for channels  in proximity to the
+completely depolarizing channel but
+it is deficient close to unitary channels.}
+
+\subsection{Description of the Circuit for a Pauli Channel} %{{{
+\label{subsec: Description of the circuit}
 
@@
 \cpnote{No me gusta como está organizado este parrafo. Le puedes dar una iterada?}
+\tbnote{Propongo el párrafo en naranja para sustituirlo}
+
 To design the circuit, we remember that a Pauli channel as the one in
@@
 The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined by $|\gamma_1 \rangle \cdots |\gamma_N\rangle$.
+
+{\color{orange} Cambiar por:  To design the circuit that implements \ref{eq: pauli channel N-qubit}, we construct a state that incorportes
+probabilities $k_{\gamma}$ on ancilla qubits and subsequently apply controlled 
+Pauli operations on the principal qubits.
+The circuit that does this is presented in fig. (\ref{fig: circuit-pauli})
+and works by creating the state
+\begin{eqnarray}
+\label{eq: state}
+\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
+\end{eqnarray}
+on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
+|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
+the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined by $|\gamma_1\rangle \cdots |\gamma_N\rangle$.
+}
 
@@
 \includegraphics{images/circuito_general.pdf}
-\caption{\cpnote{Revisa el archivo images/circuito\_general.pdf y el makefile correspondiente} {\bf Circuit for an $N$-qubit Pauli channel on $N$ qubits.}
+\caption{\cpnote{Revisa el archivo images/circuito\_general.pdf y el makefile correspondiente} \tbnote{Oh, ya veo, gracias!.} {\bf Circuit for an $N$-qubit Pauli channel on $N$ qubits.}
 The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
-on the $2N$ ancilla qubits denoted by $\tilde{q}$. 
-Then, for every vector $\vec{\gamma}$, it applies the operator $\sigma_{\vec{\gamma}}$ 
-if the ancilla qubits are in the state $\vec{\gamma}$.}
+on the $2N$ ancilla qubits denoted by $\tilde{q}$. }
 \label{fig: circuit-pauli}
@@
 de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
-Itera (quizá solo quitando esas dos palabras)}
-This means that when measured in the computational basis, the state given in eq.~(\ref{eq: state})
+Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
+When measured in the computational basis, the state given in eq.~(\ref{eq: state})
 collapses to $|\vec{\gamma}\rangle$ with a 
@@
 Esa libertad la hemos considerado? De alguna manera colapsan curvas de las que
-hemos visto?}
+hemos visto?} \tbnote{Sí, es una libertad que se tiene y he considerado y significa que hay muchas elecciones de $b_{\gamma}$ para un mismo canal.
+Es una de las varias cosas que complicaba determinar uno a uno qué canales se pueden hacer.}
 
+%}}}
 \subsection{Simulation for one-qubit Pauli channels} % {{{
@@
 \cpnote{Es raro tener una sola subseccion. De perdida dos, o ninguna. Charlemso a ver como 
-reorganizar las secciones (creo que el flujo si va bien hasta ahora)}
+reorganizar las secciones (creo que el flujo si va bien hasta ahora)} \tbnote{Va.
+Me pareció ponerle su propia subsección a la parte anterior porque creo que esto y lo anterior sí debe ir separado, así que mejor dos subsecciones.}
 
@@
  which is a special case of fig. \ref{fig: circuit-pauli}
- but with all qubits \cpnote{y compuertas , etc digamos que details} explicitly shown.
+ but with all details \cpnote{y compuertas , etc digamos que details}\tbnote{Va, listo} explicitly shown.
 
@@
 \centering
-\begin{quantikz}
-\lstick{$q_0$} & \qw & \gate{\sigma_1} & \gate{\sigma_2} & \gate{\sigma_3} & \qw \\
-\lstick{$\tilde{q}_0$} & \gate[wires=2][3cm]{\quad\quad \text{Create the two qubits state}\quad\quad} & \octrl{-1} & \ctrl{-1} & \ctrl{-1} & \qw \\
-\lstick{$\tilde{q}_1$} & \gateinput{$\;\;\;\;\;b_0 |0 \rangle |0 \rangle + b_1 |0 \rangle |1 \rangle + b_2 |1 \rangle |0 \rangle + b_3 |1 \rangle |1 \rangle $} & \ctrl{-2} & \octrl{-2}  & \ctrl{-2} & \qw
-\end{quantikz}
-\caption{\cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho. 
+\includegraphics{images/circuito_unqubit.pdf}
+\caption{\cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho.} \tbnote{Va, lo hice así, espero haberlo hecho bien.} \cpnote{ 
 Otra cosa quizá para discutir.  La creacion del estado especial de dos qubits no esta
 aca explicita. Eso creo que si lo podemos hacer en general, o no? Como sería eso? Lo discutimos
-a ver si lo pones?
-} {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).}
+a ver si lo pones?} \tbnote{Sí. En la figura que está ahora lo puse (antes sólo había un bloque que
+ decía que se crea el estado $|b\rangle$ sobre los qubits de ancilla).
+Ahora que lo pienso, sí lo prefiero así con la creación explícita y creo que mejora a la discusión después,
+porque muestra que en general se necesitan tres ángulos y es lo que luego buscamos 
+reducir a sólo uno}
+ {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).
+Here we have two ancilla qubits, and the state 
+$b_{00} |00\rangle + b_{01} |01\rangle + b_{10} |10\rangle + b_{11}|11\rangle$ 
+is created on them with the help of three rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) - \arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, 
+$ \theta_1 = 2 \arccos(\sqrt{k_{00} + k_{01}})$ and
+$ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) + \arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$. }
 \label{fig: citcuit-pauli-1} 
@@
 For each of these channels, we used quantum process tomography~\cite{Qiskit,
-Chuang:1996} to obtain the Choi matrix corresponding to the implementation of
-the circuit $\mathcal{C}_{I}$ .
-Then, we compared this Choi matrix with the theoretical
-Choi matrix $\mathcal{C}_T$ of the channel we wanted to implement\cpnote{Quizá
-referirnos mejor al canal? Lo discutimos}.
+Chuang:1996} to obtain the {\color{red} Choi matrix} {\color{orange} operator $\xi_I$}  corresponding to the implementation of
+the circuit {\color{red} $\mathcal{C}_{I}$} .
+Then, we compared this {\color{red} Choi matrix} {\color{orange} operator} with the theoretical
+{\color{red} Choi matrix $\mathcal{C}_T$} {\color{orange} operator $\xi_T$} 
+of the channel we wanted to implement.
+\cpnote{Quizá referirnos mejor al canal? Lo discutimos.} 
+\tbnote{Ah sí, mejor. Cambié lo que puse en rojo por lo que está en naranja.}
 
-To perform this comparison, we used the diamond norm~\cite{Aharonov},
-which allows us to discriminate \cpnote{creo qeu todas lasnormas nos
-permiten discriminar entre canales. itera} between quantum channels.
-Suppose an agent is given one of the channels $\mathcal{C}_I$, $\mathcal{C}_T$
-with probability $1/2$ for each \cpnote{que pasa para una probabilidad $p$?
-Otra cosa, los canales no se caracterizan por lo general po rla matriz 
-de choi, tonces por aca quizá hay problemas. Discutamos notacion.},
+To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
+which gives us a method of discriminating \cpnote{creo qeu todas lasnormas nos
+permiten discriminar entre canales. itera} \tbnote{Lo cambié un poco para que no se entienda que diamond es la única que lo hace} between quantum channels.
+Suppose an agent is given one of the channels $\xi_I$, $\xi_T$
+with probability $1/2$ for each \cpnote{que pasa para una probabilidad $p$?}
+\tbnote{Hay una expresión similar pero que depende de $p$. Lo pongo con $p$ en general?} 
+\cpnote{Otra cosa, los canales no se caracterizan por lo general po rla matriz 
+de choi, tonces por aca quizá hay problemas. Discutamos notacion.} \tbnote{Sip, lo cambié},
 and tries to guess which channel they received
@@
 \label{eq: probability-success}
-p_{succ} = \dfrac{1}{2}+ \dfrac{1}{2} ||\mathcal{C}_I - \mathcal{C}_T ||_{\diamond},
+p_{succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
 \end{equation}
@@
 means that the channels are the same \cpnote{qioza una frase explicando porque
-esto es razonable}, while $p_{succ}=1$ indicates that they are perfectly
-distinguishable \cpnote{hummm ejemplo al menos para nosotros.}.
+esto es razonable}
+\tbnote{Cambiar la oración pasada por:} {\color{orange} Notice that if the channels are the same, then $p_{succ}=1/2$. 
+This is expected because in this situation the agent
+has no way of distinguishing the channels and has no choice but to completely
+guess, which results in a probability of success of $1/2$.}
+On the other hand, $p_{succ}=1$ indicates that the channels are perfectly
+distinguishable \cpnote{hummm ejemplo al menos para nosotros.} 
+\tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
+el que aplica $\sigma_z$ y tienen $p_{succ}=1$.
+De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
+(para $i\neq j$), se cumple esto.
+También quería ejemplos no unitarios, pero no encontré.}
 
@@
 analyzed. \cpnote{Falta analisis de los resultados. } 
+\tbnote{Agregar: } {\color{orange} We can see that channels close to the 
+completely depolarizing
+channel (that is close to the center of the tetrahedron)
+have a low $p_{succ}$, while those 
+close to unitary channels have much higher $p_{succ}$.
+This means that channels closer to the 
+completely depolarizing channel are simulated better on the quantum computers.
+This is reasonable because quantum computers are prone to errors
+that depolarize qubits, which isn't very problematic
+when trying to simulate depolarization but it is 
+when simulating unitary processes.}
 
 \cpnote{Mejorar la figura, quizá dejando la tridimensional y ademas poniendo unos 6 cortes. Probar
-con diferentes colores.}
+con diferentes colores.
+}
 
@@
 \end{figure}
+
+\newpage
+\tbnote{Algunas paletas de colores diferentes:}
+
+\begin{figure}
+\centering
+\includegraphics[width=.32\columnwidth]{images/tetra-col1.png}
+\includegraphics[width=.32\columnwidth]{images/tetra-col2.png}
+\includegraphics[width=.32\columnwidth]{images/tetra-col3.png} \\[1ex]
+\includegraphics[width=.32\columnwidth]{images/tetra-col4.png}
+\includegraphics[width=.32\columnwidth]{images/tetra-col5.png}
+\includegraphics[width=.32\columnwidth]{images/tetra-col6.png}\\[1ex]
+\includegraphics[width=.32\columnwidth]{images/tetra-col7.png}
+\includegraphics[width=.32\columnwidth]{images/tetra-col8.png}
+\includegraphics[width=.32\columnwidth]{images/tetra-col9.png}\\[1ex]
+\includegraphics[width=.32\columnwidth]{images/tetra-col10.png}
+\includegraphics[width=.32\columnwidth]{images/tetra-col11.png}
+\includegraphics[width=.32\columnwidth]{images/tetra-col12.png}\\[1ex]
+\includegraphics[width=.32\columnwidth]{images/tetra-col13.png}
+\includegraphics[width=.32\columnwidth]{images/tetra-col14.png}
+\includegraphics[width=.32\columnwidth]{images/tetra-col16.png}\\[1ex]
+\caption{Algunos colores posibles }
+\end{figure}
+
+\begin{figure}
+\centering
+\begin{subfigure}{.9\textwidth}
+\centering
+\includegraphics[width=.30\columnwidth]{images/corte1.png}
+\includegraphics[width=.30\columnwidth]{images/corte2.png}
+\includegraphics[width=.30\columnwidth]{images/corte3.png} \\[1ex]
+\includegraphics[width=.30\columnwidth]{images/corte4.png}
+\includegraphics[width=.30\columnwidth]{images/corte5.png}
+\end{subfigure}%
+\begin{subfigure}{0.1\textwidth}
+\includegraphics[width=.8\columnwidth]{images/col.png}\\[1ex]
+\end{subfigure}
+\caption{\tbnote{Aquí hay algunos cortes de la figura anterior.
+De qué forma lo agrego a la figura anterior?}}
+\end{figure}
+
+\newpage
 

### 2023-05-08 main.tex
.

@@
 \DeclareMathOperator{\tr}{tr}
+\newtheorem{definition}{Definition}
+\newtheorem{theorem}{Theorem}
 
@@
 \begin{eqnarray}
-\label{eq: state}
+\label{eq: state0}
 \sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
@@
 For the particular case of a Pauli channel on one qubit, the circuit that
-simulates it can be constructed as in fig.~\ref{fig: citcuit-pauli-1},
+simulates it can be constructed as in fig.~\ref{fig: circuit-pauli-1},
  which is a special case of fig. \ref{fig: circuit-pauli}
@@
 $ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) + \arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$. }
-\label{fig: citcuit-pauli-1} 
+\label{fig: circuit-pauli-1} 
 \end{figure}
@@
 \label{sec: OPR Circuits}
-Dynamical maps can be implemented using the same circuit as 
-in Fig~(\ref{fig: circuit-pauli}), with the only difference that now the state 
-to be created on the ancilla qubits depends on parameter $p$ 
-and therefore is given by 
+Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
+of fig.~(\ref{fig: circuit-pauli}). However, there is one difference: 
+the state to be created on the ancilla qubits now 
+depends on a parameter $p$, and it is represented by the expression:
 \begin{eqnarray}
@@
 \end{eqnarray}
+Thus, we temporarily shift our focus from Pauli
+channels and dynamical maps to the general problem of 
+creating a circuit to generate a curve of
+states like the one described in eq. (\ref{eq: parametrized state}).
 
-\textbf{Puntos:}
-\begin{itemize}
-\item As said before, to implement a Pauli dynamical map, 
-we need to create the parametrized $2n$-qubit state 
-$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
-\item However, creating this state will in general require many rotations parametrized by $p$. 
-For example, for the case of a Pauli dynamical map on 1 qubit, 
-the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
-In general, to create a parametrized state on $2n$ ancilla qubits will require
-$2n-1$ rotations parametrized by $p$.
-\item How can we reduce the amount of parametrized rotations used?
-\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
-\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
+In general, producing this curve of states will require multiple rotations
+parametrized by $p$. For instance, in the case of a two-qubit curve of states,
+we would typically need three rotations that depend on $p$, s
+imilar to those illustrated for the ancilla qubits in fig. (\ref{fig: circuit-pauli-1}).
+Moreover, creating an $N$-qubit curve of states
+usually necessitates $N-1$ parametrized rotations.
+
+However, it is desirable to minimize the number of parametrized rotations in our circuit.
+This leads us to the following question: which curves of states,
+such as the one described in eq. (\ref{eq: parametrized state}), 
+can be generated using only a single parametrized rotation? 
+To clarify this, we provide the following definition for a circuit with one parametrized rotation.
+
+\begin{definition}{\textbf{OPR Circuit:}}
+An OPR (One-Parameterized Rotation) circuit is a parametrized quantum
+circuit that includes only one gate dependent on a parameter $p$.
+Moreover, the parametrized gate is a one-qubit rotation about any axis,
+whether controlled or not.
+\end{definition}
+
+Based on this definition, we aim to determine which curves of 
+states can be generated using OPR circuits. 
+To accomplish this, we begin by proving that any OPR circuit exhibits 
+a specific form, as stated in the following theorem.
+
+\begin{theorem}
+An $N-$qubit OPR circuit can always be transformed into the form shown in
+fig.~(\ref{fig:OPR-circuit}).
+\end{theorem}
+
+\begin{figure}[h!]
+\centering
+\includegraphics{images/OPR-circuit.pdf}
+\caption{\textbf{General form of an OPR circuit}.
+Any OPR circuit can be transformed into this form,
+where the rotation on the last qubit
+can be controlled or not by any of the other qubits.
+$A$ and $B$
+are $N$-qubit gates that do not depend on the parameter $p$ and
+$s= s(p)$ is a function of the parameter}
+\label{fig:OPR-circuit}
+\end{figure}
+
+\textbf{Proof:} 
+First, we observe that according to the
+definition, an OPR circuit always consists of an operation $B$ followed 
+by the parametrized rotation and then another operation $A$, 
+where $A$ and $B$ are not parametrized.
+
+Next, we note that it is not necessary to consider rotations about an arbitrary axis,
+as a rotation about any axis $\hat{n}$ parameterized by $p$
+can be transformed into a rotation about $\sigma_3$ without introducing 
+gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
+is a function of $p$ (the factor of 2 is for convenience later on) 
+and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
+We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
+where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
+The rotation can then be rewritten as follows:
 \begin{eqnarray}
-U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
+R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
 \end{eqnarray}
-\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
-\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
-aunque se puede y debe achicar bastante.
-\end{itemize}
+Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
+any OPR circuit can be transformed into a circuit where the parametrized
+ rotation is around $\sigma_3$ instead of an arbitrary axis. 
+Moreover, without loss of generality, we can choose the last qubit as the target qubit for the rotation.
+
+Therefore, an OPR circuit can be transformed such
+that the rotation is around $\sigma_3$ and is applied to the last qubit 
+(possibly controlled by other qubits), 
+resulting in the form depicted in fig. (\ref{fig:OPR-circuit}). $\blacksquare$ \\
+$\;$\\
+
+With the aid of this theorem, we can now determine the curves
+of states of $N$ qubits that can be generated using an OPR circuit. 
+This result is stated in the following theorem.
+
+\begin{theorem}
+An OPR circuit always implements an operator whose matrix,
+in the computational basis, has the form:
+\begin{eqnarray}
+U = (|\vec{v}_0|, |\vec{v}_1|, |\vec{v}_2|, \cdots, |\vec{v}_{2^n-1}|),
+\end{eqnarray}
+where the column vectors are given by $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$,
+with $\vec{a}_j ,\vec{b}_j, \vec{c}_j$ orthogonal and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.
+\end{theorem}
+\textbf{Proof:} 
+Using Theorem 1, we know that any OPR circuit can be transformed into the 
+form shown in Figure (\ref{fig:OPR-circuit}).
+Hence, we only need to consider the operator corresponding to that circuit. 
+The $j$-th column of the circuit's matrix represents the result of applying the circuit to the state $|j\rangle$.
+
+First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$.
+This can be rewritten by separating the
+first $N-1$ qubits from the last one as:
+\begin{equation}
+B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right).
+\end{equation}
+After the operator $B$, the circuit applies a controlled rotation to the last qubit.
+To simplify the analysis, we separate the states of
+the first $N-1$ qubits into those that fulfill the control conditions 
+(which we denote as the set $C$)
+and those that do not.
+Therefore, the state can be written as
+\begin{eqnarray}
+B|j\rangle = \sum_{k \in C} \left(B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right) + \sum_{k \not\in C} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j}|k\rangle |1\rangle \right),
+\end{eqnarray}
+After $B$ creates this state, we need to apply the controlled rotation to the result. 
+This rotation will only be applied for the states on the first sum (since they fulfill the control conditions)
+and not to the others. Therefore, we apply the gate to the last qubit of the first sum, 
+remembering that $R_z(2s)$ acts by adding a phase $e^{-is}$ to $|0\rangle$
+and a phase $e^{is}$ to $|1\rangle$, and the result is:
+\begin{small}
+\begin{eqnarray}
+&e^{-is} \sum_{k \in Ctrl} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle 
++ \sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
+& \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
+\end{eqnarray}
+\end{small}
+where $\vec{a'} = \sum_{k \in Ctrl} B_{2k,j}|k\rangle|0\rangle \;,\; \vec{b'}_j = \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle \;,\; \vec{c'}_j =\sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)$.
+ These vectors are clearly orthogonal because they are each linear combinations of different 
+orthogonal states of the computational basis. 
+Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the norm of the $j-$th column of $B$, 
+which is unitary.
+
+Finally, after having applied the rotation, the circuit applies gate $A$, 
+so that the result is given by:
+\begin{eqnarray}
+e^{-is} A \vec{a'}_j + e^{is} A \vec{b'}_j + A \vec{c'}_j = e^{-is} \vec{a}_j + e^{is} \vec{b}_j + \vec{c}_j = \vec{v}_j,
+\end{eqnarray}
+where $\vec{a}_j = A \vec{a'}_j , \vec{b}_j = A \vec{b'}_j , \vec{c}_j = A \vec{c'}_j$ are still orthogonal
+vectors that satisfy $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$ because $A$ is unitary. 
+Therefore, we conclude that the circuit takes a state $|j\rangle$ and converts it
+ into the state represented by the vector $\vec{v}_j$, which means that the matrix representation of the circuit's operation in the 
+computational base is
+ $U = (|\vec{v}_0|, |\vec{v}_1|, \cdots, |\vec{v}_{2^n-1}|)$. $\blacksquare$  \\
+ $\;$ \\
+
+Therefore, from this theorem we conclude that
+the kind of curves of states that can be created
+using an OPR circuit are always of the form
+\begin{align*}
+|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
+\end{align*}
+where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
+$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
+%\textbf{Puntos:}
+%\begin{itemize}
+%\item As said before, to implement a Pauli dynamical map, 
+%we need to create the parametrized $2n$-qubit state 
+%$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
+%\item However, creating this state will in general require many rotations parametrized by $p$. 
+%For example, for the case of a Pauli dynamical map on 1 qubit, 
+%the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
+%In general, to create a parametrized state on $2n$ ancilla qubits will require
+%$2n-1$ rotations parametrized by $p$.
+%\item How can we reduce the amount of parametrized rotations used?
+%\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
+%\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
+%\begin{eqnarray}
+%U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
+%\end{eqnarray}
+%\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
+%\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
+%aunque se puede y debe achicar bastante.
+%\end{itemize}
+\newpage
 % }}}
@@
 \label{sec: OPR circuit for a Pauli map}
-\textbf{Puntos:}
+\tbnote{Sección no escrita aún, sólo es el medio resumen que tenía.}
+We can now use the last theorem to conclude directly which Pauli dynamical maps
+can be created using an OPR circuit.
+For OPR circuits, the ancilla state has to be created with only one parametrized curve. Then, the theorem for OPR circuits implies that a map
+\begin{eqnarray}
+\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
+\end{eqnarray}
+can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
+\begin{eqnarray}
+\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} \cos s + \vec{b} \sin s
+\end{eqnarray}
+where $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors in $\mathbb{C}^{2n}$ 
+and $|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2= 1$.
+
+We can see some examples of Pauli dynamical
+maps of one qubit that can be implemented with an OPR circuit:
 \begin{itemize}
-\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
-\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
-and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
-\item \textbf{Results:} Show results of simulating those maps on a quantum computer. 
-Lo tengo para parabolic y para depolarizing.
+\item \textbf{$\sigma_3$ parabolic map:} We take as an example the Pauli dynamical map for one qubit defined as
+\begin{eqnarray}
+\epsilon(\rho) = \dfrac{1}{4} (1-p)^2 \sigma_0 \rho \sigma_0 + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
+\end{eqnarray}
+with $p \in [-1,1]$. \\
+
+To implement this dynamical map using the circuit presented in figure \ref{fig:OPR-circuit}, it is necessary to create the state
+\begin{eqnarray}
+\left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right)
+\end{eqnarray}
+on the $2$ ancilla qubits. Luckily, this state can be written in the form $\vec{c} + \vec{a} \cos s + \vec{b} \sin s$ as
+\begin{eqnarray}
+\begin{pmatrix}
+1/2 \\
+0 \\ 
+0 \\
+1/2
+\end{pmatrix} + \begin{pmatrix}
+0 \\
+1/2 \\
+1/2 \\
+0
+\end{pmatrix}  \cos s + \begin{pmatrix}
+-1/2 \\
+0 \\
+0 \\
+1/2
+\end{pmatrix} \sin s
+\end{eqnarray}
+with $s = \arcsin p$.
+According to theorem 1, the fact that the state we need to create over the ancilla qubits can be written like this implies that the dynamical map can be simulated in a quantum computer using only one parametrized rotation.
+The circuit used will have the same form as that in figure , where the part used to create the state on the ancilla qubits will be:
+\begin{figure}[h!]
+\centering
+\begin{quantikz}
+\lstick{$aq_0$} & \gate[wires=2]{B} & \ctrl{1} & \gate[wires=2]{A} & \qw \\
+\lstick{$aq_{1}$} & & \gate{R_{\sigma_2}(2s)} & & \qw  \\
+\end{quantikz}
+\caption{Circuit to create 2-qubit state}
+\end{figure}
+
+where according to theorem 1, matrices $A$ and $B$ can be chosen as:
+\begin{eqnarray}
+A &= \begin{pmatrix}
+*  & c_0 / \sqrt{1-r^2} & -b_0/r & a_0 /r \\
+*  & c_1 / \sqrt{1-r^2} & -b_1/r & a_1 /r \\ 
+* & c_2 / \sqrt{1-r^2} & -b_2/r & a_2/r \\
+* & c_3 / \sqrt{1-r^2} & -b_3/r & a_3/r \\
+\end{pmatrix} = \begin{pmatrix}
+0 & 1/\sqrt{2} & -1/\sqrt{2} & 0 \\
+-1/\sqrt{2} & 0 & 0 & 1/\sqrt{2} \\
+1/\sqrt{2} & 0 & 0 & 1/\sqrt{2} \\
+0 & 1/\sqrt{2} & 1/\sqrt{2} & 0
+\end{pmatrix} \\
+B& = \begin{pmatrix}
+0 & 0 & 0 & 1 \\
+0 & 1 & 0 & 0\\
+0 & 0& 1 & 0 \\
+1 & 0 & 0 & 0 
+\end{pmatrix}
+\end{eqnarray}
 \end{itemize}
+
+%\textbf{Puntos:}
+%\begin{itemize}
+%\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
+%\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
+%and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
+%\end{itemize}
 % }}}
+
+\newpage
 \section{Exponential maps $e^{iHt}$} % {{{
@@
 \appendix
-\input{Cosas-Escritas-Antes}
+%\input{Cosas-Escritas-Antes}
 

### 2023-05-09 main.tex
hacky sack

@@
 \renewcommand{\figurename}{Fig}
-
+\renewcommand{\succ}{\textrm{succ}}
+
+\newcommand{\fref}[1]{Fig.~\ref{#1}}
+\newcommand{\eref}[1]{eq.~(\ref{#1})}
 % Use the PLoS provided BiBTeX style
@@
 \label{sec: Circuit for a Pauli Channel}
-\cpnote{Acá voy}
+% Intro {{{
 
@@
 and analyze the results using the diamond norm.
-\cpnote{Quizá en una frase poner el resultado aca o ampliar
-tantito} \tbnote{Va, agregué lo siguiente: 
-We conclude that the circuit performs optimally for channels  in proximity to the
-completely depolarizing channel but
-it is deficient close to unitary channels.}
-
+We find that close to the depolarizing channel, the general circuit simulator 
+can implement such channels with the highest fidelity. 
+% produce the highest 
+% \cpnote{Quizá en una frase poner el resultado aca o ampliar
+% tantito} \tbnote{Va, agregué lo siguiente: 
+% We conclude that the circuit performs optimally for channels  in proximity to the
+% completely depolarizing channel but
+% it is deficient close to unitary channels.}
+% }}} 
 \subsection{Description of the Circuit for a Pauli Channel} %{{{
@@
 
-\cpnote{Yo abriría este parrafo con una frase que de la idea muy general. Decir 
-algo asi como que vamos a crear un estado conque contenga a las $k$s 
-como coeficientes y leugo controlar la aplicación de los Pauli strings. Luego
-ya dar los detalles. Así incluso mas escueto de lo que pongo. Por ejemplo:
-To design the circiot that implements 13, we construct a state that incorportes
-probabilities $k$ and subsequently apply controlled operation. In particular... }
-\cpnote{No me gusta como está organizado este parrafo. Le puedes dar una iterada?}
-\tbnote{Propongo el párrafo en naranja para sustituirlo}
-
-To design the circuit, we remember that a Pauli channel as the one in
-eq.~(\ref{eq: pauli channel N-qubit})
-applies each Pauli operator $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
-Given this, it is easy to construct a quantum circuit that implements 
-a Pauli channel with the help of $2N$ ancilla qubits,
-the circuit that does this is presented in fig. (\ref{fig: circuit-pauli}).
-The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
-\begin{eqnarray}
-\label{eq: state0}
-\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
-\end{eqnarray}
-in the ancilla qubits, 
-where $b_{\vec{\gamma}}$ are numbers such that $
-|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
-The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined by $|\gamma_1 \rangle \cdots |\gamma_N\rangle$.
-
-{\color{orange} Cambiar por:  To design the circuit that implements \ref{eq: pauli channel N-qubit}, we construct a state that incorportes
-probabilities $k_{\gamma}$ on ancilla qubits and subsequently apply controlled 
-Pauli operations on the principal qubits.
-The circuit that does this is presented in fig. (\ref{fig: circuit-pauli})
-and works by creating the state
-\begin{eqnarray}
-\label{eq: state}
-\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
-\end{eqnarray}
-on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
-|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
-the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined by $|\gamma_1\rangle \cdots |\gamma_N\rangle$.
-}
-
-%Moreover $|\vec{\gamma}\rangle$ is defined as a $2n$ qubit state given by
-%\begin{eqnarray}
-%|\vec{\gamma} \rangle = |\gamma_1\rangle |\gamma_2 \rangle \cdots |\gamma_N \rangle,
-%\end{eqnarray}
-%where $|\gamma_i \rangle$ is the $2$ qubit state $|00\rangle, |01\rangle , |10\rangle$ or $|11\rangle$ when $\gamma_i = 0,1,2,3$ respectively. \\
-
-\begin{figure}[h!]
+% \cpnote{Yo abriría este parrafo con una frase que de la idea muy general. Decir 
+% algo asi como que vamos a crear un estado conque contenga a las $k$s 
+% como coeficientes y leugo controlar la aplicación de los Pauli strings. Luego
+% ya dar los detalles. Así incluso mas escueto de lo que pongo. Por ejemplo:
+% To design the circiot that implements 13, we construct a state that incorportes
+% probabilities $k$ and subsequently apply controlled operation. In particular... }
+% \cpnote{No me gusta como está organizado este parrafo. Le puedes dar una iterada?}
+% \tbnote{Propongo el párrafo en naranja para sustituirlo}
+
+% To design the circuit, we recall that a Pauli channel, as the one in
+% eq.~(\ref{eq: pauli channel N-qubit}), applies each Pauli operator
+% $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
+% Given this, it is easy to construct a quantum circuit that implements 
+% a Pauli channel with the help of $2N$ ancilla qubits,
+% see \fref{fig: circuit-pauli}.
+% The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
+% \begin{eqnarray}
+% \label{eq: state0}
+% \sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
+% \end{eqnarray}
+% in the ancilla qubits, 
+% where $b_{\vec{\gamma}}$ are numbers such that $
+% |b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
+% The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined as $|\gamma_1 \rangle
+% \cdots |\gamma_N\rangle$.
+
+% {\color{orange} Cambiar por:  
+To design the circuit that implements \eref{eq: pauli channel N-qubit}, we construct a state that 
+includes the probabilities $k_{\gamma}$ on the ancilla qubits and subsequently
+apply controlled Pauli operations on the main qubits.  The circuit that does
+this is presented in \fref{fig: circuit-pauli}.
+
+\begin{figure} % {{{
 \centering
@@
 \includegraphics{images/circuito_general.pdf}
-\caption{\cpnote{Revisa el archivo images/circuito\_general.pdf y el makefile correspondiente} \tbnote{Oh, ya veo, gracias!.} {\bf Circuit for an $N$-qubit Pauli channel on $N$ qubits.}
+\caption{{\bf Circuit for an $N$-qubit
+Pauli channel on $N$ qubits.}
 The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
@@
 \label{fig: circuit-pauli}
-\end{figure}
-
-\cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
-de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
-Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
+\end{figure} % }}}
+
+The first part of the circuit involves the creation of the state
+\begin{eqnarray}
+\label{eq: state}
+\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
+\end{eqnarray}
+on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
+|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
+the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
+\cdots |\gamma_N\rangle$.
+% \cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
+% de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
+% Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
 When measured in the computational basis, the state given in eq.~(\ref{eq: state})
@@
 The circuit in fig.~(\ref{fig: circuit-pauli}) uses this fact
-to operate $\sigma_{\vec{\gamma}}$ on the principal qubits
+to apply $\sigma_{\vec{\gamma}}$ on the main qubits
 with a probability $k_{\vec\gamma}$ by using controlled operations 
-that apply $\sigma_{\vec{\gamma}}$ to the principal qubits
-only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
-Therefore, the circuit from fig.~(\ref{fig: circuit-pauli}) 
-applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
-with a probability $k_{\vec{\gamma}}$, 
-just as a Pauli channel is supposed to do.  
+conditioned on the state of the system being $|\vec{\gamma}\rangle$,
+just as the Pauli channel is supposed to do.  
+% 
+% that apply $\sigma_{\vec{\gamma}}$ to the main qubits
+% only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
+% 
+% Therefore, the circuit from fig.~(\ref{fig: circuit-pauli}) 
+% applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
+% with a probability $k_{\vec{\gamma}}$, 
+% just as a Pauli channel is supposed to do.
+
+\cpnote{Evaluar si al final ponemos algo al respecto de este comentario}
 \cpnote{Del circuito, parece ue las fases de las bs gammas no omportan mucho (o nada). 
@@
 \label{subsec: Simulation for one-qubit Pauli channels}
-\cpnote{Es raro tener una sola subseccion. De perdida dos, o ninguna. Charlemso a ver como 
-reorganizar las secciones (creo que el flujo si va bien hasta ahora)} \tbnote{Va.
-Me pareció ponerle su propia subsección a la parte anterior porque creo que esto y lo anterior sí debe ir separado, así que mejor dos subsecciones.}
+
+\cpnote{Acá voy}
+
+% \cpnote{Es raro tener una sola subseccion. De perdida dos, o ninguna. Charlemso
+% a ver como reorganizar las secciones (creo que el flujo si va bien hasta
+% ahora)} \tbnote{Va. Me pareció ponerle su propia subsección a la parte anterior
+% porque creo que esto y lo anterior sí debe ir separado, así que mejor dos
+% subsecciones.}
 
@@
 which is a special case of fig. \ref{fig: circuit-pauli}
- but with all details \cpnote{y compuertas , etc digamos que details}\tbnote{Va, listo} explicitly shown.
-
-\begin{figure}[h!]
+but with all details  explicitly shown.
+
+\begin{figure} % {{{
 \centering
 \includegraphics{images/circuito_unqubit.pdf}
-\caption{\cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho.} \tbnote{Va, lo hice así, espero haberlo hecho bien.} \cpnote{ 
-Otra cosa quizá para discutir.  La creacion del estado especial de dos qubits no esta
-aca explicita. Eso creo que si lo podemos hacer en general, o no? Como sería eso? Lo discutimos
-a ver si lo pones?} \tbnote{Sí. En la figura que está ahora lo puse (antes sólo había un bloque que
- decía que se crea el estado $|b\rangle$ sobre los qubits de ancilla).
-Ahora que lo pienso, sí lo prefiero así con la creación explícita y creo que mejora a la discusión después,
-porque muestra que en general se necesitan tres ángulos y es lo que luego buscamos 
-reducir a sólo uno}
- {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel, which is a particular case of Fig~(\ref{fig: circuit-pauli}).
-Here we have two ancilla qubits, and the state 
-$b_{00} |00\rangle + b_{01} |01\rangle + b_{10} |10\rangle + b_{11}|11\rangle$ 
-is created on them with the help of three rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) - \arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, 
-$ \theta_1 = 2 \arccos(\sqrt{k_{00} + k_{01}})$ and
-$ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) + \arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$. }
+\caption{
+% \cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho.} \tbnote{Va, lo hice así, espero haberlo hecho bien.} \cpnote{ 
+% Otra cosa quizá para discutir.  La creacion del estado especial de dos qubits no esta
+% aca explicita. Eso creo que si lo podemos hacer en general, o no? Como sería eso? Lo discutimos
+% a ver si lo pones?} \tbnote{Sí. En la figura que está ahora lo puse (antes sólo había un bloque que
+%  decía que se crea el estado $|b\rangle$ sobre los qubits de ancilla).
+% Ahora que lo pienso, sí lo prefiero así con la creación explícita y creo que mejora a la discusión después,
+% porque muestra que en general se necesitan tres ángulos y es lo que luego buscamos 
+% reducir a sólo uno}
+\cpnote{No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
+el lugar apropiado en el texto}
+{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
+which is a particular case of Fig~(\ref{fig: circuit-pauli}).  Here we have two
+ancilla qubits, and the state $b_{00} |00\rangle + b_{01} |01\rangle + b_{10}
+|10\rangle + b_{11}|11\rangle$ is created on them with the help of three
+rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
+\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, $ \theta_1 = 2 \arccos(\sqrt{k_{00} +
+k_{01}})$ and $ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
+\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$. }
 \label{fig: circuit-pauli-1} 
-\end{figure}
-Taking advantage of the quantum computers that IBM has available~\cite{Qiskit},
-we sampled $249$ one-qubit Pauli channels and simulated them using the 
-ibmq-lima quantum computer. 
-For each of these channels, we used quantum process tomography~\cite{Qiskit,
-Chuang:1996} to obtain the {\color{red} Choi matrix} {\color{orange} operator $\xi_I$}  corresponding to the implementation of
-the circuit {\color{red} $\mathcal{C}_{I}$} .
-Then, we compared this {\color{red} Choi matrix} {\color{orange} operator} with the theoretical
-{\color{red} Choi matrix $\mathcal{C}_T$} {\color{orange} operator $\xi_T$} 
-of the channel we wanted to implement.
-\cpnote{Quizá referirnos mejor al canal? Lo discutimos.} 
+\end{figure} % }}}
+
+Using the quantum computers that IBM has available~\cite{Qiskit}, we sampled
+$249$ one-qubit Pauli channels and simulated them using the ibmq-lima quantum
+computer.  For each of these channels, we used quantum process
+tomography~\cite{Qiskit, Chuang:1996} to obtain the 
+operator $\xi_I$ corresponding to the implementation of the
+circuit.  Then, we compared this {\color{red}
+Choi matrix} {\color{orange} operator} with the theoretical {\color{red} Choi
+matrix $\mathcal{C}_T$} {\color{orange} operator $\xi_T$} of the channel we
+wanted to implement.  \cpnote{Quizá referirnos mejor al canal? Lo discutimos.}
 \tbnote{Ah sí, mejor. Cambié lo que puse en rojo por lo que está en naranja.}
 
-To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
-which gives us a method of discriminating \cpnote{creo qeu todas lasnormas nos
-permiten discriminar entre canales. itera} \tbnote{Lo cambié un poco para que no se entienda que diamond es la única que lo hace} between quantum channels.
-Suppose an agent is given one of the channels $\xi_I$, $\xi_T$
-with probability $1/2$ for each \cpnote{que pasa para una probabilidad $p$?}
-\tbnote{Hay una expresión similar pero que depende de $p$. Lo pongo con $p$ en general?} 
-\cpnote{Otra cosa, los canales no se caracterizan por lo general po rla matriz 
-de choi, tonces por aca quizá hay problemas. Discutamos notacion.} \tbnote{Sip, lo cambié},
+We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
+with the probability that one can distinguish two channels \cpnote{Revisa esta 
+frase a ver si te parece}.
+% To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
+% which gives us a method of discriminating \cpnote{no solo discrimina... todas
+% las normas lo hacen, pero nos permite ver que tan parecidos son dos canales. 
+% Es como la fidelidad. Itera.} between quantum channels \cpnote{Tambien esta frase
+% no conecta bien con lo que sigue}.
+In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
+with probability $1/2$ each,
 and tries to guess which channel they received
-by passing through it a state $\rho$ and measuring the result.
+by applying it to a state $\rho$ and measuring the result.
 Then, the maximal probability of success (out of all possible states $\rho$) that
@@
 \label{eq: probability-success}
-p_{succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
+p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
 \end{equation}
-where $|| \cdot ||_{\diamond}$ is the diamond norm.  Notice that $p_{succ}=1/2$
-means that the channels are the same \cpnote{qioza una frase explicando porque
-esto es razonable}
-\tbnote{Cambiar la oración pasada por:} {\color{orange} Notice that if the channels are the same, then $p_{succ}=1/2$. 
+where $|| \cdot ||_{\diamond}$ is the diamond norm \cpnote{no la hemos 
+definido matemáticamente}.  
+% Notice that $p_{\succ}=1/2$
+% means that the channels are the same \cpnote{qioza una frase explicando porque
+% esto es razonable}
+% \tbnote{Cambiar la oración pasada por:} {\color{orange} 
+Notice that if the channels are the same, then $p_{\succ}=1/2$. 
 This is expected because in this situation the agent
 has no way of distinguishing the channels and has no choice but to completely
-guess, which results in a probability of success of $1/2$.}
-On the other hand, $p_{succ}=1$ indicates that the channels are perfectly
-distinguishable \cpnote{hummm ejemplo al menos para nosotros.} 
-\tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
-el que aplica $\sigma_z$ y tienen $p_{succ}=1$.
-De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
-(para $i\neq j$), se cumple esto.
-También quería ejemplos no unitarios, pero no encontré.}
+guess, which results in a probability of success of $1/2$.
+On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
+distinguishable.
+% \cpnote{hummm ejemplo al menos para nosotros.} 
+% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
+% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
+% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
+% (para $i\neq j$), se cumple esto.
+% También quería ejemplos no unitarios, pero no encontré.}
 
@@
 success defined by eq. (\ref{eq: probability-success}) for the channels
-analyzed. \cpnote{Falta analisis de los resultados. } 
-\tbnote{Agregar: } {\color{orange} We can see that channels close to the 
+analyzed. 
+We can see that channels close to the 
 completely depolarizing
 channel (that is close to the center of the tetrahedron)
-have a low $p_{succ}$, while those 
-close to unitary channels have much higher $p_{succ}$.
+have a low $p_{\succ}$, while those 
+close to unitary channels have much higher $p_{\succ}$.
 This means that channels closer to the 
@@
 when trying to simulate depolarization but it is 
-when simulating unitary processes.}
-
-\cpnote{Mejorar la figura, quizá dejando la tridimensional y ademas poniendo unos 6 cortes. Probar
-con diferentes colores.
-}
+when simulating unitary processes.
+\cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
+figuras y mas inspiracion}
+
+% \cpnote{Mejorar la figura, quizá dejando la tridimensional y ademas poniendo unos 6 cortes. Probar
+% con diferentes colores.
+% }
 
@@
 \includegraphics[width=0.45\textwidth]{probabilities-points.png}\\
-\caption{\tbnote{Al igual que antes, hay que quitar esta figura y ponerla en un archivo a parte}.
-{\bf Maximal probabilities of success for one-qubit Pauli channel} $p_{succ}$ of one-qubit Pauli channels implemented on IBM's ibmq-lima.
-The channels are plotted in the tetrahedron of Pauli channels, with a color bar indicating the distinguishability of each channel's implementation using the circuit for a 1-qubit Pauli channel.}
+\caption{{\bf Maximal probabilities of success for one-qubit Pauli channel}
+$p_{\succ}$ of one-qubit Pauli channels implemented on IBM's ibmq-lima. The
+channels are plotted in the tetrahedron of Pauli channels, with a color bar
+indicating the distinguishability of each channel's implementation using the
+circuit for a 1-qubit Pauli channel. \cpnote{Poner la barra del tamaño apropiado 
+y quizá juntar con los cortes que tenemos. Discutir en vivo con Tomas a ver que onda. 
+Tambien poner mas puntos experimentales.}}
 \label{fig: fidelity one qubit}
@@
 \end{figure}
-
-\newpage
 
@@
 % }}}
-
-\newpage
 \section{Exponential maps $e^{iHt}$} % {{{

### 2023-05-09 main.tex
refuckulated the carbonator

@@
 \includegraphics[width=.32\columnwidth]{images/tetra-col16.png}\\[1ex]
-\caption{Algunos colores posibles }
+\caption{Algunos colores posibles. Creo qeu me gustaria usar otra candidad, 
+como la fidelidad, pero definida a partir de la norma diamante. 
+Asi, 1 es perfecto y 0 esta mal. De estas, me gusta la de abajo 
+a la izquiera porque siento que distingue bien, pero si toca entnoces
+usar los mismos colores en la fig 5. Te propongo dejar un tetraedro y los
+cinco cortes para que nos quede algo de 3 columnsas y dos filas. 
+propongo tambien que se ponta la leyenda en la figura y no encima. 
+Si te haces bolas con las figuras, discutimos como hacerlas en TIKZ.  }
 \end{figure}
@@
 \label{sec: OPR Circuits}
+\cpnote{Quizá abrir con un parrafo de motivacion. Quizá lo tenemos que hablar. }
+\cpnote{No se sabe aun que son OPR circuits. Poner completo}
+
 Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
@@
 creating a circuit to generate a curve of
-states like the one described in eq. (\ref{eq: parametrized state}).
+states like the one described in \eref{eq: parametrized state}.
+\cpnote{me gusta mas usar el comando eref para que si toca cambiarlo, dependiendo 
+de la revista, lo pueda hacer de un solo jalon. Lo mismo para las 
+figuras.}
 
@@
 parametrized by $p$. For instance, in the case of a two-qubit curve of states,
-we would typically need three rotations that depend on $p$, s
-imilar to those illustrated for the ancilla qubits in fig. (\ref{fig: circuit-pauli-1}).
+we would typically need three rotations that depend on $p$, similar to those
+illustrated for the ancilla qubits in \fref{fig: circuit-pauli-1}.
 Moreover, creating an $N$-qubit curve of states
 usually necessitates $N-1$ parametrized rotations.
+\cpnote{no me salen esas cuentas.}
 
 However, it is desirable to minimize the number of parametrized rotations in our circuit.
+\cpnote{why?}
 This leads us to the following question: which curves of states,
-such as the one described in eq. (\ref{eq: parametrized state}), 
+such as the one described in \eref{eq: parametrized state}, 
 can be generated using only a single parametrized rotation? 
 To clarify this, we provide the following definition for a circuit with one parametrized rotation.
-
-\begin{definition}{\textbf{OPR Circuit:}}
-An OPR (One-Parameterized Rotation) circuit is a parametrized quantum
+\cpnote{Creo qeu los dos párrafos anteriores son uno y toca pensar cual es el
+mensaje principal y rediseñar. }
+
+\begin{definition}{\textbf{1-Parameter Rotation Circuit:}}
+A 1-Parameter Rotation (1PR) circuit is a parametrized quantum
 circuit that includes only one gate dependent on a parameter $p$.
@@
 Based on this definition, we aim to determine which curves of 
-states can be generated using OPR circuits. 
-To accomplish this, we begin by proving that any OPR circuit exhibits 
-a specific form, as stated in the following theorem.
-
-\begin{theorem}
-An $N-$qubit OPR circuit can always be transformed into the form shown in
-fig.~(\ref{fig:OPR-circuit}).
-\end{theorem}
-
-\begin{figure}[h!]
+states can be generated using OPR \cpnote{Si te parece bien el cambio 
+en la sigla, cambialos todos} circuits. 
+To accomplish this, we begin by proving that all OPR circuit have 
+a specific form.
+
+\begin{figure} % {{{
 \centering
@@
 are $N$-qubit gates that do not depend on the parameter $p$ and
-$s= s(p)$ is a function of the parameter}
+$s= s(p)$ is a function of the parameter.
+\cpnote{Parece que se te olvida la puntuacion en algunos captions. 
+por otro lado, queda la figura a mitad de la prueba. A mi me gusta dejar 
+que Latex organice solo las figuras y sin ponerle el h! ni nada. }
+}
 \label{fig:OPR-circuit}
-\end{figure}
-
+\end{figure} % }}}
+
+\begin{theorem}
+An $N-$qubit OPR circuit can always be transformed into the form shown in
+fig.~(\ref{fig:OPR-circuit}).
+\end{theorem}
 \textbf{Proof:} 
@@
  rotation is around $\sigma_3$ instead of an arbitrary axis. 
-Moreover, without loss of generality, we can choose the last qubit as the target qubit for the rotation.
+Moreover, without loss of generality, we can choose the last qubit as the
+target qubit for the rotation \cpnote{Why?}.
 
@@
 (possibly controlled by other qubits), 
-resulting in the form depicted in fig. (\ref{fig:OPR-circuit}). $\blacksquare$ \\
+resulting in the form depicted in fig. (\ref{fig:OPR-circuit}). 
+\cpnote{Creo que este ultimo parrafo sobra, aunque hay detalles aca que quizá se pueden
+poner en el planteamiento del problema.}
+$\blacksquare$ \\
 $\;$\\
@@
 \end{eqnarray}
+\cpnote{que denota el valor absoluto?}
 where the column vectors are given by $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$,
@@
 \textbf{Proof:} 
+\cpnote{Discutir la prueba, se ve demasiado larga y aburrida}
 Using Theorem 1, we know that any OPR circuit can be transformed into the 
@@
 \label{sec: OPR circuit for a Pauli map}
+
 \tbnote{Sección no escrita aún, sólo es el medio resumen que tenía.}
@@
 \textbf{Puntos:}
-
 \begin{itemize}

### 2023-05-14 main.tex
Algunas correcciones

@@
 density matrix.
-To do it, we substitute eq. (\ref{eq: Density Matrix}) 
-in eq. (\ref{eq: Pauli channel 1 qbit}):
+To do it, we substitute \eref{eq: Density Matrix} 
+in \eref{eq: Pauli channel 1 qbit}:
 \begin{equation}
@@
 \end{equation}
-Eq.~(\ref{eq: rho-transformada}) once again has the form of eq.~(\ref{eq: Density Matrix})
+\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix}
 but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
@@
 attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
-This can be seen by substituting eq. (\ref{eq:  Density matrix Nqbit}) in eq. (\ref{eq: pauli channel N-qubit})
-and using the property of eq. (\ref{eq: propiedad-pauli}):
+This can be seen by substituting \eref{eq:  Density matrix Nqbit} in \eref{eq: pauli channel N-qubit}
+and using the property of \eref{eq: propiedad-pauli}:
 \begin{align*}
@@
 % To design the circuit, we recall that a Pauli channel, as the one in
-% eq.~(\ref{eq: pauli channel N-qubit}), applies each Pauli operator
+% \eref{eq: pauli channel N-qubit}, applies each Pauli operator
 % $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
@@
 % Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
-When measured in the computational basis, the state given in eq.~(\ref{eq: state})
+When measured in the computational basis, the state given in \eref{eq: state}
 collapses to $|\vec{\gamma}\rangle$ with a 
 probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
-The circuit in fig.~(\ref{fig: circuit-pauli}) uses this fact
+The circuit in \fref{fig: circuit-pauli} uses this fact
 to apply $\sigma_{\vec{\gamma}}$ on the main qubits
@@
 % 
-% Therefore, the circuit from fig.~(\ref{fig: circuit-pauli}) 
+% Therefore, the circuit from \fref{fig: circuit-pauli} 
 % applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
@@
 For the particular case of a Pauli channel on one qubit, the circuit that
-simulates it can be constructed as in fig.~\ref{fig: circuit-pauli-1},
-which is a special case of fig. \ref{fig: circuit-pauli}
+simulates it can be constructed as in \fref{fig: circuit-pauli-1},
+which is a special case of \fref{fig: circuit-pauli}
 but with all details  explicitly shown.
+In said figure, the state 
+$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
+|10\rangle + \sqrt{k_{11}}|11\rangle$
+is created on the ancilla qubits with the help of three rotations of angles:
+\begin{subequations}
+\begin{eqnarray}
+\theta_0 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
+\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
+\label{eq:angle1} \\ 
+\theta_1 &= &2 \arccos(\sqrt{k_{00} +
+k_{01}})
+\label{eq:angle2} \\
+\theta_2 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
+\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
+\label{eq:angle3}
+\end{eqnarray}
+\label{eq:angle}
+\end{subequations}
 
@@
 \caption{
-% \cpnote{si quieres, intenta hacer la figura tu solo basado en el lo quehabía hecho.} \tbnote{Va, lo hice así, espero haberlo hecho bien.} \cpnote{ 
-% Otra cosa quizá para discutir.  La creacion del estado especial de dos qubits no esta
-% aca explicita. Eso creo que si lo podemos hacer en general, o no? Como sería eso? Lo discutimos
-% a ver si lo pones?} \tbnote{Sí. En la figura que está ahora lo puse (antes sólo había un bloque que
-%  decía que se crea el estado $|b\rangle$ sobre los qubits de ancilla).
-% Ahora que lo pienso, sí lo prefiero así con la creación explícita y creo que mejora a la discusión después,
-% porque muestra que en general se necesitan tres ángulos y es lo que luego buscamos 
-% reducir a sólo uno}
 \cpnote{No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
-el lugar apropiado en el texto}
+el lugar apropiado en el texto} \tbnote{Lo pasé al texto}
 {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
-which is a particular case of Fig~(\ref{fig: circuit-pauli}).  Here we have two
-ancilla qubits, and the state $b_{00} |00\rangle + b_{01} |01\rangle + b_{10}
-|10\rangle + b_{11}|11\rangle$ is created on them with the help of three
-rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
-\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, $ \theta_1 = 2 \arccos(\sqrt{k_{00} +
-k_{01}})$ and $ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
-\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$. }
+which is a particular case of \fref{fig: circuit-pauli}.  Here we have two
+ancilla qubits and we use three rotations
+of angles given by \eref{eq:angle} to create the state $\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
+|10\rangle + \sqrt{k_{11}}|11\rangle$
+on them.
+%and the state $b_{00} |00\rangle + b_{01} |01\rangle + b_{10}
+%|10\rangle + b_{11}|11\rangle$ is created on them with the help of three
+%rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
+%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, $ \theta_1 = 2 \arccos(\sqrt{k_{00} +
+%k_{01}})$ and $ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
+%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$.
+}
 \label{fig: circuit-pauli-1} 
@@
 Using the quantum computers that IBM has available~\cite{Qiskit}, we sampled
-$249$ one-qubit Pauli channels and simulated them using the ibmq-lima quantum
+one-qubit Pauli channels and simulated them using the ibmq-lima quantum
 computer.  For each of these channels, we used quantum process
@@
 with the probability that one can distinguish two channels \cpnote{Revisa esta 
-frase a ver si te parece}.
+frase a ver si te parece} 
+\tbnote{Sí, perfecto}.
 % To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
@@
 where $|| \cdot ||_{\diamond}$ is the diamond norm \cpnote{no la hemos 
-definido matemáticamente}.  
-% Notice that $p_{\succ}=1/2$
-% means that the channels are the same \cpnote{qioza una frase explicando porque
-% esto es razonable}
-% \tbnote{Cambiar la oración pasada por:} {\color{orange} 
+definido matemáticamente} \tbnote{Qué tal así:} {\color{orange}, defined by 
+\begin{align*}
+||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
+\end{align*}
+with $I$ the identity map,
+$|| \cdot ||_1$ the trace norm and the maximization
+done over all density matrices $\rho$.}
+
 Notice that if the channels are the same, then $p_{\succ}=1/2$. 
@@
 Finally, using the representation of Pauli channels in a tetrahedron as
-in eq.~(\ref{eq: conditions-tetrahedron}),
-we show in fig.~(\ref{fig: fidelity one qubit}) the maximal probabilities of
-success defined by eq. (\ref{eq: probability-success}) for the channels
+in \eref{eq: conditions-tetrahedron},
+we show in \fref{fig: fidelity one qubit} the maximal probabilities of
+success defined by \eref{eq: probability-success} for the channels
 analyzed. 
@@
 figuras y mas inspiracion}
+\tbnote{Va}
 
@@
 
-\begin{figure}[h!]
+\begin{figure}
 \centering
-\includegraphics[width=0.45\textwidth]{probabilities-points.png}\\
+\includegraphics[width=0.55\textwidth]{images/probabilities-points.png}\\
 \caption{{\bf Maximal probabilities of success for one-qubit Pauli channel}
@@
 y quizá juntar con los cortes que tenemos. Discutir en vivo con Tomas a ver que onda. 
-Tambien poner mas puntos experimentales.}}
+Tambien poner mas puntos experimentales.} \tbnote{Cambié lo de la barra y puse más puntos experimentales en los cortes que están en 
+la figura más abajo
+(no en esta figura porque ya se llena mucho de puntos).}
+\cpnote{ Creo qeu me gustaria usar otra candidad, 
+como la fidelidad, pero definida a partir de la norma diamante. 
+Asi, 1 es perfecto y 0 esta mal.} \tbnote{Lo que se me ocurre es algo como $2*(1-p_{succ})$ que justo cumple eso y en términos
+de la norma es $1-1/2||\xi_I - \xi_T||_{\diamond}$} \cpnote{ De estas, me gusta la de abajo 
+a la izquiera porque siento que distingue bien, pero si toca entnoces
+usar los mismos colores en la fig 5.} \tbnote{Ya agarré esos colores} \cpnote{Te propongo dejar un tetraedro y los
+cinco cortes para que nos quede algo de 3 columnsas y dos filas. 
+propongo tambien que se ponta la leyenda en la figura y no encima. 
+Si te haces bolas con las figuras, discutimos como hacerlas en TIKZ. } \tbnote{Lo puse en la figura siguiente. Poniéndolo con 3 columnas y dos filas queda
+muy chiquita la figura del tetraedro y no se llega a ver nada, así que lo puse grande y los cortes
+alrededor. }}
 \label{fig: fidelity one qubit}
@@
 
-\newpage
-\tbnote{Algunas paletas de colores diferentes:}
+%
+%\begin{figure}
+%\centering
+%\includegraphics[width=.32\columnwidth]{images/tetra-col1.png}
+%\includegraphics[width=.32\columnwidth]{images/tetra-col2.png}
+%\includegraphics[width=.32\columnwidth]{images/tetra-col3.png} \\[1ex]
+%\includegraphics[width=.32\columnwidth]{images/tetra-col4.png}
+%\includegraphics[width=.32\columnwidth]{images/tetra-col5.png}
+%\includegraphics[width=.32\columnwidth]{images/tetra-col6.png}\\[1ex]
+%\includegraphics[width=.32\columnwidth]{images/tetra-col7.png}
+%\includegraphics[width=.32\columnwidth]{images/tetra-col8.png}
+%\includegraphics[width=.32\columnwidth]{images/tetra-col9.png}\\[1ex]
+%\includegraphics[width=.32\columnwidth]{images/tetra-col10.png}
+%\includegraphics[width=.32\columnwidth]{images/tetra-col11.png}
+%\includegraphics[width=.32\columnwidth]{images/tetra-col12.png}\\[1ex]
+%\includegraphics[width=.32\columnwidth]{images/tetra-col13.png}
+%\includegraphics[width=.32\columnwidth]{images/tetra-col14.png}
+%\includegraphics[width=.32\columnwidth]{images/tetra-col16.png}\\[1ex]
+%\caption{Algunos colores posibles. \cpnote{ Creo qeu me gustaria usar otra candidad, 
+%como la fidelidad, pero definida a partir de la norma diamante. 
+%Asi, 1 es perfecto y 0 esta mal.} \tbnote{Algo como } \cpnote{ De estas, me gusta la de abajo 
+%a la izquiera porque siento que distingue bien, pero si toca entnoces
+%usar los mismos colores en la fig 5. Te propongo dejar un tetraedro y los
+%cinco cortes para que nos quede algo de 3 columnsas y dos filas. 
+%propongo tambien que se ponta la leyenda en la figura y no encima. 
+%Si te haces bolas con las figuras, discutimos como hacerlas en TIKZ. } }
+%\end{figure}
 
@@
 \centering
-\includegraphics[width=.32\columnwidth]{images/tetra-col1.png}
-\includegraphics[width=.32\columnwidth]{images/tetra-col2.png}
-\includegraphics[width=.32\columnwidth]{images/tetra-col3.png} \\[1ex]
-\includegraphics[width=.32\columnwidth]{images/tetra-col4.png}
-\includegraphics[width=.32\columnwidth]{images/tetra-col5.png}
-\includegraphics[width=.32\columnwidth]{images/tetra-col6.png}\\[1ex]
-\includegraphics[width=.32\columnwidth]{images/tetra-col7.png}
-\includegraphics[width=.32\columnwidth]{images/tetra-col8.png}
-\includegraphics[width=.32\columnwidth]{images/tetra-col9.png}\\[1ex]
-\includegraphics[width=.32\columnwidth]{images/tetra-col10.png}
-\includegraphics[width=.32\columnwidth]{images/tetra-col11.png}
-\includegraphics[width=.32\columnwidth]{images/tetra-col12.png}\\[1ex]
-\includegraphics[width=.32\columnwidth]{images/tetra-col13.png}
-\includegraphics[width=.32\columnwidth]{images/tetra-col14.png}
-\includegraphics[width=.32\columnwidth]{images/tetra-col16.png}\\[1ex]
-\caption{Algunos colores posibles. Creo qeu me gustaria usar otra candidad, 
-como la fidelidad, pero definida a partir de la norma diamante. 
-Asi, 1 es perfecto y 0 esta mal. De estas, me gusta la de abajo 
-a la izquiera porque siento que distingue bien, pero si toca entnoces
-usar los mismos colores en la fig 5. Te propongo dejar un tetraedro y los
-cinco cortes para que nos quede algo de 3 columnsas y dos filas. 
-propongo tambien que se ponta la leyenda en la figura y no encima. 
-Si te haces bolas con las figuras, discutimos como hacerlas en TIKZ.  }
-\end{figure}
-
-\begin{figure}
+\begin{subfigure}{0.9\textwidth}
+\begin{subfigure}{.666\textwidth}
 \centering
-\begin{subfigure}{.9\textwidth}
-\centering
-\includegraphics[width=.30\columnwidth]{images/corte1.png}
-\includegraphics[width=.30\columnwidth]{images/corte2.png}
-\includegraphics[width=.30\columnwidth]{images/corte3.png} \\[1ex]
-\includegraphics[width=.30\columnwidth]{images/corte4.png}
-\includegraphics[width=.30\columnwidth]{images/corte5.png}
+\includegraphics[width=.95\columnwidth]{images/tetra-def.png}
+\end{subfigure}%
+\begin{subfigure}{.333\textwidth}
+\includegraphics[width=.95\columnwidth]{images/corte1-2.png} \\
+\includegraphics[width=.95\columnwidth]{images/corte2-2.png} \\
+\end{subfigure}
+\includegraphics[width=.322\columnwidth]{images/corte3-2.png}
+\includegraphics[width=.322\columnwidth]{images/corte4-2.png}
+\includegraphics[width=.322\columnwidth]{images/corte5-2.png}
 \end{subfigure}%
 \begin{subfigure}{0.1\textwidth}
-\includegraphics[width=.8\columnwidth]{images/col.png}\\[1ex]
+\includegraphics[width=.8\columnwidth]{images/col-2.png} \\ [2ex]
 \end{subfigure}
-\caption{\tbnote{Aquí hay algunos cortes de la figura anterior.
-De qué forma lo agrego a la figura anterior?}}
+\caption{\tbnote{Aquí está una forma alternativa en que puede quedar la figura. 
+Usé $2(1-p)$ en lugar de $p$ para que se cumpla lo de
+que $0$ es lo peor y $1$ lo mejor.}}
 \end{figure}
@@
 % }}}
-\section{OPR Circuits} % {{{
-\label{sec: OPR Circuits}
+
+\newpage
+\section{One Parameter Circuits} % {{{
+\label{sec: 1PR Circuits}
 \cpnote{Quizá abrir con un parrafo de motivacion. Quizá lo tenemos que hablar. }
-\cpnote{No se sabe aun que son OPR circuits. Poner completo}
+\cpnote{No se sabe aun que son 1PR circuits. Poner completo} \tbnote{Ya.}
 
 Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
-of fig.~(\ref{fig: circuit-pauli}). However, there is one difference: 
+of \fref{fig: circuit-pauli}. However, there is one difference: 
 the state to be created on the ancilla qubits now 
@@
 de la revista, lo pueda hacer de un solo jalon. Lo mismo para las 
-figuras.}
+figuras.} \tbnote{Ah va, lo puse en todas.}
 
@@
 Moreover, creating an $N$-qubit curve of states
-usually necessitates $N-1$ parametrized rotations.
-\cpnote{no me salen esas cuentas.}
+usually necessitates $2^N-1$ parametrized rotations.
+\cpnote{no me salen esas cuentas.} \tbnote{Se me fue el 2.}
 
@@
 mensaje principal y rediseñar. }
+\tbnote{De acuerdo, mejor así?:.}
+
+{\color{orange} In general, producing this curve of states for $N$ qubits will require
+$2^N-1$ rotations parametrized by $p$,
+such as the three rotations used for the ancilla
+qubits in \fref{fig: circuit-pauli-1}.
+However, it would be preferable to achieve the same effect using only one parametrized rotation. 
+This would allow us to treat said rotation 
+as a knob that smoothly traverses the curve of states.
+Consequently, we are faced with the question of which curves of states, 
+such as the one described in \eref{eq: parametrized state}, 
+can be produced using just a single parametrized rotation. 
+To clarify this, we provide the following definition 
+for a circuit with one parametrized rotation.}
 
@@
 Based on this definition, we aim to determine which curves of 
-states can be generated using OPR \cpnote{Si te parece bien el cambio 
-en la sigla, cambialos todos} circuits. 
-To accomplish this, we begin by proving that all OPR circuit have 
-a specific form.
+states can be generated using 1PR \cpnote{Si te parece bien el cambio 
+en la sigla, cambialos todos} 
+\tbnote{Sí me parece, los cambié} circuits. 
+To accomplish this, we begin by proving that all 1PR circuits have 
+{\color{orange} the form depicted in \fref{fig:1PR-circuit},
+where the rotation is around $\sigma_3$ and
+is applied to the last qubit.}
 
@@
 \includegraphics{images/OPR-circuit.pdf}
-\caption{\textbf{General form of an OPR circuit}.
-Any OPR circuit can be transformed into this form,
+\caption{\textbf{General form of a 1PR circuit}.
+Any 1PR circuit can be transformed into this form,
 where the rotation on the last qubit
@@
 por otro lado, queda la figura a mitad de la prueba. A mi me gusta dejar 
-que Latex organice solo las figuras y sin ponerle el h! ni nada. }
+que Latex organice solo las figuras y sin ponerle el h! ni nada. } \tbnote{Va}
 }
-\label{fig:OPR-circuit}
+\label{fig:1PR-circuit}
 \end{figure} % }}}
@@
 \begin{theorem}
-An $N-$qubit OPR circuit can always be transformed into the form shown in
-fig.~(\ref{fig:OPR-circuit}).
+An $N-$qubit 1PR circuit can always be transformed 
+into the form shown in \fref{fig:1PR-circuit}.
 \end{theorem}
@@
 First, we observe that according to the
-definition, an OPR circuit always consists of an operation $B$ followed 
+definition, a 1PR circuit always consists of an operation $B$ followed 
 by the parametrized rotation and then another operation $A$, 
@@
 Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
-any OPR circuit can be transformed into a circuit where the parametrized
+any 1PR circuit can be transformed into a circuit where the parametrized
  rotation is around $\sigma_3$ instead of an arbitrary axis. 
 Moreover, without loss of generality, we can choose the last qubit as the
-target qubit for the rotation \cpnote{Why?}.
-
-Therefore, an OPR circuit can be transformed such
+target qubit for the rotation \cpnote{Why?} 
+{\color{orange} , since if it weren't, we could use
+swap gates to convert the rotation
+to the last qubit without adding gates
+that depend on $p$. }.
+
+Therefore, a 1PR circuit can be transformed such
 that the rotation is around $\sigma_3$ and is applied to the last qubit 
 (possibly controlled by other qubits), 
-resulting in the form depicted in fig. (\ref{fig:OPR-circuit}). 
+resulting in the form depicted in \fref{fig:1PR-circuit}. 
 \cpnote{Creo que este ultimo parrafo sobra, aunque hay detalles aca que quizá se pueden
-poner en el planteamiento del problema.}
+poner en el planteamiento del problema.} \tbnote{Lo pasé arriba justo antes del teorema y quitaría este párrafo entonces }
 $\blacksquare$ \\
@@
 With the aid of this theorem, we can now determine the curves
-of states of $N$ qubits that can be generated using an OPR circuit. 
+of states of $N$ qubits that can be generated using a 1PR circuit. 
 This result is stated in the following theorem.
@@
 \begin{theorem}
-An OPR circuit always implements an operator whose matrix,
+A 1PR circuit always implements an operator whose matrix,
 in the computational basis, has the form:
 \begin{eqnarray}
-U = (|\vec{v}_0|, |\vec{v}_1|, |\vec{v}_2|, \cdots, |\vec{v}_{2^n-1}|),
-\end{eqnarray}
-\cpnote{que denota el valor absoluto?}
+U = (\vec{v}_0, \vec{v}_1, \vec{v}_2, \cdots, \vec{v}_{2^n-1}),
+\end{eqnarray}
 where the column vectors are given by $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$,
@@
 \cpnote{Discutir la prueba, se ve demasiado larga y aburrida}
-Using Theorem 1, we know that any OPR circuit can be transformed into the 
-form shown in Figure (\ref{fig:OPR-circuit}).
-Hence, we only need to consider the operator corresponding to that circuit. 
-The $j$-th column of the circuit's matrix represents the result of applying the circuit to the state $|j\rangle$.
-
-First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$.
-This can be rewritten by separating the
+\tbnote{La cambié un poco, pero aún así.}
+Denoting by $U$ the matrix for the 1PR circuit,
+we can conclude from theorem 1 that $U=ARB$,
+where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
+applied to the last qubit and controlled by some of the other
+ones. 
+We will calculate the $j$-th column of this matrix,
+which is given by $U|j\rangle$.
+
+First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
+which can be rewritten by separating the
 first $N-1$ qubits from the last one as:
@@
 \end{equation}
-After the operator $B$, the circuit applies a controlled rotation to the last qubit.
+After the operator $B$, we need to apply $R$.
 To simplify the analysis, we separate the states of
-the first $N-1$ qubits into those that fulfill the control conditions 
-(which we denote as the set $C$)
-and those that do not.
-Therefore, the state can be written as
-\begin{eqnarray}
-B|j\rangle = \sum_{k \in C} \left(B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right) + \sum_{k \not\in C} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j}|k\rangle |1\rangle \right),
-\end{eqnarray}
-After $B$ creates this state, we need to apply the controlled rotation to the result. 
-This rotation will only be applied for the states on the first sum (since they fulfill the control conditions)
-and not to the others. Therefore, we apply the gate to the last qubit of the first sum, 
-remembering that $R_z(2s)$ acts by adding a phase $e^{-is}$ to $|0\rangle$
-and a phase $e^{is}$ to $|1\rangle$, and the result is:
+the first $N-1$ qubits into those that fulfill the control conditions of the rotation
+(which we denote as the set $\mathcal{C}$)
+and those that do not, and write it as
+\begin{eqnarray}
+B|j\rangle = \sum_{k \in \mathcal{C}} \left(B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right) + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j}|k\rangle |1\rangle \right),
+\end{eqnarray}
+Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
+and not the others. Therefore,  
+remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
+and a phase $e^{is}$ to $|1\rangle$, the result is:
 \begin{small}
 \begin{eqnarray}
-&e^{-is} \sum_{k \in Ctrl} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle 
-+ \sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
+&e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
++ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
 & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
@@
 \end{small}
-where $\vec{a'} = \sum_{k \in Ctrl} B_{2k,j}|k\rangle|0\rangle \;,\; \vec{b'}_j = \sum_{k \in Ctrl} B_{2k+1,j} |k\rangle |1 \rangle \;,\; \vec{c'}_j =\sum_{k \not\in Ctrl} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)$.
+where $\vec{a'} = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle \;,\; \vec{b'}_j = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle \;,\; \vec{c'}_j =\sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)$.
  These vectors are clearly orthogonal because they are each linear combinations of different 
 orthogonal states of the computational basis. 
-Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the norm of the $j-$th column of $B$, 
+Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the norm of the $j$th column of $B$, 
 which is unitary.
@@
 
-Therefore, from this theorem we conclude that
-the kind of curves of states that can be created
-using an OPR circuit are always of the form
-\begin{align*}
-|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
-\end{align*}
-where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
-$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
-%\textbf{Puntos:}
+%Therefore, from this theorem we conclude that
+%the kind of curves of states that can be created
+%using a 1PR circuit are always of the form
+%\begin{align*}
+%|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
+%\end{align*}
+%where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
+%$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
+%%\textbf{Puntos:}
 %\begin{itemize}
@@
 %\item How can we reduce the amount of parametrized rotations used?
-%\item \textbf{OPR Circuit:} Define an OPR circuit (a circuit with one parametrized rotation)
-%\item \textbf{Theorem about OPR circuits:} \textit{An OPR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
+%\item \textbf{1PR Circuit:} Define an 1PR circuit (a circuit with one parametrized rotation)
+%\item \textbf{Theorem about 1PR circuits:} \textit{An 1PR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
 %\begin{eqnarray}
@@
 % }}}
-\section{OPR circuit for a Pauli map} % {{{
-\label{sec: OPR circuit for a Pauli map}
+\section{1PR circuit for a Pauli map} % {{{
+\label{sec: 1PR circuit for a Pauli map}
 
@@
 We can now use the last theorem to conclude directly which Pauli dynamical maps
-can be created using an OPR circuit.
-For OPR circuits, the ancilla state has to be created with only one parametrized curve. Then, the theorem for OPR circuits implies that a map
+can be created using a 1PR circuit.
+For 1PR circuits, the ancilla state has to be created with only one parametrized curve. Then, the theorem for 1PR circuits implies that a map
 \begin{eqnarray}
@@
 We can see some examples of Pauli dynamical
-maps of one qubit that can be implemented with an OPR circuit:
+maps of one qubit that can be implemented with a 1PR circuit:
 \begin{itemize}
@@
 
-To implement this dynamical map using the circuit presented in figure \ref{fig:OPR-circuit}, it is necessary to create the state
+To implement this dynamical map using the circuit presented in \fref{fig:1PR-circuit}, it is necessary to create the state
 \begin{eqnarray}
@@
 %\begin{itemize}
-%\item Use the last theorem to conclude directly which maps can be created using an OPR circuit.
+%\item Use the last theorem to conclude directly which maps can be created using an 1PR circuit.
 %\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
@@
 \begin{itemize}
-\item We will apply the results about OPR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
-\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with an OPR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with an OPR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
+\item We will apply the results about 1PR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
+\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with a 1PR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with a 1PR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
 \item \textbf{Proof:}  Es b\'asicamente usar que $H = QDQ^{-1}$ para una matriz $Q$ que no depende de $t$ y por lo tanto no agrega compuertas parametrizadas al circuito. 
-\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using an OPR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
+\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using a 1PR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
 \item \textbf{Proof:} Estoy buscando formas de simplificar la prueba, porque es medio larguita.
@@
 Luego  usar el teorema de la sección 3 y notar que sólo hay tres tipos de  $\lambda$s posibles y luego notar que deben de tener esas degeneraciones.
-\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito OPR que hace la operación a partir de una $H$ que cumpla la hipótesis.
+\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito 1PR que hace la operación a partir de una $H$ que cumpla la hipótesis.
 \item \textbf{Examples.} Mencionar que por el teorema, los ejemplos son sistemas con 3 energías separadas por la misma distancia y con las degeneraciones dadas en el teorema. 

### 2023-05-15 main.tex
Algunas más

@@
 mensaje principal y rediseñar. }
-\tbnote{De acuerdo, mejor así?:.}
+\tbnote{De acuerdo, Lo cambié a esto:}
 
@@
 {\color{orange} the form depicted in \fref{fig:1PR-circuit},
-where the rotation is around $\sigma_3$ and
+where the parametrized rotation is around $\sigma_3$ and
 is applied to the last qubit.}
@@
 {\color{orange} , since if it weren't, we could use
-swap gates to convert the rotation
+swap gates to move the rotation
 to the last qubit without adding gates
@@
 remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
-and a phase $e^{is}$ to $|1\rangle$, the result is:
+and a phase $e^{is}$ to $|1\rangle$, $RB|j\rangle$ is:
 \begin{small}
@@
 \end{small}
-where $\vec{a'} = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle \;,\; \vec{b'}_j = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle \;,\; \vec{c'}_j =\sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)$.
+where $\vec{a'} = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$, $\vec{b'}_j = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle$, $\vec{c'}_j =\sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)$.
  These vectors are clearly orthogonal because they are each linear combinations of different 
@@
 \begin{eqnarray}
-e^{-is} A \vec{a'}_j + e^{is} A \vec{b'}_j + A \vec{c'}_j = e^{-is} \vec{a}_j + e^{is} \vec{b}_j + \vec{c}_j = \vec{v}_j,
+U|j\rangle = ARB|j\rangle = e^{-is} A \vec{a'}_j + e^{is} A \vec{b'}_j + A \vec{c'}_j = e^{-is} \vec{a}_j + e^{is} \vec{b}_j + \vec{c}_j = \vec{v}_j,
 \end{eqnarray}
@@
 computational base is
- $U = (|\vec{v}_0|, |\vec{v}_1|, \cdots, |\vec{v}_{2^n-1}|)$. $\blacksquare$  \\
+ $U = (\vec{v}_0, \vec{v}_1, \cdots, \vec{v}_{2^n-1})$. $\blacksquare$  \\
  $\;$ \\
+
+This theorem implies that starting from the state $|0\rangle$,
+the only curves we could expect to create
+with a 1PR circuit are those of the form
+\begin{equation}
+|\eta(p)\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
+\label{eq:curve-states}
+\end{equation}
+with 
+\begin{equation}
+|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1  \; \text{and} \; \vec{a}, \vec{b}, \vec{c} \; \text{are orthogonal vectors}.
+\label{eq:conditions-vecs}
+\end{equation}
+Furthermore, we can show a way to create these curves of states
+with a 1PR circuit.
+To do it, we can use the circuit of \fref{fig:1PR-circuit} with the parametrized
+rotation on the last qubit controlled by all the others
+and with matrices $A$ and $B$ defined as:
+\begin{align*}
+B = (\vec{d}, *,*, \cdots,*), \; 
+A = (* , \cdots, *, \vec{c}/|\vec{c}|, \vec{b}/|\vec{b}|, \vec{a}/|\vec{a}|).
+\end{align*}
+Here the column vector $\vec{d}$ is defined as 
+$(0,0, \cdots,0 ,|\vec{c}|, |\vec{b}|, |\vec{a}|)$
+and the asterisks can be completed in any
+way such that these matrices are unitary.
+Then, starting from the initial state $|0\rangle = (1,0,0,\cdots,0)$
+and applying the matrices $ARB$ defined
+like this, some calculations lead us to 
+the resulting curve of states
+of \eref{eq:curve-states}.
 
@@
 
-\tbnote{Sección no escrita aún, sólo es el medio resumen que tenía.}
+\tbnote{Sección no escrita del todo aún, sólo es un medio resumen que tenía.}
 We can now use the last theorem to conclude directly which Pauli dynamical maps
 can be created using a 1PR circuit.
-For 1PR circuits, the ancilla state has to be created with only one parametrized curve. Then, the theorem for 1PR circuits implies that a map
+For 1PR circuits, the ancilla state of \ref{fig: circuit-pauli} 
+has to be created with only one parametrized curve. Therefore, theorem 2 implies that a map
 \begin{eqnarray}
@@
 \begin{eqnarray}
-\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} \cos s + \vec{b} \sin s
+\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is}
 \end{eqnarray}
@@
 
-We can see some examples of Pauli dynamical
-maps of one qubit that can be implemented with a 1PR circuit:
+For the particular case of one qubit,
+we show some examples of Pauli dynamical maps that can be
+implemented with a 1PR circuit, which are plotted
+in \fref{fig:curves}.
+
+\begin{figure} % {{{
+\centering
+\includegraphics{images/curvas.png}
+\caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
+The curves painted in the tetrahedron
+represent Pauli dynamical maps that can be implemented with 1PR circuits.
+In particular, the depolarizing (purple), bit flip (blue),
+phase flip (green), bit-phase flip (red)
+and parabolic (orange). }
+\label{fig:curves}
+\end{figure}
+
 \begin{itemize}
-\item \textbf{$\sigma_3$ parabolic map:} We take as an example the Pauli dynamical map for one qubit defined as
+\item \textbf{Bit flip map:} 
+This Pauli dynamical map is defined as
+\begin{align*}
+\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1
+\end{align*}
+for $p \in [0,1]$. 
+Therefore, the curve of state $|\beta(p)\rangle$ needed on the ancilla
+qubits is such that 
+$|\beta_0(p)|^2= (1-p)^2$, $|\beta_1(p)|^2 = p$, $|\beta_2(p)|^2 = |\beta_3(p)|^2 = 0$.
+In particular, if we take the $\beta_j$ to be real,
+we need to create the curve of states:
+\begin{align*}
+|\beta(p)\rangle = (\sqrt{1-p},\sqrt{p},0,0).
+\end{align*}
+This curve can be rewritten as
+\begin{align*}
+|\beta(p) \rangle = e^{is} \left( \dfrac{1}{2}, - \dfrac{i}{2},0,0 \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2},0,0 \right),
+\end{align*}
+with $s= \arcsin(\sqrt{p})$.
+Therefore, we can see that the curve satisfies the conditions of theorem 2 
+and it can be created with a 1PR circuit.
+The exact same thing can be done
+for the phase flip and bit phase flip dynamical maps
+changing $\sigma_1$ with
+$\sigma_3$ and $\sigma_2$ respectively.
+
+\item \textbf{Depolarizing:} This dynamical map is given by
+\begin{align*}
+\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
+\end{align*}
+with $p \in [0,1]$. 
+Therefore, taking the $\beta_j$ to be real,
+the curve of states needed to create on the ancilla qubits is
+\begin{align*}
+|\beta(p) \rangle = \left( \sqrt{1-3p/4}, \sqrt{p/4}, \sqrt{p/4},\sqrt{p/4} \right).
+\end{align*}
+This state can be rewritten as:
+\begin{align*}
+|\beta(p)\rangle = e^{is} \left( \dfrac{1}{2}, \dfrac{-i}{2\sqrt{3}},\dfrac{-i}{2\sqrt{3}},\dfrac{-i}{2\sqrt{3}} \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2\sqrt{3}},\dfrac{i}{2\sqrt{3}},\dfrac{i}{2\sqrt{3}}\right)
+\end{align*}
+with $s = \arcsin(\sqrt{3p/4}$.
+We can see that the curve satisfies the conditions of theorem 2, which
+means that it can be created with a 
+1PR circuit.
+
+\item \textbf{Parabolic dynamical map:} Finally, we define a parabolic dynamical map as:
 \begin{eqnarray}
@@
 \end{eqnarray}
-with $p \in [-1,1]$. \\
-
-To implement this dynamical map using the circuit presented in \fref{fig:1PR-circuit}, it is necessary to create the state
-\begin{eqnarray}
-\left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right)
-\end{eqnarray}
-on the $2$ ancilla qubits. Luckily, this state can be written in the form $\vec{c} + \vec{a} \cos s + \vec{b} \sin s$ as
-\begin{eqnarray}
-\begin{pmatrix}
-1/2 \\
-0 \\ 
-0 \\
-1/2
-\end{pmatrix} + \begin{pmatrix}
-0 \\
-1/2 \\
-1/2 \\
-0
-\end{pmatrix}  \cos s + \begin{pmatrix}
--1/2 \\
-0 \\
-0 \\
-1/2
-\end{pmatrix} \sin s
-\end{eqnarray}
-with $s = \arcsin p$.
-According to theorem 1, the fact that the state we need to create over the ancilla qubits can be written like this implies that the dynamical map can be simulated in a quantum computer using only one parametrized rotation.
-The circuit used will have the same form as that in figure , where the part used to create the state on the ancilla qubits will be:
-\begin{figure}[h!]
+with $p \in [-1,1]$. 
+If we take the $\beta_j$ to be real,
+this dynamical map can be implemented
+by creating the curve of states:
+\begin{eqnarray}
+|\beta(p)\rangle = \left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right).
+\end{eqnarray}
+This can be rewritten as
+\begin{align*}
+|\beta(p)\rangle = \left( \dfrac{1}{2},0,0, \dfrac{1}{2} \right) + e^{is} \left( \dfrac{i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{-i}{4} \right) + e^{-is}  \left( \dfrac{-i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{i}{4} \right),
+\end{align*}
+with $s = \arcsin(p)$, so that
+this map fulfills the conditions of theorem 2.
+\end{itemize}
+
+We can construct other examples of 
+Pauli dynamical maps
+such that the curve of states $|\beta(p)\rangle$ requires
+can be implemented with a 1PR circuit.
+To do it, we only need to choose the three vectors $\vec{a}, \vec{b},\vec{c}$
+that satisfy the conditions of theorem 2.
+
+This can be done systematically for the case of curves of two qubits
+(that is, for Pauli dynamical maps of one qubit)
+with the following procedure:
+\begin{itemize}
+\item[1.] We first choose the norms $|\vec{a}|, |\vec{b}|, |\vec{c}|$
+such that $|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1$
+by choosing two angles $\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and 
+defining:
+\begin{align*}
+|\vec{a}| = \sin \nu \cos \mu, \; |\vec{b}| = \sin \nu \sin \mu , \; |\vec{c}| = \cos \nu.
+\end{align*}
+\item[2.] We define $\vec{a'} = (|\vec{a}|,0,0,0),$ $\vec{b'} = (0,|\vec{b}|,0,0),$ $\vec{c'} = (0,0,|\vec{c}|,0)$.
+\item[3.] We select a unitary matrix $U$
+whose first row is $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$,
+with $\theta \in [0,2\pi]$ and use it to define $\vec{a} = U \vec{a'}, \vec{b} = U \vec{b'}, \vec{c} = U \vec{c'}$.
+
+This way, since the primed vectors are orthogonal and their squared norms add up to one,
+so do the unprimed vectors. 
+Moreover, we have that $\vec{a}+ \vec{b}+ \vec{c} = (e^{i\theta},0,0,0)$,
+which is a consequence of the first row of $U$ being $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$ because:
+\begin{align*}
+\vec{a} + \vec{b} + \vec{c} = U (\vec{a'} + \vec{b'} + \vec{c'}) = U(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
+\end{align*}
+The last step is because the first entry of $U(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
+is obtained by calculating the dot product of the first row of $U$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
+$e^{i\theta}$. 
+Furthermore, the other entries have to be $0$,
+since otherwise the norm of the result would be greater than
+one but $U$ preserves the norm.
+\end{itemize}
+
+Following this procedure for random
+angles and unitary matrices $U$, 
+we plot four Pauli dynamical maps 
+that can be implemented with a 1PR circuit in \fref{fig:curves-random}.
+
+\begin{figure} % {{{
 \centering
-\begin{quantikz}
-\lstick{$aq_0$} & \gate[wires=2]{B} & \ctrl{1} & \gate[wires=2]{A} & \qw \\
-\lstick{$aq_{1}$} & & \gate{R_{\sigma_2}(2s)} & & \qw  \\
-\end{quantikz}
-\caption{Circuit to create 2-qubit state}
+\includegraphics{images/curvas-azar.png}
+\caption{{\bf Random Pauli dynamical maps that can be implemented with a 1PR circuit.}
+The curves painted in the tetrahedron
+represent Pauli dynamical maps that can be implemented with 1PR circuits
+that were selected at random using the procedure detailed before.}
+\label{fig:curves-random}
 \end{figure}
-
-where according to theorem 1, matrices $A$ and $B$ can be chosen as:
-\begin{eqnarray}
-A &= \begin{pmatrix}
-*  & c_0 / \sqrt{1-r^2} & -b_0/r & a_0 /r \\
-*  & c_1 / \sqrt{1-r^2} & -b_1/r & a_1 /r \\ 
-* & c_2 / \sqrt{1-r^2} & -b_2/r & a_2/r \\
-* & c_3 / \sqrt{1-r^2} & -b_3/r & a_3/r \\
-\end{pmatrix} = \begin{pmatrix}
-0 & 1/\sqrt{2} & -1/\sqrt{2} & 0 \\
--1/\sqrt{2} & 0 & 0 & 1/\sqrt{2} \\
-1/\sqrt{2} & 0 & 0 & 1/\sqrt{2} \\
-0 & 1/\sqrt{2} & 1/\sqrt{2} & 0
-\end{pmatrix} \\
-B& = \begin{pmatrix}
-0 & 0 & 0 & 1 \\
-0 & 1 & 0 & 0\\
-0 & 0& 1 & 0 \\
-1 & 0 & 0 & 0 
-\end{pmatrix}
-\end{eqnarray}
-\end{itemize}
 

### 2023-05-16 main.tex
Otros cambios

@@
 This theorem implies that starting from the state $|0\rangle$,
-the only curves we could expect to create
+the only curves of states we could expect to create
 with a 1PR circuit are those of the form
@@
 \begin{equation}
-|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1  \; \text{and} \; \vec{a}, \vec{b}, \vec{c} \; \text{are orthogonal vectors}.
+|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1  \; \text{and} \; \vec{a}, \vec{b}, \vec{c} \; \text{orthogonal vectors}.
 \label{eq:conditions-vecs}
 \end{equation}
-Furthermore, we can show a way to create these curves of states
+Furthermore, we can exhibit a way to create any of these curves of states
 with a 1PR circuit.
 To do it, we can use the circuit of \fref{fig:1PR-circuit} with the parametrized
-rotation on the last qubit controlled by all the others
-and with matrices $A$ and $B$ defined as:
+rotation $R$ on the last qubit controlled by all the other qubits
+and matrices $A$ and $B$ defined as:
 \begin{align*}
@@
 Here the column vector $\vec{d}$ is defined as 
-$(0,0, \cdots,0 ,|\vec{c}|, |\vec{b}|, |\vec{a}|)$
+$(0,0, \cdots,0 ,|\vec{c}|, |\vec{b}|, |\vec{a}|)^T$
 and the asterisks can be completed in any
@@
 and applying the matrices $ARB$ defined
-like this, some calculations lead us to 
+like this, some direct calculations lead us  to 
 the resulting curve of states
@@
 
-\tbnote{Sección no escrita del todo aún, sólo es un medio resumen que tenía.}
 We can now use the last theorem to conclude directly which Pauli dynamical maps
-can be created using a 1PR circuit.
-For 1PR circuits, the ancilla state of \ref{fig: circuit-pauli} 
-has to be created with only one parametrized curve. Therefore, theorem 2 implies that a map
+can be implemented using a 1PR circuit.
+With this condition, the curve of states of \eref{eq: parametrized state} 
+has to be created on the ancilla qubits with only one parametrized curve. 
+Therefore, the results of the last section imply that the the map
 \begin{eqnarray}
@@
 \begin{eqnarray}
-\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is}
+\label{eq:vec}
+\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
 \end{eqnarray}
@@
 For the particular case of one qubit,
-we show some examples of Pauli dynamical maps that can be
+we can show some examples of Pauli dynamical maps that can be
 implemented with a 1PR circuit, which are plotted
@@
 \item \textbf{Bit flip map:} 
-This Pauli dynamical map is defined as
+This dynamical map is defined as
 \begin{align*}
@@
 for $p \in [0,1]$. 
-Therefore, the curve of state $|\beta(p)\rangle$ needed on the ancilla
+Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
 qubits is such that 
@@
 \begin{align*}
-|\beta(p)\rangle = (\sqrt{1-p},\sqrt{p},0,0).
+|\beta(p)\rangle = \left(\sqrt{1-p},\sqrt{p},0,0\right).
 \end{align*}
-This curve can be rewritten as
+This can be rewritten as
 \begin{align*}
@@
 with $s= \arcsin(\sqrt{p})$.
-Therefore, we can see that the curve satisfies the conditions of theorem 2 
+Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
 and it can be created with a 1PR circuit.
@@
 \end{align*}
-with $s = \arcsin(\sqrt{3p/4}$.
-We can see that the curve satisfies the conditions of theorem 2, which
-means that it can be created with a 
+with $s = \arcsin(\sqrt{3p/4})$.
+We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
 1PR circuit.
 
-\item \textbf{Parabolic dynamical map:} Finally, we define a parabolic dynamical map as:
+\item \textbf{Parabolic dynamical map:} Finally, we define the parabolic dynamical map as:
 \begin{eqnarray}
@@
 If we take the $\beta_j$ to be real,
-this dynamical map can be implemented
-by creating the curve of states:
+we need to create the curve of states:
 \begin{eqnarray}
@@
 with $s = \arcsin(p)$, so that
-this map fulfills the conditions of theorem 2.
+this map fulfills the conditions of  \eref{eq:conditions-vecs}.
 \end{itemize}
 
-We can construct other examples of 
+Furthermore, we can construct other examples of 
 Pauli dynamical maps
-such that the curve of states $|\beta(p)\rangle$ requires
+such that the curve of states $|\beta(p)\rangle$ 
 can be implemented with a 1PR circuit.
 To do it, we only need to choose the three vectors $\vec{a}, \vec{b},\vec{c}$
-that satisfy the conditions of theorem 2.
-
-This can be done systematically for the case of curves of two qubits
+that satisfy the conditions of  \eref{eq:conditions-vecs}.
+
+For example, this can be done systematically for the case of curves of states of two qubits
 (that is, for Pauli dynamical maps of one qubit)
@@
 such that $|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1$
-by choosing two angles $\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and 
+by selecting two angles $\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and 
 defining:
@@
 \item[2.] We define $\vec{a'} = (|\vec{a}|,0,0,0),$ $\vec{b'} = (0,|\vec{b}|,0,0),$ $\vec{c'} = (0,0,|\vec{c}|,0)$.
-\item[3.] We select a unitary matrix $U$
-whose first row is $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$,
-with $\theta \in [0,2\pi]$ and use it to define $\vec{a} = U \vec{a'}, \vec{b} = U \vec{b'}, \vec{c} = U \vec{c'}$.
-
+\item[3.] Finally, we select a unitary matrix $V$
+and use it to define the vectors $\vec{a} = V \vec{a'}, \vec{b} = V \vec{b'}, \vec{c} = V \vec{c'}$.
 This way, since the primed vectors are orthogonal and their squared norms add up to one,
-so do the unprimed vectors. 
-Moreover, we have that $\vec{a}+ \vec{b}+ \vec{c} = (e^{i\theta},0,0,0)$,
-which is a consequence of the first row of $U$ being $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$ because:
+so do the unprimed vectors and therefore 
+fulfill the conditions of  \eref{eq:conditions-vecs}. 
+\end{itemize}
+
+Following this procedure for random
+angles and unitary matrices $V$, 
+we plot four Pauli dynamical maps 
+that can be implemented with a 1PR circuit in \fref{fig:curves-random}.
+These maps where constructed with the additional condition
+of passing through the identity channel.
+To do that, we ensure that the vectors also satisfy
+$\vec{a} + \vec{b} + \vec{c} = (e^{i \theta},0,0,0)$ with $\theta$ an arbitrary
+number.
+This way, when $s = 0$ in \eref{eq:vec}, the constructed state
+is $(e^{i \theta},0,0,0)$, which
+corresponds with the identity channel.
+
+To fulfill this additional condition,  we restrict the first row of
+$V$ to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
+That way, 
 \begin{align*}
@@
 \end{align*}
-The last step is because the first entry of $U(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
+The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
 is obtained by calculating the dot product of the first row of $U$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
@@
 since otherwise the norm of the result would be greater than
-one but $U$ preserves the norm.
-\end{itemize}
-
-Following this procedure for random
-angles and unitary matrices $U$, 
-we plot four Pauli dynamical maps 
-that can be implemented with a 1PR circuit in \fref{fig:curves-random}.
+one but $V$ preserves the norm.
 

### 2023-05-16 main.tex
Pequeño arreglo

@@
 $\vec{a} + \vec{b} + \vec{c} = (e^{i \theta},0,0,0)$ with $\theta$ an arbitrary
-number.
+real number.
 This way, when $s = 0$ in \eref{eq:vec}, the constructed state
@@
 \begin{align*}
-\vec{a} + \vec{b} + \vec{c} = U (\vec{a'} + \vec{b'} + \vec{c'}) = U(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
+\vec{a} + \vec{b} + \vec{c} = V (\vec{a'} + \vec{b'} + \vec{c'}) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
 \end{align*}
 The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
-is obtained by calculating the dot product of the first row of $U$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
+is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
 $e^{i\theta}$. 

### 2023-05-16 main.tex
Pequeño arreglo 2

@@
 \begin{equation}
-|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1  \; \text{and} \; \vec{a}, \vec{b}, \vec{c} \; \text{orthogonal vectors}.
+|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1  \; \text{and} \; \vec{a}, \vec{b}, \vec{c} \; \text{orthogonal vectors},
 \label{eq:conditions-vecs}
 \end{equation}
-Furthermore, we can exhibit a way to create any of these curves of states
-with a 1PR circuit.
-To do it, we can use the circuit of \fref{fig:1PR-circuit} with the parametrized
-rotation $R$ on the last qubit controlled by all the other qubits
-and matrices $A$ and $B$ defined as:
+and $s = s(p)$ a function of $p$.
+Furthermore, we can exhibit a 1PR circuit to create any of these curves of states.
+To do it, we can use the circuit of \fref{fig:1PR-circuit} and set the parametrized
+rotation $R$ on the last qubit to be controlled by all the other qubits..
+Moreover, we define the matrices $A$ and $B$ as:
 \begin{align*}
 B = (\vec{d}, *,*, \cdots,*), \; 
-A = (* , \cdots, *, \vec{c}/|\vec{c}|, \vec{b}/|\vec{b}|, \vec{a}/|\vec{a}|).
+A = (* , \cdots, *, \vec{c}/|\vec{c}|, \vec{b}/|\vec{b}|, \vec{a}/|\vec{a}|),
 \end{align*}
-Here the column vector $\vec{d}$ is defined as 
+where the column vector $\vec{d}$ is defined as 
 $(0,0, \cdots,0 ,|\vec{c}|, |\vec{b}|, |\vec{a}|)^T$
-and the asterisks can be completed in any
+and the asterisks can be filled up in any
 way such that these matrices are unitary.
 Then, starting from the initial state $|0\rangle = (1,0,0,\cdots,0)$
-and applying the matrices $ARB$ defined
-like this, some direct calculations lead us  to 
+and applying the circuit (whose matrix is $ARB$), some direct calculations lead us  to 
 the resulting curve of states
@@
 
-We can now use the last theorem to conclude directly which Pauli dynamical maps
-can be implemented using a 1PR circuit.
-With this condition, the curve of states of \eref{eq: parametrized state} 
-has to be created on the ancilla qubits with only one parametrized curve. 
+We can now use the previous results to conclude directly which Pauli dynamical maps
+can be implemented with a 1PR circuit.
+Given this condition, the curve of states of \eref{eq: parametrized state}  needed 
+to implement the map
+has to be constructed with only one parametrized rotation. 
 Therefore, the results of the last section imply that the the map
@@
 For the particular case of one qubit,
-we can show some examples of Pauli dynamical maps that can be
-implemented with a 1PR circuit, which are plotted
+we can show some examples of Pauli dynamical maps
+implementable with a 1PR circuit, which are plotted
 in \fref{fig:curves}.
@@
 The exact same thing can be done
-for the phase flip and bit phase flip dynamical maps
-changing $\sigma_1$ with
+for the phase flip and bit phase flip dynamical maps by
+changing $\sigma_1$ to
 $\sigma_3$ and $\sigma_2$ respectively.
@@
 \begin{eqnarray}
-\epsilon(\rho) = \dfrac{1}{4} (1-p)^2 \sigma_0 \rho \sigma_0 + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
+\epsilon(\rho) = \dfrac{1}{4} (1-p)^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
 \end{eqnarray}
@@
 Furthermore, we can construct other examples of 
-Pauli dynamical maps
-such that the curve of states $|\beta(p)\rangle$ 
+Pauli dynamical maps such that it
 can be implemented with a 1PR circuit.
@@
 that satisfy the conditions of  \eref{eq:conditions-vecs}.
-
 For example, this can be done systematically for the case of curves of states of two qubits
@@
 \item[1.] We first choose the norms $|\vec{a}|, |\vec{b}|, |\vec{c}|$
-such that $|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1$
-by selecting two angles $\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and 
-defining:
+such that $|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1$. 
+This can be done by selecting two angles
+$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
 \begin{align*}
@@
 \item[2.] We define $\vec{a'} = (|\vec{a}|,0,0,0),$ $\vec{b'} = (0,|\vec{b}|,0,0),$ $\vec{c'} = (0,0,|\vec{c}|,0)$.
-\item[3.] Finally, we select a unitary matrix $V$
+\item[3.] Finally, we choose a unitary matrix $V$
 and use it to define the vectors $\vec{a} = V \vec{a'}, \vec{b} = V \vec{b'}, \vec{c} = V \vec{c'}$.
@@
 These maps where constructed with the additional condition
-of passing through the identity channel.
+of the map passing through the identity channel.
 To do that, we ensure that the vectors also satisfy
@@
 since otherwise the norm of the result would be greater than
-one but $V$ preserves the norm.
+$1$ but $V$ is unitary and therefore preserves the norm.
 

### 2023-05-21 Cosas-Escritas-Antes.tex
Cambios

@@
 \subsection{Unitary evolution $U = e^{iHt}$}
+\section{Exponential maps $e^{iHt}$} % {{{
+\label{sec: Exponential maps}
+\textbf{Puntos:}
+\begin{itemize}
+\item We will apply the results about 1PR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
+\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with a 1PR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with a 1PR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
+\item \textbf{Proof:}  Es b\'asicamente usar que $H = QDQ^{-1}$ para una matriz $Q$ que no depende de $t$ y por lo tanto no agrega compuertas parametrizadas al circuito. 
+\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using a 1PR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
+\item \textbf{Proof:} Estoy buscando formas de simplificar la prueba, porque es medio larguita.
+Pero básicamente es usar el lema y entonces preocuparnos sólo por $D$.
+Luego  usar el teorema de la sección 3 y notar que sólo hay tres tipos de  $\lambda$s posibles y luego notar que deben de tener esas degeneraciones.
+\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito 1PR que hace la operación a partir de una $H$ que cumpla la hipótesis.
+\item \textbf{Examples.} Mencionar que por el teorema, los ejemplos son sistemas con 3 energías separadas por la misma distancia y con las degeneraciones dadas en el teorema. 
+La verdad que no se me ocurren sistemas físicos comunes que cumplan eso.
+\begin{itemize}
+\item Cualquier matriz $H$ de un qubit cumple el teorema.
+\item Cualquier matriz de $n$ qubits que sea el producto tensorial de matrices de Pauli para cada partícula (o sea algo como $\sigma_{i_1} \otimes \sigma_{i_2} \otimes \cdots \otimes \sigma_{i_n}$) cumple el teorema.
+\item Estoy viendo para cadenas de espines si hay condiciones para las que cumplan las hipótesis del teorema, pero no he encontrado aún.
+\end{itemize}
+\item Hice explícitamente el circuito de 2 qubits para $H = \sigma_3 \otimes \sigma_2$ y lo simulé en las computadoras de IBM, obteniendo una fidelidad de $0.85$.
+\end{itemize}
+% }}}
+\newpage
 

### 2023-05-21 main.tex
Cambios

@@
 \section{Introduction} % {{{
-
-% }}}
-\section{Quantum Channels}  \label{sec: Pauli Channels} % {{{
+\tbnote{Poner intro luego}
+
+% }}}
+\section{Pauli channels and dynamical maps}  \label{sec: Pauli Channels} % {{{
 \cpnote{Es raro qeu la seccion y una subseccion se llamen igual. Por discutir con Tomas}
@@
 \caption{\tbnote{Aquí está una forma alternativa en que puede quedar la figura. 
-Usé $2(1-p)$ en lugar de $p$ para que se cumpla lo de
+Usé $2(1-p_{succ})$ en lugar de $p_{succ}$ para que se cumpla lo de
 que $0$ es lo peor y $1$ lo mejor.}}
@@
 usually necessitates $2^N-1$ parametrized rotations.
-\cpnote{no me salen esas cuentas.} \tbnote{Se me fue el 2.}
+\cpnote{no me salen esas cuentas.} \tbnote{Se me olvidaba el 2, ya está bien}
 
@@
 However, it would be preferable to achieve the same effect using only one parametrized rotation. 
-This would allow us to treat said rotation 
+This would allow us to interpret said rotation 
 as a knob that smoothly traverses the curve of states.
@@
 To accomplish this, we begin by proving that all 1PR circuits have 
-{\color{orange} the form depicted in \fref{fig:1PR-circuit},
+the form depicted in \fref{fig:1PR-circuit},
 where the parametrized rotation is around $\sigma_3$ and
-is applied to the last qubit.}
+is applied to the last qubit.
 
@@
 \cpnote{Discutir la prueba, se ve demasiado larga y aburrida}
-\tbnote{La cambié un poco, pero aún así.}
+\tbnote{La cambié un poco, pero no sé qué más cambiarle.}
 Denoting by $U$ the matrix for the 1PR circuit,
@@
 We will calculate the $j$-th column of this matrix,
-which is given by $U|j\rangle$.
+which is given by $U|j\rangle$
+and confirm that it has the form $\vec{v}_j$ as defined above.
 
@@
 \end{equation}
-After the operator $B$, we need to apply $R$.
+After the operator $B$, the circuit applies the  controlled rotation $R$.
 To simplify the analysis, we separate the states of
@@
 remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
-and a phase $e^{is}$ to $|1\rangle$, $RB|j\rangle$ is:
+and a phase $e^{is}$ to $|1\rangle$, $RB|j\rangle$ is equal to:
 \begin{small}
@@
 \end{small}
-where $\vec{a'} = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$, $\vec{b'}_j = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle$, $\vec{c'}_j =\sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)$.
+where $\vec{a'} = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$, $\vec{b'}_j = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle$, $\vec{c'}_j =\sum_{k \not\in \mathcal{C}} \big( B_{2k,j} |k\rangle |0\rangle+$ $ B_{2k+1} |k\rangle |j \rangle \big)$.
  These vectors are clearly orthogonal because they are each linear combinations of different 
-orthogonal states of the computational basis. 
-Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the norm of the $j$th column of $B$, 
+orthogonal states of the computational base. 
+Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
 which is unitary.
@@
 
-This theorem implies that starting from the state $|0\rangle$,
+This theorem implies that starting from the state $|0\rangle$ (or any 
+other starting state),
 the only curves of states we could expect to create
-with a 1PR circuit are those of the form
+with a 1PR circuit are those of the form $U|0\rangle$, that is, curves such as:
 \begin{equation}
@@
 and $s = s(p)$ a function of $p$.
-Furthermore, we can exhibit a 1PR circuit to create any of these curves of states.
-To do it, we can use the circuit of \fref{fig:1PR-circuit} and set the parametrized
-rotation $R$ on the last qubit to be controlled by all the other qubits..
-Moreover, we define the matrices $A$ and $B$ as:
+Furthermore, given a curve of states as the one in
+\eref{eq:curve-states}, we can always construct a 1PR circuit to create it.
+One way of doing it, is to use the circuit of \fref{fig:1PR-circuit}, setting the parametrized
+rotation $R$ on the last qubit to be controlled by all the other qubits
+and defining the matrices $A$ and $B$ as
 \begin{align*}
 B = (\vec{d}, *,*, \cdots,*), \; 
-A = (* , \cdots, *, \vec{c}/|\vec{c}|, \vec{b}/|\vec{b}|, \vec{a}/|\vec{a}|),
+A = (* , \cdots, *, \vec{c}/|\vec{c}|, \vec{b}/|\vec{b}|, \vec{a}/|\vec{a}|).
 \end{align*}
-where the column vector $\vec{d}$ is defined as 
+Here the column vector $\vec{d}$ is defined as 
 $(0,0, \cdots,0 ,|\vec{c}|, |\vec{b}|, |\vec{a}|)^T$
@@
 Then, starting from the initial state $|0\rangle = (1,0,0,\cdots,0)$
-and applying the circuit (whose matrix is $ARB$), some direct calculations lead us  to 
+and applying the circuit  of \fref{fig:1PR-circuit} (whose matrix representation is $ARB$), some direct calculations lead us  to 
 the resulting curve of states
@@
 % }}}
-\section{Exponential maps $e^{iHt}$} % {{{
-\label{sec: Exponential maps}
-\textbf{Puntos:}
-\begin{itemize}
-\item We will apply the results about 1PR circuit to another kind of operation, those given by $U  = e^{iHt}$ where $H$ is hermitian  and time independent.
-\item \textbf{Lemma:}\textit{ The $n$-qubit operator $U^{iHt}$ can be implemented with a 1PR circuit of $n$ qubits if and only if $D = \text{diag}(e^{i\lambda_0 t}, \cdots, e^{i \lambda_{2^n-1}t})$ can be implemented with a 1PR circuit of $n$ qubits, where $\lambda_j$ are the eigenvalues of $H$.}
-\item \textbf{Proof:}  Es b\'asicamente usar que $H = QDQ^{-1}$ para una matriz $Q$ que no depende de $t$ y por lo tanto no agrega compuertas parametrizadas al circuito. 
-\item \textbf{Theorem:} \textit{ A n-qubit operator of the form $U = e^{iHt}$ can be implemented using a 1PR circuit if and only if the eigenvalues of $H$ are $-\lambda,0,\lambda$ (for $\lambda$ a real number) and the degeneracies of $\lambda$ and $-\lambda$ are both equal to $2^j$ for some $j\in \{0,1,\cdots,n-1\}$.}
-\item \textbf{Proof:} Estoy buscando formas de simplificar la prueba, porque es medio larguita.
-Pero básicamente es usar el lema y entonces preocuparnos sólo por $D$.
-Luego  usar el teorema de la sección 3 y notar que sólo hay tres tipos de  $\lambda$s posibles y luego notar que deben de tener esas degeneraciones.
-\item \textbf{Proof del regreso:} Aquí quiero recalcar que la prueba es constructiva, ya que consiste en mostrar cómo construir el circuito 1PR que hace la operación a partir de una $H$ que cumpla la hipótesis.
-\item \textbf{Examples.} Mencionar que por el teorema, los ejemplos son sistemas con 3 energías separadas por la misma distancia y con las degeneraciones dadas en el teorema. 
-La verdad que no se me ocurren sistemas físicos comunes que cumplan eso.
-\begin{itemize}
-\item Cualquier matriz $H$ de un qubit cumple el teorema.
-\item Cualquier matriz de $n$ qubits que sea el producto tensorial de matrices de Pauli para cada partícula (o sea algo como $\sigma_{i_1} \otimes \sigma_{i_2} \otimes \cdots \otimes \sigma_{i_n}$) cumple el teorema.
-\item Estoy viendo para cadenas de espines si hay condiciones para las que cumplan las hipótesis del teorema, pero no he encontrado aún.
-\end{itemize}
-\item Hice explícitamente el circuito de 2 qubits para $H = \sigma_3 \otimes \sigma_2$ y lo simulé en las computadoras de IBM, obteniendo una fidelidad de $0.85$.
-\end{itemize}
-% }}}
+
 \section{Conclusion} % {{{

### 2023-05-22 main.tex
SIMONE, WE WENT OVER THIS. EXPANDTAB.

@@
 \section{Pauli channels and dynamical maps}  \label{sec: Pauli Channels} % {{{
-\cpnote{Es raro qeu la seccion y una subseccion se llamen igual. Por discutir con Tomas}
-\tbnote{Lo cambié}
-\cpnote{El texto esta bien, pero creo qeu la distribucino de subsecciones esta chistosna y 
-los titulo tambien. Platicar con Tomas a ver a que llegamos. }
-
 % Intro  {{{
-\textbf{Lista de puntos:}
-\begin{itemize}
-\item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
-\item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
-\item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
-\end{itemize}
-
-In this section \cpnote{ser coherente con las subsecciones que se tienen nota que no 
-hay mencion a los quantum channels. Menos
-cuadrado, quizá pasar por chatgpt. hacerlo al final cuanod se tenga el capitulo
-por lo menos leido y aprobado en principio de mi parte.} \tbnote{Ya} we introduce the
-concept of quantum channels, focusing on a specific type called Pauli channels.
-Furthermore, we define Pauli dynamical maps, which
-are curves of Pauli channels parametrized by a variable.
-% }}}
-%\subsection*{Quantum Channels} \label{subsec: Quantum Channels} % {{{
-
-% \cpnote{Creo que toca iterar, pensando un poco en nivel licenciatura. ver ejemplos }
-% \cpnote{Tambien creo que no es coherente tener una subseccion para esto si 
-% lo qeu se quiere decir en la seccion es otra cosa.}
+% \textbf{Lista de puntos:}
+% \begin{itemize}
+% \item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
+% \item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
+% \item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
+% \end{itemize}
+
+In this section  we introduce the concept of quantum channels, focusing on a
+specific type called Pauli channels.  Furthermore, we define Pauli dynamical
+maps, which are curves of Pauli channels parametrized by a variable.
+% }}}
+\subsection{Quantum Channels} \label{subsec: Quantum Channels} % {{{
 
@@
 
-To describe open systems, instead of state vectors,
-we use matrices $\rho$ that act on $\mathcal{H}$.
-These matrices are called density matrices, and they include information about the system's interaction with its environment. 
-For a density matrix $\rho$ to be physically valid, 
-it must satisfy two conditions: $\tr(\rho) = 1$ and it must be positive semi-definite,
-which is denoted as $\rho \geq 0$~\cite{chuangbook}.
-
-Knowing this, we can now define quantum channels.
-Quantum channels are operators $\mathcal{E}$ that
-can describe the evolution of open quantum systems, such that $\rho \rightarrow \mathcal{E}(\rho)$.
-Quantum channels are the most general linear operations
-that a quantum system can undergo independently of its
-past~\cite{zimansbook,cirac}.
-These channels are constructed based on three fundamental properties: 
-linearity, trace preservation, and complete positivity.
-
-Linearity ensures that a quantum channel $\mathcal{E}$ maps any ensemble
-of density matrices into the corresponding ensemble of their evolution.
-The trace preserving property is given by $\tr (\mathcal{E}[\rho]) = \tr (\rho) =
-1$ and guarantees that the quantum channel does not change the condition that $\tr(\rho) = 1$.
-Finally, the channel should also preserve
-the condition $\rho \geq 0$, and a map that does this is called a positive map.
-However, positivity of $\mathcal{E}$ is not enough, 
-and we actually require the more restrictive condition of complete positivity.
-Complete positivity means that
-$\mathcal{E} \otimes \mathbb{I}_n$ is positive for
-any positive integer $n$ 
-(where $\mathbb{I}_n$ is the $n\times n$ identity matrix).
-This ensures that even if the principal system is entangled with another system,
-applying $\mathcal{E}$ to the principal system while doing nothing to the
- other one still results in  a positive semidefinite state for the principal system~\cite{chuangbook}.
-
-Given a quantum channel $\mathcal{E}$, 
-the condition of trace preservation is straightforward to verify but complete positivity is not as simple.
-To test complete positivity of a quantum channel, 
-Jamiołkowski and Choi~\cite{choi,jamil} developed a simple algorithm that exploits the
+To describe open systems, instead of state vectors, we use matrices $\rho$ that
+act on $\mathcal{H}$.  These matrices are called density matrices, and they
+include information about the system's interaction with its environment.  For a
+density matrix $\rho$ to be physically valid, it must satisfy two conditions:
+$\tr(\rho) = 1$ and it must be positive semi-definite, which is denoted as
+$\rho \geq 0$~\cite{chuangbook}.
+
+Knowing this, we can now define quantum channels.  Quantum channels are
+operators $\mathcal{E}$ that can describe the evolution of open quantum
+systems, such that $\rho \rightarrow \mathcal{E}(\rho)$.  Quantum channels are
+the most general linear operations that a quantum system can undergo
+independently of its past~\cite{zimansbook,cirac}.  These channels are
+constructed based on three fundamental properties: linearity, trace
+preservation, and complete positivity.
+
+Linearity ensures that a quantum channel $\mathcal{E}$ maps any ensemble of
+density matrices into the corresponding ensemble of their evolution.  The trace
+preserving property is given by $\tr (\mathcal{E}[\rho]) = \tr (\rho) = 1$ and
+guarantees that the quantum channel does not change the condition that
+$\tr(\rho) = 1$.  Finally, the channel should also preserve the condition $\rho
+\geq 0$, and a map that does this is called a positive map.  However,
+positivity of $\mathcal{E}$ is not enough, and we actually require the more
+restrictive condition of complete positivity.  Complete positivity means that
+$\mathcal{E} \otimes \mathbb{I}_n$ is positive for any positive integer $n$
+(where $\mathbb{I}_n$ is the $n\times n$ identity matrix).  This ensures that
+even if the principal system is entangled with another system, applying
+$\mathcal{E}$ to the principal system while doing nothing to the other one
+still results in  a positive semidefinite state for the principal
+system~\cite{chuangbook}.
+
+Given a quantum channel $\mathcal{E}$, the condition of trace preservation is
+straightforward to verify but complete positivity is not as simple.  To test
+complete positivity of a quantum channel, Jamiołkowski and
+Choi~\cite{choi,jamil} developed a simple algorithm that exploits the
 isomorphism between a channel $\mathcal{E}$ and the state $\mathcal{D} =
 (\mathbb{I} \otimes \mathcal{E}) [|\Omega \rangle \langle  \Omega|]$, where
-$|\Omega\rangle = 1/\text{dim}(\mathcal{H}) \sum_{i}^{\text{dim}(\mathcal{H})} |i \rangle |i \rangle$ is a maximally entangled state between the original system and
-an ancilla.  Remarkably, the map $\mathcal{E}$
-is completely positive if and only if $\mathcal{D}$ (also known as the Choi or
-dynamical matrix of $\mathcal{E}$) is positive semidefinite.
-
-\cpnote{Le hice un par de cambios pequeños pero la veo bastante bien. }
-\tbnote{Perfecto, gracias!}
-% }}}
-\subsection{Pauli Channels} 
-\label{subsec: Pauli Channels} % {{{
+$|\Omega\rangle = 1/\text{dim}(\mathcal{H}) \sum_{i}^{\text{dim}(\mathcal{H})}
+|i \rangle |i \rangle$ is a maximally entangled state between the original
+system and an ancilla.  Remarkably, the map $\mathcal{E}$ is completely
+positive if and only if $\mathcal{D}$ (also known as the Choi or dynamical
+matrix of $\mathcal{E}$) is positive semidefinite.
+
+% }}}
+\subsection{Pauli Channels}  \label{subsec: Pauli Channels} % {{{
 
@@
 
-\cpnote{Acá voy}
-
-% \cpnote{Es raro tener una sola subseccion. De perdida dos, o ninguna. Charlemso
-% a ver como reorganizar las secciones (creo que el flujo si va bien hasta
-% ahora)} \tbnote{Va. Me pareció ponerle su propia subsección a la parte anterior
-% porque creo que esto y lo anterior sí debe ir separado, así que mejor dos
-% subsecciones.}
-
 For the particular case of a Pauli channel on one qubit, the circuit that
@@
 \end{subequations}
+\cpnote{Acá te falto la puntuación en las ecuaciones. Porotro lado me gustaría ver la 
+forma que tienen las ecuaciones en exponenciales o en funciones trigonometricas
+que quizá estén mas bonitas.}
 
@@
 \caption{
-\cpnote{No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
-el lugar apropiado en el texto} \tbnote{Lo pasé al texto}
+% \cpnote{ No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
+% el lugar apropiado en el texto} \tbnote{Lo pasé al texto}
 {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
@@
 ancilla qubits and we use three rotations
-of angles given by \eref{eq:angle} to create the state $\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
+of angles given by \eref{eq:angle} to create the state $\sqrt{k_{00}}
+|00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
 |10\rangle + \sqrt{k_{11}}|11\rangle$
 on them.
+\cpnote{Creo qeu este seria el estado ecuacion 14, pero como qeuno está limpio. 
+Creo quepodemos nombrar ese estado y luego referirnos acá por el nobmre y la referencia 
+a la ecuación.}
 %and the state $b_{00} |00\rangle + b_{01} |01\rangle + b_{10}
@@
 one-qubit Pauli channels and simulated them using the ibmq-lima quantum
-computer.  For each of these channels, we used quantum process
+computer\cpnote{la computadora no la usamos para samplear sino solo para simular. Modificar
+la frase.}.  For each of these channels, we used quantum process
 tomography~\cite{Qiskit, Chuang:1996} to obtain the 
 operator $\xi_I$ corresponding to the implementation of the
-circuit.  Then, we compared this {\color{red}
-Choi matrix} {\color{orange} operator} with the theoretical {\color{red} Choi
-matrix $\mathcal{C}_T$} {\color{orange} operator $\xi_T$} of the channel we
-wanted to implement.  \cpnote{Quizá referirnos mejor al canal? Lo discutimos.}
-\tbnote{Ah sí, mejor. Cambié lo que puse en rojo por lo que está en naranja.}
-
+circuit.  Then, we compared this operator with the ideal 
+channel $\xi_T$  we
+wanted to implement.
+
+\cpnote{Toca rediseñar este parrafo mejor. La figura que al final nos interesa es 
+la $f$, pero no se menciona acá. Toca como que hacer que el párrafo gire alrededor de ella. }
 We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
-with the probability that one can distinguish two channels \cpnote{Revisa esta 
-frase a ver si te parece} 
-\tbnote{Sí, perfecto}.
+with the probability that one can distinguish two channels.
 % To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
@@
 \end{equation}
-where $|| \cdot ||_{\diamond}$ is the diamond norm \cpnote{no la hemos 
-definido matemáticamente} \tbnote{Qué tal así:} {\color{orange}, defined by 
+where $|| \cdot ||_{\diamond}$ is the diamond norm, defined by 
 \begin{align*}
@@
 $|| \cdot ||_1$ the trace norm and the maximization
-done over all density matrices $\rho$.}
+done over all density matrices $\rho$.
+\cpnote{Esa definicion esta bonita y me gusta, pero supongo qeu no es asi somo la 
+calculas. }
 
@@
 distinguishable.
+\cpnote{Creo qeu el ejemplo debería ir con la $f$ que definamos, quizá pasando por la 
+norma diamante, o por la p succ. Eso si, si no la ocupamos (la psucc) tonces quitarla.}
 % \cpnote{hummm ejemplo al menos para nosotros.} 
@@
 % }}}
-
-\newpage
 \section{One Parameter Circuits} % {{{
@@
 \label{fig:curves}
-\end{figure}
+\end{figure} % }}}
 
@@
 \label{fig:curves-random}
-\end{figure}
+\end{figure} % }}}
 

### 2023-05-22 main.tex
Yes, I was being sarcastic.

@@
 
-% \cpnote{Mejorar la figura, quizá dejando la tridimensional y ademas poniendo unos 6 cortes. Probar
-% con diferentes colores.
-% }
-
-\begin{figure}
-\centering
-\includegraphics[width=0.55\textwidth]{images/probabilities-points.png}\\
-\caption{{\bf Maximal probabilities of success for one-qubit Pauli channel}
-$p_{\succ}$ of one-qubit Pauli channels implemented on IBM's ibmq-lima. The
-channels are plotted in the tetrahedron of Pauli channels, with a color bar
-indicating the distinguishability of each channel's implementation using the
-circuit for a 1-qubit Pauli channel. \cpnote{Poner la barra del tamaño apropiado 
-y quizá juntar con los cortes que tenemos. Discutir en vivo con Tomas a ver que onda. 
-Tambien poner mas puntos experimentales.} \tbnote{Cambié lo de la barra y puse más puntos experimentales en los cortes que están en 
-la figura más abajo
-(no en esta figura porque ya se llena mucho de puntos).}
-\cpnote{ Creo qeu me gustaria usar otra candidad, 
-como la fidelidad, pero definida a partir de la norma diamante. 
-Asi, 1 es perfecto y 0 esta mal.} \tbnote{Lo que se me ocurre es algo como $2*(1-p_{succ})$ que justo cumple eso y en términos
-de la norma es $1-1/2||\xi_I - \xi_T||_{\diamond}$} \cpnote{ De estas, me gusta la de abajo 
-a la izquiera porque siento que distingue bien, pero si toca entnoces
-usar los mismos colores en la fig 5.} \tbnote{Ya agarré esos colores} \cpnote{Te propongo dejar un tetraedro y los
-cinco cortes para que nos quede algo de 3 columnsas y dos filas. 
-propongo tambien que se ponta la leyenda en la figura y no encima. 
-Si te haces bolas con las figuras, discutimos como hacerlas en TIKZ. } \tbnote{Lo puse en la figura siguiente. Poniéndolo con 3 columnas y dos filas queda
-muy chiquita la figura del tetraedro y no se llega a ver nada, así que lo puse grande y los cortes
-alrededor. }}
-\label{fig: fidelity one qubit}
-\end{figure}
-
-%
-%\begin{figure}
-%\centering
-%\includegraphics[width=.32\columnwidth]{images/tetra-col1.png}
-%\includegraphics[width=.32\columnwidth]{images/tetra-col2.png}
-%\includegraphics[width=.32\columnwidth]{images/tetra-col3.png} \\[1ex]
-%\includegraphics[width=.32\columnwidth]{images/tetra-col4.png}
-%\includegraphics[width=.32\columnwidth]{images/tetra-col5.png}
-%\includegraphics[width=.32\columnwidth]{images/tetra-col6.png}\\[1ex]
-%\includegraphics[width=.32\columnwidth]{images/tetra-col7.png}
-%\includegraphics[width=.32\columnwidth]{images/tetra-col8.png}
-%\includegraphics[width=.32\columnwidth]{images/tetra-col9.png}\\[1ex]
-%\includegraphics[width=.32\columnwidth]{images/tetra-col10.png}
-%\includegraphics[width=.32\columnwidth]{images/tetra-col11.png}
-%\includegraphics[width=.32\columnwidth]{images/tetra-col12.png}\\[1ex]
-%\includegraphics[width=.32\columnwidth]{images/tetra-col13.png}
-%\includegraphics[width=.32\columnwidth]{images/tetra-col14.png}
-%\includegraphics[width=.32\columnwidth]{images/tetra-col16.png}\\[1ex]
-%\caption{Algunos colores posibles. \cpnote{ Creo qeu me gustaria usar otra candidad, 
-%como la fidelidad, pero definida a partir de la norma diamante. 
-%Asi, 1 es perfecto y 0 esta mal.} \tbnote{Algo como } \cpnote{ De estas, me gusta la de abajo 
-%a la izquiera porque siento que distingue bien, pero si toca entnoces
-%usar los mismos colores en la fig 5. Te propongo dejar un tetraedro y los
-%cinco cortes para que nos quede algo de 3 columnsas y dos filas. 
-%propongo tambien que se ponta la leyenda en la figura y no encima. 
-%Si te haces bolas con las figuras, discutimos como hacerlas en TIKZ. } }
-%\end{figure}
-
 \begin{figure}
@@
 \end{subfigure}
-\caption{\tbnote{Aquí está una forma alternativa en que puede quedar la figura. 
+\caption{\cpnote{}\tbnote{Aquí está una forma alternativa en que puede quedar la figura. 
 Usé $2(1-p_{succ})$ en lugar de $p_{succ}$ para que se cumpla lo de

### 2023-05-22 main.tex
fail

@@
 \end{subfigure}
-\caption{\cpnote{}\tbnote{Aquí está una forma alternativa en que puede quedar la figura. 
-Usé $2(1-p_{succ})$ en lugar de $p_{succ}$ para que se cumpla lo de
-que $0$ es lo peor y $1$ lo mejor.}}
+\caption{\cpnote{porfa escribe el caption.} \tbnote{Aquí está una forma
+alternativa en que puede quedar la figura.  Usé $2(1-p_{succ})$ en lugar de
+$p_{succ}$ para que se cumpla lo de que $0$ es lo peor y $1$ lo mejor.}}
 \end{figure}
@@
 \label{sec: 1PR Circuits}
-\cpnote{Quizá abrir con un parrafo de motivacion. Quizá lo tenemos que hablar. }
-\cpnote{No se sabe aun que son 1PR circuits. Poner completo} \tbnote{Ya.}
 
@@
 states like the one described in \eref{eq: parametrized state}.
-\cpnote{me gusta mas usar el comando eref para que si toca cambiarlo, dependiendo 
-de la revista, lo pueda hacer de un solo jalon. Lo mismo para las 
-figuras.} \tbnote{Ah va, lo puse en todas.}
-
-In general, producing this curve of states will require multiple rotations
-parametrized by $p$. For instance, in the case of a two-qubit curve of states,
-we would typically need three rotations that depend on $p$, similar to those
-illustrated for the ancilla qubits in \fref{fig: circuit-pauli-1}.
-Moreover, creating an $N$-qubit curve of states
-usually necessitates $2^N-1$ parametrized rotations.
-\cpnote{no me salen esas cuentas.} \tbnote{Se me olvidaba el 2, ya está bien}
-
-However, it is desirable to minimize the number of parametrized rotations in our circuit.
-\cpnote{why?}
-This leads us to the following question: which curves of states,
-such as the one described in \eref{eq: parametrized state}, 
-can be generated using only a single parametrized rotation? 
-To clarify this, we provide the following definition for a circuit with one parametrized rotation.
-\cpnote{Creo qeu los dos párrafos anteriores son uno y toca pensar cual es el
-mensaje principal y rediseñar. }
-\tbnote{De acuerdo, Lo cambié a esto:}
-
-{\color{orange} In general, producing this curve of states for $N$ qubits will require
-$2^N-1$ rotations parametrized by $p$,
+
+In general, producing this curve of states for $N$ qubits will require
+$2^N-1$ rotations parametrized by $p$\cpnote{De de donde sale este numero?},
 such as the three rotations used for the ancilla
@@
 To clarify this, we provide the following definition 
-for a circuit with one parametrized rotation.}
+for a circuit with one parametrized rotation.
 
@@
 Based on this definition, we aim to determine which curves of 
-states can be generated using 1PR \cpnote{Si te parece bien el cambio 
-en la sigla, cambialos todos} 
-\tbnote{Sí me parece, los cambié} circuits. 
+states can be generated using 1PR circuits. 
 To accomplish this, we begin by proving that all 1PR circuits have 
@@
 $s= s(p)$ is a function of the parameter.
-\cpnote{Parece que se te olvida la puntuacion en algunos captions. 
-por otro lado, queda la figura a mitad de la prueba. A mi me gusta dejar 
-que Latex organice solo las figuras y sin ponerle el h! ni nada. } \tbnote{Va}
 }
@@
 Moreover, without loss of generality, we can choose the last qubit as the
-target qubit for the rotation \cpnote{Why?} 
-{\color{orange} , since if it weren't, we could use
+target qubit for the rotation, since if it weren't, we could use
 swap gates to move the rotation
 to the last qubit without adding gates
-that depend on $p$. }.
+that depend on $p$.
 
@@
 resulting in the form depicted in \fref{fig:1PR-circuit}. 
-\cpnote{Creo que este ultimo parrafo sobra, aunque hay detalles aca que quizá se pueden
-poner en el planteamiento del problema.} \tbnote{Lo pasé arriba justo antes del teorema y quitaría este párrafo entonces }
 $\blacksquare$ \\
@@
 remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
-and a phase $e^{is}$ to $|1\rangle$, $RB|j\rangle$ is equal to:
-\begin{small}
-\begin{eqnarray}
-&e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
-+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
-& \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
-\end{eqnarray}
-\end{small}
-where $\vec{a'} = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$, $\vec{b'}_j = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle$, $\vec{c'}_j =\sum_{k \not\in \mathcal{C}} \big( B_{2k,j} |k\rangle |0\rangle+$ $ B_{2k+1} |k\rangle |j \rangle \big)$.
+and a phase $e^{is}$ to $|1\rangle$,
+% \begin{small}
+% \begin{eqnarray}
+% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
+% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
+% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
+% \end{eqnarray}
+% \end{small}
+% test
+\begin{align}
+RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
++ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1}
+|k\rangle |j \rangle \right) \nonumber \\
+& = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
+\end{align}
+where $\vec{a'} = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$,
+$\vec{b'}_j = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle$,
+$\vec{c'}_j =\sum_{k \not\in \mathcal{C}} \big( B_{2k,j} |k\rangle |0\rangle+$
+$ B_{2k+1} |k\rangle |j \rangle \big)$.
+\cpnote{Preferira que tuvieramos que los kets fisicos tuvieran la notacion de
+ket. Intenta modificarlo asi y luego sigo con la prueba. Ya no me está pareciendo 
+tan latosa. Trata tambien que los nombres que usas sean como consistentes o tengan 
+algo que decir de su contenido.}
 These vectors are clearly orthogonal because they are each linear combinations of different 
@@
 %\end{itemize}
-\newpage
 % }}}

### 2023-05-23 main.tex
Cambios

@@
 swap gates to move the rotation
-to the last qubit without adding gates
+to the first qubit without adding gates
 that depend on $p$.
@@
 \begin{theorem}
-A 1PR circuit always implements an operator whose matrix,
-in the computational basis, has the form:
-\begin{eqnarray}
-U = (\vec{v}_0, \vec{v}_1, \vec{v}_2, \cdots, \vec{v}_{2^n-1}),
-\end{eqnarray}
-where the column vectors are given by $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$,
-with $\vec{a}_j ,\vec{b}_j, \vec{c}_j$ orthogonal and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.
+Consider a 1PR circuit of $N$ qubits
+and denote by $U$ the operator it implements on this system. 
+Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
+we have that:
+\begin{align*}
+U|j\rangle = e^{is} |a^j\rangle + e^{-is} |b^j\rangle + |c^j\rangle
+\end{align*}
+with $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $|a^j|^2 + |b^j|^2 + |c^j|^2 = 1$.
 \end{theorem}
@@
 \tbnote{La cambié un poco, pero no sé qué más cambiarle.}
-Denoting by $U$ the matrix for the 1PR circuit,
-we can conclude from theorem 1 that $U=ARB$,
+We can conclude from theorem 1 that $U=ARB$,
 where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
-applied to the last qubit and controlled by some of the other
-ones. 
-We will calculate the $j$-th column of this matrix,
-which is given by $U|j\rangle$
-and confirm that it has the form $\vec{v}_j$ as defined above.
+applied to the last qubit and controlled by some of the other ones.
 
 First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
-which can be rewritten by separating the
-first $N-1$ qubits from the last one as:
+with $B_{i,j}$ the entries of matrix $B$.
+This can be rewritten by separating last qubit from the other $N-1$:
 \begin{equation}
-B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right).
+B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right).
 \end{equation}
@@
 and those that do not, and write it as
-\begin{eqnarray}
-B|j\rangle = \sum_{k \in \mathcal{C}} \left(B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j} |k\rangle |1 \rangle \right) + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1,j}|k\rangle |1\rangle \right),
-\end{eqnarray}
+\begin{align}
+B|j\rangle = \sum_{k \in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right),
+\end{align}
 Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
@@
 remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
-and a phase $e^{is}$ to $|1\rangle$,
+and a phase $e^{is}$ to $|1\rangle$, we have that,
 % \begin{small}
@@
 \begin{align}
-RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
-+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1}
-|k\rangle |j \rangle \right) \nonumber \\
-& = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
+RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
++ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
+& = e^{-is} |\mathfrak{b}^{j}\rangle + e^{is} |\mathfrak{a}^j\rangle + |\mathfrak{c}^j\rangle
 \end{align}
-where $\vec{a'} = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$,
-$\vec{b'}_j = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle$,
-$\vec{c'}_j =\sum_{k \not\in \mathcal{C}} \big( B_{2k,j} |k\rangle |0\rangle+$
-$ B_{2k+1} |k\rangle |j \rangle \big)$.
+where we defined $|\mathfrak{a}^j \rangle = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$,
+$|\mathfrak{b}^j\rangle = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle$,
+$|\mathfrak{c}^j\rangle =\sum_{k \not\in \mathcal{C}}\big( B_{2k,j} |k\rangle|0\rangle+$ $B_{2k+1,j} |k \rangle |1\rangle  \big)$.
 \cpnote{Preferira que tuvieramos que los kets fisicos tuvieran la notacion de
@@
 tan latosa. Trata tambien que los nombres que usas sean como consistentes o tengan 
-algo que decir de su contenido.}
-These vectors are clearly orthogonal because they are each linear combinations of different 
-orthogonal states of the computational base. 
-Moreover, they satisfy $|\vec{a'}_j|^2 + |\vec{b'}_j|^2 + |\vec{c'}_j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
+algo que decir de su contenido.} \tbnote{Ya hice unos cambios}
+These states are clearly orthogonal because they are each linear combinations of different 
+orthogonal states of the computational basis. 
+Moreover, they satisfy  $|\mathfrak{a}^j|^2 + |\mathfrak{b}^j|^2 + |\mathfrak{c}^j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
 which is unitary.
@@
 \begin{eqnarray}
-U|j\rangle = ARB|j\rangle = e^{-is} A \vec{a'}_j + e^{is} A \vec{b'}_j + A \vec{c'}_j = e^{-is} \vec{a}_j + e^{is} \vec{b}_j + \vec{c}_j = \vec{v}_j,
+U|j\rangle = ARB|j\rangle = e^{-is} A |\mathfrak{a}^j\rangle + e^{is} A |\mathfrak{b}^j\rangle + A |\mathfrak{c}^j\rangle = e^{-is} |a^j\rangle + e^{is} |b^j\rangle + |c^j\rangle,
 \end{eqnarray}
-where $\vec{a}_j = A \vec{a'}_j , \vec{b}_j = A \vec{b'}_j , \vec{c}_j = A \vec{c'}_j$ are still orthogonal
-vectors that satisfy $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$ because $A$ is unitary. 
-Therefore, we conclude that the circuit takes a state $|j\rangle$ and converts it
- into the state represented by the vector $\vec{v}_j$, which means that the matrix representation of the circuit's operation in the 
-computational base is
- $U = (\vec{v}_0, \vec{v}_1, \cdots, \vec{v}_{2^n-1})$. $\blacksquare$  \\
+where $|a^j\rangle = A |\mathfrak{a}^j\rangle, |b^j\rangle = A |\mathfrak{b}^j\rangle, |c^j\rangle = A |\mathfrak{c}^j\rangle$ are still orthogonal
+states that satisfy $|a|^2 + |b|^2 + |c|^2 = 1$ because $A$ is unitary. $\blacksquare$  \\
  $\;$ \\
@@
 \begin{equation}
-|\eta(p)\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
+|\eta(p)\rangle = |c\rangle + e^{is}|a\rangle + e^{-is} |b\rangle,
 \label{eq:curve-states}
@@
 \begin{equation}
-|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1  \; \text{and} \; \vec{a}, \vec{b}, \vec{c} \; \text{orthogonal vectors},
+|a|^2 + |b|^2 + |c|^2 = 1  \; \text{and} \; |a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
 \label{eq:conditions-vecs}
@@
 rotation $R$ on the last qubit to be controlled by all the other qubits
-and defining the matrices $A$ and $B$ as
-\begin{align*}
-B = (\vec{d}, *,*, \cdots,*), \; 
-A = (* , \cdots, *, \vec{c}/|\vec{c}|, \vec{b}/|\vec{b}|, \vec{a}/|\vec{a}|).
-\end{align*}
-Here the column vector $\vec{d}$ is defined as 
-$(0,0, \cdots,0 ,|\vec{c}|, |\vec{b}|, |\vec{a}|)^T$
-and the asterisks can be filled up in any
-way such that these matrices are unitary.
-Then, starting from the initial state $|0\rangle = (1,0,0,\cdots,0)$
-and applying the circuit  of \fref{fig:1PR-circuit} (whose matrix representation is $ARB$), some direct calculations lead us  to 
+and defining the operators $A$ and $B$ by:
+\begin{align*}
+&B|0\rangle = |a| |2^{N}-1 \rangle + |b| |2^{N}-2\rangle + |c| |2^N-3\rangle, \\
+&A|2^N-1 \rangle = \frac{1}{|a|} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{|b|}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{|c|}|c\rangle.
+\end{align*}
+The rest of the operators $A$ and $B$ can be
+defined arbitrarily in any way such that they are unitary.
+Then, starting from the initial state $|0\rangle$
+and applying the circuit  of \fref{fig:1PR-circuit}, 
+some direct calculations lead us  to 
 the resulting curve of states
 of \eref{eq:curve-states}.
+To see it, notice that rewriting the expression of  $B|0\rangle$ by separating the
+first $N-1$ qubits from the last one,
+we have that $$B|0\rangle = |a| |2^{N-1}-1\rangle |1\rangle + |b| |2^{N-1}-1\rangle |0\rangle + |c| |2^{N-1}-2\rangle |1\rangle.$$
+Then, since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies
+to the first two terms of $B|0\rangle$ 
+and gives as a result
+$$
+RB|0\rangle =|a| e^{is} |2^{N-1}-1\rangle |1\rangle + |b| e^{-is} |2^{N-1}-1\rangle |0\rangle + |c| |2^{N-1}-2\rangle |1\rangle.
+$$
+Finally, applying $A$ as defined above to this state leads to the desired result.
 
@@
 \label{eq:vec}
-\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = \vec{c} + \vec{a} e^{is} + \vec{b} e^{-is},
+\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is} |a\rangle + e^{-is}|b\rangle,
 \end{eqnarray}
-where $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors in $\mathbb{C}^{2n}$ 
-and $|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2= 1$.
+where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states in  
+and $|a|^2+  |b|^2 + |c|^2= 1$.
 
@@
 Furthermore, we can construct other examples of 
-Pauli dynamical maps such that it
+Pauli dynamical maps such that they
 can be implemented with a 1PR circuit.
-To do it, we only need to choose the three vectors $\vec{a}, \vec{b},\vec{c}$
+To do it, we only need to choose the three states $|a\rangle, |b\rangle, |c\rangle$
 that satisfy the conditions of  \eref{eq:conditions-vecs}.
@@
 \begin{itemize}
-\item[1.] We first choose the norms $|\vec{a}|, |\vec{b}|, |\vec{c}|$
-such that $|\vec{a}|^2 + |\vec{b}|^2 + |\vec{c}|^2 = 1$. 
+\item[1.] We first choose the norms $|a|, |b|, |c|$
+such that $|a|^2 + |b|^2 + |c|^2 = 1$. 
 This can be done by selecting two angles
@@
 \begin{align*}
-|\vec{a}| = \sin \nu \cos \mu, \; |\vec{b}| = \sin \nu \sin \mu , \; |\vec{c}| = \cos \nu.
-\end{align*}
-\item[2.] We define $\vec{a'} = (|\vec{a}|,0,0,0),$ $\vec{b'} = (0,|\vec{b}|,0,0),$ $\vec{c'} = (0,0,|\vec{c}|,0)$.
+|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
+\end{align*}
+\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle |c| |2\rangle$.
 \item[3.] Finally, we choose a unitary matrix $V$
-and use it to define the vectors $\vec{a} = V \vec{a'}, \vec{b} = V \vec{b'}, \vec{c} = V \vec{c'}$.
-This way, since the primed vectors are orthogonal and their squared norms add up to one,
-so do the unprimed vectors and therefore 
+and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
+This way, since the primed states are orthogonal and their squared norms add up to one,
+so do the unprimed states and therefore 
 fulfill the conditions of  \eref{eq:conditions-vecs}. 
@@
 To do that, we ensure that the vectors also satisfy
-$\vec{a} + \vec{b} + \vec{c} = (e^{i \theta},0,0,0)$ with $\theta$ an arbitrary
+$|a\rangle + |b\rangle + |c\rangle = e^{i \theta}|0\rangle$ with $\theta$ an arbitrary
 real number.
 This way, when $s = 0$ in \eref{eq:vec}, the constructed state
-is $(e^{i \theta},0,0,0)$, which
+is $e^{i \theta}|0\rangle$, which
 corresponds with the identity channel.
@@
 To fulfill this additional condition,  we restrict the first row of
-$V$ to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
+$V$ writen as a matrix in 
+the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
 That way, 
 \begin{align*}
-\vec{a} + \vec{b} + \vec{c} = V (\vec{a'} + \vec{b'} + \vec{c'}) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
+|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
 \end{align*}

### 2023-05-29 main.tex
Más cambios
Correcciones

@@
 \label{eq: state}
+\text{Ancilla state =} 
 \sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
@@
 but with all details  explicitly shown.
-In said figure, the state 
+In said figure, the ancilla state
+of \eref{eq: state} can be taken to be
 $\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
 |10\rangle + \sqrt{k_{11}}|11\rangle$
-is created on the ancilla qubits with the help of three rotations of angles:
+and it is created on the ancilla qubits with the help of three rotations of angles:
 \begin{subequations}
 \begin{eqnarray}
-\theta_0 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
-\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
+\theta_0 &= &\arctan(\sqrt{k_{01}/k_{00}}) -
+\arctan(\sqrt{k_{11}/k_{10}}),
 \label{eq:angle1} \\ 
 \theta_1 &= &2 \arccos(\sqrt{k_{00} +
-k_{01}})
+k_{01}}),
 \label{eq:angle2} \\
-\theta_2 &= &\arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
-\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})
+\theta_2 &= &\arctan(\sqrt{k_{01}/k_{00}}) +
+\arctan(\sqrt{k_{11}/k_{10}}).
 \label{eq:angle3}
@@
 que quizá estén mas bonitas.}
+\tbnote{Ya puse la puntuación y lo puse en términos de arctan.
+La suma de arcotangentes se puede juntar en una 
+sola arctan, pero con un argumento que ya queda muy complicado y 
+creo que está mejor así.}
 
@@
 ancilla qubits and we use three rotations
-of angles given by \eref{eq:angle} to create the state $\sqrt{k_{00}}
-|00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
-|10\rangle + \sqrt{k_{11}}|11\rangle$
-on them.
+of angles given by \eref{eq:angle} to create the Ancilla State of
+of \eref{eq: state} for the two ancilla qubits.
 \cpnote{Creo qeu este seria el estado ecuacion 14, pero como qeuno está limpio. 
 Creo quepodemos nombrar ese estado y luego referirnos acá por el nobmre y la referencia 
-a la ecuación.}
-%and the state $b_{00} |00\rangle + b_{01} |01\rangle + b_{10}
-%|10\rangle + b_{11}|11\rangle$ is created on them with the help of three
-%rotations of angles $\theta_0 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) -
-%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$, $ \theta_1 = 2 \arccos(\sqrt{k_{00} +
-%k_{01}})$ and $ \theta_2 = \arg(\sqrt{k_{00}} + i \sqrt{k_{01}}) +
-%\arg(\sqrt{k_{10}} + i\sqrt{k_{11}})$.
+a la ecuación.} \tbnote{Ya}
 }
@@
 
-Using the quantum computers that IBM has available~\cite{Qiskit}, we sampled
-one-qubit Pauli channels and simulated them using the ibmq-lima quantum
-computer\cpnote{la computadora no la usamos para samplear sino solo para simular. Modificar
-la frase.}.  For each of these channels, we used quantum process
+We took a sample of one-qubit Pauli channels and
+used the ibmq-lima quantum computer that IBM has available~\cite{Qiskit}
+to simulate them. \cpnote{la computadora no la usamos para samplear sino solo para simular. Modificar
+la frase.}
+\tbnote{Ya.}  For each of these channels, we used quantum process
 tomography~\cite{Qiskit, Chuang:1996} to obtain the 
@@
 la $f$, pero no se menciona acá. Toca como que hacer que el párrafo gire alrededor de ella. }
-We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
-with the probability that one can distinguish two channels.
-% To perform this comparison, we used the diamond norm~\cite{Aharonov,Wilde},
-% which gives us a method of discriminating \cpnote{no solo discrimina... todas
-% las normas lo hacen, pero nos permite ver que tan parecidos son dos canales. 
-% Es como la fidelidad. Itera.} between quantum channels \cpnote{Tambien esta frase
-% no conecta bien con lo que sigue}.
-In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
-with probability $1/2$ each,
-and tries to guess which channel they received
-by applying it to a state $\rho$ and measuring the result.
-Then, the maximal probability of success (out of all possible states $\rho$) that
-the agent guesses correctly is~\cite{Benenti}:
-\begin{equation}
-\label{eq: probability-success}
-p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
-\end{equation}
-where $|| \cdot ||_{\diamond}$ is the diamond norm, defined by 
+
+\tbnote{Rediseño párrafo anterior: }
+{\color{orange}  We took a sample of one-qubit Pauli channels
+and evaluated their implementation on IBM's
+ibmq-lima quantum computer~\cite{Qiskit},
+as shown in \fref{fig:fids}. 
+For each of the channels sampled, we used 
+quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the 
+operator $\xi_I$ corresponding to the implementation of the
+circuit in the quantum computer. 
+Then, we compared $\xi_I$ with the theoretical 
+operator $\xi_T$ of the Pauli channel we wanted to implement.
+To see how close the operators $\xi_I$ and 
+$\xi_T$ are, we shall use the
+diamond distance~\cite{Aharonov,Wilde}, which is defined by}
+
+%We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
+%with the probability that one can distinguish two channels.
+%In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
+%with probability $1/2$ each,
+%and tries to guess which channel they received
+%by applying it to a state $\rho$ and measuring the result.
+%Then, the maximal probability of success (out of all possible states $\rho$) that
+%the agent guesses correctly is~\cite{Benenti}:
+%\begin{equation}
+%\label{eq: probability-success}
+%p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
+%\end{equation}
+%where $|| \cdot ||_{\diamond}$ is the diamond norm, defined by
+
 \begin{align*}
@@
 done over all density matrices $\rho$.
+{\color{orange} The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.}
 \cpnote{Esa definicion esta bonita y me gusta, pero supongo qeu no es asi somo la 
 calculas. } 
-
-Notice that if the channels are the same, then $p_{\succ}=1/2$. 
-This is expected because in this situation the agent
-has no way of distinguishing the channels and has no choice but to completely
-guess, which results in a probability of success of $1/2$.
-On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
-distinguishable.
+\tbnote{La calculo usando una función en la librería de Qiskit
+que se basa en la referencia que puse,
+pero la verdad no sé bien cómo funciona.}
+
+%Notice that if the channels are the same, then $p_{\succ}=1/2$. 
+%This is expected because in this situation the agent
+%has no way of distinguishing the channels and has no choice but to completely
+%guess, which results in a probability of success of $1/2$.
+%On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
+%distinguishable.
 \cpnote{Creo qeu el ejemplo debería ir con la $f$ que definamos, quizá pasando por la 
 norma diamante, o por la p succ. Eso si, si no la ocupamos (la psucc) tonces quitarla.}
+\tbnote{Va, ya puse directo con la $f$ y quité lo de psucc}
+
+{\color{orange} When the two channels are the same,
+the diamond distance has a value of $0$, while in the case that the channels
+are completely distingushable, the distance reaches its maximum value of $2$~\cite{Benenti}.
+For the analysis done in \fref{fig:fids}, we define a sort of ``diamond fidelity'' as:
+
+\begin{align}
+f = 1 - \dfrac{1}{2} ||\varepsilon_I - \varepsilon_T ||_{\diamond},
+\label{eq:diamond-fid}
+\end{align}
+which is a number between $0$ and $1$,
+with $1$ indicating that the channels are completely
+equal and $0$ the opposite.
+}
 % \cpnote{hummm ejemplo al menos para nosotros.} 
@@
 in \eref{eq: conditions-tetrahedron},
-we show in \fref{fig: fidelity one qubit} the maximal probabilities of
-success defined by \eref{eq: probability-success} for the channels
+we show in \fref{fig:fids} the diamond fidelity defined by \eref{eq:diamond-fid} for the channels
 analyzed. 
@@
 channel (that is close to the center of the tetrahedron)
-have a low $p_{\succ}$, while those 
-close to unitary channels have much higher $p_{\succ}$.
+have a high $f$, while those 
+close to unitary channels have much lower $f$.
 This means that channels closer to the 
@@
 alternativa en que puede quedar la figura.  Usé $2(1-p_{succ})$ en lugar de
-$p_{succ}$ para que se cumpla lo de que $0$ es lo peor y $1$ lo mejor.}}
+$p_{succ}$ para que se cumpla lo de que $0$ es lo peor y $1$ lo mejor.} Results of the diamond fidelities as defined in \eref{eq:diamond-fid} for a sample of Pauli channels in the tetrahedron.
+Notice that channels close to the center of the tetrahedron have high fidelities,
+while those close to the borders do not. 
+Moreover, we show the results for cuts of the tetrahedron at different values of $\tau_3$.}
+\label{fig:fids}
 \end{figure}
@@
 In general, producing this curve of states for $N$ qubits will require
-$2^N-1$ rotations parametrized by $p$\cpnote{De de donde sale este numero?},
+many rotations parametrized by $p$,
 such as the three rotations used for the ancilla
@@
 \begin{align*}
-\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1
+\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
 \end{align*}
@@
 \begin{align*}
-|\beta(p)\rangle = \left(\sqrt{1-p},\sqrt{p},0,0\right).
+|\beta(p)\rangle = \sqrt{1-p} |0\rangle +\sqrt{p} |1\rangle.
 \end{align*}
@@
 \begin{align*}
-|\beta(p) \rangle = e^{is} \left( \dfrac{1}{2}, - \dfrac{i}{2},0,0 \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2},0,0 \right),
+|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |0\rangle - \dfrac{i}{2} |1\rangle \right) + e^{-is} \left( \frac{1}{2} |0\rangle + \frac{i}{2} |1\rangle \right),
 \end{align*}
@@
 with $p \in [0,1]$. 
-Therefore, taking the $\beta_j$ to be real,
+Then, taking the $\beta_j$ to be real,
 the curve of states needed to create on the ancilla qubits is
 \begin{align*}
-|\beta(p) \rangle = \left( \sqrt{1-3p/4}, \sqrt{p/4}, \sqrt{p/4},\sqrt{p/4} \right).
+|\beta(p) \rangle = \sqrt{1-3p/4} |0\rangle + \sqrt{p/4} |1\rangle + \sqrt{p/4} |2 \rangle  + \sqrt{p/4} |3\rangle.
 \end{align*}
@@
 \begin{align*}
-|\beta(p)\rangle = e^{is} \left( \dfrac{1}{2}, \dfrac{-i}{2\sqrt{3}},\dfrac{-i}{2\sqrt{3}},\dfrac{-i}{2\sqrt{3}} \right) + e^{-is} \left( \dfrac{1}{2}, \dfrac{i}{2\sqrt{3}},\dfrac{i}{2\sqrt{3}},\dfrac{i}{2\sqrt{3}}\right)
+|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |0\rangle - \dfrac{i}{2\sqrt{3}} |1\rangle - \dfrac{i}{2\sqrt{3}} |2 \rangle - \dfrac{i}{2\sqrt{3}} |3\rangle \right) \\
+& + e^{-is} \left( \dfrac{1}{2} |0\rangle + \dfrac{i}{2\sqrt{3}} |1\rangle + \dfrac{i}{2\sqrt{3}} |2\rangle + \dfrac{i}{2\sqrt{3}} |3 \rangle \right),
 \end{align*}
@@
 \begin{eqnarray}
-|\beta(p)\rangle = \left(\dfrac{1}{2} (1-p) , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2} \sqrt{1-p^2} , \dfrac{1}{2}(1+p) \right).
+|\beta(p)\rangle = \dfrac{1}{2} (1-p) |0\rangle + \dfrac{1}{2} \sqrt{1-p^2} |1\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |2\rangle +  \dfrac{1}{2}(1+p) |3\rangle.
 \end{eqnarray}
@@
 \begin{align*}
-|\beta(p)\rangle = \left( \dfrac{1}{2},0,0, \dfrac{1}{2} \right) + e^{is} \left( \dfrac{i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{-i}{4} \right) + e^{-is}  \left( \dfrac{-i}{4}, \dfrac{1}{4}, \dfrac{1}{4}, \dfrac{i}{4} \right),
+|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|0\rangle + \dfrac{1}{2} |3\rangle \right) + e^{is} \left( \dfrac{i}{4}|0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle - \dfrac{i}{4} |3\rangle \right) \\
+& + e^{-is}  \left( \dfrac{-i}{4} |0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle + \dfrac{i}{4} |3\rangle \right),
 \end{align*}
@@
 \end{align*}
-\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle |c| |2\rangle$.
+\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle = |c| |2\rangle$.
 \item[3.] Finally, we choose a unitary matrix $V$

### 2023-06-01 main.tex
added super-widget 2.0.

@@
 \end{subequations}
-\cpnote{Acá te falto la puntuación en las ecuaciones. Porotro lado me gustaría ver la 
-forma que tienen las ecuaciones en exponenciales o en funciones trigonometricas
-que quizá estén mas bonitas.}
-\tbnote{Ya puse la puntuación y lo puse en términos de arctan.
-La suma de arcotangentes se puede juntar en una 
-sola arctan, pero con un argumento que ya queda muy complicado y 
-creo que está mejor así.}
+\cpnote{Quisiera ver las ecuaciones sin la teheta despejada. Por ejemplo la de theta 1
+es $\cos^2 (\theta_1/2) = k00 + k01$ bueno mas bonita, pero asi. Luego las de tehta0 y theta2 
+quizá tambien sean sencillas. Las quiero ver!!!}
 
@@
 used the ibmq-lima quantum computer that IBM has available~\cite{Qiskit}
-to simulate them. \cpnote{la computadora no la usamos para samplear sino solo para simular. Modificar
-la frase.}
-\tbnote{Ya.}  For each of these channels, we used quantum process
+to simulate them. For each of these channels, we used quantum process
 tomography~\cite{Qiskit, Chuang:1996} to obtain the 
@@
 
-\cpnote{Toca rediseñar este parrafo mejor. La figura que al final nos interesa es 
-la $f$, pero no se menciona acá. Toca como que hacer que el párrafo gire alrededor de ella. }
-
-\tbnote{Rediseño párrafo anterior: }
-{\color{orange}  We took a sample of one-qubit Pauli channels
+% \cpnote{Toca rediseñar este parrafo mejor. La figura que al final nos interesa
+% es la $f$, pero no se menciona acá. Toca como que hacer que el párrafo gire
+% alrededor de ella. }
+
+% \tbnote{Rediseño párrafo anterior: }
+% {\color{orange}  
+We took a sample of one-qubit Pauli channels
 and evaluated their implementation on IBM's
@@
 $\xi_T$ are, we shall use the
-diamond distance~\cite{Aharonov,Wilde}, which is defined by}
-
-%We shall use the diamond norm~\cite{Aharonov,Wilde}, which has a simple physical meaning related
-%with the probability that one can distinguish two channels.
-%In particular, suppose an agent is given one of the channels $\xi_I$, $\xi_T$
-%with probability $1/2$ each,
-%and tries to guess which channel they received
-%by applying it to a state $\rho$ and measuring the result.
-%Then, the maximal probability of success (out of all possible states $\rho$) that
-%the agent guesses correctly is~\cite{Benenti}:
-%\begin{equation}
-%\label{eq: probability-success}
-%p_{\succ} = \dfrac{1}{2}+ \dfrac{1}{4} ||\xi_I - \xi_T ||_{\diamond},
-%\end{equation}
-%where $|| \cdot ||_{\diamond}$ is the diamond norm, defined by
-
-\begin{align*}
+diamond distance~\cite{Aharonov,Wilde}, which is defined by
+\begin{equation}
 ||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
-\end{align*}
+\end{equation}
 with $I$ the identity map,
@@
 done over all density matrices $\rho$.
-{\color{orange} The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.}
-\cpnote{Esa definicion esta bonita y me gusta, pero supongo qeu no es asi somo la 
-calculas. } 
-\tbnote{La calculo usando una función en la librería de Qiskit
-que se basa en la referencia que puse,
-pero la verdad no sé bien cómo funciona.}
-
-%Notice that if the channels are the same, then $p_{\succ}=1/2$. 
-%This is expected because in this situation the agent
-%has no way of distinguishing the channels and has no choice but to completely
-%guess, which results in a probability of success of $1/2$.
-%On the other hand, $p_{\succ}=1$ indicates that the channels are perfectly
-%distinguishable.
-\cpnote{Creo qeu el ejemplo debería ir con la $f$ que definamos, quizá pasando por la 
-norma diamante, o por la p succ. Eso si, si no la ocupamos (la psucc) tonces quitarla.}
-\tbnote{Va, ya puse directo con la $f$ y quité lo de psucc}
-
-{\color{orange} When the two channels are the same,
+The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.
+When the two channels are the same,
 the diamond distance has a value of $0$, while in the case that the channels
@@
 For the analysis done in \fref{fig:fids}, we define a sort of ``diamond fidelity'' as: 
-
-\begin{align}
+\begin{equation}
 f = 1 - \dfrac{1}{2} ||\varepsilon_I - \varepsilon_T ||_{\diamond},
 \label{eq:diamond-fid}
-\end{align}
-which is a number between $0$ and $1$,
-with $1$ indicating that the channels are completely
-equal and $0$ the opposite.
-}
+\end{equation}
+which ranges from $0$, when the channels have a maximum distance, to  $1$,
+when they are exactly equal.
+
 % \cpnote{hummm ejemplo al menos para nosotros.} 
@@
 when trying to simulate depolarization but it is 
-when simulating unitary processes.
+when simulating unitary processes. \cpnote{Tambien creo qeu debemos comentar que nuestra 
+simulación para operaciones unitarias no es optima, porque usamos un monton de compuertas 
+y además operaciones doblemente controladas.}
 \cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
@@
 
-\begin{figure}
+\begin{figure} % {{{
 \centering
@@
 \end{subfigure}
-\caption{\cpnote{porfa escribe el caption.} \tbnote{Aquí está una forma
-alternativa en que puede quedar la figura.  Usé $2(1-p_{succ})$ en lugar de
-$p_{succ}$ para que se cumpla lo de que $0$ es lo peor y $1$ lo mejor.} Results of the diamond fidelities as defined in \eref{eq:diamond-fid} for a sample of Pauli channels in the tetrahedron.
-Notice that channels close to the center of the tetrahedron have high fidelities,
-while those close to the borders do not. 
-Moreover, we show the results for cuts of the tetrahedron at different values of $\tau_3$.}
+\caption{Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
+for a sample of Pauli channels in the tetrahedron.  Notice that channels close
+to the center of the tetrahedron have high fidelities, while those close to the
+borders do not.  Moreover, we show the results for cuts of the tetrahedron at
+different values of $\tau_3$.}
 \label{fig:fids}
-\end{figure}
+\end{figure} % }}}
 
@@
 \textbf{Proof:} 
-\cpnote{Discutir la prueba, se ve demasiado larga y aburrida}
-\tbnote{La cambié un poco, pero no sé qué más cambiarle.}
+\cpnote{Sugiero cambiar la a gargoleada por una a con gorro o con tilde. No se 
+usa asi cambiar de fuente.}
 We can conclude from theorem 1 that $U=ARB$,
@@
 \begin{align}
-B|j\rangle = \sum_{k \in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right),
+B|j\rangle = 
+   \sum_{k \in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle 
+                                     + B_{2k+1,j} |k \rangle |1\rangle  \right) 
+   + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  
+                                      + B_{2k+1,j} |k \rangle |1\rangle  \right).
 \end{align}
+
+\cpnote{Separo el parrafo par auqe cada matriz tenga como su propio espacio.}
 Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
@@
 $|\mathfrak{c}^j\rangle =\sum_{k \not\in \mathcal{C}}\big( B_{2k,j} |k\rangle|0\rangle+$ $B_{2k+1,j} |k \rangle |1\rangle  \big)$.
-\cpnote{Preferira que tuvieramos que los kets fisicos tuvieran la notacion de
-ket. Intenta modificarlo asi y luego sigo con la prueba. Ya no me está pareciendo 
-tan latosa. Trata tambien que los nombres que usas sean como consistentes o tengan 
-algo que decir de su contenido.} \tbnote{Ya hice unos cambios}
+\cpnote{Acá puedes usar align. Creo que es mucho para dejarlas en el texto. Recuerda la puntuacion. 
+Me está gustando mucho la explicacion. Simple y clara. }
 These states are clearly orthogonal because they are each linear combinations of different 
@@
  $\;$ \\
+
+\cpnote{Acá voy}
 
@@
 % }}}
+
 \section{1PR circuit for a Pauli map} % {{{

### 2023-06-02 main.tex
Algunos cambios

@@
 \section{Introduction} % {{{
-\tbnote{Poner intro luego}
+\tbnote{Poner intro luego. Ver libro de writing science}
 
@@
 quizá tambien sean sencillas. Las quiero ver!!!}
+\tbnote{Ah, ya entiendo. Las única forma que veo de escribirlas es:
+\begin{align*}
+\tan \theta_0 = \dfrac{\sqrt{k_{01}/k_{00}} - \sqrt{k_{11}/k_{10}}}{1+\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}}} \\
+\tan \theta_2 = \dfrac{\sqrt{k_{01}/k_{00}} + \sqrt{k_{11}/k_{10}}}{1-\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}}}
+\end{align*}
+No veo cómo escribir ecuaciones de las thetas no despejadas que sean sencillas.
+}
 
@@
 y además operaciones doblemente controladas.}
+\tbnote{Algo como: }
+{\color{orange} Moreover, the algorithm of \fref{fig: circuit-pauli-1} is not optimal for unitary channels 
+(that is, the channels corresponding to the vertices of the tetrahedron). 
+These straightforward channels could be accomplished more efficiently by simply applying the corresponding Pauli operation directly.
+Nevertheless, due to its general design to accommodate any Pauli channel, the algorithm employs numerous quantum gates even in such scenarios.}
 \cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
@@
 \cpnote{Sugiero cambiar la a gargoleada por una a con gorro o con tilde. No se 
-usa asi cambiar de fuente.}
+usa asi cambiar de fuente.} \tbnote{Va, listo}
 We can conclude from theorem 1 that $U=ARB$,
@@
 
-\cpnote{Separo el parrafo par auqe cada matriz tenga como su propio espacio.}
+\cpnote{Separo el parrafo par auqe cada matriz tenga como su propio espacio.} \tbnote{Va, excelente.}
 Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
@@
 + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
-& = e^{-is} |\mathfrak{b}^{j}\rangle + e^{is} |\mathfrak{a}^j\rangle + |\mathfrak{c}^j\rangle
+& = e^{-is} |\tilde{b}^{j}\rangle + e^{is} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle
 \end{align}
-where we defined $|\mathfrak{a}^j \rangle = \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle$,
-$|\mathfrak{b}^j\rangle = \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle$,
-$|\mathfrak{c}^j\rangle =\sum_{k \not\in \mathcal{C}}\big( B_{2k,j} |k\rangle|0\rangle+$ $B_{2k+1,j} |k \rangle |1\rangle  \big)$.
+where we defined
+\begin{align*}
+|\tilde{a}^j \rangle &= \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle,\\
+|\tilde{b}^j\rangle &= \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle,\\
+|\tilde{c}^j\rangle &= \sum_{k \not\in \mathcal{C}}\left( B_{2k,j} |k\rangle|0\rangle+ B_{2k+1,j} |k \rangle |1\rangle  \right).
+\end{align*}
 \cpnote{Acá puedes usar align. Creo que es mucho para dejarlas en el texto. Recuerda la puntuacion. 
 Me está gustando mucho la explicacion. Simple y clara. }
+\tbnote{Listo.}
 These states are clearly orthogonal because they are each linear combinations of different 
 orthogonal states of the computational basis. 
-Moreover, they satisfy  $|\mathfrak{a}^j|^2 + |\mathfrak{b}^j|^2 + |\mathfrak{c}^j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
+Moreover, they satisfy  $|\tilde{a}^j|^2 + |\tilde{b}^j|^2 + |\tilde{c}^j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
 which is unitary.
@@
 \begin{eqnarray}
-U|j\rangle = ARB|j\rangle = e^{-is} A |\mathfrak{a}^j\rangle + e^{is} A |\mathfrak{b}^j\rangle + A |\mathfrak{c}^j\rangle = e^{-is} |a^j\rangle + e^{is} |b^j\rangle + |c^j\rangle,
+U|j\rangle = ARB|j\rangle = e^{-is} A |\tilde{a}^j\rangle + e^{is} A |\tilde{b}^j\rangle + A |\tilde{c}^j\rangle = e^{-is} |a^j\rangle + e^{is} |b^j\rangle + |c^j\rangle,
 \end{eqnarray}
-where $|a^j\rangle = A |\mathfrak{a}^j\rangle, |b^j\rangle = A |\mathfrak{b}^j\rangle, |c^j\rangle = A |\mathfrak{c}^j\rangle$ are still orthogonal
+where $|a^j\rangle = A |\tilde{a}^j\rangle, |b^j\rangle = A |\tilde{b}^j\rangle, |c^j\rangle = A |\tilde{c}^j\rangle$ are still orthogonal
 states that satisfy $|a|^2 + |b|^2 + |c|^2 = 1$ because $A$ is unitary. $\blacksquare$  \\
@@
 implementable with a 1PR circuit, which are plotted
-in \fref{fig:curves}.
-
-\begin{figure} % {{{
+in \fref{fig:curves1}.
+
+\begin{figure}
+\captionsetup[subfigure]{justification=centering}
 \centering
-\includegraphics{images/curvas.png}
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=.9\linewidth]{images/curvas.png}
+   \caption{}
+  \label{fig:curves1}
+\end{subfigure}%
+\begin{subfigure}{.45\textwidth}
+  \centering
+  \includegraphics[width=.9\linewidth]{images/curvas-azar.png}
+  \caption{}
+  \label{fig:curves2}
+\end{subfigure}
 \caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
-The curves painted in the tetrahedron
+The curves painted in these tetrahedrons
 represent Pauli dynamical maps that can be implemented with 1PR circuits.
-In particular, the depolarizing (purple), bit flip (blue),
+(a) shows the dynamical maps mentioned in the main 
+text, which are: depolarizing (purple), bit flip (blue),
 phase flip (green), bit-phase flip (red)
-and parabolic (orange). }
+and parabolic (orange).
+(b) shows dynamical maps selected at random that can be implemented with 1PR 
+circuits.}
 \label{fig:curves}
-\end{figure} % }}}
+\end{figure}
 
@@
 we plot four Pauli dynamical maps 
-that can be implemented with a 1PR circuit in \fref{fig:curves-random}.
+that can be implemented with a 1PR circuit in \fref{fig:curves2}.
 These maps where constructed with the additional condition
@@
 
-\begin{figure} % {{{
-\centering
-\includegraphics{images/curvas-azar.png}
-\caption{{\bf Random Pauli dynamical maps that can be implemented with a 1PR circuit.}
-The curves painted in the tetrahedron
-represent Pauli dynamical maps that can be implemented with 1PR circuits
-that were selected at random using the procedure detailed before.}
-\label{fig:curves-random}
-\end{figure} % }}}
-
-%\textbf{Puntos:}
-%\begin{itemize}
-%\item Use the last theorem to conclude directly which maps can be created using an 1PR circuit.
-%\item \textbf{Examples:} Show examples that satisfy these conditions: Bit-Flip, parabolic maps, etc. 
-%and an example that doesn't satisfy the conditions (ejemplo está en la tesis).
-%\end{itemize}
-% }}}
-
 \section{Conclusion} % {{{
-
-CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
-Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna.
-Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-Nam condimentum sem eget mollis euismod.
-Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex.
-Nunc est dui, sodales sed mauris nec, auctor sagittis leo.
-Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor.
-For more information, see \nameref{S1_Appendix}.
+\tbnote{Poner luego}
 % }}}
@@
 
+\tbnote{Ver qué se debe de poner aquí según el template y también arreglar las imágenes de acuerdo a él.}
 % Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.

### 2023-06-02 main.tex
Reset error count between rows. herpderp

@@
 system is uniquely associated with a point in a unit sphere.
-% \cpnote{explicar un poco mejor. Me parece que para el publico vale 
-% la pena ser un poco mas explicito. pero no estoy muy seguro.}
 
@@
 % produce the highest 
-% \cpnote{Quizá en una frase poner el resultado aca o ampliar
-% tantito} \tbnote{Va, agregué lo siguiente: 
-% We conclude that the circuit performs optimally for channels  in proximity to the
-% completely depolarizing channel but
-% it is deficient close to unitary channels.}
 % }}} 
@@
 \label{subsec: Description of the circuit}
-
-% \cpnote{Yo abriría este parrafo con una frase que de la idea muy general. Decir 
-% algo asi como que vamos a crear un estado conque contenga a las $k$s 
-% como coeficientes y leugo controlar la aplicación de los Pauli strings. Luego
-% ya dar los detalles. Así incluso mas escueto de lo que pongo. Por ejemplo:
-% To design the circiot that implements 13, we construct a state that incorportes
-% probabilities $k$ and subsequently apply controlled operation. In particular... }
-% \cpnote{No me gusta como está organizado este parrafo. Le puedes dar una iterada?}
-% \tbnote{Propongo el párrafo en naranja para sustituirlo}
 
@@
 \cdots |\gamma_N\rangle$.
-% \cpnote{La primera frase es cierta, pero no le veo el sentido acá. Trata de reformular el parrafo 
-% de nuevo. Croe que el ``This means'' definitivamente no va y es el que le da un sentido ``raro''. 
-% Itera (quizá solo quitando esas dos palabras)} \tbnote{Concuerdo, quité eso.}
 When measured in the computational basis, the state given in \eref{eq: state}
@@
 \begin{align*}
-\tan \theta_0 = \dfrac{\sqrt{k_{01}/k_{00}} - \sqrt{k_{11}/k_{10}}}{1+\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}}} \\
-\tan \theta_2 = \dfrac{\sqrt{k_{01}/k_{00}} + \sqrt{k_{11}/k_{10}}}{1-\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}}}
+\tan \theta_0 = \dfrac{\sqrt{k_{01}/k_{00}} - \sqrt{k_{11}/k_{10} }}{1+\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }} \\
+\tan \theta_2 = \dfrac{\sqrt{k_{01}/k_{00}} + \sqrt{k_{11}/k_{10} }}{1-\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }}
 \end{align*}
@@
 \caption{
-% \cpnote{ No me gusta que esté tan cargado de ecuaciones el caption. Metelas en
-% el lugar apropiado en el texto} \tbnote{Lo pasé al texto}
 {\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
@@
 of \eref{eq: state} for the two ancilla qubits.
-\cpnote{Creo qeu este seria el estado ecuacion 14, pero como qeuno está limpio. 
-Creo quepodemos nombrar ese estado y luego referirnos acá por el nobmre y la referencia 
-a la ecuación.} \tbnote{Ya}
 }
@@
 
-% \cpnote{Toca rediseñar este parrafo mejor. La figura que al final nos interesa
-% es la $f$, pero no se menciona acá. Toca como que hacer que el párrafo gire
-% alrededor de ella. }
-
-% \tbnote{Rediseño párrafo anterior: }
-% {\color{orange}  
 We took a sample of one-qubit Pauli channels
@@
 when they are exactly equal.
-
-% \cpnote{hummm ejemplo al menos para nosotros.} 
-% \tbnote{Un ejemplo que comprobé es considerar el canal que aplica $\sigma_x$ y 
-% el que aplica $\sigma_z$ y tienen $p_{\succ}=1$.
-% De hecho, al tomar dos canales que consistan en aplicar $\sigma_i$ y $\sigma_j$ 
-% (para $i\neq j$), se cumple esto.
-% También quería ejemplos no unitarios, pero no encontré.}
 
@@
 \textbf{Proof:} 
-\cpnote{Sugiero cambiar la a gargoleada por una a con gorro o con tilde. No se 
-usa asi cambiar de fuente.} \tbnote{Va, listo}
 We can conclude from theorem 1 that $U=ARB$,
@@
 
-\cpnote{Separo el parrafo par auqe cada matriz tenga como su propio espacio.} \tbnote{Va, excelente.}
 Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
@@
 \end{align*}
-\cpnote{Acá puedes usar align. Creo que es mucho para dejarlas en el texto. Recuerda la puntuacion. 
-Me está gustando mucho la explicacion. Simple y clara. }
-\tbnote{Listo.}
 These states are clearly orthogonal because they are each linear combinations of different 
@@
 
-\cpnote{Acá voy}
-
 This theorem implies that starting from the state $|0\rangle$ (or any 
-other starting state),
+other state),
 the only curves of states we could expect to create
-with a 1PR circuit are those of the form $U|0\rangle$, that is, curves such as:
+with a 1PR circuit are those of the form 
 \begin{equation}
@@
 \begin{equation}
-|a|^2 + |b|^2 + |c|^2 = 1  \; \text{and} \; |a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
+|a|^2 + |b|^2 + |c|^2 = 1,  \quad
+\langle a |b\rangle =
+\langle a |c\rangle =
+\langle b |c\rangle = 0
+% , |b\rangle, |c\rangle \; \text{orthogonal states},
+%  \text{and} \; |a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
 \label{eq:conditions-vecs}
@@
 and $s = s(p)$ a function of $p$.
+\cpnote{Es un poco confusa la notacion. Hablas de la norma de a con $|a|$, pero ahi parece
+que $a$ es un vector. Sugiero cambiar a $\langle a | a \rangle$ o algo asi sin cargar mucho
+la notacion. }
+\cpnote{Tambien siento qeu las palabras son un poco raras. Sugiero pasarlo por Chatgpt y 
+luego tunearlo (todo este parrafo). Avisame cuando quede eso!}
 Furthermore, given a curve of states as the one in
@@
 
+% }}}
 \section{Conclusion} % {{{

### 2023-06-05 main.tex
Correcciones

@@
 \section{Introduction} % {{{
-\tbnote{Poner intro luego. Ver libro de writing science}
+\tbnote{versión muy preliminar de la intro, para ir teniendo algo escrito de una vez. }\\
+
+Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
+with a recent particular interest in simulating the evolution of open systems, 
+which are described by the theory of quantum channels~\cite{cleve,Zanetti,Xin,Wei}. 
+Among the various types of quantum channels for a system of qubits, 
+Pauli channels hold special significance due to their simplicity 
+and relevance in the context of quantum computing~\cite{Zbigniew,geometry}, 
+as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.
+
+In this article, our primary objective is to present a 
+quantum algorithm capable of simulating Pauli channels on quantum computers, 
+and we demonstrate its implementation using IBM's quantum computers. 
+This algorithm is designed to simulate any Pauli channel on a system of $N$ qubits,
+and works by utilizing $2N$ ancilla qubits.
+
+Expanding beyond discrete Pauli channels,
+we introduce the concept of Pauli dynamical maps, 
+which are defined as a continuous parametrization of
+$N$-qubit Pauli channels. 
+Consequently, we adapt the algorithm developed for Pauli channels 
+to accommodate these dynamical maps by employing a 
+parametrized quantum circuit, that is, 
+a quantum circuit in which some of the
+ operations depend on a variable parameter~\cite{cerezo}.
+
+The investigation of parametrized quantum
+circuits holds extensive importance, 
+as they find applications in quantum machine learning~\cite{Benedetti}
+and describe general quantum transformations dependent on a parameter. Substantial research has been 
+devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}. 
+In this article, we contribute to this body of work by establishing theorem \ref{theorem2},
+which outlines the types of transformations that 
+can be done using a parametrized quantum with the condition that only one
+ single-qubit operation in the circuit may depend on the parameter. 
+We explicitly find the mathematical conditions for these types of
+transformations and conclude about which 
+Pauli dynamical maps can be done with them.
 
@@
 
+\tbnote{Obteniendo el seno y coseno de estos ángulos tampoco se 
+consigue algo mucho mejor:
+\begin{align*}
+\cos \theta_0 = \dfrac{\sqrt{k_{00} k_{10}} + \sqrt{k_{01} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}} \\
+\sin \theta_0 =  \dfrac{\sqrt{k_{01} k_{10}} - \sqrt{k_{00} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}}  \\
+\cos \theta_2 = \sqrt{\dfrac{k_{00}k_{10}}{(k_{00}+k_{01})(k_{10}+k_{11})}} \left( -1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right) \\
+\sin \theta_2 =  - \sqrt{\dfrac{k_{00}k_{10} + k_{01}k_{11} - 2 \sqrt{k_{00} k_{01} k_{10} k_{11}}}{(k_{00} + k_{01}) (k_{10} + k_{11})}} \left(\sqrt{\dfrac{k_{01}}{k_{00}}} + \sqrt{\dfrac{k_{11}}{k_{10}}} \right) \left(-1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right)^{-1}
+\end{align*}
+Probé combinar estas cantidades de diferentes formas, pero ninguna se simplificaba.}
+
 \begin{figure} % {{{
@@
 \begin{theorem}
+\label{theorem2}
 Consider a 1PR circuit of $N$ qubits
@@
 \end{align*}
-with $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $|a^j|^2 + |b^j|^2 + |c^j|^2 = 1$.
+with $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
+c^j|c^j \rangle = 1$.
 \end{theorem}
@@
 orthogonal states of the computational basis. 
-Moreover, they satisfy  $|\tilde{a}^j|^2 + |\tilde{b}^j|^2 + |\tilde{c}^j|^2 = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
+Moreover, they satisfy  $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle c^j| c^j\rangle = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
 which is unitary.
@@
 where $|a^j\rangle = A |\tilde{a}^j\rangle, |b^j\rangle = A |\tilde{b}^j\rangle, |c^j\rangle = A |\tilde{c}^j\rangle$ are still orthogonal
-states that satisfy $|a|^2 + |b|^2 + |c|^2 = 1$ because $A$ is unitary. $\blacksquare$  \\
+states that satisfy $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$ because $A$ is unitary. $\blacksquare$  \\
  $\;$ \\
 
-This theorem implies that starting from the state $|0\rangle$ (or any 
-other state),
-the only curves of states we could expect to create
-with a 1PR circuit are those of the form 
+This theorem implies that when starting from the state $|0\rangle$ 
+or any other initial state, the only possible curves of states that can be 
+created using a 1PR circuit are of the following form:
 \begin{equation}
@@
 \end{equation}
-with 
+with conditions defined by the equations: 
 \begin{equation}
-|a|^2 + |b|^2 + |c|^2 = 1,  \quad
+\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1,  \quad
 \langle a |b\rangle =
@@
 % , |b\rangle, |c\rangle \; \text{orthogonal states},
-%  \text{and} \; |a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
+%  \text{and} \; a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
 \label{eq:conditions-vecs}
 \end{equation}
-and $s = s(p)$ a function of $p$.
+where $s = s(p)$ is a function of $p$. 
 \cpnote{Es un poco confusa la notacion. Hablas de la norma de a con $|a|$, pero ahi parece
 que $a$ es un vector. Sugiero cambiar a $\langle a | a \rangle$ o algo asi sin cargar mucho
-la notacion. }
+la notacion. } \tbnote{Va, concuerdo, listo}
 \cpnote{Tambien siento qeu las palabras son un poco raras. Sugiero pasarlo por Chatgpt y 
-luego tunearlo (todo este parrafo). Avisame cuando quede eso!}
-Furthermore, given a curve of states as the one in
-\eref{eq:curve-states}, we can always construct a 1PR circuit to create it.
-One way of doing it, is to use the circuit of \fref{fig:1PR-circuit}, setting the parametrized
-rotation $R$ on the last qubit to be controlled by all the other qubits
-and defining the operators $A$ and $B$ by:
-\begin{align*}
-&B|0\rangle = |a| |2^{N}-1 \rangle + |b| |2^{N}-2\rangle + |c| |2^N-3\rangle, \\
-&A|2^N-1 \rangle = \frac{1}{|a|} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{|b|}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{|c|}|c\rangle.
-\end{align*}
-The rest of the operators $A$ and $B$ can be
-defined arbitrarily in any way such that they are unitary.
-Then, starting from the initial state $|0\rangle$
-and applying the circuit  of \fref{fig:1PR-circuit}, 
-some direct calculations lead us  to 
-the resulting curve of states
-of \eref{eq:curve-states}.
-To see it, notice that rewriting the expression of  $B|0\rangle$ by separating the
-first $N-1$ qubits from the last one,
-we have that $$B|0\rangle = |a| |2^{N-1}-1\rangle |1\rangle + |b| |2^{N-1}-1\rangle |0\rangle + |c| |2^{N-1}-2\rangle |1\rangle.$$
-Then, since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies
-to the first two terms of $B|0\rangle$ 
-and gives as a result
+luego tunearlo (todo este parrafo). Avisame cuando quede eso!} \tbnote{Ya}
+
+Moreover, it is possible to construct a 1PR circuit to generate any given curve of 
+states described by \eref{eq:curve-states}. 
+One approach to achieve this is by utilizing the circuit 
+depicted in \fref{fig:1PR-circuit}, 
+with the parametrized rotation $R$ applied to the last qubit controlled by all the 
+other qubits. The operators $A$ and $B$ can be defined as follows:
+\begin{align*}
+&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \\
+&A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
+\end{align*}
+The rest of the operators $A$ and $B$ can be defined
+in any arbitrary manner as long as they are unitary.
+By starting from the initial state $|0\rangle$ and 
+applying the circuit shown in \fref{fig:1PR-circuit}, straightforward calculations 
+lead us to obtain the resulting curve of states described in Equation (\ref{eq:curve-states}).
+
+To see it, we can rewrite the expression of $B|0\rangle$ by 
+separating the first $N-1$ qubits from the last one:
+$$B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.$$
+Since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$. As a result, we obtain:
+
 $$
-RB|0\rangle =|a| e^{is} |2^{N-1}-1\rangle |1\rangle + |b| e^{-is} |2^{N-1}-1\rangle |0\rangle + |c| |2^{N-1}-2\rangle |1\rangle.
+RB|0\rangle =\sqrt{\langle a | a \rangle} e^{is} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} e^{-is} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.
 $$
-Finally, applying $A$ as defined above to this state leads to the desired result.
+Finally, applying the defined operator $A$ to this state yields the desired result.
 
@@
 \end{eqnarray}
-where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states in  
-and $|a|^2+  |b|^2 + |c|^2= 1$.
+where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states  
+and $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$.
 
@@
 \item[1.] We first choose the norms $|a|, |b|, |c|$
-such that $|a|^2 + |b|^2 + |c|^2 = 1$. 
+such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
 This can be done by selecting two angles
@@
 \section{Conclusion} % {{{
-\tbnote{Poner luego}
+\tbnote{Primera versión para ir teniendo algo escrito }\\
+
+In this work, we have undertaken the study of Pauli channels on systems of $N$ qubits, 
+proposing an algorithm capable of implementing them on a quantum computer
+with the assistance of $2N$ ancilla qubits.
+ By running this algorithm on one of IBM's quantum computers, 
+we observed that the fidelity of the simulated channels was highest for those 
+closely resembling the totally depolarizing channel, 
+and decreased as the channels approached unitary behavior. 
+This performance can be attributed to the limitations and susceptibility to errors 
+inherent in current quantum computers. 
+Furthermore, being as general as it is,
+the algorithm isn’t efficient for unitary channels, 
+which can be done in a much simpler manner.
+
+Additionally, we extended our investigation 
+to encompass Pauli dynamical maps by leveraging the concept of a parametrized quantum circuit. 
+Through this extension, we determined the mathematical conditions under which a
+parametrized quantum circuit requires only one single-qubit 
+rotation dependent on the parameter. Notably, theorem \ref{theorem2} establishes these
+ conditions as applicable to any parametrized quantum circuit, 
+ providing a general framework to describe the type of algorithms achievable using 
+only one single-qubit parametrized rotation.
 % }}}

### 2023-06-05 main.tex
Cambios intro y angulos

@@
 \\
-Tomás Basile\textsuperscript{1\Yinyang},
+Tomás Basile\textsuperscript{1,2\Yinyang},
 Carlos Pineda\textsuperscript{2*\Yinyang},
@@
 \section{Introduction} % {{{
+
+Puntos hechos en el artículo:
+\begin{itemize}
+\item Propuesta de algoritmo para canal es de Pauli de N qubits y su simulación en compus cuánticas
+\item Condiciones para que un circuito parametrizado use una sola rotación parametrizada. En particular luego aplicadas al algoritmo para mapas dinámicos de Pauli.
+\end{itemize}
+
 \tbnote{versión muy preliminar de la intro, para ir teniendo algo escrito de una vez. }\\
@@
 
-In this article, our primary objective is to present a 
+On the other hand, we shall also work with parametrized quantum circuits, that is,  
+a quantum circuit in which some of the operations depend on a variable parameter~\cite{cerezo}. 
+The investigation of parametrized quantum
+circuits holds extensive importance, 
+as they find applications in quantum machine learning~\cite{Benedetti}
+and describe general quantum transformations dependent on a parameter. Substantial research has been 
+devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}.
+
+In this article, our first objective is to present a 
 quantum algorithm capable of simulating Pauli channels on quantum computers, 
@@
 to accommodate these dynamical maps by employing a 
-parametrized quantum circuit, that is, 
-a quantum circuit in which some of the
- operations depend on a variable parameter~\cite{cerezo}.
-
-The investigation of parametrized quantum
-circuits holds extensive importance, 
-as they find applications in quantum machine learning~\cite{Benedetti}
-and describe general quantum transformations dependent on a parameter. Substantial research has been 
-devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}. 
-In this article, we contribute to this body of work by establishing theorem \ref{theorem2},
-which outlines the types of transformations that 
-can be done using a parametrized quantum with the condition that only one
+parametrized quantum circuit. 
+We contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2}.
+This theorem outlines the types of transformations that 
+can be done using a parametrized quantum circuit with the condition that only one
  single-qubit operation in the circuit may depend on the parameter.
@@
 
+The paper is organized as follows: In section \ref{sec: Pauli Channels} 
+we give the definition of quantum channels and focus particularly on Pauli channels for systems of
+$N$ qubits. 
+In section \ref{sec: Circuit for a Pauli Channel} we show the proposed circuit 
+to implement a Pauli channel of $N$ qubits in a quantum computer. 
+Furthermore, we simulate it on IBM’s computers for the special case of $N=1$
+and obtain the fidelity of this implementation.  
+In section \ref{sec: 1PR Circuits} we shift our focus to parametrized quantum circuits with the goal of
+generalizing the circuit for Pauli channels to one for Pauli dynamical maps. 
+We introduce theorem \ref{theorem2} to establish what operations can be done with a 
+parametrized circuit that uses only one single-qubit operation dependent on the parameter.
+Finally, in section \ref{sec: 1PR circuit for a Pauli map} 
+we apply this theorem for the circuit of Pauli dynamical
+maps and show a couple of maps that fulfill the theorem's conditions.
+
 % }}}
 \section{Pauli channels and dynamical maps}  \label{sec: Pauli Channels} % {{{
+
 % Intro  {{{
@@
 quizá tambien sean sencillas. Las quiero ver!!!}
-\tbnote{Ah, ya entiendo. Las única forma que veo de escribirlas es:
-\begin{align*}
-\tan \theta_0 = \dfrac{\sqrt{k_{01}/k_{00}} - \sqrt{k_{11}/k_{10} }}{1+\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }} \\
-\tan \theta_2 = \dfrac{\sqrt{k_{01}/k_{00}} + \sqrt{k_{11}/k_{10} }}{1-\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }}
-\end{align*}
-No veo cómo escribir ecuaciones de las thetas no despejadas que sean sencillas.
+%\tbnote{Ah, ya entiendo. Las única forma que veo de escribirlas es:
+%\begin{align*}
+%\tan \theta_0 = \dfrac{\sqrt{k_{01}/k_{00}} - \sqrt{k_{11}/k_{10} }}{1+\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }} \\
+%\tan \theta_2 = \dfrac{\sqrt{k_{01}/k_{00}} + \sqrt{k_{11}/k_{10} }}{1-\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }}
+%\end{align*}
+%No veo cómo escribir ecuaciones de las thetas no despejadas que sean sencillas.
+%}
+
+%\tbnote{Obteniendo el seno y coseno de estos ángulos tampoco se 
+%consigue algo mucho mejor:
+%\begin{align*}
+%\cos \theta_0 = \dfrac{\sqrt{k_{00} k_{10}} + \sqrt{k_{01} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}} \\
+%\sin \theta_0 =  \dfrac{\sqrt{k_{01} k_{10}} - \sqrt{k_{00} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}}  \\
+%\cos \theta_2 = \sqrt{\dfrac{k_{00}k_{10}}{(k_{00}+k_{01})(k_{10}+k_{11})}} \left( -1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right) \\
+%\sin \theta_2 =  - \sqrt{\dfrac{k_{00}k_{10} + k_{01}k_{11} - 2 \sqrt{k_{00} k_{01} k_{10} k_{11}}}{(k_{00} + k_{01}) (k_{10} + k_{11})}} \left(\sqrt{\dfrac{k_{01}}{k_{00}}} + \sqrt{\dfrac{k_{11}}{k_{10}}} \right) \left(-1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right)^{-1}
+%\end{align*}
+%Probé combinar estas cantidades de diferentes formas, pero ninguna se simplificaba.}
+
+\tbnote{Creo que la mejor forma es la siguiente (nota:
+intercambié los ángulos 0 y 1 en la imagen para que 1 y 2
+sean los que van juntos y el 0 por separado, en lugar de que los juntos sean el 0 y 2) :}
+\tbnote{of angles defined by the following equations:
+\begin{align*}
+\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}}\\
+\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}} \\
+\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}
+\end{align*}
+También podría quitar los factores de 2 que hay aquí y meter factores de 2 en los ángulos del circuito.
 }
-
-\tbnote{Obteniendo el seno y coseno de estos ángulos tampoco se 
-consigue algo mucho mejor:
-\begin{align*}
-\cos \theta_0 = \dfrac{\sqrt{k_{00} k_{10}} + \sqrt{k_{01} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}} \\
-\sin \theta_0 =  \dfrac{\sqrt{k_{01} k_{10}} - \sqrt{k_{00} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}}  \\
-\cos \theta_2 = \sqrt{\dfrac{k_{00}k_{10}}{(k_{00}+k_{01})(k_{10}+k_{11})}} \left( -1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right) \\
-\sin \theta_2 =  - \sqrt{\dfrac{k_{00}k_{10} + k_{01}k_{11} - 2 \sqrt{k_{00} k_{01} k_{10} k_{11}}}{(k_{00} + k_{01}) (k_{10} + k_{11})}} \left(\sqrt{\dfrac{k_{01}}{k_{00}}} + \sqrt{\dfrac{k_{11}}{k_{10}}} \right) \left(-1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right)^{-1}
-\end{align*}
-Probé combinar estas cantidades de diferentes formas, pero ninguna se simplificaba.}
 

### 2023-06-07 main.tex
Merge pull my finger request

@@
 |10\rangle + \sqrt{k_{11}}|11\rangle$
-and it is created on the ancilla qubits with the help of three rotations of angles:
-\begin{subequations}
-\begin{eqnarray}
-\theta_0 &= &\arctan(\sqrt{k_{01}/k_{00}}) -
-\arctan(\sqrt{k_{11}/k_{10}}),
-\label{eq:angle1} \\ 
-\theta_1 &= &2 \arccos(\sqrt{k_{00} +
-k_{01}}),
-\label{eq:angle2} \\
-\theta_2 &= &\arctan(\sqrt{k_{01}/k_{00}}) +
-\arctan(\sqrt{k_{11}/k_{10}}).
-\label{eq:angle3}
-\end{eqnarray}
-\label{eq:angle}
-\end{subequations}
-\cpnote{Quisiera ver las ecuaciones sin la teheta despejada. Por ejemplo la de theta 1
-es $\cos^2 (\theta_1/2) = k00 + k01$ bueno mas bonita, pero asi. Luego las de tehta0 y theta2 
-quizá tambien sean sencillas. Las quiero ver!!!}
-%\tbnote{Ah, ya entiendo. Las única forma que veo de escribirlas es:
-%\begin{align*}
-%\tan \theta_0 = \dfrac{\sqrt{k_{01}/k_{00}} - \sqrt{k_{11}/k_{10} }}{1+\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }} \\
-%\tan \theta_2 = \dfrac{\sqrt{k_{01}/k_{00}} + \sqrt{k_{11}/k_{10} }}{1-\sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}} }}
-%\end{align*}
-%No veo cómo escribir ecuaciones de las thetas no despejadas que sean sencillas.
-%}
-
-%\tbnote{Obteniendo el seno y coseno de estos ángulos tampoco se 
-%consigue algo mucho mejor:
-%\begin{align*}
-%\cos \theta_0 = \dfrac{\sqrt{k_{00} k_{10}} + \sqrt{k_{01} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}} \\
-%\sin \theta_0 =  \dfrac{\sqrt{k_{01} k_{10}} - \sqrt{k_{00} k_{11}}}{\sqrt{(k_{00} + k_{01}) (k_{10} + k_{11})}}  \\
-%\cos \theta_2 = \sqrt{\dfrac{k_{00}k_{10}}{(k_{00}+k_{01})(k_{10}+k_{11})}} \left( -1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right) \\
-%\sin \theta_2 =  - \sqrt{\dfrac{k_{00}k_{10} + k_{01}k_{11} - 2 \sqrt{k_{00} k_{01} k_{10} k_{11}}}{(k_{00} + k_{01}) (k_{10} + k_{11})}} \left(\sqrt{\dfrac{k_{01}}{k_{00}}} + \sqrt{\dfrac{k_{11}}{k_{10}}} \right) \left(-1 + \sqrt{\dfrac{k_{01}k_{11}}{k_{00}k_{10}}} \right)^{-1}
-%\end{align*}
-%Probé combinar estas cantidades de diferentes formas, pero ninguna se simplificaba.}
-
-\tbnote{Creo que la mejor forma es la siguiente (nota:
-intercambié los ángulos 0 y 1 en la imagen para que 1 y 2
-sean los que van juntos y el 0 por separado, en lugar de que los juntos sean el 0 y 2) :}
-\tbnote{of angles defined by the following equations:
-\begin{align*}
-\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}}\\
-\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}} \\
-\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}
-\end{align*}
-También podría quitar los factores de 2 que hay aquí y meter factores de 2 en los ángulos del circuito.
-}
+and it is created on the ancilla qubits with the help of three rotations of angles
+defined by the following equations:
+\begin{align*}
+\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\\
+\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}}, \\
+\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.
+\end{align*}
 
@@
 
-We took a sample of one-qubit Pauli channels and
-used the ibmq-lima quantum computer that IBM has available~\cite{Qiskit}
-to simulate them. For each of these channels, we used quantum process
-tomography~\cite{Qiskit, Chuang:1996} to obtain the 
-operator $\xi_I$ corresponding to the implementation of the
-circuit.  Then, we compared this operator with the ideal 
-channel $\xi_T$  we
-wanted to implement.
+% We took a sample of one-qubit Pauli channels and
+% used the ibmq-lima quantum computer that IBM has available~\cite{Qiskit}
+% to simulate them. For each of these channels, we used quantum process
+% tomography~\cite{Qiskit, Chuang:1996} to obtain the 
+% operator $\xi_I$ corresponding to the implementation of the
+% circuit.  Then, we compared this operator with the ideal 
+% channel $\xi_T$  we
+% wanted to implement.
 
@@
 the diamond distance has a value of $0$, while in the case that the channels
-are completely distingushable, the distance reaches its maximum value of $2$~\cite{Benenti}.
+are completely distinguishable, the distance reaches its maximum value of $2$~\cite{Benenti}.
 For the analysis done in \fref{fig:fids}, we define a sort of ``diamond fidelity'' as: 
@@
 when trying to simulate depolarization but it is 
-when simulating unitary processes. \cpnote{Tambien creo qeu debemos comentar que nuestra 
-simulación para operaciones unitarias no es optima, porque usamos un monton de compuertas 
-y además operaciones doblemente controladas.}
-\tbnote{Algo como: }
-{\color{orange} Moreover, the algorithm of \fref{fig: circuit-pauli-1} is not optimal for unitary channels 
-(that is, the channels corresponding to the vertices of the tetrahedron). 
-These straightforward channels could be accomplished more efficiently by simply applying the corresponding Pauli operation directly.
-Nevertheless, due to its general design to accommodate any Pauli channel, the algorithm employs numerous quantum gates even in such scenarios.}
-\cpnote{Siento qeu aun falta algo de análisis pero lo dejamos para cuando tengamos mas
-figuras y mas inspiracion}
-\tbnote{Va}
+when simulating unitary processes. Moreover, the algorithm of \fref{fig:
+circuit-pauli-1} is not optimal for unitary channels (that is, the channels
+corresponding to the vertices of the tetrahedron).  These straightforward
+channels could be accomplished more efficiently by simply applying the
+corresponding Pauli operation directly. Nevertheless, due to its general design
+to accommodate any Pauli channel, the algorithm employs numerous quantum gates
+even in such scenarios.
+\cpnote{Iterar este parrafo cuando estemos cerca del final. Ta un tilin chafa.}
 
@@
 where $s = s(p)$ is a function of $p$. 
-\cpnote{Es un poco confusa la notacion. Hablas de la norma de a con $|a|$, pero ahi parece
-que $a$ es un vector. Sugiero cambiar a $\langle a | a \rangle$ o algo asi sin cargar mucho
-la notacion. } \tbnote{Va, concuerdo, listo}
-\cpnote{Tambien siento qeu las palabras son un poco raras. Sugiero pasarlo por Chatgpt y 
-luego tunearlo (todo este parrafo). Avisame cuando quede eso!} \tbnote{Ya}
+% \cpnote{Es un poco confusa la notacion. Hablas de la norma de a con $|a|$, pero ahi parece
+% que $a$ es un vector. Sugiero cambiar a $\langle a | a \rangle$ o algo asi sin cargar mucho
+% la notacion. } \tbnote{Va, concuerdo, listo}
+% \cpnote{Tambien siento qeu las palabras son un poco raras. Sugiero pasarlo por Chatgpt y 
+% luego tunearlo (todo este parrafo). Avisame cuando quede eso!} \tbnote{Ya}
 
@@
 \end{align*}
-The rest of the operators $A$ and $B$ can be defined
+The remaining part of the operators $A$ and $B$ can be defined
 in any arbitrary manner as long as they are unitary.
@@
 % }}}
-
 \section{1PR circuit for a Pauli map} % {{{
@@
 can be implemented with a 1PR circuit.
-Given this condition, the curve of states of \eref{eq: parametrized state}  needed 
+Given this condition \cpnote{which?}, the curve of states of \eref{eq: parametrized state}  needed 
 to implement the map
@@
 where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states  
-and $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$.
+and $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$ \cpnote{redundante, refierete mejor a la ecuacion anterior, a la 24 pues. Ahora, también creo qeu la pedendencia
+con $p$ no está clara del lado derecho. Quizpa si se escribe $s(p)$ en vez de 
+$s$ es mejor, pero piensale tambien . }.
 
@@
 
-\begin{figure}
+\begin{figure} % {{{
 \captionsetup[subfigure]{justification=centering}
@@
 \item \textbf{Bit flip map:} 
+\cpnote{Aca solo usas dos niveles, pero el caso general requiere 2 qubits. Ahora, si solo 
+se requiere un qubit, pues está chido pero toca decirlo. Quizá dejarlo como un ultimo ejemplo. 
+Toca citar acá tambien el trabajo de los brasileños... a ver si lo encuentro, Andrea 
+Valdez me va a pasar la cita. De hecho pordemos leer el articulo para inspiracion y citar}
 This dynamical map is defined as
@@
 \end{align*}
-with $s= \arcsin(\sqrt{p})$.
+with $s= \arcsin(\sqrt{p})$\cpnote{Que tal si lo dejamos como $\sin s= \sqrt{p}$? Si estas de 
+acuerdo igual cambia los siguientes}.
 Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
@@
 1PR circuit.
+\cpnote{De nuevo, quizá aca convenga tener notacion de qubits y no de sistemas de 4 niveles}
 
@@
 \item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle = |c| |2\rangle$.
-\item[3.] Finally, we choose a unitary matrix $V$
+\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
+la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
+los detalles. }
 and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
@@
 
+\cpnote{Esta parte está desordenada. Porque parece qeu das el procedimiento 
+en los 3 putnos de arriba y leugo que siempre no, qu evalta algo. Trata de iterar el paso 3 
+estos dos parrafos para que tengan un flujo mas chido. }
 To fulfill this additional condition,  we restrict the first row of
@@
 % }}}
+
 \section{Conclusion} % {{{
@@
 % Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-\paragraph*{S1 Fig.}
-\label{S1_Fig}
-{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
-
-\paragraph*{S2 Fig.}
-\label{S2_Fig}
-{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+% \paragraph*{S1 Fig.}
+% \label{S1_Fig}
+% {\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
+% 
+% \paragraph*{S2 Fig.}
+% \label{S2_Fig}
+% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
 Etiam eget sapien nibh.
@@
 Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 File.}
-\label{S1_File}
-{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+% 
+% \paragraph*{S1 File.}
+% \label{S1_File}
+% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
 Etiam eget sapien nibh.
@@
 Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Video.}
-\label{S1_Video}
-{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
+% 
+% \paragraph*{S1 Video.}
+% \label{S1_Video}
+% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
 Etiam eget sapien nibh.
@@
 Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Appendix.}
-\label{S1_Appendix}
-{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+% 
+% \paragraph*{S1 Appendix.}
+% \label{S1_Appendix}
+% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
 Etiam eget sapien nibh.
@@
 Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\paragraph*{S1 Table.}
-\label{S1_Table}
-{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
+% 
+% \paragraph*{S1 Table.}
+% \label{S1_Table}
+% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
 Etiam eget sapien nibh.

### 2023-06-08 main.tex
correcciones y citas brasil

@@
 
-\tbnote{versión muy preliminar de la intro, para ir teniendo algo escrito de una vez. }\\
-
 Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
 with a recent particular interest in simulating the evolution of open systems, 
-which are described by the theory of quantum channels~\cite{cleve,Zanetti,Xin,Wei}. 
+which are described by the theory of quantum channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
+{\color{purple} For example, this has been done using optical arrangements
+to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
 Among the various types of quantum channels for a system of qubits, 
@@
 defined by the following equations:
-\begin{align*}
+\begin{align}
+\label{eq:angle}
 \cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\\
@@
 \tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.
-\end{align*}
+\end{align}
 
@@
 \label{theorem2}
-Consider a 1PR circuit of $N$ qubits
+Consider a 1PR circuit of $N$ qubits parametrized by $p$
 and denote by $U$ the operator it implements on this system. 
@@
 \begin{align*}
-U|j\rangle = e^{is} |a^j\rangle + e^{-is} |b^j\rangle + |c^j\rangle
-\end{align*}
-with $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
+U|j\rangle = e^{is(p)} |a^j\rangle + e^{-is(p)} |b^j\rangle + |c^j\rangle
+\end{align*}
+with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
 c^j|c^j \rangle = 1$.
@@
 and not the others. Therefore,  
-remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is}$ to $|0\rangle$
-and a phase $e^{is}$ to $|1\rangle$, we have that,
+remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is(p)}$ to $|0\rangle$
+and a phase $e^{is(p)}$ to $|1\rangle$, we have that,
 % \begin{small}
@@
 \begin{align}
-RB|j\rangle& = e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
+RB|j\rangle& = e^{-is(p)} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is(p)} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
 + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
-& = e^{-is} |\tilde{b}^{j}\rangle + e^{is} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle
+& = e^{-is(p)} |\tilde{b}^{j}\rangle + e^{is(p)} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle
 \end{align}
@@
 \begin{eqnarray}
-U|j\rangle = ARB|j\rangle = e^{-is} A |\tilde{a}^j\rangle + e^{is} A |\tilde{b}^j\rangle + A |\tilde{c}^j\rangle = e^{-is} |a^j\rangle + e^{is} |b^j\rangle + |c^j\rangle,
+U|j\rangle = ARB|j\rangle = e^{-is(p)} A |\tilde{a}^j\rangle + e^{is(p)} A |\tilde{b}^j\rangle + A |\tilde{c}^j\rangle = e^{-is(p)} |a^j\rangle + e^{is(p)} |b^j\rangle + |c^j\rangle,
 \end{eqnarray}
@@
 \begin{equation}
-|\eta(p)\rangle = |c\rangle + e^{is}|a\rangle + e^{-is} |b\rangle,
+|\eta(p)\rangle = |c\rangle + e^{is(p)}|a\rangle + e^{-is(p)} |b\rangle,
 \label{eq:curve-states}
@@
 \langle a |c\rangle =
-\langle b |c\rangle = 0
-% , |b\rangle, |c\rangle \; \text{orthogonal states},
-%  \text{and} \; a\rangle, |b\rangle, |c\rangle \; \text{orthogonal states},
+\langle b |c\rangle = 0.
 \label{eq:conditions-vecs}
 \end{equation}
-where $s = s(p)$ is a function of $p$. 
 % \cpnote{Es un poco confusa la notacion. Hablas de la norma de a con $|a|$, pero ahi parece
@@
 $$
-RB|0\rangle =\sqrt{\langle a | a \rangle} e^{is} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} e^{-is} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.
+RB|0\rangle =\sqrt{\langle a | a \rangle} e^{is(p)} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} e^{-is(p)} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.
 $$
@@
 can be implemented with a 1PR circuit.
-Given this condition \cpnote{which?}, the curve of states of \eref{eq: parametrized state}  needed 
+Given the condition of theorem \ref{theorem2}, the curve of states of \eref{eq: parametrized state}  needed 
 to implement the map
@@
 \label{eq:vec}
-\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is} |a\rangle + e^{-is}|b\rangle,
+\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
 \end{eqnarray}
+{\color{red}
 where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states  
-and $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$ \cpnote{redundante, refierete mejor a la ecuacion anterior, a la 24 pues. Ahora, también creo qeu la pedendencia
-con $p$ no está clara del lado derecho. Quizpa si se escribe $s(p)$ en vez de 
-$s$ es mejor, pero piensale tambien . }.
+and $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$}
+ \cpnote{redundante, refierete mejor a la ecuacion anterior, a la 24 pues. Ahora, también creo qeu la pedendencia
+con $p$ no está clara del lado derecho.}
+
+\tbnote{Va, algo así (quitar lo 
+rojo, dejar lo morado):}
+
+{\color{purple} where $|a\rangle,|b\rangle,|c\rangle$ fulfill
+the conditions of \eref{eq:conditions-vecs}.}
+
+\cpnote{
+ Quizpa si se escribe $s(p)$ en vez de 
+$s$ es mejor, pero piensale tambien . } 
+\tbnote{Es cierto, mejor, ya lo puse}.\\
 
@@
 \begin{itemize}
-\item \textbf{Bit flip map:} 
-\cpnote{Aca solo usas dos niveles, pero el caso general requiere 2 qubits. Ahora, si solo 
-se requiere un qubit, pues está chido pero toca decirlo. Quizá dejarlo como un ultimo ejemplo. 
-Toca citar acá tambien el trabajo de los brasileños... a ver si lo encuentro, Andrea 
-Valdez me va a pasar la cita. De hecho pordemos leer el articulo para inspiracion y citar}
-This dynamical map is defined as
-\begin{align*}
-\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
-\end{align*}
-for $p \in [0,1]$. 
+\item \textbf{Depolarizing:} This dynamical map is given by
+\begin{align*}
+\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
+\end{align*}
+with $p \in [0,1]$. 
 Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
 qubits is such that 
-$|\beta_0(p)|^2= (1-p)^2$, $|\beta_1(p)|^2 = p$, $|\beta_2(p)|^2 = |\beta_3(p)|^2 = 0$.
-In particular, if we take the $\beta_j$ to be real,
-we need to create the curve of states:
-\begin{align*}
-|\beta(p)\rangle = \sqrt{1-p} |0\rangle +\sqrt{p} |1\rangle.
-\end{align*}
-This can be rewritten as
-\begin{align*}
-|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |0\rangle - \dfrac{i}{2} |1\rangle \right) + e^{-is} \left( \frac{1}{2} |0\rangle + \frac{i}{2} |1\rangle \right),
-\end{align*}
-with $s= \arcsin(\sqrt{p})$\cpnote{Que tal si lo dejamos como $\sin s= \sqrt{p}$? Si estas de 
-acuerdo igual cambia los siguientes}.
-Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
-and it can be created with a 1PR circuit.
-The exact same thing can be done
-for the phase flip and bit phase flip dynamical maps by
-changing $\sigma_1$ to
-$\sigma_3$ and $\sigma_2$ respectively.
-
-\item \textbf{Depolarizing:} This dynamical map is given by
-\begin{align*}
-\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
-\end{align*}
-with $p \in [0,1]$. 
+$|\beta_0(p)|^2= (1-3p/4)$, $|\beta_1(p)|^2 = |\beta_2(p)|^2 = |\beta_3(p)|^2 = p/4$.
 Then, taking the $\beta_j$ to be real,
-the curve of states needed to create on the ancilla qubits is
-\begin{align*}
-|\beta(p) \rangle = \sqrt{1-3p/4} |0\rangle + \sqrt{p/4} |1\rangle + \sqrt{p/4} |2 \rangle  + \sqrt{p/4} |3\rangle.
+thi curve of states is
+\begin{align*}
+|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
 \end{align*}
@@
 \begin{align*}
-|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |0\rangle - \dfrac{i}{2\sqrt{3}} |1\rangle - \dfrac{i}{2\sqrt{3}} |2 \rangle - \dfrac{i}{2\sqrt{3}} |3\rangle \right) \\
-& + e^{-is} \left( \dfrac{1}{2} |0\rangle + \dfrac{i}{2\sqrt{3}} |1\rangle + \dfrac{i}{2\sqrt{3}} |2\rangle + \dfrac{i}{2\sqrt{3}} |3 \rangle \right),
-\end{align*}
-with $s = \arcsin(\sqrt{3p/4})$.
+|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
+& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
+\end{align*}
+with $\sin s = \sqrt{3p/4}$.
 We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
@@
 \cpnote{De nuevo, quizá aca convenga tener notacion de qubits y no de sistemas de 4 niveles}
-
-\item \textbf{Parabolic dynamical map:} Finally, we define the parabolic dynamical map as:
+\tbnote{Va, listo.}
+
+\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
 \begin{eqnarray}
@@
 If we take the $\beta_j$ to be real,
-we need to create the curve of states:
+the curve of states needed on the ancilla qubits is:
 \begin{eqnarray}
-|\beta(p)\rangle = \dfrac{1}{2} (1-p) |0\rangle + \dfrac{1}{2} \sqrt{1-p^2} |1\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |2\rangle +  \dfrac{1}{2}(1+p) |3\rangle.
+|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
 \end{eqnarray}
@@
 \begin{align*}
-|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|0\rangle + \dfrac{1}{2} |3\rangle \right) + e^{is} \left( \dfrac{i}{4}|0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle - \dfrac{i}{4} |3\rangle \right) \\
-& + e^{-is}  \left( \dfrac{-i}{4} |0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle + \dfrac{i}{4} |3\rangle \right),
-\end{align*}
-with $s = \arcsin(p)$, so that
+|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
+& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
+\end{align*}
+with $\sin s = p$, so that
 this map fulfills the conditions of  \eref{eq:conditions-vecs}.
+
+\item \textbf{Bit flip map:} 
+\cpnote{Aca solo usas dos niveles, pero el caso general requiere 2 qubits. Ahora, si solo 
+se requiere un qubit, pues está chido pero toca decirlo. Quizá dejarlo como un ultimo ejemplo. 
+Toca citar acá tambien el trabajo de los brasileños... a ver si lo encuentro, Andrea 
+Valdez me va a pasar la cita.
+De hecho pordemos leer el articulo para inspiracion y citar} \tbnote{Va, puse explícitamente lo de que sólo se usa un qubit más abajo} \tbnote{Tambien puse la cita del trabajo brasileño}
+This dynamical map is defined as
+\begin{align*}
+\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
+\end{align*}
+for $p \in [0,1]$. 
+In particular, if we take the $\beta_j$ to be real,
+we need to create the curve of states:
+\begin{align*}
+|\beta(p)\rangle = \sqrt{1-p} |00\rangle +\sqrt{p} |01\rangle.
+\end{align*}
+This can be rewritten as
+\begin{align*}
+|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |00\rangle - \dfrac{i}{2} |01\rangle \right) + e^{-is} \left( \frac{1}{2} |00\rangle + \frac{i}{2} |01\rangle \right),
+\end{align*}
+with $\sin s= \sqrt{p}$\cpnote{Que tal si lo dejamos como $\sin s= \sqrt{p}$? Si estas de 
+acuerdo igual cambia los siguientes} \tbnote{Va, ya los cambié}.
+Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
+and it can be created with a 1PR circuit.
+{\color{purple} Note that in this case we actually only need one ancilla qubit
+since the state $|\beta(p)\rangle$ is only two dimensional.}
+
+The exact same thing can be done
+for the phase flip and bit phase flip dynamical maps by
+changing $\sigma_1$ to
+$\sigma_3$ and $\sigma_2$ respectively.
+{\color{purple}
+For example, the bit phase flip map was implemented in \cite{Andrea, Andrea_4qb} 
+using an optical arrangement, and  it was indeed done 
+by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate).}
+
 \end{itemize}
@@
 and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
-This way, since the primed states are orthogonal and their squared norms add up to one,
+This way, given that the primed states are orthogonal and their squared norms add up to one,
 so do the unprimed states and therefore 
 fulfill the conditions of  \eref{eq:conditions-vecs}.
+
+{\color{purple} However, since a Pauli dynamical map should begin at the
+identity channel, we need to add the condition that $|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$, with
+$\theta$ an arbitrary real number. 
+This way, when $s = 0$ in \eref{eq:vec}, the constructed state
+is $e^{i \theta}|0\rangle$, which
+corresponds with the identity channel.
+
+To fulfill this additional condition,  we restrict the first row of
+$V$ written as a matrix in 
+the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
+That way, 
+\begin{align*}
+|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
+\end{align*}
+The last equality comes from the fact
+that the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
+is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
+$e^{i\theta}$. 
+Furthermore, the other entries have to be $0$,
+since otherwise the norm of the result would be greater than
+$1$ but $V$ is unitary and therefore preserves the norm.}
 \end{itemize}
@@
 angles and unitary matrices $V$, 
-we plot four Pauli dynamical maps 
+we plot four Pauli dynamical maps  selected at random
 that can be implemented with a 1PR circuit in \fref{fig:curves2}.
+
+{\color{red}
 These maps where constructed with the additional condition
@@
 estos dos parrafos para que tengan un flujo mas chido. }
+\tbnote{Va, lo cambié y agregué esto al paso 3. Propongo quitar lo rojo y dejar lo morado}
 To fulfill this additional condition,  we restrict the first row of
@@
 $1$ but $V$ is unitary and therefore preserves the norm.
+}
 

### 2023-06-10 main.tex
.
Revision

@@
 Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
-with a recent particular interest in simulating the evolution of open systems, 
+with a recent particular interest in simulating the evolution of open quantum systems, 
 which are described by the theory of quantum channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
@@
 
-On the other hand, we shall also work with parametrized quantum circuits, that is,  
-a quantum circuit in which some of the operations depend on a variable parameter~\cite{cerezo}. 
-The investigation of parametrized quantum
-circuits holds extensive importance, 
-as they find applications in quantum machine learning~\cite{Benedetti}
-and describe general quantum transformations dependent on a parameter. Substantial research has been 
+Additionally , we shall also work with parametrized quantum circuits, that is,  
+quantum circuits in which some of the operations depend on variable parameters~\cite{cerezo}. 
+These circuits play an important 
+part in applications such as quantum machine learning~\cite{Benedetti}
+and describing general quantum transformations dependent on parameters. Substantial research has been 
 devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}.
@@
 we introduce the concept of Pauli dynamical maps, 
-which are defined as a continuous parametrization of
+defined as a continuous parametrization of
 $N$-qubit Pauli channels. 
-Consequently, we adapt the algorithm developed for Pauli channels 
+We adapt the algorithm developed for Pauli channels 
 to accommodate these dynamical maps by employing a 
 parametrized quantum circuit. 
-We contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2}.
-This theorem outlines the types of transformations that 
-can be done using a parametrized quantum circuit with the condition that only one
+Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
+which outlines the types of transformations that 
+can be done using a parametrized circuit with the condition that only one
  single-qubit operation in the circuit may depend on the parameter.
@@
 The paper is organized as follows: In section \ref{sec: Pauli Channels} 
-we give the definition of quantum channels and focus particularly on Pauli channels for systems of
+we provide  the definition of quantum channels and focus specifically on Pauli channels for systems of
 $N$ qubits. 
-In section \ref{sec: Circuit for a Pauli Channel} we show the proposed circuit 
-to implement a Pauli channel of $N$ qubits in a quantum computer. 
+In section \ref{sec: Circuit for a Pauli Channel} we present  the proposed circuit 
+for implementing a Pauli channel of $N$ qubits in a quantum computer. 
 Furthermore, we simulate it on IBM’s computers for the special case of $N=1$
 and obtain the fidelity of this implementation.  
-In section \ref{sec: 1PR Circuits} we shift our focus to parametrized quantum circuits with the goal of
-generalizing the circuit for Pauli channels to one for Pauli dynamical maps. 
-We introduce theorem \ref{theorem2} to establish what operations can be done with a 
-parametrized circuit that uses only one single-qubit operation dependent on the parameter.
+Section \ref{sec: 1PR Circuits} shifts the focus to parametrized quantum circuits, 
+aiming to generalize the circuit for Pauli channels to accommodate Pauli dynamical maps. 
+We introduce theorem \ref{theorem2} to determine the operations that can be 
+performed using a parametrized circuit 
+with only one single-qubit operation dependent on the parameter.
 Finally, in section \ref{sec: 1PR circuit for a Pauli map} 
@@
 
-In this work, we have undertaken the study of Pauli channels on systems of $N$ qubits, 
-proposing an algorithm capable of implementing them on a quantum computer
-with the assistance of $2N$ ancilla qubits.
+In this study, we focused on the analysis of Pauli channels in N-qubit systems and
+developed an algorithm to implement them on a quantum computer.
  By running this algorithm on one of IBM's quantum computers, 
@@
 the algorithm isn’t efficient for unitary channels, 
-which can be done in a much simpler manner.
+which can be done in a much straightforward manner.
 
@@
 % }}}
-\section{Supporting information} % {{{
-
-\tbnote{Ver qué se debe de poner aquí según el template y también arreglar las imágenes de acuerdo a él.}
+
+%\section{Supporting information} % {{{
+
 % Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.

### 2023-06-11 main.tex
Cambios

@@
 
-% textcomp package and marvosym package for additional characters
+% textcomp cpackage and marvosym package for additional characters
 \usepackage{textcomp,marvosym}
@@
 \usepackage{array}
+\usepackage{caption}
+\captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Fig}}
 
@@
 
-\newcommand{\fref}[1]{Fig.~\ref{#1}}
-\newcommand{\eref}[1]{eq.~(\ref{#1})}
+\newcommand{\fref}[1]{Fig~\ref{#1}}
+\newcommand{\eref}[1]{Eq~(\ref{#1})}
 % Use the PLoS provided BiBTeX style
@@
 \mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
-& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
+& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} {(A^{\otimes^N})}_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
 \end{align*}
 which means that applying the Pauli channel multiplies the 
-components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} (A^{\otimes^N})_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
+components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} {(A^{\otimes^N})}_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
 % }}}
@@
 \centering
-% \begin{quantikz}
-% \lstick{$q:\; |0\rangle^{\otimes N}$} & \qw & \gate{\sigma_{\vec{\gamma} }} \gategroup[wires=2,steps
-% =1,style={dashed, inner sep=4pt}]{Repeat for all $\vec{\gamma}$}
-% \gategroup[wires=2,steps
-% =1,style={dashed, inner sep=4pt}, label style = {label position = below, yshift = 0.15cm}]
-% {$|\vec{\gamma}\rangle$} & \qw \\
-% \lstick{$\tilde{q}:\; |0\rangle^{\otimes 2N}$} & \gate[wires=1]{\text{Create the $2N$ qubits state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}   |\vec{\gamma} \rangle$}} & \ctrl{-1} 
-% % \gategroup[wires=1,steps
-% %=1,style={color=white, inner sep=0pt}, label style= {label position=below}]{$|\vec{\gamma}\rangle$} 
-% & \qw 
-% \end{quantikz}
 \includegraphics{images/circuito_general.pdf}
@@
 on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
-|b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$ and
+{|b_{\vec{\gamma}}|}^2 = k_{\vec{\gamma}}$ and
 the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
@@
 collapses to $|\vec{\gamma}\rangle$ with a 
-probability $|b_{\vec{\gamma}}|^2 = k_{\vec\gamma}$. 
+probability ${|b_{\vec{\gamma}}|}^2 = k_{\vec\gamma}$. 
 The circuit in \fref{fig: circuit-pauli} uses this fact
@@
 
-Finally, using the representation of Pauli channels in a tetrahedron as
-in \eref{eq: conditions-tetrahedron},
-we show in \fref{fig:fids} the diamond fidelity defined by \eref{eq:diamond-fid} for the channels
-analyzed. 
-We can see that channels close to the 
-completely depolarizing
-channel (that is close to the center of the tetrahedron)
-have a high $f$, while those 
-close to unitary channels have much lower $f$.
-This means that channels closer to the 
-completely depolarizing channel are simulated better on the quantum computers.
-This is reasonable because quantum computers are prone to errors
-that depolarize qubits, which isn't very problematic
-when trying to simulate depolarization but it is 
-when simulating unitary processes. Moreover, the algorithm of \fref{fig:
-circuit-pauli-1} is not optimal for unitary channels (that is, the channels
-corresponding to the vertices of the tetrahedron).  These straightforward
-channels could be accomplished more efficiently by simply applying the
-corresponding Pauli operation directly. Nevertheless, due to its general design
-to accommodate any Pauli channel, the algorithm employs numerous quantum gates
-even in such scenarios.
-\cpnote{Iterar este parrafo cuando estemos cerca del final. Ta un tilin chafa.}
-
 \begin{figure} % {{{
@@
 
+Finally, using the representation of Pauli channels in a tetrahedron as
+in \eref{eq: conditions-tetrahedron},
+we show in \fref{fig:fids} the diamond fidelity defined by \eref{eq:diamond-fid} for the channels
+analyzed. 
+We can see that channels close to the 
+completely depolarizing
+channel (that is close to the center of the tetrahedron)
+have a high $f$, while those 
+close to unitary channels have much lower $f$.
+This means that channels closer to the 
+completely depolarizing channel are simulated better on the quantum computers.
+This is reasonable because quantum computers are prone to errors
+that depolarize qubits, which isn't very problematic
+when trying to simulate depolarization but it is 
+when simulating unitary processes. Moreover, the algorithm of \fref{fig:
+circuit-pauli-1} is not optimal for unitary channels (that is, the channels
+corresponding to the vertices of the tetrahedron).  These straightforward
+channels could be accomplished more efficiently by simply applying the
+corresponding Pauli operation directly. Nevertheless, due to its general design
+to accommodate any Pauli channel, the algorithm employs numerous quantum gates
+even in such scenarios.
+\cpnote{Iterar este parrafo cuando estemos cerca del final. Ta un tilin chafa.}
+
 % }}}
@@
 applying the circuit shown in \fref{fig:1PR-circuit}, straightforward calculations 
-lead us to obtain the resulting curve of states described in Equation (\ref{eq:curve-states}).
+lead us to obtain the resulting curve of states described in \eref{eq:curve-states}.
 
@@
 qubits is such that 
-$|\beta_0(p)|^2= (1-3p/4)$, $|\beta_1(p)|^2 = |\beta_2(p)|^2 = |\beta_3(p)|^2 = p/4$.
+${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 = {|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.
 Then, taking the $\beta_j$ to be real,
@@
 \begin{eqnarray}
-\epsilon(\rho) = \dfrac{1}{4} (1-p)^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} (1+p)^2 \sigma_3 \rho \sigma_3 ,
+\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3 ,
 \end{eqnarray}
@@
 can be implemented with a 1PR circuit.
-To do it, we only need to choose the three states $|a\rangle, |b\rangle, |c\rangle$
+To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
 that satisfy the conditions of  \eref{eq:conditions-vecs}.
@@
 \begin{itemize}
-\item[1.] We first choose the norms $|a|, |b|, |c|$
+\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
 such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
 This can be done by selecting two angles
-$\mu \in [0, \pi/2] , \nu \in [0,\pi/2]$ and defining:
+$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
 \begin{align*}
@@
 \end{align*}
-\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle,$ $|c'\rangle = |c| |2\rangle$.
+\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
 \item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
@@
 los detalles. }
-and use it to define the states $|a\rangle = V |a'\rangle, |b\rangle = V |b'\rangle, |c\rangle = V |c'\rangle$.
+and use it to define the states $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$.
 This way, given that the primed states are orthogonal and their squared norms add up to one,
@@
 \begin{align*}
-|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
+|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
 \end{align*}
 The last equality comes from the fact
-that the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
-is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
+that the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
+is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
 $e^{i\theta}$. 
@@
 \begin{align*}
-|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T = (e^{i\theta},0,0,0)^T.
-\end{align*}
-The last step is because the first entry of $V(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$
-is obtained by calculating the dot product of the first row of $V$ with $(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)^T$, which gives
+|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
+\end{align*}
+The last step is because the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
+is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
 $e^{i\theta}$. 

### 2023-06-12 main.tex
(\ /) (O.o) (> <) Bunny approves these changes.

@@
 to implement the map
-has to be constructed with only one parametrized rotation. 
+has to be constructed with only one parametrized rotation\cpnote{no entiendo esta frase}. 
 Therefore, the results of the last section imply that the the map
@@
 \end{eqnarray}
-{\color{red}
-where $|a\rangle,|b\rangle,|c\rangle$ are orthogonal states  
-and $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$}
- \cpnote{redundante, refierete mejor a la ecuacion anterior, a la 24 pues. Ahora, también creo qeu la pedendencia
-con $p$ no está clara del lado derecho.}
-
-\tbnote{Va, algo así (quitar lo 
-rojo, dejar lo morado):}
-
-{\color{purple} where $|a\rangle,|b\rangle,|c\rangle$ fulfill
-the conditions of \eref{eq:conditions-vecs}.}
-
-\cpnote{
- Quizpa si se escribe $s(p)$ en vez de 
-$s$ es mejor, pero piensale tambien . } 
-\tbnote{Es cierto, mejor, ya lo puse}.\\
-
-For the particular case of one qubit,
-we can show some examples of Pauli dynamical maps
-implementable with a 1PR circuit, which are plotted
-in \fref{fig:curves1}.
+where $|a\rangle,|b\rangle,|c\rangle$ fulfill
+the conditions of \eref{eq:conditions-vecs}.
+
+For the particular case of one qubit, we can show some examples of Pauli
+dynamical maps implementable with a 1PR circuit, which are plotted in
+\fref{fig:curves1}.
 
@@
 Then, taking the $\beta_j$ to be real,
-thi curve of states is
+this curve of states is \cpnote{supongo qeye hay muchas curvas. Es correcto eso? Quizá un ``this curve of states can be'' sea mas preciso.}
 \begin{align*}
@@
 \begin{align*}
-|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
-& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
+|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle 
+      - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
+& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle 
+      + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
 \end{align*}
@@
 1PR circuit.
-\cpnote{De nuevo, quizá aca convenga tener notacion de qubits y no de sistemas de 4 niveles}
-\tbnote{Va, listo.}
 
 \item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
+\cpnote{este mapa no es muy comun. Toca comentar algo al respecto. No se si acá o mas arriba. Si, ya se donde. En el parrafo antes de los ejemplos. }
 \begin{eqnarray}
@@
 \item \textbf{Bit flip map:} 
-\cpnote{Aca solo usas dos niveles, pero el caso general requiere 2 qubits. Ahora, si solo 
-se requiere un qubit, pues está chido pero toca decirlo. Quizá dejarlo como un ultimo ejemplo. 
-Toca citar acá tambien el trabajo de los brasileños... a ver si lo encuentro, Andrea 
-Valdez me va a pasar la cita.
-De hecho pordemos leer el articulo para inspiracion y citar} \tbnote{Va, puse explícitamente lo de que sólo se usa un qubit más abajo} \tbnote{Tambien puse la cita del trabajo brasileño}
 This dynamical map is defined as
@@
 \end{align*}
-with $\sin s= \sqrt{p}$\cpnote{Que tal si lo dejamos como $\sin s= \sqrt{p}$? Si estas de 
-acuerdo igual cambia los siguientes} \tbnote{Va, ya los cambié}.
+with $\sin s= \sqrt{p}$.
 Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
 and it can be created with a 1PR circuit.
-{\color{purple} Note that in this case we actually only need one ancilla qubit
-since the state $|\beta(p)\rangle$ is only two dimensional.}
+Note that in this case we actually only need one ancilla qubit
+since the state $|\beta(p)\rangle$ is only two dimensional.
 
@@
 $\sigma_3$ and $\sigma_2$ respectively.
-{\color{purple}
 For example, the bit phase flip map was implemented in \cite{Andrea, Andrea_4qb} 
 using an optical arrangement, and  it was indeed done 
-by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate).}
+by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate).
 
@@
 los detalles. }
+\cpnote{Sigo sin saber coo escoges la matriz V. Espero platicar contigo}
 and use it to define the states $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$.
@@
 
-{\color{purple} However, since a Pauli dynamical map should begin at the
+However, since a Pauli dynamical map should begin at the
 identity channel, we need to add the condition that $|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$, with
@@
 since otherwise the norm of the result would be greater than
-$1$ but $V$ is unitary and therefore preserves the norm.}
+$1$ but $V$ is unitary and therefore preserves the norm.
+\cpnote{Creo qeu ahora está demasiado largo. jejej. hablemos y tratamos de hacer algo que se 
+acomode bien a lo que ambos nos parezca.}
 \end{itemize}
@@
 
-{\color{red}
-These maps where constructed with the additional condition
-of the map passing through the identity channel.
-To do that, we ensure that the vectors also satisfy
-$|a\rangle + |b\rangle + |c\rangle = e^{i \theta}|0\rangle$ with $\theta$ an arbitrary
-real number.
-This way, when $s = 0$ in \eref{eq:vec}, the constructed state
-is $e^{i \theta}|0\rangle$, which
-corresponds with the identity channel.
-
-\cpnote{Esta parte está desordenada. Porque parece qeu das el procedimiento 
-en los 3 putnos de arriba y leugo que siempre no, qu evalta algo. Trata de iterar el paso 3 
-estos dos parrafos para que tengan un flujo mas chido. }
-\tbnote{Va, lo cambié y agregué esto al paso 3. Propongo quitar lo rojo y dejar lo morado}
-To fulfill this additional condition,  we restrict the first row of
-$V$ writen as a matrix in 
-the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
-That way, 
-\begin{align*}
-|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
-\end{align*}
-The last step is because the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
-is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
-$e^{i\theta}$. 
-Furthermore, the other entries have to be $0$,
-since otherwise the norm of the result would be greater than
-$1$ but $V$ is unitary and therefore preserves the norm.
-}
-
-% }}}
-
+% }}}
 \section{Conclusion} % {{{
@@
 
-In this study, we focused on the analysis of Pauli channels in N-qubit systems and
+In this study, we focused on the analysis of Pauli channels in $N$-qubit systems and
 developed an algorithm to implement them on a quantum computer.
@@
 only one single-qubit parametrized rotation.
+
+\cpnote{Leiste como escribir una conclusion? Aca falta algo importante. Si ya lo leiste, 
+dale una pensanda y si no, leelo a la luz de lo uqe escribiste. En todo caso, me parece una
+muy buena primera iteracion para las conclusiones!!! }
 % }}}

### 2023-06-12 main.tex
Arrrrgggg

@@
 
+\cpnote{Porfa 3 propuestas de titulo y un intento de abstract. Ese es mas facil que la intro!
+de neuvo, quizá vale la pena que te einspires en otros abstracts de PlosOne}
+
 Puntos hechos en el artículo:
@@
 with a recent particular interest in simulating the evolution of open quantum systems, 
-which are described by the theory of quantum channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
+which are described by the theory of quantum
+channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
 {\color{purple} For example, this has been done using optical arrangements
 to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
+\cpnote{Se siente forzada. nos toca encontrar mas ejemplos e introducirla de
+manera mas natural. Quizá mas adelante}
 Among the various types of quantum channels for a system of qubits, 
@@
 and relevance in the context of quantum computing~\cite{Zbigniew,geometry}, 
+\cpnote{Aca citar nuestros trabajos con Davalos. }
 as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.
-
-Additionally , we shall also work with parametrized quantum circuits, that is,  
+\cpnote{Creo que la transición de general a particular va demasiado rapido. Quizá hacerle 
+ver a Tomas y luego reescribirlo yo}
+
+\cpnote{De nuevo una transicion muy abrupta. Para que ver los circuitos? Priero 
+hablar de los circuitos, quizá una frase, luego hablar de los parametrizadso, 
+Aca quiza citar a Barrero en innsbruk con sus vainas de enlazamiento}
+Additionally, we shall also work with parametrized quantum circuits, that is,  
 quantum circuits in which some of the operations depend on variable parameters~\cite{cerezo}. 
@@
 Pauli dynamical maps can be done with them. 
+\cpnote{Me gustaron mucho estos dos ultimos parrafos. Croe que se puede ir mencionando las secciones
+y poner la info del siguiente parrafo aca. Ahora, no lo pongas a lo bestia, sino realmente
+integrando e hilando las ideas. Si hay preguntas, me dices que tos.}
 

### 2023-06-13 main.tex
Cambios

@@
 \section*{Abstract}
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
+Pauli channels are fundamental in the context of quantum computing as they model noise in quantum devices. 
+We propose a quantum algorithm for simulating Pauli channels on quantum computers 
+and extend it to encompass Pauli dynamical maps 
+(parametrized Pauli channels).
+A parametrized quantum circuit is employed to accommodate for dynamical maps. 
+We also establish the mathematical conditions for an
+N-qubit transformation to be achievable using a parametrized circuit where
+only one single-qubit operation depends on the parameter. 
+The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
+for the case of one qubit, and the fidelity of this implementation is obtained.
 
@@
 %\section*{Author summary}
-%Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.
-Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
 
@@
 de neuvo, quizá vale la pena que te einspires en otros abstracts de PlosOne}
+\tbnote{Va, ya puse un abstract basado en lo que vi en articulos de PlosOne}
+\tbnote{Para el título, tengo las siguientes propuestas:}
+{\color{green}
+\begin{itemize}
+\item Quantum Algorithm for Simulation of Parametrized Pauli Channels.
+\item Parametrized Pauli Channels Simulation in Quantum Computes.
+\item Quantum Simulation of Pauli Channels: Algorithm, Implementation and 
+generalization to parametrized channels.
+\end{itemize}
+}
 
@@
 with a recent particular interest in simulating the evolution of open quantum systems, 
-which are described by the theory of quantum
+which can be described by the theory of quantum
 channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
-{\color{purple} For example, this has been done using optical arrangements
+{\color{red} For example, this has been done using optical arrangements
 to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
@@
 manera mas natural. Quizá mas adelante}
+\tbnote{Va, es cierto.
+Puedo incluir más trabajos y hablarlo más en general para que no se sienta forzado:}
+{\color{purple}
+Such systems have been simulated because of their many applications, 
+such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
+studying dissipative processes~\cite{Barreiro}
+and modeling non-Markovian dynamics~\cite{Marsden}.
+}
+
 Among the various types of quantum channels for a system of qubits, 
 Pauli channels hold special significance due to their simplicity 
-and relevance in the context of quantum computing~\cite{Zbigniew,geometry}, 
-\cpnote{Aca citar nuestros trabajos con Davalos. }
+and relevance in the context of quantum computing~\cite{Davalos,Zbigniew,geometry}, 
+\cpnote{Aca citar nuestros trabajos con Davalos. } \tbnote{Ya agregué la cita}
 as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.
@@
 ver a Tomas y luego reescribirlo yo}
+\tbnote{Va, sí lo veo, gracias!}
 
@@
 Aca quiza citar a Barrero en innsbruk con sus vainas de enlazamiento}
-Additionally, we shall also work with parametrized quantum circuits, that is,  
+\tbnote{Lo de Barreiro es una de las citas que agregué nuevas arriba}
+\tbnote{Para lo de lo abrupto, quizá una frase como:} 
+{\color{purple} To represent the algorithms
+done in quantum computers, either
+to simulate a physical system or for some other purpose,
+one often uses a quantum circuit~\cite{chuangbook}.}
+In this work, we shall also work with parametrized quantum circuits, that is,  
 quantum circuits in which some of the operations depend on variable parameters~\cite{cerezo}. 
@@
 integrando e hilando las ideas. Si hay preguntas, me dices que tos.}
-
+\tbnote{Va, pongo una versión de estos dos últimos párrafos pero incluyendo lo de las secciones del siguiente aquí:}
+
+{\color{purple}  
+In this article,
+after providing the definition of quantum
+channels and $N$-qubit Pauli channels
+in section \ref{sec: Pauli Channels},
+ our first objective is to present a 
+quantum algorithm capable of simulating Pauli channels on quantum computers.
+We do this in section \ref{sec: Circuit for a Pauli Channel},
+where we also demonstrate its implementation using IBM's quantum computers for 
+the particular case of single-qubit Pauli channels.
+
+Expanding beyond discrete Pauli channels,
+we introduce the concept of Pauli dynamical maps, 
+defined as a continuous parametrization of
+$N$-qubit Pauli channels. 
+Therefore, in section \ref{sec: 1PR Circuits}
+we shift our focus to study parametrized
+quantum channels, 
+aiming to
+adapt the algorithm developed for channels 
+to dynamical maps. 
+Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
+which  sets the mathematical conditions for the transformations that 
+can be done using a parametrized circuit with the condition that only one
+ single-qubit operation in the circuit may depend on the parameter.
+Finally, in section \ref{sec: 1PR circuit for a Pauli map},
+we conclude about the 
+Pauli dynamical maps that fulfill the conditions of theorem \ref{theorem2}. 
+}
+
+\tbnote{Y esto ya se va entonces}
+{\color{red}
 The paper is organized as follows: In section \ref{sec: Pauli Channels} 
@@
 we apply this theorem for the circuit of Pauli dynamical
-maps and show a couple of maps that fulfill the theorem's conditions.
+maps and show a couple of maps that fulfill the theorem's conditions.}
 
@@
 can be implemented with a 1PR circuit.
-Given the condition of theorem \ref{theorem2}, the curve of states of \eref{eq: parametrized state}  needed 
+{\color{red} Given the condition of theorem \ref{theorem2}, the curve of states of \eref{eq: parametrized state}  needed 
 to implement the map
-has to be constructed with only one parametrized rotation\cpnote{no entiendo esta frase}. 
-Therefore, the results of the last section imply that the the map
+has to be constructed with only one parametrized rotation.}
+\cpnote{no entiendo esta frase} 
+\tbnote{Si, no está bien escrita. Cambiar por:}
+{\color{purple} For this, the curve of states of \eref{eq: parametrized state} 
+has to be constructed with only one parametrized rotation,
+so it has to satisfy the conditions of theorem \ref{theorem2}.
+}
+Therefore, this implies that the the map
 \begin{eqnarray}
@@
 \fref{fig:curves1}. 
+{\color{purple} The examples we show include some the most common maps: the bit flip, phase flip, bit-phase flip and depolarizing.
+However, we also include a more uncommon map, which we call the parabolic dynamical map,
+defined in \eref{eq:parab} and shown in \fref{fig:curves1}.
+This map traces a parabola inside the tetrahedron connecting two of its vertices
+and it describes a frontier in the tetrahedron between Pauli channels
+that are reachable by Lindbladian dynamics and those that are not~\cite{Davalos}.
+}
 
@@
 Then, taking the $\beta_j$ to be real,
-this curve of states is \cpnote{supongo qeye hay muchas curvas. Es correcto eso? Quizá un ``this curve of states can be'' sea mas preciso.}
+this curve of states can be \cpnote{supongo qeye hay muchas curvas. Es correcto eso? Quizá un ``this curve of states can be'' sea mas preciso.} 
+\tbnote{Sí es correcto, va}
 \begin{align*}
@@
 \item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
-\cpnote{este mapa no es muy comun. Toca comentar algo al respecto. No se si acá o mas arriba. Si, ya se donde. En el parrafo antes de los ejemplos. }
+\cpnote{este mapa no es muy comun. Toca comentar algo al respecto. No se si acá o mas arriba. Si, ya se donde. En el parrafo antes de los ejemplos. } \tbnote{Va, listo, lo puse en morado}
 \begin{eqnarray}
-\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3 ,
+\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3,
+\label{eq:parab}
 \end{eqnarray}
@@
 If we take the $\beta_j$ to be real,
-the curve of states needed on the ancilla qubits is:
+the curve of states needed on the ancilla qubits can be:
 \begin{eqnarray}
@@
 \cpnote{Sigo sin saber coo escoges la matriz V. Espero platicar contigo}
+\tbnote{No, no lo hago con CUE ni nada así por lo de que el
+primer renglon debe de tner una forma particular y no sabría cómo agregar eso tras
+elegir una matriz de CUE.}
+\tbnote{Lo que hago es empezar con ese renglon y busco un segundo renglón que sea ortogonal al primero y normalizado.
+Para ello, tomo tres vectores $w_1, w_2, w_3$
+normalizados y ortogonales al primer renglon.
+Entonces, el segundo renglon será en general
+de la forma $r_1 w_1 + r_2 w_2 + r_3 w_3$
+con $r_i$ complejos y que $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ (para que el 
+segundo renglon esté normalizado).
+Entonces, busco esos $r_1, r_2, r_3$ al azar  
+(básicamente las partes reales e imaginarias
+de las $r_i$ deben de estar en una 6-esfera,
+por lo que escojo un punto al azar en dicha esfera).}
+
 and use it to define the states $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$.
@@
 acomode bien a lo que ambos nos parezca.}
+\tbnote{Jaja sí, va}
 \end{itemize}
@@
 
-In this study, we focused on the analysis of Pauli channels in $N$-qubit systems and
+In this work, we focused on the analysis of Pauli channels in $N$-qubit systems and
 developed an algorithm to implement them on a quantum computer.
@@
 which can be done in a much straightforward manner.
+{\color{purple}
+Consequently, this work presents another example of the
+simulation of open quantum systems, and their
+implementation in a quantum computer. }
 
@@
 only one single-qubit parametrized rotation.
+{\color{purple} Therefore, it can be useful for simplifying any algorithm
+that requires a parametrized quantum circuit,
+such as those for quantum machine learning.}
 
@@
 dale una pensanda y si no, leelo a la luz de lo uqe escribiste. En todo caso, me parece una
-muy buena primera iteracion para las conclusiones!!! }
+muy buena primera iteracion para las conclusiones!! }
+\tbnote{Ah, supongo que lo de volver a expandir y hablar en general para terminar de hacer la forma de ``hourglass''
+en el artículo. Agregué algo en morado para eso.}
+
 % }}}
@@
 % }}}
+
 \section{Acknowledgments} % {{{
@@
 \tbnote{Poner la bibliografía como ellos dicen (copiarla toda aquí en lugar de ponerla en un archivo .bib)}
-\textbf{References}
 \bibliography{Bibliography}

### 2023-06-14 main.tex
Ediciones

@@
 
+\tbnote{O algo como lo siguiente:}
+
+{\color{purple}
+In this work, we found a quantum algorithm for 
+simulating Pauli channels in $N$-qubit systems and
+generalized it to Pauli dynamical maps.
+We observed that the fidelity of 
+simulating Pauli channels on one of IBM's quantum computers
+was highest for those closest to the totally depolarizing channel and fell off close to unitary channels,
+which was attributed to the current limitations of quantum computers.
+Additionally, when working with Pauli dynamical maps,
+we determined in theorem \ref{theorem2} the general mathematical conditions
+under which a parametrized quantum circuit requires only one single-qubuit rotation dependent on the parameter.
+
+Therefore, this work presents another example of the current
+exploration into simulating open quantum
+systems in quantum computers,
+and we find the big effect that the error of quantum computers have
+on these simulations.
+On the other hand, the result
+of theorem \ref{theorem2}
+can be used for any quantum algorithm that requires parametrized circuits,
+such as those used for quantum machine learning.
+}
+
 % }}}

### 2023-06-22 main.tex
Cambios

--- 2023-06-13 main.tex
@@
 acomode bien a lo que ambos nos parezca.}
-\tbnote{Jaja sí, va}
+\tbnote{Jaja sí, va}\\
+
+Finally, we choose a unitary matrix $V$ with the condition that its first
+row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
+with $\theta$ an arbitrary real number.
+That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
+and since $V$ is unitary, these unprimed vectors will fulfill the conditions of \eref{eq:conditions-vecs}.
+Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
+since it implies that when $s=0$, the 
+state created in \eref{eq:vec}
+is
+$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
+which  corresponds with applying the identity channel.
+
+The choice of such a matrix $V$ can be done at random as follows:
+After setting the first row,
+construct three vectors $\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to it
+using the Gram-Schmidt process.
+Then select random complex numbers $r_1, r_2, r_3$ such
+that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and
+define the second row of $V$ to be
+$r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
+Once the first two rows are chosen, use Gram-Schmidt to find two vectors
+$\vec{v}_1, \vec{v}_2$ orthogonal to 
+them and similarly define the third row as $q_1 \vec{v}_1+ q_2 \vec{v}_2$
+with $|q_1|^2 + |q_2|^2$ and $q_1,q_2$
+selected at random. 
+Finally, there is only one choice for the fourth row so that it is 
+orthonormal to the first three
+and a random phase can be given to it.
+
 \end{itemize}
@@
 en el artículo. Agregué algo en morado para eso.}
+
+\tbnote{Mejor quitar todo lo anterior y dejar esto:}
+
+{\color{purple}
+In this work, we found a quantum algorithm for 
+simulating Pauli channels in $N$-qubit systems and
+generalized it to Pauli dynamical maps.
+We observed that the fidelity of 
+simulating single-qubit Pauli channels on one of IBM's quantum computers
+was highest for those closest to the totally depolarizing channel and fell off close to unitary channels,
+which was attributed to the current limitations of quantum computers.
+Additionally, when working with Pauli dynamical maps,
+we determined in theorem \ref{theorem2} the general mathematical conditions
+under which a parametrized quantum circuit requires only one single-qubit rotation dependent on the parameter.
+
+Therefore, this work presents another example of the current
+exploration into simulating open quantum
+systems in quantum computers,
+and we observe the big effect that the error of quantum computers have
+on these simulations.
+On the other hand, the result
+of theorem \ref{theorem2}
+shows what can be done with the condition of using only one
+parametrized rotation and
+can be applied to any quantum algorithm that requires parametrized circuits,
+such as those used for quantum machine learning.
+}
 

### 2023-06-22 main.tex
Programming the flux capacitor

@@
 {\Large
-\textbf\newline{Title of submission to PLOS journals} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
+\textbf\newline{Quantum simulation of Pauli channels and dynamical maps: algorithm and implementation } % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
 }
@@
 \section*{Abstract}
-Pauli channels are fundamental in the context of quantum computing as they model noise in quantum devices. 
-We propose a quantum algorithm for simulating Pauli channels on quantum computers 
+\cpnote{Revisar}
+Pauli channels are fundamental in the context of quantum computing as they
+model noise in quantum devices.  We propose a quantum algorithm for simulating
+Pauli channels on quantum computers 
 and extend it to encompass Pauli dynamical maps 
@@
 for the case of one qubit, and the fidelity of this implementation is obtained. 
-
 % Please keep the Author Summary between 150 and 200 words
@@
 \section{Introduction} % {{{
-
-\cpnote{Porfa 3 propuestas de titulo y un intento de abstract. Ese es mas facil que la intro!
-de neuvo, quizá vale la pena que te einspires en otros abstracts de PlosOne}
-\tbnote{Va, ya puse un abstract basado en lo que vi en articulos de PlosOne}
-\tbnote{Para el título, tengo las siguientes propuestas:}
-{\color{green}
-\begin{itemize}
-\item Quantum Algorithm for Simulation of Parametrized Pauli Channels.
-\item Parametrized Pauli Channels Simulation in Quantum Computes.
-\item Quantum Simulation of Pauli Channels: Algorithm, Implementation and 
-generalization to parametrized channels.
-\end{itemize}
-}
-
-Puntos hechos en el artículo:
-\begin{itemize}
-\item Propuesta de algoritmo para canal es de Pauli de N qubits y su simulación en compus cuánticas
-\item Condiciones para que un circuito parametrizado use una sola rotación parametrizada. En particular luego aplicadas al algoritmo para mapas dinámicos de Pauli.
-\end{itemize}
 
@@
 
-In this article, our first objective is to present a 
-quantum algorithm capable of simulating Pauli channels on quantum computers, 
-and we demonstrate its implementation using IBM's quantum computers. 
-This algorithm is designed to simulate any Pauli channel on a system of $N$ qubits,
-and works by utilizing $2N$ ancilla qubits.
-
-Expanding beyond discrete Pauli channels,
-we introduce the concept of Pauli dynamical maps, 
-defined as a continuous parametrization of
-$N$-qubit Pauli channels. 
-We adapt the algorithm developed for Pauli channels 
-to accommodate these dynamical maps by employing a 
-parametrized quantum circuit. 
-Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
-which outlines the types of transformations that 
-can be done using a parametrized circuit with the condition that only one
- single-qubit operation in the circuit may depend on the parameter.
-We explicitly find the mathematical conditions for these types of
-transformations and conclude about which 
-Pauli dynamical maps can be done with them. 
-\cpnote{Me gustaron mucho estos dos ultimos parrafos. Croe que se puede ir mencionando las secciones
-y poner la info del siguiente parrafo aca. Ahora, no lo pongas a lo bestia, sino realmente
-integrando e hilando las ideas. Si hay preguntas, me dices que tos.}
-\tbnote{Va, pongo una versión de estos dos últimos párrafos pero incluyendo lo de las secciones del siguiente aquí:}
+% In this article, our first objective is to present a 
+% quantum algorithm capable of simulating Pauli channels on quantum computers, 
+% and we demonstrate its implementation using IBM's quantum computers. 
+% This algorithm is designed to simulate any Pauli channel on a system of $N$ qubits,
+% and works by utilizing $2N$ ancilla qubits.
+% 
+% Expanding beyond discrete Pauli channels,
+% we introduce the concept of Pauli dynamical maps, 
+% defined as a continuous parametrization of
+% $N$-qubit Pauli channels. 
+% We adapt the algorithm developed for Pauli channels 
+% to accommodate these dynamical maps by employing a 
+% parametrized quantum circuit. 
+% Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
+% which outlines the types of transformations that 
+% can be done using a parametrized circuit with the condition that only one
+%  single-qubit operation in the circuit may depend on the parameter.
+% We explicitly find the mathematical conditions for these types of
+% transformations and conclude about which 
+% Pauli dynamical maps can be done with them. 
+% \cpnote{Me gustaron mucho estos dos ultimos parrafos. Croe que se puede ir mencionando las secciones
+% y poner la info del siguiente parrafo aca. Ahora, no lo pongas a lo bestia, sino realmente
+% integrando e hilando las ideas. Si hay preguntas, me dices que tos.}
+% \tbnote{Va, pongo una versión de estos dos últimos párrafos pero incluyendo lo de las secciones del siguiente aquí:}
+%
 
@@
 }
-
-\tbnote{Y esto ya se va entonces}
-{\color{red}
-The paper is organized as follows: In section \ref{sec: Pauli Channels} 
-we provide  the definition of quantum channels and focus specifically on Pauli channels for systems of
-$N$ qubits. 
-In section \ref{sec: Circuit for a Pauli Channel} we present  the proposed circuit 
-for implementing a Pauli channel of $N$ qubits in a quantum computer. 
-Furthermore, we simulate it on IBM’s computers for the special case of $N=1$
-and obtain the fidelity of this implementation.  
-Section \ref{sec: 1PR Circuits} shifts the focus to parametrized quantum circuits, 
-aiming to generalize the circuit for Pauli channels to accommodate Pauli dynamical maps. 
-We introduce theorem \ref{theorem2} to determine the operations that can be 
-performed using a parametrized circuit 
-with only one single-qubit operation dependent on the parameter.
-Finally, in section \ref{sec: 1PR circuit for a Pauli map} 
-we apply this theorem for the circuit of Pauli dynamical
-maps and show a couple of maps that fulfill the theorem's conditions.}
 
@@
 
-\cpnote{Evaluar si al final ponemos algo al respecto de este comentario}
-\cpnote{Del circuito, parece ue las fases de las bs gammas no omportan mucho (o nada). 
-Esa libertad la hemos considerado? De alguna manera colapsan curvas de las que
-hemos visto?} \tbnote{Sí, es una libertad que se tiene y he considerado y significa que hay muchas elecciones de $b_{\gamma}$ para un mismo canal.
-Es una de las varias cosas que complicaba determinar uno a uno qué canales se pueden hacer.}
+% \cpnote{Evaluar si al final ponemos algo al respecto de este comentario}
+% \cpnote{Del circuito, parece ue las fases de las bs gammas no omportan mucho (o nada). 
+% Esa libertad la hemos considerado? De alguna manera colapsan curvas de las que
+% hemos visto?} \tbnote{Sí, es una libertad que se tiene y he considerado y significa que hay muchas elecciones de $b_{\gamma}$ para un mismo canal.
+% Es una de las varias cosas que complicaba determinar uno a uno qué canales se pueden hacer.}
+%
 
@@
 
+{\color{purple}
 Finally, we choose a unitary matrix $V$ with the condition that its first
@@
 and a random phase can be given to it.
+}
 

### 2023-06-22 main.tex
Your heart's been aching but you're too shy to say it

@@
 
-Since their inception, quantum computers were proposed as powerful tools for the simulation of quantum systems,
-with a recent particular interest in simulating the evolution of open quantum systems, 
-which can be described by the theory of quantum
-channels~\cite{cleve,Zanetti,Xin,Wei}. \tbnote{Cita a Andrea}
-{\color{red} For example, this has been done using optical arrangements
-to study the emergence of multipartite entanglement \cite{Andrea,Andrea_AD}.}
-\cpnote{Se siente forzada. nos toca encontrar mas ejemplos e introducirla de
-manera mas natural. Quizá mas adelante}
-\tbnote{Va, es cierto.
-Puedo incluir más trabajos y hablarlo más en general para que no se sienta forzado:}
-{\color{purple}
+Since their inception, quantum computers were proposed as powerful tools for
+the simulation of quantum systems~\cite{feynman1982simulating}. 
+% Several 
+% kinds of quantum systems have been simulated, like \cpnote{PONER ALGO ACA Y CITAR. 
+% Te puedes inspirar en las introducciones de articulos que simulen sistemas cuanticos}. 
+Being open quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
+practical~\cite{breuer2007theory} interest, there has been efforts
+towards the simulation of the evolution of open quantum
+systems~\cite{cleve,Zanetti,Xin,Wei}\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.}.
 Such systems have been simulated because of their many applications, 
@@
 and modeling non-Markovian dynamics~\cite{Marsden}.
-}
-
-Among the various types of quantum channels for a system of qubits, 
-Pauli channels hold special significance due to their simplicity 
-and relevance in the context of quantum computing~\cite{Davalos,Zbigniew,geometry}, 
-\cpnote{Aca citar nuestros trabajos con Davalos. } \tbnote{Ya agregué la cita}
-as they serve as effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.
-\cpnote{Creo que la transición de general a particular va demasiado rapido. Quizá hacerle 
-ver a Tomas y luego reescribirlo yo}
-\tbnote{Va, sí lo veo, gracias!}
-
-\cpnote{De nuevo una transicion muy abrupta. Para que ver los circuitos? Priero 
-hablar de los circuitos, quizá una frase, luego hablar de los parametrizadso, 
-Aca quiza citar a Barrero en innsbruk con sus vainas de enlazamiento}
-\tbnote{Lo de Barreiro es una de las citas que agregué nuevas arriba}
-\tbnote{Para lo de lo abrupto, quizá una frase como:} 
-{\color{purple} To represent the algorithms
-done in quantum computers, either
-to simulate a physical system or for some other purpose,
-one often uses a quantum circuit~\cite{chuangbook}.}
-In this work, we shall also work with parametrized quantum circuits, that is,  
-quantum circuits in which some of the operations depend on variable parameters~\cite{cerezo}. 
-These circuits play an important 
-part in applications such as quantum machine learning~\cite{Benedetti}
-and describing general quantum transformations dependent on parameters. Substantial research has been 
-devoted to enhancing the efficiency of these circuits~\cite{Watanabe,Rasmussen}.
-
-% In this article, our first objective is to present a 
-% quantum algorithm capable of simulating Pauli channels on quantum computers, 
-% and we demonstrate its implementation using IBM's quantum computers. 
-% This algorithm is designed to simulate any Pauli channel on a system of $N$ qubits,
-% and works by utilizing $2N$ ancilla qubits.
-% 
-% Expanding beyond discrete Pauli channels,
-% we introduce the concept of Pauli dynamical maps, 
-% defined as a continuous parametrization of
-% $N$-qubit Pauli channels. 
-% We adapt the algorithm developed for Pauli channels 
-% to accommodate these dynamical maps by employing a 
-% parametrized quantum circuit. 
-% Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
-% which outlines the types of transformations that 
-% can be done using a parametrized circuit with the condition that only one
-%  single-qubit operation in the circuit may depend on the parameter.
-% We explicitly find the mathematical conditions for these types of
-% transformations and conclude about which 
-% Pauli dynamical maps can be done with them. 
-% \cpnote{Me gustaron mucho estos dos ultimos parrafos. Croe que se puede ir mencionando las secciones
-% y poner la info del siguiente parrafo aca. Ahora, no lo pongas a lo bestia, sino realmente
-% integrando e hilando las ideas. Si hay preguntas, me dices que tos.}
-% \tbnote{Va, pongo una versión de estos dos últimos párrafos pero incluyendo lo de las secciones del siguiente aquí:}
-%
-
-{\color{purple}  
-In this article,
-after providing the definition of quantum
-channels and $N$-qubit Pauli channels
-in section \ref{sec: Pauli Channels},
- our first objective is to present a 
-quantum algorithm capable of simulating Pauli channels on quantum computers.
-We do this in section \ref{sec: Circuit for a Pauli Channel},
-where we also demonstrate its implementation using IBM's quantum computers for 
-the particular case of single-qubit Pauli channels.
-
-Expanding beyond discrete Pauli channels,
-we introduce the concept of Pauli dynamical maps, 
-defined as a continuous parametrization of
-$N$-qubit Pauli channels. 
-Therefore, in section \ref{sec: 1PR Circuits}
-we shift our focus to study parametrized
-quantum channels, 
-aiming to
-adapt the algorithm developed for channels 
-to dynamical maps. 
-Furthermore, we contribute to the body of work related to parametrized quantum circuits by establishing theorem \ref{theorem2},
-which  sets the mathematical conditions for the transformations that 
-can be done using a parametrized circuit with the condition that only one
- single-qubit operation in the circuit may depend on the parameter.
-Finally, in section \ref{sec: 1PR circuit for a Pauli map},
-we conclude about the 
-Pauli dynamical maps that fulfill the conditions of theorem \ref{theorem2}. 
-}
+Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
+and withing them, the simplest class of channels that produce decoherence are
+Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
+effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.
+
+To represent the algorithms implemented in quantum computers, either to
+simulate a physical system or for some other purpose, one often uses a quantum
+circuit~\cite{chuangbook}.  In this work, we shall also work with parametrized
+quantum circuits, that is,  quantum circuits in which some of the operations
+depend on variable parameters~\cite{cerezo}.  These circuits play an important
+part in applications such as quantum machine learning~\cite{Benedetti} and
+describing general quantum transformations dependent on parameters. Substantial
+research has been devoted to enhancing the efficiency of these
+circuits~\cite{Watanabe,Rasmussen}.
+
+We start by providing the definition of quantum channels, the general framework
+used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
+Our first objective is to present a quantum algorithm capable of simulating
+Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
+for a Pauli Channel}, where we also demonstrate its implementation using IBM's
+quantum computers for the particular case of single-qubit Pauli channels. 
+Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
+dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
+channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
+study parametrized quantum channels, aiming to adapt the algorithm developed
+for channels to dynamical maps.  Furthermore, we contribute to the body of work
+related to parametrized quantum circuits by establishing a theorem,
+which  sets the mathematical conditions for the transformations
+that can be done using a parametrized circuit with the condition that only a
+controlled \cpnote{el caso general es controlado, correcto?} single-qubit
+operation in the circuit may depend on the parameter.  Finally, in
+section \ref{sec: 1PR circuit for a Pauli map}, we conclude about the Pauli
+dynamical maps that fulfill the conditions of theorem \ref{theorem2}.
 
@@
 
-Finally, using the representation of Pauli channels in a tetrahedron as
-in \eref{eq: conditions-tetrahedron},
-we show in \fref{fig:fids} the diamond fidelity defined by \eref{eq:diamond-fid} for the channels
-analyzed. 
-We can see that channels close to the 
-completely depolarizing
-channel (that is close to the center of the tetrahedron)
-have a high $f$, while those 
-close to unitary channels have much lower $f$.
-This means that channels closer to the 
-completely depolarizing channel are simulated better on the quantum computers.
-This is reasonable because quantum computers are prone to errors
-that depolarize qubits, which isn't very problematic
-when trying to simulate depolarization but it is 
-when simulating unitary processes. Moreover, the algorithm of \fref{fig:
-circuit-pauli-1} is not optimal for unitary channels (that is, the channels
-corresponding to the vertices of the tetrahedron).  These straightforward
-channels could be accomplished more efficiently by simply applying the
-corresponding Pauli operation directly. Nevertheless, due to its general design
-to accommodate any Pauli channel, the algorithm employs numerous quantum gates
-even in such scenarios.
-\cpnote{Iterar este parrafo cuando estemos cerca del final. Ta un tilin chafa.}
+Finally, using the representation of Pauli channels in a tetrahedron as in
+\eref{eq: conditions-tetrahedron}, we show in \fref{fig:fids} the diamond
+fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
+see that channels close to the completely depolarizing channel (that is close
+to the center of the tetrahedron) have a high $f$, while those close to unitary
+channels have much lower $f$.  This is reasonable because quantum computers are
+prone to errors that depolarize qubits, which isn't very problematic when
+trying to simulate depolarization but it is when simulating unitary processes.
+Moreover, the algorithm of \fref{fig: circuit-pauli-1} is not optimal for
+unitary channels (that is, the channels corresponding to the vertices of the
+tetrahedron).  These straightforward channels could be accomplished more
+efficiently by simply applying the corresponding Pauli operation directly.
+Nevertheless, due to its general design to accommodate any Pauli channel, the
+algorithm employs numerous quantum gates even in such scenarios.
 
@@
 \fref{fig:curves1}. 
-{\color{purple} The examples we show include some the most common maps: the bit flip, phase flip, bit-phase flip and depolarizing.
-However, we also include a more uncommon map, which we call the parabolic dynamical map,
+The examples we show include some the most common maps: the bit flip, phase flip, bit-phase flip and depolarizing.
+However, we also include the parabolic dynamical map,
 defined in \eref{eq:parab} and shown in \fref{fig:curves1}.
@@
 that are reachable by Lindbladian dynamics and those that are not~\cite{Davalos}.
-}
 
@@
 Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
-qubits is such that 
-${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 = {|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.
-Then, taking the $\beta_j$ to be real,
-this curve of states can be \cpnote{supongo qeye hay muchas curvas. Es correcto eso? Quizá un ``this curve of states can be'' sea mas preciso.} 
-\tbnote{Sí es correcto, va}
+qubits is such that ${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 =
+{|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.  Then, taking the $\beta_j$ to be
+real, the curve of states can be 
 \begin{align*}
@@
 \item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
-\cpnote{este mapa no es muy comun. Toca comentar algo al respecto. No se si acá o mas arriba. Si, ya se donde. En el parrafo antes de los ejemplos. } \tbnote{Va, listo, lo puse en morado}
 \begin{eqnarray}
@@
 \item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
-\item[3.] Finally, we choose a unitary matrix $V$ \cpnote{Esta supongo qeu 
-la escoges aleatoriamente, y que la tomas por ahi del CUE. Lo platicamos y metemos 
-los detalles. }
-\cpnote{Sigo sin saber coo escoges la matriz V. Espero platicar contigo}
-\tbnote{No, no lo hago con CUE ni nada así por lo de que el
-primer renglon debe de tner una forma particular y no sabría cómo agregar eso tras
-elegir una matriz de CUE.}
-\tbnote{Lo que hago es empezar con ese renglon y busco un segundo renglón que sea ortogonal al primero y normalizado.
-Para ello, tomo tres vectores $w_1, w_2, w_3$
-normalizados y ortogonales al primer renglon.
-Entonces, el segundo renglon será en general
-de la forma $r_1 w_1 + r_2 w_2 + r_3 w_3$
-con $r_i$ complejos y que $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ (para que el 
-segundo renglon esté normalizado).
-Entonces, busco esos $r_1, r_2, r_3$ al azar  
-(básicamente las partes reales e imaginarias
-de las $r_i$ deben de estar en una 6-esfera,
-por lo que escojo un punto al azar en dicha esfera).}
-
-and use it to define the states $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$.
-This way, given that the primed states are orthogonal and their squared norms add up to one,
-so do the unprimed states and therefore 
-fulfill the conditions of  \eref{eq:conditions-vecs}.
-
-However, since a Pauli dynamical map should begin at the
-identity channel, we need to add the condition that $|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$, with
-$\theta$ an arbitrary real number. 
-This way, when $s = 0$ in \eref{eq:vec}, the constructed state
-is $e^{i \theta}|0\rangle$, which
-corresponds with the identity channel.
-
-To fulfill this additional condition,  we restrict the first row of
-$V$ written as a matrix in 
-the computational basis to be $e^{i\theta} (|\vec{a}|, |\vec{b}|, |\vec{c}|,0)$. 
-That way, 
-\begin{align*}
-|a\rangle + |b\rangle + |c\rangle = V (|a'\rangle + |b'\rangle + |c'\rangle ) = V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T = {(e^{i\theta},0,0,0)}^T.
-\end{align*}
-The last equality comes from the fact
-that the first entry of $V{(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$
-is obtained by calculating the dot product of the first row of $V$ with ${(|\vec{a}|, |\vec{b}|, |\vec{c}|,0)}^T$, which gives
-$e^{i\theta}$. 
-Furthermore, the other entries have to be $0$,
-since otherwise the norm of the result would be greater than
-$1$ but $V$ is unitary and therefore preserves the norm.
-\cpnote{Creo qeu ahora está demasiado largo. jejej. hablemos y tratamos de hacer algo que se 
-acomode bien a lo que ambos nos parezca.}
-\tbnote{Jaja sí, va}\\
-
-{\color{purple}
+\item[3.] 
 Finally, we choose a unitary matrix $V$ with the condition that its first
 row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
-with $\theta$ an arbitrary real number.
+with $\theta$ a uniform random phase.
 That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
-and since $V$ is unitary, these unprimed vectors will fulfill the conditions of \eref{eq:conditions-vecs}.
+and since $V$ is unitary, these unprimed vectors will fulfill the conditions of
+\eref{eq:conditions-vecs}\cpnote{aun no construimos la $V$ asi que aun no es
+unitaria. Aclarame ese punto y le sigo al resto del parrafo}.
 Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
@@
 which  corresponds with applying the identity channel.
-
-The choice of such a matrix $V$ can be done at random as follows:
-After setting the first row,
-construct three vectors $\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to it
-using the Gram-Schmidt process.
-Then select random complex numbers $r_1, r_2, r_3$ such
-that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and
-define the second row of $V$ to be
-$r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
+Next, construct three vectors $\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to
+the first row using the Gram-Schmidt process.  Then select random complex
+numbers $r_1, r_2, r_3$ such that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and define
+the second row of $V$ to be $r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
 Once the first two rows are chosen, use Gram-Schmidt to find two vectors
@@
 and a random phase can be given to it.
-}
-
 \end{itemize}
@@
 \section{Conclusion} % {{{
-\tbnote{Primera versión para ir teniendo algo escrito }\\
-
-In this work, we focused on the analysis of Pauli channels in $N$-qubit systems and
-developed an algorithm to implement them on a quantum computer.
- By running this algorithm on one of IBM's quantum computers, 
-we observed that the fidelity of the simulated channels was highest for those 
-closely resembling the totally depolarizing channel, 
-and decreased as the channels approached unitary behavior. 
-This performance can be attributed to the limitations and susceptibility to errors 
-inherent in current quantum computers. 
-Furthermore, being as general as it is,
-the algorithm isn’t efficient for unitary channels, 
-which can be done in a much straightforward manner.
-{\color{purple}
-Consequently, this work presents another example of the
-simulation of open quantum systems, and their
-implementation in a quantum computer. }
-
-Additionally, we extended our investigation 
-to encompass Pauli dynamical maps by leveraging the concept of a parametrized quantum circuit. 
-Through this extension, we determined the mathematical conditions under which a
-parametrized quantum circuit requires only one single-qubit 
-rotation dependent on the parameter. Notably, theorem \ref{theorem2} establishes these
- conditions as applicable to any parametrized quantum circuit, 
- providing a general framework to describe the type of algorithms achievable using 
-only one single-qubit parametrized rotation.
-{\color{purple} Therefore, it can be useful for simplifying any algorithm
-that requires a parametrized quantum circuit,
-such as those for quantum machine learning.}
-
-\cpnote{Leiste como escribir una conclusion? Aca falta algo importante. Si ya lo leiste, 
-dale una pensanda y si no, leelo a la luz de lo uqe escribiste. En todo caso, me parece una
-muy buena primera iteracion para las conclusiones!! }
-\tbnote{Ah, supongo que lo de volver a expandir y hablar en general para terminar de hacer la forma de ``hourglass''
-en el artículo. Agregué algo en morado para eso.}
-
-\tbnote{Mejor quitar todo lo anterior y dejar esto:}
+
+\cpnote{Reitera. Dale a lo qeu discutimos el espacio. a lo de la decoherencia nota
+que no lo tomamos como un resultado importante. Aca le das mucho mas espacio 
+del que croe que merece. Inspirate en la intro. }
 
@@
 \section{Acknowledgments} % {{{
-Support by projects CONACyT 285754, 254515 and UNAM-PAPIIT IG100518, IG101421 is
-acknowledged.
+Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.
 

### 2023-06-23 main.tex
Otros cambios

@@
 towards the simulation of the evolution of open quantum
-systems~\cite{cleve,Zanetti,Xin,Wei}\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.}.
+systems~\cite{cleve,Zanetti,Xin,Wei}.\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.} \tbnote{La primera habla al principio en general
+de simulación de sistemas abiertos y los otros tres porque se relacionan más con este trabajo
+porque lo hacen en particular con el formalismo de canales cuánticos}
 Such systems have been simulated because of their many applications, 
@@
 that can be done using a parametrized circuit with the condition that only a
-controlled \cpnote{el caso general es controlado, correcto?} single-qubit
+controlled \cpnote{el caso general es controlado, correcto?} \tbnote{Sí} single-qubit
 operation in the circuit may depend on the parameter.  Finally, in
@@
 \eref{eq:conditions-vecs}\cpnote{aun no construimos la $V$ asi que aun no es
-unitaria. Aclarame ese punto y le sigo al resto del parrafo}.
+unitaria. Aclarame ese punto y le sigo al resto del parrafo}
+\tbnote{Ah, es que más bien la idea era primero decir que el siguiente paso es
+usar una matriz unitaria (con la condición
+mencionada sobre el primer renglón)
+y explicar cómo la usamos y por qué.
+Ya luego mostrar cómo se puede construir dicha 
+matriz al azar. También se puede hacer al revés,
+pero no me convencía decir todo lo de cómo 
+construir la matriz sin decir antes para qué}
+.
 Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
@@
 which  corresponds with applying the identity channel.
-Next, construct three vectors $\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to
-the first row using the Gram-Schmidt process.  Then select random complex
-numbers $r_1, r_2, r_3$ such that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and define
+
+Such a matrix $V$ can be randomly constructed by first finding three vectors 
+$\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to
+the first row using the Gram-Schmidt process.  Then selecting random complex
+numbers $r_1, r_2, r_3$ such that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and defining
 the second row of $V$ to be $r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
@@
 del que croe que merece. Inspirate en la intro. }
+\tbnote{Ah va, listo}
 
@@
 simulating Pauli channels in $N$-qubit systems and
-generalized it to Pauli dynamical maps.
-We observed that the fidelity of 
-simulating single-qubit Pauli channels on one of IBM's quantum computers
-was highest for those closest to the totally depolarizing channel and fell off close to unitary channels,
-which was attributed to the current limitations of quantum computers.
-Additionally, when working with Pauli dynamical maps,
-we determined in theorem \ref{theorem2} the general mathematical conditions
-under which a parametrized quantum circuit requires only one single-qubit rotation dependent on the parameter.
-
-Therefore, this work presents another example of the current
+generalized it to Pauli dynamical maps
+by using parametrized quantum circuits.
+Furthermore, we implemented single-qubit Pauli channels
+on one of IBM's quantum computers
+and obtained their fidelities. 
+Finally, when working with Pauli dynamical maps,
+we searched for a way of simplifying the parametrized circuit
+by requiring that only one single-qubit rotation depends on the parameter.
+In theorem \ref{theorem2} we found the general mathematical conditions for 
+this, applicable to any parametrized circuit.
+
+Therefore, this work presents yet another example of the current
 exploration into simulating open quantum

### 2023-06-23 main.tex
Same as last commit with changes

@@
 can be implemented with a 1PR circuit.
-{\color{red} Given the condition of theorem \ref{theorem2}, the curve of states of \eref{eq: parametrized state}  needed 
-to implement the map
-has to be constructed with only one parametrized rotation.}
-\cpnote{no entiendo esta frase} 
-\tbnote{Si, no está bien escrita. Cambiar por:}
 {\color{purple} For this, the curve of states of \eref{eq: parametrized state} 
@@
 }
-Therefore, this implies that the the map
+\cpnote{Sigue estando redundante. Dices que cuales se pueden implentar con 1pr circuit y que 
+enticones tiene que ser construidas con un 1pr. Quizá integra las dos frases o has algo}
+Therefore, this implies that the map
 \begin{eqnarray}

### 2023-06-23 main.tex
Citas

@@
 towards the simulation of the evolution of open quantum
-systems~\cite{cleve,Zanetti,Xin,Wei}.\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.} \tbnote{La primera habla al principio en general
-de simulación de sistemas abiertos y los otros tres porque se relacionan más con este trabajo
-porque lo hacen en particular con el formalismo de canales cuánticos}
+systems~\cite{cleve,Zanetti,Xin,Wei}.\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.}
+\tbnote{Cambié un poco, agregué unos artículos que vi mucho más populares:}
+{\color{purple} 
+open quantum systems~\cite{Garcia, Wang,Weimer} and specifically for
+quantum channels~\cite{Xin,Wei,Zanetti}.
+}
+
 Such systems have been simulated because of their many applications, 
@@
 that can be done using a parametrized circuit with the condition that only a
-controlled \cpnote{el caso general es controlado, correcto?} \tbnote{Sí} single-qubit
+controlled single-qubit
 operation in the circuit may depend on the parameter.  Finally, in

### 2023-06-29 main.tex
I'm sorry.

@@
 \usepackage{hyperref}
-\usepackage[inline]{showlabels}
+% \usepackage[inline]{showlabels}
 \usepackage{bbm,bm}
@@
 \usepackage{amsfonts}
-\usepackage{showlabels}
 
@@
 \vspace*{0.2in}
-
-% Title must be 250 characters or less.
 
@@
 \section*{Abstract}
-\cpnote{Revisar}
+% \cpnote{Revisar}
 Pauli channels are fundamental in the context of quantum computing as they
-model noise in quantum devices.  We propose a quantum algorithm for simulating
-Pauli channels on quantum computers 
+model the simplest kind of noise in quantum devices.  We propose a quantum
+algorithm for simulating
+Pauli channels 
 and extend it to encompass Pauli dynamical maps 
@@
 We also establish the mathematical conditions for an
-N-qubit transformation to be achievable using a parametrized circuit where
+$N$-qubit transformation to be achievable using a parametrized circuit where
 only one single-qubit operation depends on the parameter. 
 The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
-for the case of one qubit, and the fidelity of this implementation is obtained. 
+for the case of one qubit, and the fidelity of this implementation is reported. 
 % Please keep the Author Summary between 150 and 200 words
@@
 
-\linenumbers
+% \linenumbers
 
@@
 Since their inception, quantum computers were proposed as powerful tools for
-the simulation of quantum systems~\cite{feynman1982simulating}. 
-% Several 
-% kinds of quantum systems have been simulated, like \cpnote{PONER ALGO ACA Y CITAR. 
-% Te puedes inspirar en las introducciones de articulos que simulen sistemas cuanticos}. 
-Being open quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
-practical~\cite{breuer2007theory} interest, there has been efforts
-towards the simulation of the evolution of open quantum
-systems~\cite{cleve,Zanetti,Xin,Wei}.\cpnote{porque escogiste estas citas? Me parece qeu la ce cleve no está completa.}
-\tbnote{Cambié un poco, agregué unos artículos que vi mucho más populares:}
-{\color{purple} 
-open quantum systems~\cite{Garcia, Wang,Weimer} and specifically for
-quantum channels~\cite{Xin,Wei,Zanetti}.
-}
+the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
+quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
+practical~\cite{breuer2007theory} interest, there has been efforts towards the
+simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
+and specifically for quantum channels~\cite{Xin,Wei,Zanetti}.
 
@@
 % }}}
-\section{Circuit for a Pauli Channel} % {{{
+\section{Circuit for a Pauli channel} % {{{
 \label{sec: Circuit for a Pauli Channel}
@@
 % }}}
-\section{One Parameter Circuits} % {{{
+\section{One parameter circuits} % {{{
 \label{sec: 1PR Circuits}
@@
 % }}}
-
 \section{Conclusion} % {{{
@@
 % }}}
-
 %\section{Supporting information} % {{{
@@
 % }}}
-
 \section{Acknowledgments} % {{{
@@
 % }}}
-\newpage
 \appendix
-%\input{Cosas-Escritas-Antes}
-
 \end{document}

### 2023-06-29 main.tex
No time to commit.. My people need me!

@@
 can be implemented with a 1PR circuit.
-{\color{purple} For this, the curve of states of \eref{eq: parametrized state} 
+For this, the curve of states of \eref{eq: parametrized state} 
 has to be constructed with only one parametrized rotation,
 so it has to satisfy the conditions of theorem \ref{theorem2}.
-}
-\cpnote{Sigue estando redundante. Dices que cuales se pueden implentar con 1pr circuit y que 
-enticones tiene que ser construidas con un 1pr. Quizá integra las dos frases o has algo}
 Therefore, this implies that the map
@@
 and since $V$ is unitary, these unprimed vectors will fulfill the conditions of
-\eref{eq:conditions-vecs}\cpnote{aun no construimos la $V$ asi que aun no es
-unitaria. Aclarame ese punto y le sigo al resto del parrafo}
-\tbnote{Ah, es que más bien la idea era primero decir que el siguiente paso es
-usar una matriz unitaria (con la condición
-mencionada sobre el primer renglón)
-y explicar cómo la usamos y por qué.
-Ya luego mostrar cómo se puede construir dicha 
-matriz al azar. También se puede hacer al revés,
-pero no me convencía decir todo lo de cómo 
-construir la matriz sin decir antes para qué}
-.
+\eref{eq:conditions-vecs}.
 Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
@@
 
-\cpnote{Reitera. Dale a lo qeu discutimos el espacio. a lo de la decoherencia nota
-que no lo tomamos como un resultado importante. Aca le das mucho mas espacio 
-del que croe que merece. Inspirate en la intro. }
-\tbnote{Ah va, listo}
-
-{\color{purple}
 In this work, we found a quantum algorithm for 
@@
 such as those used for quantum machine learning.
-}
 
@@
 
-\nolinenumbers
+% \nolinenumbers
 
@@
 %\end{thebibliography}
+\cpnote{Revisa con cuidado la bibliografia.
+Los nombres parece que estan bien, pero los doi parece que no estan completos.
+Hay nombres de revistas raros.
+Cre oque en plos one se abrevian, pero entonces haslos otodos abreviavos.
+Revis que todos tengan año, numero y pagina y que esté homogeneo.
+Revisa con cuidaod como son las abreviaciones de los journals (son estandard pero no recuerdo odnde está esa informacion).
+Ver revisando el procedimiento para someter a Plos One y al arxiv.
+Avisame cuando estes listo.
+}
+
 \tbnote{Poner la bibliografía como ellos dicen (copiarla toda aquí en lugar de ponerla en un archivo .bib)}

### 2023-07-01 Template/main.tex
...

--- 2023-06-29 main.tex
@@
 
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
 % cite package, to clean up citations in the main text. Do not remove.
@@
 
-% \linenumbers
+\linenumbers
 
@@
 Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
-effective models for the noise affecting quantum devices~\cite{Flammia,Fawzi}.
+effective models for the noise affecting quantum devices~\cite{Flammia}.
 
@@
 research has been devoted to enhancing the efficiency of these
-circuits~\cite{Watanabe,Rasmussen}.
+circuits~\cite{Rasmussen}.
 
@@
 % Intro  {{{
-% \textbf{Lista de puntos:}
-% \begin{itemize}
-% \item \textbf{Circuit for a Pauli channel:}  Propose a circuit to simulate a Pauli channel on $n$ qubits. It works by creating a $2n$-qubit state on ancilla qubits.
-% \item \textbf{Simulation:} Show the fidelities of simulating the circuit on a quantum computer for many one-qubit channels inside the tetrahedron.
-% \item \textbf{For Pauli dynamical maps}: See how the circuit generalizes to parametrized channels and notice that many rotations are needed to create the $2n$-ancilla qubit state. \\
-% \end{itemize}
 
@@
 % }}}
-\subsection{Quantum Channels} \label{subsec: Quantum Channels} % {{{
+\subsection{Quantum channels} \label{subsec: Quantum Channels} % {{{
 
@@
 quantum systems are usually open, which means that they interact with their
-environment~\cite{Breuer}.  For instance, the system's state may become
+environment~\cite{breuer2007theory}.  For instance, the system's state may become
 entangled with the environment, leading to a loss of information about the
@@
 % }}}
-\subsection{Pauli Channels}  \label{subsec: Pauli Channels} % {{{
+\subsection{Pauli channels}  \label{subsec: Pauli Channels} % {{{
 
@@
 \item \textbf{Bit Flip Channel:} This is a channel that with probability $1-p$ leaves the qubit as it is 
-and with probability $p$ it applies the $\sigma_1$ matrix 
+and with probability $p$ applies the $\sigma_1$ matrix 
 (which flips the basis states $|0\rangle$ and $|1\rangle$ of the qubit), and
@@
 has to be inside a tetrahedron with
-vertices $(1,1,1), (1,-1,-1),(-1,1,-1)$ and $(-1,-1,1)$. 
+vertices $(1,1,1), (1,-1,-1), (-1,1,-1)$ and $(-1,-1,1)$. 
 Therefore, the $\tau_{1,2,3}$ are numbers between 
@@
 % }}}
-\subsection{Pauli Dynamical Maps} % {{{
+\subsection{Pauli dynamical maps} % {{{
 \label{subsec: Pauli Dynamical Maps}
@@
 % }}} 
-\subsection{Description of the Circuit for a Pauli Channel} %{{{
+\subsection{Description of the circuit for a Pauli channel} %{{{
 \label{subsec: Description of the circuit}
 
-% To design the circuit, we recall that a Pauli channel, as the one in
-% \eref{eq: pauli channel N-qubit}, applies each Pauli operator
-% $\sigma_{\vec{\gamma}}$ on $\rho$ with a probability $k_{\vec{\gamma}}$.
-% Given this, it is easy to construct a quantum circuit that implements 
-% a Pauli channel with the help of $2N$ ancilla qubits,
-% see \fref{fig: circuit-pauli}.
-% The general idea is to produce the probabilities $k_{\gamma}$ by creating the state
-% \begin{eqnarray}
-% \label{eq: state0}
-% \sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
-% \end{eqnarray}
-% in the ancilla qubits, 
-% where $b_{\vec{\gamma}}$ are numbers such that $
-% |b_{\vec{\gamma}}|^2 = k_{\vec{\gamma}}$.
-% The $2N$-qubit state $|\vec{\gamma}\rangle$  is defined as $|\gamma_1 \rangle
-% \cdots |\gamma_N\rangle$.
-
-% {\color{orange} Cambiar por:  
 To design the circuit that implements \eref{eq: pauli channel N-qubit}, we construct a state that 
@@
 apply controlled Pauli operations on the main qubits.  The circuit that does
-this is presented in \fref{fig: circuit-pauli}.
-
-\begin{figure} % {{{
+this is presented in \fref{Fig1}.
+
+\begin{figure}[!h] % {{{
 \centering
-\includegraphics{images/circuito_general.pdf}
+%\includegraphics{images/circuito_general.pdf}
 \caption{{\bf Circuit for an $N$-qubit
-Pauli channel on $N$ qubits.}
+Pauli channel.}
 The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
-on the $2N$ ancilla qubits denoted by $\tilde{q}$. }
-\label{fig: circuit-pauli}
+on the $2N$ ancilla qubits denoted by $\tilde{q}$.}
+\label{Fig1}
 \end{figure} % }}}
@@
 probability ${|b_{\vec{\gamma}}|}^2 = k_{\vec\gamma}$. 
-The circuit in \fref{fig: circuit-pauli} uses this fact
+The circuit in \fref{Fig1} uses this fact
 to apply $\sigma_{\vec{\gamma}}$ on the main qubits
@@
 just as the Pauli channel is supposed to do.
-% 
-% that apply $\sigma_{\vec{\gamma}}$ to the main qubits
-% only if the ancilla qubits are in the state $|\vec{\gamma}\rangle$.
-% 
-% Therefore, the circuit from \fref{fig: circuit-pauli} 
-% applies each operation $\sigma_{\vec{\gamma}}$ to the principal qubits 
-% with a probability $k_{\vec{\gamma}}$, 
-% just as a Pauli channel is supposed to do.
-
-% \cpnote{Evaluar si al final ponemos algo al respecto de este comentario}
-% \cpnote{Del circuito, parece ue las fases de las bs gammas no omportan mucho (o nada). 
-% Esa libertad la hemos considerado? De alguna manera colapsan curvas de las que
-% hemos visto?} \tbnote{Sí, es una libertad que se tiene y he considerado y significa que hay muchas elecciones de $b_{\gamma}$ para un mismo canal.
-% Es una de las varias cosas que complicaba determinar uno a uno qué canales se pueden hacer.}
-%
 
@@
 For the particular case of a Pauli channel on one qubit, the circuit that
-simulates it can be constructed as in \fref{fig: circuit-pauli-1},
-which is a special case of \fref{fig: circuit-pauli}
+simulates it can be constructed as in \fref{Fig2},
+which is a special case of \fref{Fig1}
 but with all details  explicitly shown.
@@
 \label{eq:angle}
-\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\\
+\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\nonumber \\
 \tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}},  \\
-\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.
+\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.  \nonumber
 \end{align}
 
-\begin{figure} % {{{
+\begin{figure}[!h] % {{{
 \centering
-\includegraphics{images/circuito_unqubit.pdf}
+%\includegraphics{images/circuito_unqubit.pdf}
 \caption{
-{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
-which is a particular case of \fref{fig: circuit-pauli}.  Here we have two
+{\bf One-qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
+which is a particular case of \fref{Fig1}.  Here we have two
 ancilla qubits and we use three rotations
@@
 }
-\label{fig: circuit-pauli-1} 
+\label{Fig2} 
 \end{figure} % }}}
@@
 ibmq-lima quantum computer~\cite{Qiskit},
-as shown in \fref{fig:fids}. 
+as shown in \fref{Fig3}. 
 For each of the channels sampled, we used 
@@
 $\xi_T$ are, we shall use the
-diamond distance~\cite{Aharonov,Wilde}, which is defined by
+diamond distance~\cite{wildebook}, which is defined by
 \begin{equation}
@@
 are completely distinguishable, the distance reaches its maximum value of $2$~\cite{Benenti}.
-For the analysis done in \fref{fig:fids}, we define a sort of ``diamond fidelity'' as: 
+For the analysis done in \fref{Fig3}, we define a sort of ``diamond fidelity'' as: 
 \begin{equation}
@@
 
-\begin{figure} % {{{
+\begin{figure}[!h] % {{{
 \centering
-\begin{subfigure}{0.9\textwidth}
-\begin{subfigure}{.666\textwidth}
-\centering
-\includegraphics[width=.95\columnwidth]{images/tetra-def.png}
-\end{subfigure}%
-\begin{subfigure}{.333\textwidth}
-\includegraphics[width=.95\columnwidth]{images/corte1-2.png} \\
-\includegraphics[width=.95\columnwidth]{images/corte2-2.png} \\
-\end{subfigure}
-\includegraphics[width=.322\columnwidth]{images/corte3-2.png}
-\includegraphics[width=.322\columnwidth]{images/corte4-2.png}
-\includegraphics[width=.322\columnwidth]{images/corte5-2.png}
-\end{subfigure}%
-\begin{subfigure}{0.1\textwidth}
-\includegraphics[width=.8\columnwidth]{images/col-2.png} \\ [2ex]
-\end{subfigure}
-\caption{Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
-for a sample of Pauli channels in the tetrahedron.  Notice that channels close
+\caption{{\bf Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
+for a sample of Pauli channels in the tetrahedron.}  Notice that channels close
 to the center of the tetrahedron have high fidelities, while those close to the
@@
 different values of $\tau_3$.}
-\label{fig:fids}
+\label{Fig3}
 \end{figure} % }}}
@@
 Finally, using the representation of Pauli channels in a tetrahedron as in
-\eref{eq: conditions-tetrahedron}, we show in \fref{fig:fids} the diamond
+\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
 fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
@@
 trying to simulate depolarization but it is when simulating unitary processes.
-Moreover, the algorithm of \fref{fig: circuit-pauli-1} is not optimal for
+Moreover, the algorithm of \fref{Fig2} is not optimal for
 unitary channels (that is, the channels corresponding to the vertices of the
@@
 Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
-of \fref{fig: circuit-pauli}. However, there is one difference: 
+of \fref{Fig1}. However, there is one difference: 
 the state to be created on the ancilla qubits now 
@@
 such as the three rotations used for the ancilla
-qubits in \fref{fig: circuit-pauli-1}.
+qubits in \fref{Fig2}.
 However, it would be preferable to achieve the same effect using only one parametrized rotation. 
@@
 To accomplish this, we begin by proving that all 1PR circuits have 
-the form depicted in \fref{fig:1PR-circuit},
+the form depicted in \fref{Fig4},
 where the parametrized rotation is around $\sigma_3$ and
@@
 
-\begin{figure} % {{{
+\begin{figure}[!h] % {{{
 \centering
-\includegraphics{images/OPR-circuit.pdf}
+%\includegraphics{images/OPR-circuit.pdf}
 \caption{\textbf{General form of a 1PR circuit}.
@@
 }
-\label{fig:1PR-circuit}
+\label{Fig4}
 \end{figure} % }}}
@@
 An $N-$qubit 1PR circuit can always be transformed 
-into the form shown in \fref{fig:1PR-circuit}.
+into the form shown in \fref{Fig4}.
 \end{theorem}
@@
 (possibly controlled by other qubits), 
-resulting in the form depicted in \fref{fig:1PR-circuit}. 
+resulting in the form depicted in \fref{Fig4}. 
 $\blacksquare$ \\
@@
 + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
-& = e^{-is(p)} |\tilde{b}^{j}\rangle + e^{is(p)} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle
+& = e^{-is(p)} |\tilde{b}^{j}\rangle + e^{is(p)} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle,
 \end{align}
@@
 \end{equation}
-% \cpnote{Es un poco confusa la notacion. Hablas de la norma de a con $|a|$, pero ahi parece
-% que $a$ es un vector. Sugiero cambiar a $\langle a | a \rangle$ o algo asi sin cargar mucho
-% la notacion. } \tbnote{Va, concuerdo, listo}
-% \cpnote{Tambien siento qeu las palabras son un poco raras. Sugiero pasarlo por Chatgpt y 
-% luego tunearlo (todo este parrafo). Avisame cuando quede eso!} \tbnote{Ya}
 
@@
 One approach to achieve this is by utilizing the circuit 
-depicted in \fref{fig:1PR-circuit}, 
+depicted in \fref{Fig4}, 
 with the parametrized rotation $R$ applied to the last qubit controlled by all the 
@@
 By starting from the initial state $|0\rangle$ and 
-applying the circuit shown in \fref{fig:1PR-circuit}, straightforward calculations 
+applying the circuit shown in \fref{Fig4}, straightforward calculations 
 lead us to obtain the resulting curve of states described in \eref{eq:curve-states}.
@@
 $$
+
 Finally, applying the defined operator $A$ to this state yields the desired result.
 
-%Therefore, from this theorem we conclude that
-%the kind of curves of states that can be created
-%using a 1PR circuit are always of the form
-%\begin{align*}
-%|b(p)\rangle= e^{is} \vec{a} + e^{-is} \vec{b} + \vec{c},
-%\end{align*}
-%where $s$ is a function of $p$, $\vec{a},\vec{b},\vec{c}$ are orthogonal vectors and
-%$|\vec{a}|^2+  |\vec{b}|^2 + |\vec{c}|^2 = 1$.
-%%\textbf{Puntos:}
-%\begin{itemize}
-%\item As said before, to implement a Pauli dynamical map, 
-%we need to create the parametrized $2n$-qubit state 
-%$\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle$ on the ancilla qubits.
-%\item However, creating this state will in general require many rotations parametrized by $p$. 
-%For example, for the case of a Pauli dynamical map on 1 qubit, 
-%the parametrized state of the $2$ ancilla qubits in general requires $3$ parametrized rotations and can be constructed as follows: (poner circuito).\\
-%In general, to create a parametrized state on $2n$ ancilla qubits will require
-%$2n-1$ rotations parametrized by $p$.
-%\item How can we reduce the amount of parametrized rotations used?
-%\item \textbf{1PR Circuit:} Define an 1PR circuit (a circuit with one parametrized rotation)
-%\item \textbf{Theorem about 1PR circuits:} \textit{An 1PR circuit on $n$ qubits with parameter $p$ always has an operator of the form:}
-%\begin{eqnarray}
-%U = (\vec{v}_0| \vec{v}_1| \cdots| \vec{v}_{2^n-1})
-%\end{eqnarray}
-%\textit{where $s = s(p)$ and the column vectors are $\vec{v}_j = e^{is} \vec{a}_j + e^{-is} \vec{b}_j + \vec{c}_j$, with $\vec{a}_j, \vec{b}_j, \vec{c}_j$ orthogonal vectors and $|\vec{a}_j|^2 + |\vec{b}_j|^2 + |\vec{c}_j|^2 = 1$.}
-%\item \textbf{Proof:} La prueba está dentro de las ``Cosas-Escritas-Antes'', 
-%aunque se puede y debe achicar bastante.
-%\end{itemize}
-% }}}
 \section{1PR circuit for a Pauli map} % {{{
@@
 dynamical maps implementable with a 1PR circuit, which are plotted in
-\fref{fig:curves1}. 
-The examples we show include some the most common maps: the bit flip, phase flip, bit-phase flip and depolarizing.
+\fref{Fig5}. 
+The examples we show include some of the most common maps: the bit flip, phase flip, bit-phase flip and depolarizing.
 However, we also include the parabolic dynamical map,
-defined in \eref{eq:parab} and shown in \fref{fig:curves1}.
+defined in \eref{eq:parab} and shown in \fref{Fig5}.
 This map traces a parabola inside the tetrahedron connecting two of its vertices
@@
 
-\begin{figure} % {{{
-\captionsetup[subfigure]{justification=centering}
+\begin{figure}[!h] % {{{
+%\captionsetup[subfigure]{justification=centering}
 \centering
-\begin{subfigure}{.45\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{images/curvas.png}
-   \caption{}
-  \label{fig:curves1}
-\end{subfigure}%
-\begin{subfigure}{.45\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{images/curvas-azar.png}
-  \caption{}
-  \label{fig:curves2}
-\end{subfigure}
+%\begin{subfigure}{.45\textwidth}
+%  \centering
+%  \includegraphics[width=.9\linewidth]{images/curvas.png}
+%   \caption{}
+%  \label{Fig51}
+%\end{subfigure}%
+%\begin{subfigure}{.45\textwidth}
+%  \centering
+%  \includegraphics[width=.9\linewidth]{images/curvas-azar.png}
+%  \caption{}
+%  \label{Fig5-2}
+%\end{subfigure}
 \caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
@@
 circuits.}
-\label{fig:curves}
+\label{Fig5}
 \end{figure} % }}}
@@
 we plot four Pauli dynamical maps  selected at random
-that can be implemented with a 1PR circuit in \fref{fig:curves2}.
+that can be implemented with a 1PR circuit in \fref{Fig5}.
 
@@
 
-% \nolinenumbers
-
-% }}}
-% Biblbiografia {{{
 % Either type in your references using
@@
 % step-by-step instructions.
-% 
-%\begin{thebibliography}{10}
-%
-%\bibitem{bib1}
-%Conant GC, Wolfe KH.
-%\newblock {{T}urning a hobby into a job: how duplicated genes find new
-%  functions}.
-%\newblock Nat Rev Genet. 2008 Dec;9(12):938--950.
-
-%\bibitem{bib2}
-%Ohno S.
-%\newblock Evolution by gene duplication.
-%\newblock London: George Alien \& Unwin Ltd. Berlin, %Heidelberg and New York:
-%  Springer-Verlag.; 1970.
-
-%\bibitem{bib3}
-%Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
-%\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
-%  infection through a transposon insertion followed by a {D}uplication}.
-%\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
-%
-%\end{thebibliography}
-\cpnote{Revisa con cuidado la bibliografia.
-Los nombres parece que estan bien, pero los doi parece que no estan completos.
-Hay nombres de revistas raros.
-Cre oque en plos one se abrevian, pero entonces haslos otodos abreviavos.
-Revis que todos tengan año, numero y pagina y que esté homogeneo.
-Revisa con cuidaod como son las abreviaciones de los journals (son estandard pero no recuerdo odnde está esa informacion).
-Ver revisando el procedimiento para someter a Plos One y al arxiv.
-Avisame cuando estes listo.
-}
-
-\tbnote{Poner la bibliografía como ellos dicen (copiarla toda aquí en lugar de ponerla en un archivo .bib)}
-\bibliography{Bibliography}
+
+\begin{thebibliography}{10}
+
+\bibitem{feynman1982simulating}
+Feynman RP.
+\newblock Simulating physics with computers.
+\newblock Int J Theor Phys. 1982;21(6/7):467--488.
+
+\bibitem{Zur91}
+Zurek WH.
+\newblock Decoherence and the transition from quantum to classical.
+\newblock Phys Today. 1991;44(10):36--44.
+
+\bibitem{RevModPhys.76.1267}
+Schlosshauer M.
+\newblock Decoherence, the measurement problem, and interpretations of quantum
+  mechanics.
+\newblock Rev Mod Phys. 2005;76(4):1267--1305.
+
+\bibitem{breuer2007theory}
+Breuer HP, Petruccione F.
+\newblock The theory of open quantum systems.
+\newblock 1st ed. New York: Oxford University Press; 2002.
+
+\bibitem{Garcia}
+García-Pérez G, Rossi M, Maniscalco S.
+\newblock IBM Q Experience as a versatile experimental testbed for simulating
+  open quantum systems.
+\newblock npj Quantum Inf. 2020;6(1):1--11.
+
+\bibitem{Wang}
+Wang H, Ashhab S, Nori F.
+\newblock Quantum algorithm for simulating the dynamics of an open quantum
+  system.
+\newblock Phys Rev A. 2011;83(6):062317.
+
+\bibitem{Weimer}
+Weimer H, Kshetrimayum A, Or\'us R.
+\newblock Simulation methods for open quantum many-body systems.
+\newblock Rev Mod Phys. 2021;93(1):015008.
+
+\bibitem{Xin}
+Xin T, Wei SJ, Pedernales JS, Solano E, Long GL.
+\newblock Quantum simulation of quantum channels in nuclear magnetic resonance.
+\newblock Phys Rev A. 2017;96(6):062303.
+
+\bibitem{Wei}
+Wei S, Xin T, Long G.
+\newblock Efficient universal quantum channel simulation in IBM's cloud quantum
+  computer.
+\newblock Sci China Phys Mech Astron. 2018;61(7):70311.
+
+\bibitem{Zanetti}
+Zanetti M, Pinto D, Basso M, Maziero J.
+\newblock Simulating noisy quantum channels via quantum state preparation
+  algorithms.
+\newblock Phys B At Mol Opt Phys. 2023;56(11):115501.
+
+\bibitem{Andrea}
+Far\'ias OJ, Aguilar GH, Vald\'es-Hern\'andez A, Ribeiro PHS, Davidovich L,
+  Walborn SP.
+\newblock Observation of the emergence of multipartite entanglement between a
+  bipartite system and its environment.
+\newblock Phys Rev Lett. 2012;109(15):150403.
+
+\bibitem{Andrea_AD}
+Aguilar GH, Vald\'es-Hern\'andez A, Davidovich L, Walborn SP, Souto~Ribeiro PH.
+\newblock Experimental entanglement redistribution under decoherence channels.
+\newblock Phys Rev Lett. 2014;113(24):240501.
+
+\bibitem{Barreiro}
+Barreiro J, Müller M, Schindler P, Nigg D, Monz T, Chwalla M, et~al.
+\newblock An open-system quantum simulator with trapped ions.
+\newblock Nature. 2011;470(7335):486--491.
+
+\bibitem{Marsden}
+Head-Marsden K, Krastanov S, Mazziotti D, Narang P.
+\newblock Capturing non-Markovian dynamics on near-term quantum computers.
+\newblock Phys Rev Res. 2021;3:013182.
+
+\bibitem{chuangbook}
+Nielsen MA, Chuang IL.
+\newblock Quantum computation and quantum information: 10th anniversary
+  edition.
+\newblock 10th ed. New York: Cambridge University Press; 2011.
+
+\bibitem{geometry}
+Bengtsson I, {\. Z}yczkowski K.
+\newblock Geometry of quantum states: an introduction to quantum entanglement.
+\newblock 1st ed. Cambridge: Cambridge University Press; 2006.
+
+\bibitem{Zbigniew}
+Puchała Z, Łukasz Rudnicki, {\. Z}yczkowski K.
+\newblock Pauli semigroups and unistochastic quantum channels.
+\newblock Phys Lett A. 2019;383(20):2376--2381.
+
+\bibitem{Davalos}
+Davalos D, Ziman M, Pineda C.
+\newblock Divisibility of qubit channels and dynamical maps.
+\newblock Quantum. 2019;3:144.
+
+\bibitem{Flammia}
+Steven F, Joel W.
+\newblock Efficient estimation of Pauli channels.
+\newblock ACM. 2020;1(3):1--32.
+
+\bibitem{cerezo}
+Cerezo M, Arrasmith A, Babbush R, Benjamin SC, Endo S, Fujii K, et~al.
+\newblock Variational quantum algorithms.
+\newblock Nat Rev Phys. 2020;3(9):625--644.
+
+\bibitem{Benedetti}
+Benedetti M, Lloyd E, Sack S, Fiorentini M.
+\newblock Parameterized quantum circuits as machine learning models.
+\newblock Quantum Sci Technol. 2019;4(4):043001.
+
+\bibitem{Rasmussen}
+Rasmussen S, Loft N, Bækkegaard T, Kues M, Zinner N.
+\newblock Reducing the amount of single-qubit rotations in VQE and related
+  algorithms.
+\newblock Adv Quantum Technol. 2020;3:2000063.
+
+\bibitem{Rieffel}
+Rieffel E, Polak W.
+\newblock Quantum computing: a gentle introduction.
+\newblock 1st ed. Massachusetts: The MIT Press; 2011.
+
+\bibitem{zimansbook}
+Heinosaari T, Ziman M.
+\newblock {The Mathematical Language of Quantum Theory: From Uncertainty to
+  Entanglement}.
+\newblock 2nd ed. Cambridge: Cambridge University Press; 2012.
+
+\bibitem{cirac}
+Wolf MM, Cirac JI.
+\newblock Dividing quantum channels.
+\newblock Comm Math Phys. 2008;279(1):147--168.
+
+\bibitem{choi}
+Choi MD.
+\newblock Completely positive linear maps on complex matrices.
+\newblock Linear Algebra Appl. 1975;10(3):285--290.
+
+\bibitem{jamil}
+Jamiołkowski A.
+\newblock Linear transformations which preserve trace and positive
+  semidefiniteness of operators.
+\newblock Rep Math Phys. 1972;3(4):275--278.
+
+\bibitem{Marinescu}
+Marinescu D, Marinescu G.
+\newblock Classical and Quantum Information.
+\newblock 1st ed. Oxford: Elsevier; 2012.
+
+\bibitem{Terhal}
+Terhal BM.
+\newblock Quantum error correction for quantum memories.
+\newblock Rev Mod Phys. 2015;87(2):307--346.
+
+\bibitem{Qiskit}
+{Qiskit contributors}. Qiskit: An Open-source Framework for Quantum Computing;
+  2023.
+
+\bibitem{Chuang:1996}
+Chuang IL, Nielsen MA.
+\newblock {Prescription for experimental determination of the dynamics of a
+  quantum black box}.
+\newblock J Mod Opt. 1997;44:2455--2467.
+
+\bibitem{wildebook}
+Wilde M.
+\newblock From classical to quantum Shannon theory.
+\newblock 2nd ed. Cambridge: Cambridge University Press; 2019.
+
+\bibitem{Watrous}
+Watrous J.
+\newblock Simpler semidefinite programs for completely bounded norms.
+\newblock Theor Comput Sci. 2013;19(8):1--19.
+
+\bibitem{Benenti}
+Benenti G, Strini G.
+\newblock Computing the distance between quantum channels: usefulness of the
+  Fano representation.
+\newblock J Phys B At Mol Opt Phys. 2010;43(21):215508.
+
+\bibitem{Andrea_4qb}
+Aguilar GH, Far\'ias OJ, Vald\'es-Hern\'andez A, Souto~Ribeiro PH,
+  Davidovich L, Walborn SP.
+\newblock Flow of quantum correlations from a two-qubit system to its
+  environment.
+\newblock Phys Rev A. 2014;89(2):022339.
+
+\end{thebibliography}
 

### 2023-07-01 Template/plos_latex_template.tex
...

% Template for PLoS
% Version 3.6 Aug 2022
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%

% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage[nopatch=eqnum]{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Title of submission to PLOS journals} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Name1 Surname\textsuperscript{1,2\Yinyang},
Name2 Surname\textsuperscript{2\Yinyang},
Name3 Surname\textsuperscript{2,3\textcurrency},
Name4 Surname\textsuperscript{2},
Name5 Surname\textsuperscript{2\ddag},
Name6 Surname\textsuperscript{2\ddag},
Name7 Surname\textsuperscript{1,2,3*},
with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{2} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%
% Primary Equal Contribution Note
\Yinyang These authors contributed equally to this work.

% Additional Equal Contribution Note
% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
\ddag These authors also contributed equally to this work.

% Current address notes
\textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
% \textcurrency b Insert second current address 
% \textcurrency c Insert third current address

% Deceased author note
\dag Deceased

% Group/Consortium Author Note
\textpilcrow Membership list can be found in the Acknowledgments section.

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* correspondingauthor@institute.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}
Lorem ipsum dolor sit~\cite{bib1} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{bib2} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.

\begin{eqnarray}
\label{eq:schemeP}
	\mathrm{P_Y} = \underbrace{H(Y_n) - H(Y_n|\mathbf{V}^{Y}_{n})}_{S_Y} + \underbrace{H(Y_n|\mathbf{V}^{Y}_{n})- H(Y_n|\mathbf{V}^{X,Y}_{n})}_{T_{X\rightarrow Y}},
\end{eqnarray}

\section*{Materials and methods}
\subsection*{Etiam eget sapien nibh}

% For figure citations, please use "Fig" instead of "Figure".
Nulla mi mi, Fig~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Place figure captions after the first paragraph in which they are cited.
\begin{figure}[!h]
\caption{{\bf Bold the figure title.}
Figure caption text here, please use this space for the figure panel descriptions instead of using subfigure commands. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

% Results and Discussion can be combined.
\section*{Results}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Place tables after the first paragraph in which they are cited.
\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l+l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \thickhline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

%PLOS does not support heading levels beyond the 3rd (no 4th level headings).
\subsection*{\lorem\ and \ipsum\ nunc blandit a tortor}
\subsubsection*{3rd level heading} 
Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat.

\begin{enumerate}
	\item{react}
	\item{diffuse free particles}
	\item{increment time by dt and go to 1}
\end{enumerate}

\subsection*{Sed ac quam id nisi malesuada congue}

Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\begin{itemize}
	\item First bulleted item.
	\item Second bulleted item.
	\item Third bulleted item.
\end{itemize}

\section*{Discussion}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero~\cite{bib3}.

\section*{Conclusion}

CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Appendix}.

\section*{Supporting information}

% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
\paragraph*{S1 Fig.}
\label{S1_Fig}
{\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).

\paragraph*{S2 Fig.}
\label{S2_Fig}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 File.}
\label{S1_File}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Video.}
\label{S1_Video}
{\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Appendix.}
\label{S1_Appendix}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\paragraph*{S1 Table.}
\label{S1_Table}
{\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

\nolinenumbers

% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% or
%
% Compile your BiBTeX database using our plos2015.bst
% style file and paste the contents of your .bbl file
% here. See http://journals.plos.org/plosone/s/latex for 
% step-by-step instructions.
% 
\begin{thebibliography}{10}

\bibitem{bib1}
Conant GC, Wolfe KH.
\newblock {{T}urning a hobby into a job: how duplicated genes find new
  functions}.
\newblock Nat Rev Genet. 2008 Dec;9(12):938--950.

\bibitem{bib2}
Ohno S.
\newblock Evolution by gene duplication.
\newblock London: George Alien \& Unwin Ltd. Berlin, Heidelberg and New York:
  Springer-Verlag.; 1970.

\bibitem{bib3}
Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
  infection through a transposon insertion followed by a {D}uplication}.
\newblock PLoS Genet. 2011 Oct;7(10):e1002337.

\end{thebibliography}

\end{document}

### 2023-07-05 main.tex
Un documento

@@
 
-% \linenumbers
-
 % Use "Eq" instead of "Equation" for equation citations.
@@
 apply controlled Pauli operations on the main qubits.  The circuit that does
-this is presented in \fref{fig: circuit-pauli}.
+this is presented in \fref{Fig1}.
 
@@
 \caption{{\bf Circuit for an $N$-qubit
-Pauli channel on $N$ qubits.}
+Pauli channel.}
 The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
-on the $2N$ ancilla qubits denoted by $\tilde{q}$. }
-\label{fig: circuit-pauli}
+on the $2N$ ancilla qubits denoted by $\tilde{q}$.}
+\label{Fig1}
 \end{figure} % }}}
@@
 \label{eq:angle}
-\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\\
+\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\nonumber \\
 \tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}},  \\
-\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.
+\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.  \nonumber
 \end{align}
@@
 \caption{
-{\bf One qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
-which is a particular case of \fref{fig: circuit-pauli}.  Here we have two
+{\bf One-qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
+which is a particular case of \fref{Fig1}.  Here we have two
 ancilla qubits and we use three rotations
@@
 \centering
-\includegraphics[width=.95\columnwidth]{images/tetra-def.png}
+\includegraphics[width=.95\columnwidth]{images/tetra-def.pdf}
 \end{subfigure}%
 \begin{subfigure}{.333\textwidth}
-\includegraphics[width=.95\columnwidth]{images/corte1-2.png} \\
-\includegraphics[width=.95\columnwidth]{images/corte2-2.png} \\
+\includegraphics[width=.95\columnwidth]{images/corte1-2.pdf} \\
+\includegraphics[width=.95\columnwidth]{images/corte2-2.pdf} \\
 \end{subfigure}
-\includegraphics[width=.322\columnwidth]{images/corte3-2.png}
-\includegraphics[width=.322\columnwidth]{images/corte4-2.png}
-\includegraphics[width=.322\columnwidth]{images/corte5-2.png}
+\includegraphics[width=.322\columnwidth]{images/corte3-2.pdf}
+\includegraphics[width=.322\columnwidth]{images/corte4-2.pdf}
+\includegraphics[width=.322\columnwidth]{images/corte5-2.pdf}
 \end{subfigure}%
 \begin{subfigure}{0.1\textwidth}
-\includegraphics[width=.8\columnwidth]{images/col-2.png} \\ [2ex]
+\includegraphics[width=.8\columnwidth]{images/col-2.pdf} \\ [2ex]
 \end{subfigure}
@@
 such as the three rotations used for the ancilla
-qubits in \fref{fig: circuit-pauli-1}.
+qubits in \fref{Fig2}.
 However, it would be preferable to achieve the same effect using only one parametrized rotation.
@@
 are $N$-qubit gates that do not depend on the parameter $p$ and
-$s= s(p)$ is a function of the parameter.
-}
-\label{fig:1PR-circuit}
+$s= s(p)$ is a function of the parameter.}
+\label{Fig4}
 \end{figure} % }}}
@@
   \centering
-  \includegraphics[width=.9\linewidth]{images/curvas.png}
+  \includegraphics[width=.9\linewidth]{images/curvas.pdf}
    \caption{}
-  \label{fig:curves1}
 \end{subfigure}%
@@
   \centering
-  \includegraphics[width=.9\linewidth]{images/curvas-azar.png}
+  \includegraphics[width=.9\linewidth]{images/curvas-azar.pdf}
   \caption{}
-  \label{fig:curves2}
 \end{subfigure}
@@
 % step-by-step instructions.
-% 
-%\begin{thebibliography}{10}
-%
-%\bibitem{bib1}
-%Conant GC, Wolfe KH.
-%\newblock {{T}urning a hobby into a job: how duplicated genes find new
-%  functions}.
-%\newblock Nat Rev Genet. 2008 Dec;9(12):938--950.
-
-%\bibitem{bib2}
-%Ohno S.
-%\newblock Evolution by gene duplication.
-%\newblock London: George Alien \& Unwin Ltd. Berlin, %Heidelberg and New York:
-%  Springer-Verlag.; 1970.
-
-%\bibitem{bib3}
-%Magwire MM, Bayer F, Webster CL, Cao C, Jiggins FM.
-%\newblock {{S}uccessive increases in the resistance of {D}rosophila to viral
-%  infection through a transposon insertion followed by a {D}uplication}.
-%\newblock PLoS Genet. 2011 Oct;7(10):e1002337.
-%
-%\end{thebibliography}
-\cpnote{Revisa con cuidado la bibliografia.
-Los nombres parece que estan bien, pero los doi parece que no estan completos.
-Hay nombres de revistas raros.
-Cre oque en plos one se abrevian, pero entonces haslos otodos abreviavos.
-Revis que todos tengan año, numero y pagina y que esté homogeneo.
-Revisa con cuidaod como son las abreviaciones de los journals (son estandard pero no recuerdo odnde está esa informacion).
-Ver revisando el procedimiento para someter a Plos One y al arxiv.
-Avisame cuando estes listo.
-}
-
-\tbnote{Poner la bibliografía como ellos dicen (copiarla toda aquí en lugar de ponerla en un archivo .bib)}
+
 \bibliography{Bibliography}

### 2023-07-10 main.tex
more debug... who overwrote!
figures
de-misunderestimating
Reescritura codigo

@@
 %\setlength{\headheight}{27.023pt}
-%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
 \rfoot{\thepage/\pageref{LastPage}}
@@
 controlled single-qubit
-operation in the circuit may depend on the parameter.  Finally, in
+rotation in the circuit may depend on the parameter.  Finally, in
 section \ref{sec: 1PR circuit for a Pauli map}, we conclude about the Pauli
@@
 of \eref{eq: state} can be taken to be
-$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
-|10\rangle + \sqrt{k_{11}}|11\rangle$
+$\sqrt{k_{0}} |00\rangle + \sqrt{k_{1}} |01\rangle + \sqrt{k_{2}} 
+|10\rangle + \sqrt{k_{3}}|11\rangle$
 and it is created on the ancilla qubits with the help of three rotations of angles
@@
 \label{eq:angle}
-\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\nonumber \\
-\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}},  \\
-\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.  \nonumber
+\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{0} + k_{1}},\nonumber \\
+\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{1}/k_{0}},  \\
+\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{3}/k_{2}}.  \nonumber
 \end{align}
@@
 \centering
-\begin{subfigure}{0.9\textwidth}
-\begin{subfigure}{.666\textwidth}
-\centering
-\includegraphics[width=.95\columnwidth]{images/tetra-def.pdf}
-\end{subfigure}%
-\begin{subfigure}{.333\textwidth}
-\includegraphics[width=.95\columnwidth]{images/corte1-2.pdf} \\
-\includegraphics[width=.95\columnwidth]{images/corte2-2.pdf} \\
-\end{subfigure}
-\includegraphics[width=.322\columnwidth]{images/corte3-2.pdf}
-\includegraphics[width=.322\columnwidth]{images/corte4-2.pdf}
-\includegraphics[width=.322\columnwidth]{images/corte5-2.pdf}
-\end{subfigure}%
-\begin{subfigure}{0.1\textwidth}
-\includegraphics[width=.8\columnwidth]{images/col-2.pdf} \\ [2ex]
-\end{subfigure}
-\caption{Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
-for a sample of Pauli channels in the tetrahedron.  Notice that channels close
+\includegraphics{images/fig-tetra.pdf}
+\caption{{\bf Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
+for a sample of Pauli channels in the tetrahedron.}  Notice that channels close
 to the center of the tetrahedron have high fidelities, while those close to the
@@
 
+% }}}
 \section{1PR circuit for a Pauli map} % {{{
@@
 \begin{figure} % {{{
-\captionsetup[subfigure]{justification=centering}
 \centering
-\begin{subfigure}{.45\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{images/curvas.pdf}
-   \caption{}
-\end{subfigure}%
-\begin{subfigure}{.45\textwidth}
-  \centering
-  \includegraphics[width=.9\linewidth]{images/curvas-azar.pdf}
-  \caption{}
-\end{subfigure}
+\includegraphics{images/fig-curves.pdf}
 \caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
@@
 % step-by-step instructions.
-
+% }}}
 \bibliography{Bibliography}
-
-% }}}
 \appendix

### 2023-07-13 cover_letter_plos.tex
a few bits tried to escape, but we caught them

\documentclass[12pt, addrfooterall, english]{if_letter_2013}
% \usepackage[spanish]{babel} 
\usepackage[utf8]{inputenc}
% \date{17 de Octubre de 2018}
\begin{document}
\begin{letter}{
.\vspace{-2cm}
% PLOS One\\
% Editorial 
% \adirectorcecilia
% \aquieninterese
% \apapiitmendoza
% \aconacytGelover
% \asecretariomostalac
% Dra. Maria del Carmen de la Peza Casares\\
% Directora Adjunta de Desarrollo Científico y Secretaria Técnica del FONCICYT\\
% CONACYT
}
\opening{To whom it may concern}

% Para poder recibir apoyo económico del proyecto conacyt: Básicamente solo
% tienes que devolverme a mi estatus anterior, actualmente soy becario pero debo
% ser participante. Hay que escribir una carta dirigida a: 
% 
% 
% "
% Dra. Maria del Carmen de la Peza Cázares
% Directora adjunta de desarrollo científico
% y secretaria técnica del FONCICYT

% Deseo informarle que el día de hoy me reincorporé a mis actividades después de mi viaje
% a Colombia.

% y que  posteriormente se le reintegren los gastos de un viaje que
% realizó recientemente (\$16,534.22 pesos) y del que ya se entregó la
% documentación. El motivo es que se deseaba otorgar una beca de doctorado al
% Maestro Dávalos (y se devolvió el dinero del viaje), pero no fue posible
% concretar la beca por problemas administrativos. 
% 
% La Licenciada Adela Lorán nos indico que conviene que le informemos por escrito a usted de esta situación.

% Por medio de la presente me comprometo a no ausentarme del Instituto de Física por períodos
% superiores a un mes con el fin de cumplir con el compromiso de atender al Dr.
% Roberto Kenan Uriostegui, durante el tiempo que esté realizando su estancia posdoctoral 
% bajo mi dirección. 
% 
% 
% Sin más por el momento, me despido y agradezco su atención.

I am writing on behalf of all authors to submit our research article entitled
“Quantum simulation of Pauli channels and dynamical maps: algorithm and
implementation” to be considered for publication as a research article in PLOS
One.

In this article, we focus on one of the fundamental purposes of quantum
computers since their inception: simulating quantum systems. Specifically, we
propose and simulate on a quantum computer an algorithm for implementing
Pauli channels. These channels are transformations of qubit systems typically 
arising from noise affecting quantum devices (Flammia S. and Wallman J.,
Efficient estimation of Pauli channels, 2020). Pauli channels are examples of 
the evolution of open quantum systems, which have garnered interest due to 
their applications in the study of entanglement (Farías O.J. et al, 
Observation of the emergence of multipartite entanglement between a bipartite 
system and its environment, 2012) and dissipative processes 
(Barreiro J. et al, An open-system quantum simulator with trapped ions, 2011).

Moreover, we extend the algorithm to encompass Pauli channels dependent on a
parameter, which we refer to as Pauli dynamical maps. This extension leads us
to investigate quantum algorithms with parameter-dependent operations, known as
parametrized quantum circuits.  In this manuscript, we establish the
mathematical conditions necessary for implementing any parametrized operation
using a quantum circuit using only one parametrized single qubit operation. We
believe these findings will be of interest to readers of your esteemed journal.

We declare the manuscript’s originality and exclusivity for publication. In
addition, we have not had any prior interactions with PLOS regarding this
manuscript. In the event that our manuscript is chosen for review, we kindly
suggest Dr. Fabio Sciarrino as a suitable reviewer, given his background and
expertise to evaluate our findings. We have no objections to any other
potential reviewers.

Each named author has significantly contributed to the research and preparation
of this manuscript. Furthermore, the named authors have no conflicts of
interest to disclose.

% Thank you for considering our work.
% On behalf of all authors

\closing{On behalf of all authors,}

\end{letter}
\end{document}
recepcion_cb@conacyt.mx

### 2023-09-06 Comentarios.tex
Comentarios editor

--- 2023-07-01 Template/main.tex
@@
 \begin{document}
-% Titulo, afiliacion, abstract  {{{
-\vspace*{0.2in}
+\section{Comentarios}
 
-\begin{flushleft}
-{\Large
-\textbf\newline{Quantum simulation of Pauli channels and dynamical maps: algorithm and implementation } % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Tomás Basile\textsuperscript{1,2\Yinyang},
-Carlos Pineda\textsuperscript{2*\Yinyang},
-\\
-\bigskip
-\textbf{1} Facultad de Ciencias. Universidad Nacional Autónoma de México, Ciudad de México 01000, Mexico
-\\
-\textbf{2} Instituto de Física, Universidad Nacional Autónoma de México, Ciudad de México 01000, México
-\\
-\bigskip
+\begin{enumerate}
+\item I fail to see the point here - the logic of the paper is: 
+1.
+"open quantum systems can be modeled through a class of channels representing he various types of decoherence." 2.
+"Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible."
+3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them.
 
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
+What I am missing is what do we learn by doing it which cant be learned by actually performing the Pauli channel onto a quantum system?
+For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial.
+Why would I need to decompose (not even effectively for any channel) the pauli channels to match a gate based description?
+Which class of problems can we simulate that cannot be simulated otherwise?
+Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)
 
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-% \ddag These authors also contributed equally to this work.
+Intuitively, it seems incredibly harder resource wise to create the sum b|gamma> superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.
 
-% Current address notes
-% \textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
-% \textcurrency b Insert second current address 
-% \textcurrency c Insert third current address
+\item Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.
 
-% Deceased author note
-% \dag Deceased
+\item At this point I am missing a proper defiition of a "quantum circuit" consistent with the mathematical formalism.
+The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.
 
-% Group/Consortium Author Note
-% \textpilcrow Membership list can be found in the Acknowledgments section.
+\item So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise.
 
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* carlospgmat03@gmail.com
+\item I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron. \\
 
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-% \cpnote{Revisar}
-Pauli channels are fundamental in the context of quantum computing as they
-model the simplest kind of noise in quantum devices.  We propose a quantum
-algorithm for simulating
-Pauli channels 
-and extend it to encompass Pauli dynamical maps 
-(parametrized Pauli channels).
-A parametrized quantum circuit is employed to accommodate for dynamical maps. 
-We also establish the mathematical conditions for an
-$N$-qubit transformation to be achievable using a parametrized circuit where
-only one single-qubit operation depends on the parameter. 
-The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
-for the case of one qubit, and the fidelity of this implementation is reported. 
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-%\section*{Author summary}
+El statement es: These straightforward channels could be accomplished more efficiently by
+simply applying the corresponding Pauli operation directly. \\
 
-\linenumbers
+\item but this is a severe disadvantage, that begs the question: what is the advantage? \\
 
-% Use "Eq" instead of "Equation" for equation citations.
-% }}}
-\section{Introduction} % {{{
+\item This definition is vague - given the vagueness of the term "quantum circuit".
+ Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit.
 
-Since their inception, quantum computers were proposed as powerful tools for
-the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
-quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
-practical~\cite{breuer2007theory} interest, there has been efforts towards the
-simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
-and specifically for quantum channels~\cite{Xin,Wei,Zanetti}.
+\item again, this is not a conclusion from theorem 1.
+This is literally Definition 1.
+Also, use the proper notation here - make A and B operators living on an dim N Hilbert state, and R explixitly dependent on s and operating on qubit N.
+Then the matrix representation of the operators is a $2^n\times 2^n$ matrix which is applied to the state j....
 
-Such systems have been simulated because of their many applications, 
-such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
-studying dissipative processes~\cite{Barreiro}
-and modeling non-Markovian dynamics~\cite{Marsden}.
-Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
-and withing them, the simplest class of channels that produce decoherence are
-Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
-effective models for the noise affecting quantum devices~\cite{Flammia}.
+The explanation in words in not sufficient.
 
-To represent the algorithms implemented in quantum computers, either to
-simulate a physical system or for some other purpose, one often uses a quantum
-circuit~\cite{chuangbook}.  In this work, we shall also work with parametrized
-quantum circuits, that is,  quantum circuits in which some of the operations
-depend on variable parameters~\cite{cerezo}.  These circuits play an important
-part in applications such as quantum machine learning~\cite{Benedetti} and
-describing general quantum transformations dependent on parameters. Substantial
-research has been devoted to enhancing the efficiency of these
-circuits~\cite{Rasmussen}.
+\item true only if the initial j states are normalised, but they were undefined.
 
-We start by providing the definition of quantum channels, the general framework
-used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
-Our first objective is to present a quantum algorithm capable of simulating
-Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
-for a Pauli Channel}, where we also demonstrate its implementation using IBM's
-quantum computers for the particular case of single-qubit Pauli channels. 
-Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
-dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
-channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
-study parametrized quantum channels, aiming to adapt the algorithm developed
-for channels to dynamical maps.  Furthermore, we contribute to the body of work
-related to parametrized quantum circuits by establishing a theorem,
-which  sets the mathematical conditions for the transformations
-that can be done using a parametrized circuit with the condition that only a
-controlled single-qubit
-operation in the circuit may depend on the parameter.  Finally, in
-section \ref{sec: 1PR circuit for a Pauli map}, we conclude about the Pauli
-dynamical maps that fulfill the conditions of theorem \ref{theorem2}.
+\item How can it make sense to define A and B applied respectively to the last 3 and the first qubit?
 
-% }}}
-\section{Pauli channels and dynamical maps}  \label{sec: Pauli Channels} % {{{
+\item  Please, at least give an example of this semiarbitrary construction of A and B.
 
-% Intro  {{{
+\item I don't understand what operatively is happening here. Select the state 0, apply B, apply s, apply A and then "straight forward calculations" lead to what?
 
-In this section  we introduce the concept of quantum channels, focusing on a
-specific type called Pauli channels.  Furthermore, we define Pauli dynamical
-maps, which are curves of Pauli channels parametrized by a variable.
-% }}}
-\subsection{Quantum channels} \label{subsec: Quantum Channels} % {{{
+\item so this is just the proof that the proposed operative definition of A and B is properly normalised, right?
 
-In quantum mechanics, a closed system's state is represented by a vector in a
-Hilbert space $\mathcal{H}$.  The state's evolution is unitary and given by
-Schrodinger's equation~\cite{Rieffel}.  However, in real-world situations,
-quantum systems are usually open, which means that they interact with their
-environment~\cite{breuer2007theory}.  For instance, the system's state may become
-entangled with the environment, leading to a loss of information about the
-system's state over time.
+\item there is literally one parameter in one qubit, of course it depends on one parameter...
+ how can this be a result?
 
-To describe open systems, instead of state vectors, we use matrices $\rho$ that
-act on $\mathcal{H}$.  These matrices are called density matrices, and they
-include information about the system's interaction with its environment.  For a
-density matrix $\rho$ to be physically valid, it must satisfy two conditions:
-$\tr(\rho) = 1$ and it must be positive semi-definite, which is denoted as
-$\rho \geq 0$~\cite{chuangbook}.
+ \item This is interesting, instead of giving only some random examples, I would actually explore more in details the zoology of this class of dynamical maps - if lucky, you would find class of interesting problems that can be simulated effectively in an experimental setup by just accessing one parameter (as the authors say, just with one set of waveplates, for example),
 
-Knowing this, we can now define quantum channels.  Quantum channels are
-operators $\mathcal{E}$ that can describe the evolution of open quantum
-systems, such that $\rho \rightarrow \mathcal{E}(\rho)$.  Quantum channels are
-the most general linear operations that a quantum system can undergo
-independently of its past~\cite{zimansbook,cirac}.  These channels are
-constructed based on three fundamental properties: linearity, trace
-preservation, and complete positivity.
+ \item I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit.
+I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so..
+what is the applicability of the theorem for higher dimensions?
 
-Linearity ensures that a quantum channel $\mathcal{E}$ maps any ensemble of
-density matrices into the corresponding ensemble of their evolution.  The trace
-preserving property is given by $\tr (\mathcal{E}[\rho]) = \tr (\rho) = 1$ and
-guarantees that the quantum channel does not change the condition that
-$\tr(\rho) = 1$.  Finally, the channel should also preserve the condition $\rho
-\geq 0$, and a map that does this is called a positive map.  However,
-positivity of $\mathcal{E}$ is not enough, and we actually require the more
-restrictive condition of complete positivity.  Complete positivity means that
-$\mathcal{E} \otimes \mathbb{I}_n$ is positive for any positive integer $n$
-(where $\mathbb{I}_n$ is the $n\times n$ identity matrix).  This ensures that
-even if the principal system is entangled with another system, applying
-$\mathcal{E}$ to the principal system while doing nothing to the other one
-still results in  a positive semidefinite state for the principal
-system~\cite{chuangbook}.
+ \item Imprcise (using parametrized quantum
+circuits.)
 
-Given a quantum channel $\mathcal{E}$, the condition of trace preservation is
-straightforward to verify but complete positivity is not as simple.  To test
-complete positivity of a quantum channel, Jamiołkowski and
-Choi~\cite{choi,jamil} developed a simple algorithm that exploits the
-isomorphism between a channel $\mathcal{E}$ and the state $\mathcal{D} =
-(\mathbb{I} \otimes \mathcal{E}) [|\Omega \rangle \langle  \Omega|]$, where
-$|\Omega\rangle = 1/\text{dim}(\mathcal{H}) \sum_{i}^{\text{dim}(\mathcal{H})}
-|i \rangle |i \rangle$ is a maximally entangled state between the original
-system and an ancilla.  Remarkably, the map $\mathcal{E}$ is completely
-positive if and only if $\mathcal{D}$ (also known as the Choi or dynamical
-matrix of $\mathcal{E}$) is positive semidefinite.
+ \item This reasoning I miss, simplifying for achieving what goal?
 
-% }}}
-\subsection{Pauli channels}  \label{subsec: Pauli Channels} % {{{
+ \item There is no quantification of this, it´s not even the focus of the paper
 
-We have discussed the main features of quantum channels and 
-now we turn our attention to a specific 
-type of channels for $N$-qubit systems called Pauli channels.
-First we will define these channels for single-qubit systems,
-whose most general density matrix can be written as~\cite{chuangbook}:
-\begin{equation}
-\label{eq: Density Matrix}
-\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
-\end{equation}
-with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
-The condition $\tr(\rho) = 1$ requires that $r_0 = 1$ while $\rho \geq 0$ 
-implies that the remaining $r_{1,2,3}$ form
-a vector $\vec{r}= (r_1,r_2,r_3)$ inside a unit sphere known as the Bloch sphere~\cite{Marinescu}.
-That is, every possible density matrix for a one-qubit
-system is uniquely associated with a point in a unit sphere.
+ \item citation required here
+\end{enumerate}
 
-Given a one-qubit system described by $\rho$, 
-a Pauli channel is defined as an operation that with probability $k_{\gamma}$
-applies the Pauli matrix $\sigma_{\gamma}$ to
-the system, for $\gamma = 0,1,2,3$~\cite{geometry}.
-Mathematically, the Pauli channel is written in the following way:
-\begin{eqnarray}
-\label{eq: Pauli channel 1 qbit}
-\mathcal{E}(\rho) = \sum_{\gamma=0}^3 k_{\gamma} \sigma_{\gamma} \rho \sigma_{\gamma},
-\end{eqnarray} 
-where the probabilities $k_{\gamma}$ of applying $\sigma_{\gamma}$
-are non-negative real numbers such that 
-$\sum_{\gamma} k_{\gamma} = 1$ (these conditions also ensure that the channel is 
-trace preserving and completely positive).
-
-Pauli channels are some of the 
-most fundamental noise models in quantum information science~\cite{Terhal}. 
-Some notable examples of Pauli channels are the following:
-\begin{itemize}
-\item \textbf{Bit Flip Channel:} This is a channel that with probability $1-p$ leaves the qubit as it is 
-and with probability $p$ applies the $\sigma_1$ matrix 
-(which flips the basis states $|0\rangle$ and $|1\rangle$ of the qubit), and
-so it is given by:
-\begin{align*}
-\mathcal{E}(\rho) = (1-p) \rho + p \sigma_1 \rho \sigma_1.
-\end{align*}
-Analogous channels exist using $\sigma_3$ (called the bit flip channel,
-which has a probability $p$ of adding a relative phase $\pi$ to the state) or 
-using $\sigma_2$ (called the phase flip channel, 
-which has a probability $p$ of 
-flipping the base states and also add a relative phase $\pi$).
-\item \textbf{Depolarizing channel:} 
-This channel has a probability $1-p$
-of doing nothing to the qubit and a probability $p$ of converting it into the maximally mixed state $\dfrac{1}{2} \mathbb{I}$
-and it can be written as:
-\begin{equation}
-\mathcal{E}(\rho) = (1-p)\rho + p \dfrac{1}{2} \mathbb{I} = \left(1 - \dfrac{3p}{4} \right) \sigma + \dfrac{p}{4} \sigma_1 \rho \sigma_1 + \dfrac{p}{4} \sigma_2 \rho \sigma_2+ \dfrac{p}{4} \sigma_3 \rho \sigma_3.
-\end{equation} 
-\end{itemize}
-
-We can also see how an arbitrary Pauli channel acts on an arbitrary  
-density matrix.
-To do it, we substitute \eref{eq: Density Matrix} 
-in \eref{eq: Pauli channel 1 qbit}:
-\begin{equation}
-\mathcal{E}(\rho) = \dfrac{1}{2}\sum_{\gamma,\alpha=0}^3 k_{\gamma} r_{\alpha} \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}.
-\end{equation}
-This can be simplified by using the following property of Pauli matrices:
-\begin{equation}
-\label{eq: propiedad-pauli}
-\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A_{\alpha,\gamma} = \begin{pmatrix}
-1 & 1 & 1 & 1\\
-1 & 1 & -1 &-1 \\
-1 & -1 & 1 & -1 \\
-1 & -1 & -1 & 1
-\end{pmatrix},
-\end{equation}
-which leads to
-\begin{equation}
-\label{eq: rho-transformada}
-\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
-\end{equation}
-\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix}
-but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
-This gives us another way of understanding Pauli channels
-as operations that take each component $r_{\alpha}$
-of the density matrix and multiplies them
-by $\sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}$, 
-that is:
-\begin{equation}
-\label{eq: multipliers}
-r_{\alpha}  \xrightarrow[\text{Channel}]{\text{Pauli}}  \tau_{\alpha} r_{\alpha} ,\;\; \tau_{\alpha} := \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}.
-\end{equation}
-Notice that $\tau_0 = 1$, which is a consequence of $\sum_{\gamma}k_{\gamma}=1$
-and ensures that after the channel, the resulting density matrix still has trace one. 
-Furthermore, reverting the definition of $\tau_{\alpha}$ by using that $A^{-1} = \dfrac{1}{4} A$, 
-we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\alpha} A_{\alpha,\gamma} \tau_{\alpha}$.
-Then, using that $k_{\gamma} \geq 0$
-we get the following conditions on the multipliers $\tau_{\alpha}$:
-\begin{eqnarray}
-\label{eq: conditions-tetrahedron}
-&1+\tau_i -\tau_j - \tau_k \geq 0,  \;\;\; \text{for $i,j,k$ different numbers in $\{1,2,3\}$}, \\
-&1+\tau_1 + \tau_2 + \tau_3 \geq 0.
-\end{eqnarray}
-
-These conditions imply that $(\tau_1,\tau_2,\tau_3)$
-has to be inside a tetrahedron with
-vertices $(1,1,1), (1,-1,-1), (-1,1,-1)$ and $(-1,-1,1)$. 
-Therefore, the $\tau_{1,2,3}$ are numbers between 
-$-1$ and $1$, which means that the components
-$r_{\alpha}$ of the density matrix are always 
-attenuated and possibly sign flipped.
-
-Having defined the one qubit case,  we can now generalize to $N$ qubits.
-In order to do it, we need to introduce the so-called \textit{Pauli strings}, defined as
-\begin{eqnarray}
-\label{eq: Pauli string}
-\sigma_{\vec{\alpha}} = \sigma_{\alpha_1} \otimes \sigma_{\alpha_2}\otimes \cdots \otimes \sigma_{\alpha_N},
-\end{eqnarray}
-where $\vec{\alpha}$ denotes a multi-index $(\alpha_1, \cdots, \alpha_N)$
- and $\alpha_i \in \{0,1,2,3\}$. 
-These operators form an orthogonal basis in the space of operators acting on $N$ qubits. 
- Similarly to the single-qubit case, the density matrix $\rho$ 
-of a system of $N$ qubits can be written using Pauli strings as:
-\begin{equation}
-\label{eq:  Density matrix Nqbit}
-\rho = \dfrac{1}{2^N} \sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
-\end{equation}
-Then, just as before, we define a Pauli channel as a transformation that applies 
-the operator $\sigma_{\vec{\gamma}}$ to $\rho$ with probability $k_{\vec{\gamma}}$
-and is therefore described mathematically by:
-\begin{equation}
-\label{eq: pauli channel N-qubit}
-\mathcal{E}(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}} \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
-\end{equation}
-where just as before, $k_{\vec{\gamma}}$ are non-negative real numbers such 
-that $\sum_{\vec{\gamma}} k_{\vec{\gamma}}=1$.
-
-As in the one qubit case, Pauli channels for $N$ qubits 
-attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
-This can be seen by substituting \eref{eq:  Density matrix Nqbit} in \eref{eq: pauli channel N-qubit}
-and using the property of \eref{eq: propiedad-pauli}:
-\begin{align*}
-\mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
-& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} {(A^{\otimes^N})}_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
-\end{align*}
-which means that applying the Pauli channel multiplies the 
-components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} {(A^{\otimes^N})}_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
-% }}}
-\subsection{Pauli dynamical maps} % {{{
-\label{subsec: Pauli Dynamical Maps}
-
-As seen in the last section, Pauli channels and in 
-general quantum channels are discrete maps
-that transform a density matrix $\rho$ into $\mathcal{E}(\rho)$.
-However, we could also define a continuous set of 
-channels $\varepsilon_p$ with $p$ a real parameter.
-
-For the special case of Pauli channels, we define 
-a Pauli dynamical map as a continuous parametrized 
-curve drawn inside the set of Pauli channels and starting at the identity channel. 
-Therefore, a Pauli dynamical map can be written as
-\begin{eqnarray}
-\label{eq: Pauli dynamical map}
-\mathcal{E}_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
-\end{eqnarray}
-where $p$ is a parameter in an interval $[a,b]$ 
-and $\mathcal{E}_p$ is a Pauli channel for every $p$, 
-with $\mathcal{E}_a$ being the identity channel.
-
-% }}}
-% }}}
-\section{Circuit for a Pauli channel} % {{{
-\label{sec: Circuit for a Pauli Channel}
-% Intro {{{
-
-In this section we propose a quantum circuit that simulates $N$-qubit Pauli
-channels.  Moreover, we implement the circuit for $N=1$ on a quantum computer
-and analyze the results using the diamond norm.
-We find that close to the depolarizing channel, the general circuit simulator 
-can implement such channels with the highest fidelity. 
-% produce the highest 
-% }}} 
-\subsection{Description of the circuit for a Pauli channel} %{{{
-\label{subsec: Description of the circuit}
-
-To design the circuit that implements \eref{eq: pauli channel N-qubit}, we construct a state that 
-includes the probabilities $k_{\gamma}$ on the ancilla qubits and subsequently
-apply controlled Pauli operations on the main qubits.  The circuit that does
-this is presented in \fref{Fig1}.
-
-\begin{figure}[!h] % {{{
-\centering
-%\includegraphics{images/circuito_general.pdf}
-\caption{{\bf Circuit for an $N$-qubit
-Pauli channel.}
-The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
-on the $2N$ ancilla qubits denoted by $\tilde{q}$.}
-\label{Fig1}
-\end{figure} % }}}
-
-The first part of the circuit involves the creation of the state
-\begin{eqnarray}
-\label{eq: state}
-\text{Ancilla state =} 
-\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
-\end{eqnarray}
-on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
-{|b_{\vec{\gamma}}|}^2 = k_{\vec{\gamma}}$ and
-the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
-\cdots |\gamma_N\rangle$.
-When measured in the computational basis, the state given in \eref{eq: state}
-collapses to $|\vec{\gamma}\rangle$ with a 
-probability ${|b_{\vec{\gamma}}|}^2 = k_{\vec\gamma}$. 
-The circuit in \fref{Fig1} uses this fact
-to apply $\sigma_{\vec{\gamma}}$ on the main qubits
-with a probability $k_{\vec\gamma}$ by using controlled operations 
-conditioned on the state of the system being $|\vec{\gamma}\rangle$,
-just as the Pauli channel is supposed to do.
-
-%}}}
-\subsection{Simulation for one-qubit Pauli channels} % {{{
-\label{subsec: Simulation for one-qubit Pauli channels}
-
-For the particular case of a Pauli channel on one qubit, the circuit that
-simulates it can be constructed as in \fref{Fig2},
-which is a special case of \fref{Fig1}
-but with all details  explicitly shown.
-In said figure, the ancilla state
-of \eref{eq: state} can be taken to be
-$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
-|10\rangle + \sqrt{k_{11}}|11\rangle$
-and it is created on the ancilla qubits with the help of three rotations of angles
-defined by the following equations:
-\begin{align}
-\label{eq:angle}
-\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\nonumber \\
-\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}},  \\
-\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.  \nonumber
-\end{align}
-
-\begin{figure}[!h] % {{{
-\centering
-%\includegraphics{images/circuito_unqubit.pdf}
-\caption{
-{\bf One-qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
-which is a particular case of \fref{Fig1}.  Here we have two
-ancilla qubits and we use three rotations
-of angles given by \eref{eq:angle} to create the Ancilla State of
-of \eref{eq: state} for the two ancilla qubits.
-}
-\label{Fig2} 
-\end{figure} % }}}
-
-% We took a sample of one-qubit Pauli channels and
-% used the ibmq-lima quantum computer that IBM has available~\cite{Qiskit}
-% to simulate them. For each of these channels, we used quantum process
-% tomography~\cite{Qiskit, Chuang:1996} to obtain the 
-% operator $\xi_I$ corresponding to the implementation of the
-% circuit.  Then, we compared this operator with the ideal 
-% channel $\xi_T$  we
-% wanted to implement.
-
-We took a sample of one-qubit Pauli channels
-and evaluated their implementation on IBM's
-ibmq-lima quantum computer~\cite{Qiskit},
-as shown in \fref{Fig3}. 
-For each of the channels sampled, we used 
-quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the 
-operator $\xi_I$ corresponding to the implementation of the
-circuit in the quantum computer. 
-Then, we compared $\xi_I$ with the theoretical 
-operator $\xi_T$ of the Pauli channel we wanted to implement.
-To see how close the operators $\xi_I$ and 
-$\xi_T$ are, we shall use the
-diamond distance~\cite{wildebook}, which is defined by
-\begin{equation}
-||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
-\end{equation}
-with $I$ the identity map,
-$|| \cdot ||_1$ the trace norm and the maximization
-done over all density matrices $\rho$.
-The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.
-When the two channels are the same,
-the diamond distance has a value of $0$, while in the case that the channels
-are completely distinguishable, the distance reaches its maximum value of $2$~\cite{Benenti}.
-For the analysis done in \fref{Fig3}, we define a sort of ``diamond fidelity'' as: 
-\begin{equation}
-f = 1 - \dfrac{1}{2} ||\varepsilon_I - \varepsilon_T ||_{\diamond},
-\label{eq:diamond-fid}
-\end{equation}
-which ranges from $0$, when the channels have a maximum distance, to  $1$,
-when they are exactly equal.
-
-\begin{figure}[!h] % {{{
-\centering
-\caption{{\bf Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
-for a sample of Pauli channels in the tetrahedron.}  Notice that channels close
-to the center of the tetrahedron have high fidelities, while those close to the
-borders do not.  Moreover, we show the results for cuts of the tetrahedron at
-different values of $\tau_3$.}
-\label{Fig3}
-\end{figure} % }}}
-
-Finally, using the representation of Pauli channels in a tetrahedron as in
-\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
-fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
-see that channels close to the completely depolarizing channel (that is close
-to the center of the tetrahedron) have a high $f$, while those close to unitary
-channels have much lower $f$.  This is reasonable because quantum computers are
-prone to errors that depolarize qubits, which isn't very problematic when
-trying to simulate depolarization but it is when simulating unitary processes.
-Moreover, the algorithm of \fref{Fig2} is not optimal for
-unitary channels (that is, the channels corresponding to the vertices of the
-tetrahedron).  These straightforward channels could be accomplished more
-efficiently by simply applying the corresponding Pauli operation directly.
-Nevertheless, due to its general design to accommodate any Pauli channel, the
-algorithm employs numerous quantum gates even in such scenarios.
-
-% }}}
-% }}}
-\section{One parameter circuits} % {{{
-\label{sec: 1PR Circuits}
-
-Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
-of \fref{Fig1}. However, there is one difference: 
-the state to be created on the ancilla qubits now 
-depends on a parameter $p$, and it is represented by the expression:
-\begin{eqnarray}
-\label{eq: parametrized state}
-\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
-\end{eqnarray}
-Thus, we temporarily shift our focus from Pauli
-channels and dynamical maps to the general problem of 
-creating a circuit to generate a curve of
-states like the one described in \eref{eq: parametrized state}.
-
-In general, producing this curve of states for $N$ qubits will require
-many rotations parametrized by $p$,
-such as the three rotations used for the ancilla
-qubits in \fref{Fig2}.
-However, it would be preferable to achieve the same effect using only one parametrized rotation. 
-This would allow us to interpret said rotation 
-as a knob that smoothly traverses the curve of states.
-Consequently, we are faced with the question of which curves of states, 
-such as the one described in \eref{eq: parametrized state}, 
-can be produced using just a single parametrized rotation. 
-To clarify this, we provide the following definition 
-for a circuit with one parametrized rotation.
-
-\begin{definition}{\textbf{1-Parameter Rotation Circuit:}}
-A 1-Parameter Rotation (1PR) circuit is a parametrized quantum
-circuit that includes only one gate dependent on a parameter $p$.
-Moreover, the parametrized gate is a one-qubit rotation about any axis,
-whether controlled or not.
-\end{definition}
-
-Based on this definition, we aim to determine which curves of 
-states can be generated using 1PR circuits. 
-To accomplish this, we begin by proving that all 1PR circuits have 
-the form depicted in \fref{Fig4},
-where the parametrized rotation is around $\sigma_3$ and
-is applied to the last qubit.
-
-\begin{figure}[!h] % {{{
-\centering
-%\includegraphics{images/OPR-circuit.pdf}
-\caption{\textbf{General form of a 1PR circuit}.
-Any 1PR circuit can be transformed into this form,
-where the rotation on the last qubit
-can be controlled or not by any of the other qubits.
-$A$ and $B$
-are $N$-qubit gates that do not depend on the parameter $p$ and
-$s= s(p)$ is a function of the parameter.
-}
-\label{Fig4}
-\end{figure} % }}}
-
-\begin{theorem}
-An $N-$qubit 1PR circuit can always be transformed 
-into the form shown in \fref{Fig4}.
-\end{theorem}
-\textbf{Proof:} 
-First, we observe that according to the
-definition, a 1PR circuit always consists of an operation $B$ followed 
-by the parametrized rotation and then another operation $A$, 
-where $A$ and $B$ are not parametrized.
-
-Next, we note that it is not necessary to consider rotations about an arbitrary axis,
-as a rotation about any axis $\hat{n}$ parameterized by $p$
-can be transformed into a rotation about $\sigma_3$ without introducing 
-gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
-is a function of $p$ (the factor of 2 is for convenience later on) 
-and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
-We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
-where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
-The rotation can then be rewritten as follows:
-\begin{eqnarray}
-R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
-\end{eqnarray}
-Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
-any 1PR circuit can be transformed into a circuit where the parametrized
- rotation is around $\sigma_3$ instead of an arbitrary axis. 
-Moreover, without loss of generality, we can choose the last qubit as the
-target qubit for the rotation, since if it weren't, we could use
-swap gates to move the rotation
-to the first qubit without adding gates
-that depend on $p$.
-
-Therefore, a 1PR circuit can be transformed such
-that the rotation is around $\sigma_3$ and is applied to the last qubit 
-(possibly controlled by other qubits), 
-resulting in the form depicted in \fref{Fig4}. 
-$\blacksquare$ \\
-$\;$\\
-
-With the aid of this theorem, we can now determine the curves
-of states of $N$ qubits that can be generated using a 1PR circuit. 
-This result is stated in the following theorem.
-
-\begin{theorem}
-\label{theorem2}
-Consider a 1PR circuit of $N$ qubits parametrized by $p$
-and denote by $U$ the operator it implements on this system. 
-Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
-we have that:
-\begin{align*}
-U|j\rangle = e^{is(p)} |a^j\rangle + e^{-is(p)} |b^j\rangle + |c^j\rangle
-\end{align*}
-with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
-c^j|c^j \rangle = 1$.
-\end{theorem}
-\textbf{Proof:} 
-We can conclude from theorem 1 that $U=ARB$,
-where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
-applied to the last qubit and controlled by some of the other ones.
-
-First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
-with $B_{i,j}$ the entries of matrix $B$.
-This can be rewritten by separating last qubit from the other $N-1$:
-\begin{equation}
-B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right).
-\end{equation}
-After the operator $B$, the circuit applies the  controlled rotation $R$.
-To simplify the analysis, we separate the states of
-the first $N-1$ qubits into those that fulfill the control conditions of the rotation
-(which we denote as the set $\mathcal{C}$)
-and those that do not, and write it as
-\begin{align}
-B|j\rangle = 
-   \sum_{k \in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle 
-                                     + B_{2k+1,j} |k \rangle |1\rangle  \right) 
-   + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  
-                                      + B_{2k+1,j} |k \rangle |1\rangle  \right).
-\end{align}
-
-Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
-and not the others. Therefore,  
-remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is(p)}$ to $|0\rangle$
-and a phase $e^{is(p)}$ to $|1\rangle$, we have that,
-% \begin{small}
-% \begin{eqnarray}
-% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
-% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
-% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
-% \end{eqnarray}
-% \end{small}
-% test
-\begin{align}
-RB|j\rangle& = e^{-is(p)} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is(p)} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
-+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
-& = e^{-is(p)} |\tilde{b}^{j}\rangle + e^{is(p)} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle,
-\end{align}
-where we defined
-\begin{align*}
-|\tilde{a}^j \rangle &= \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle,\\
-|\tilde{b}^j\rangle &= \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle,\\
-|\tilde{c}^j\rangle &= \sum_{k \not\in \mathcal{C}}\left( B_{2k,j} |k\rangle|0\rangle+ B_{2k+1,j} |k \rangle |1\rangle  \right).
-\end{align*}
-These states are clearly orthogonal because they are each linear combinations of different 
-orthogonal states of the computational basis. 
-Moreover, they satisfy  $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle c^j| c^j\rangle = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
-which is unitary.
-
-Finally, after having applied the rotation, the circuit applies gate $A$, 
-so that the result is given by:
-\begin{eqnarray}
-U|j\rangle = ARB|j\rangle = e^{-is(p)} A |\tilde{a}^j\rangle + e^{is(p)} A |\tilde{b}^j\rangle + A |\tilde{c}^j\rangle = e^{-is(p)} |a^j\rangle + e^{is(p)} |b^j\rangle + |c^j\rangle,
-\end{eqnarray}
-where $|a^j\rangle = A |\tilde{a}^j\rangle, |b^j\rangle = A |\tilde{b}^j\rangle, |c^j\rangle = A |\tilde{c}^j\rangle$ are still orthogonal
-states that satisfy $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$ because $A$ is unitary. $\blacksquare$  \\
- $\;$ \\
-
-This theorem implies that when starting from the state $|0\rangle$ 
-or any other initial state, the only possible curves of states that can be 
-created using a 1PR circuit are of the following form:
-\begin{equation}
-|\eta(p)\rangle = |c\rangle + e^{is(p)}|a\rangle + e^{-is(p)} |b\rangle,
-\label{eq:curve-states}
-\end{equation}
-with conditions defined by the equations: 
-\begin{equation}
-\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1,  \quad
-\langle a |b\rangle =
-\langle a |c\rangle =
-\langle b |c\rangle = 0.
-\label{eq:conditions-vecs}
-\end{equation}
-
-Moreover, it is possible to construct a 1PR circuit to generate any given curve of 
-states described by \eref{eq:curve-states}. 
-One approach to achieve this is by utilizing the circuit 
-depicted in \fref{Fig4}, 
-with the parametrized rotation $R$ applied to the last qubit controlled by all the 
-other qubits. The operators $A$ and $B$ can be defined as follows:
-\begin{align*}
-&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \\
-&A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
-\end{align*}
-The remaining part of the operators $A$ and $B$ can be defined
-in any arbitrary manner as long as they are unitary.
-By starting from the initial state $|0\rangle$ and 
-applying the circuit shown in \fref{Fig4}, straightforward calculations 
-lead us to obtain the resulting curve of states described in \eref{eq:curve-states}.
-
-To see it, we can rewrite the expression of $B|0\rangle$ by 
-separating the first $N-1$ qubits from the last one:
-$$B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.$$
-Since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$. As a result, we obtain:
-
-$$
-RB|0\rangle =\sqrt{\langle a | a \rangle} e^{is(p)} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} e^{-is(p)} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.
-$$
-
-Finally, applying the defined operator $A$ to this state yields the desired result.
-
-\section{1PR circuit for a Pauli map} % {{{
-\label{sec: 1PR circuit for a Pauli map}
-
-We can now use the previous results to conclude directly which Pauli dynamical maps
-can be implemented with a 1PR circuit.
-For this, the curve of states of \eref{eq: parametrized state} 
-has to be constructed with only one parametrized rotation,
-so it has to satisfy the conditions of theorem \ref{theorem2}.
-Therefore, this implies that the map
-\begin{eqnarray}
-\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
-\end{eqnarray}
-can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
-\begin{eqnarray}
-\label{eq:vec}
-\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
-\end{eqnarray}
-where $|a\rangle,|b\rangle,|c\rangle$ fulfill
-the conditions of \eref{eq:conditions-vecs}.
-
-For the particular case of one qubit, we can show some examples of Pauli
-dynamical maps implementable with a 1PR circuit, which are plotted in
-\fref{Fig5}. 
-The examples we show include some of the most common maps: the bit flip, phase flip, bit-phase flip and depolarizing.
-However, we also include the parabolic dynamical map,
-defined in \eref{eq:parab} and shown in \fref{Fig5}.
-This map traces a parabola inside the tetrahedron connecting two of its vertices
-and it describes a frontier in the tetrahedron between Pauli channels
-that are reachable by Lindbladian dynamics and those that are not~\cite{Davalos}.
-
-\begin{figure}[!h] % {{{
-%\captionsetup[subfigure]{justification=centering}
-\centering
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-%  \includegraphics[width=.9\linewidth]{images/curvas.png}
-%   \caption{}
-%  \label{Fig51}
-%\end{subfigure}%
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-%  \includegraphics[width=.9\linewidth]{images/curvas-azar.png}
-%  \caption{}
-%  \label{Fig5-2}
-%\end{subfigure}
-\caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
-The curves painted in these tetrahedrons
-represent Pauli dynamical maps that can be implemented with 1PR circuits.
-(a) shows the dynamical maps mentioned in the main 
-text, which are: depolarizing (purple), bit flip (blue),
-phase flip (green), bit-phase flip (red)
-and parabolic (orange).
-(b) shows dynamical maps selected at random that can be implemented with 1PR 
-circuits.}
-\label{Fig5}
-\end{figure} % }}}
-
-\begin{itemize}
-\item \textbf{Depolarizing:} This dynamical map is given by
-\begin{align*}
-\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
-\end{align*}
-with $p \in [0,1]$. 
-Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
-qubits is such that ${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 =
-{|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.  Then, taking the $\beta_j$ to be
-real, the curve of states can be 
-\begin{align*}
-|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
-\end{align*}
-This state can be rewritten as:
-\begin{align*}
-|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle 
-      - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
-& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle 
-      + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
-\end{align*}
-with $\sin s = \sqrt{3p/4}$.
-We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
-1PR circuit.
-
-\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
-\begin{eqnarray}
-\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3,
-\label{eq:parab}
-\end{eqnarray}
-with $p \in [-1,1]$. 
-If we take the $\beta_j$ to be real,
-the curve of states needed on the ancilla qubits can be:
-\begin{eqnarray}
-|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
-\end{eqnarray}
-This can be rewritten as
-\begin{align*}
-|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
-& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
-\end{align*}
-with $\sin s = p$, so that
-this map fulfills the conditions of  \eref{eq:conditions-vecs}.
-
-\item \textbf{Bit flip map:} 
-This dynamical map is defined as
-\begin{align*}
-\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
-\end{align*}
-for $p \in [0,1]$. 
-In particular, if we take the $\beta_j$ to be real,
-we need to create the curve of states:
-\begin{align*}
-|\beta(p)\rangle = \sqrt{1-p} |00\rangle +\sqrt{p} |01\rangle.
-\end{align*}
-This can be rewritten as
-\begin{align*}
-|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |00\rangle - \dfrac{i}{2} |01\rangle \right) + e^{-is} \left( \frac{1}{2} |00\rangle + \frac{i}{2} |01\rangle \right),
-\end{align*}
-with $\sin s= \sqrt{p}$.
-Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
-and it can be created with a 1PR circuit.
-Note that in this case we actually only need one ancilla qubit
-since the state $|\beta(p)\rangle$ is only two dimensional.
-
-The exact same thing can be done
-for the phase flip and bit phase flip dynamical maps by
-changing $\sigma_1$ to
-$\sigma_3$ and $\sigma_2$ respectively.
-For example, the bit phase flip map was implemented in \cite{Andrea, Andrea_4qb} 
-using an optical arrangement, and  it was indeed done 
-by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate).
-
-\end{itemize}
-
-Furthermore, we can construct other examples of 
-Pauli dynamical maps such that they
-can be implemented with a 1PR circuit.
-To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
-that satisfy the conditions of  \eref{eq:conditions-vecs}.
-For example, this can be done systematically for the case of curves of states of two qubits
-(that is, for Pauli dynamical maps of one qubit)
-with the following procedure:
-\begin{itemize}
-\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
-such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
-This can be done by selecting two angles
-$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
-\begin{align*}
-|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
-\end{align*}
-\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
-\item[3.] 
-Finally, we choose a unitary matrix $V$ with the condition that its first
-row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
-with $\theta$ a uniform random phase.
-That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
-and since $V$ is unitary, these unprimed vectors will fulfill the conditions of
-\eref{eq:conditions-vecs}.
-Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
-since it implies that when $s=0$, the 
-state created in \eref{eq:vec}
-is
-$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
-which  corresponds with applying the identity channel.
-
-Such a matrix $V$ can be randomly constructed by first finding three vectors 
-$\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to
-the first row using the Gram-Schmidt process.  Then selecting random complex
-numbers $r_1, r_2, r_3$ such that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and defining
-the second row of $V$ to be $r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
-Once the first two rows are chosen, use Gram-Schmidt to find two vectors
-$\vec{v}_1, \vec{v}_2$ orthogonal to 
-them and similarly define the third row as $q_1 \vec{v}_1+ q_2 \vec{v}_2$
-with $|q_1|^2 + |q_2|^2$ and $q_1,q_2$
-selected at random. 
-Finally, there is only one choice for the fourth row so that it is 
-orthonormal to the first three
-and a random phase can be given to it.
-\end{itemize}
-
-Following this procedure for random
-angles and unitary matrices $V$, 
-we plot four Pauli dynamical maps  selected at random
-that can be implemented with a 1PR circuit in \fref{Fig5}.
-
-% }}}
-\section{Conclusion} % {{{
-
-In this work, we found a quantum algorithm for 
-simulating Pauli channels in $N$-qubit systems and
-generalized it to Pauli dynamical maps
-by using parametrized quantum circuits.
-Furthermore, we implemented single-qubit Pauli channels
-on one of IBM's quantum computers
-and obtained their fidelities. 
-Finally, when working with Pauli dynamical maps,
-we searched for a way of simplifying the parametrized circuit
-by requiring that only one single-qubit rotation depends on the parameter.
-In theorem \ref{theorem2} we found the general mathematical conditions for 
-this, applicable to any parametrized circuit.
-
-Therefore, this work presents yet another example of the current
-exploration into simulating open quantum
-systems in quantum computers,
-and we observe the big effect that the error of quantum computers have
-on these simulations.
-On the other hand, the result
-of theorem \ref{theorem2}
-shows what can be done with the condition of using only one
-parametrized rotation and
-can be applied to any quantum algorithm that requires parametrized circuits,
-such as those used for quantum machine learning.
-
-% }}}
-%\section{Supporting information} % {{{
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-% \paragraph*{S1 Fig.}
-% \label{S1_Fig}
-% {\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
-% 
-% \paragraph*{S2 Fig.}
-% \label{S2_Fig}
-% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-% 
-% \paragraph*{S1 File.}
-% \label{S1_File}
-% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-% 
-% \paragraph*{S1 Video.}
-% \label{S1_Video}
-% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-% 
-% \paragraph*{S1 Appendix.}
-% \label{S1_Appendix}
-% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-% 
-% \paragraph*{S1 Table.}
-% \label{S1_Table}
-% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-% }}}
-\section{Acknowledgments} % {{{
-Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here. See http://journals.plos.org/plosone/s/latex for 
-% step-by-step instructions.
-
-\begin{thebibliography}{10}
-
-\bibitem{feynman1982simulating}
-Feynman RP.
-\newblock Simulating physics with computers.
-\newblock Int J Theor Phys. 1982;21(6/7):467--488.
-
-\bibitem{Zur91}
-Zurek WH.
-\newblock Decoherence and the transition from quantum to classical.
-\newblock Phys Today. 1991;44(10):36--44.
-
-\bibitem{RevModPhys.76.1267}
-Schlosshauer M.
-\newblock Decoherence, the measurement problem, and interpretations of quantum
-  mechanics.
-\newblock Rev Mod Phys. 2005;76(4):1267--1305.
-
-\bibitem{breuer2007theory}
-Breuer HP, Petruccione F.
-\newblock The theory of open quantum systems.
-\newblock 1st ed. New York: Oxford University Press; 2002.
-
-\bibitem{Garcia}
-García-Pérez G, Rossi M, Maniscalco S.
-\newblock IBM Q Experience as a versatile experimental testbed for simulating
-  open quantum systems.
-\newblock npj Quantum Inf. 2020;6(1):1--11.
-
-\bibitem{Wang}
-Wang H, Ashhab S, Nori F.
-\newblock Quantum algorithm for simulating the dynamics of an open quantum
-  system.
-\newblock Phys Rev A. 2011;83(6):062317.
-
-\bibitem{Weimer}
-Weimer H, Kshetrimayum A, Or\'us R.
-\newblock Simulation methods for open quantum many-body systems.
-\newblock Rev Mod Phys. 2021;93(1):015008.
-
-\bibitem{Xin}
-Xin T, Wei SJ, Pedernales JS, Solano E, Long GL.
-\newblock Quantum simulation of quantum channels in nuclear magnetic resonance.
-\newblock Phys Rev A. 2017;96(6):062303.
-
-\bibitem{Wei}
-Wei S, Xin T, Long G.
-\newblock Efficient universal quantum channel simulation in IBM's cloud quantum
-  computer.
-\newblock Sci China Phys Mech Astron. 2018;61(7):70311.
-
-\bibitem{Zanetti}
-Zanetti M, Pinto D, Basso M, Maziero J.
-\newblock Simulating noisy quantum channels via quantum state preparation
-  algorithms.
-\newblock Phys B At Mol Opt Phys. 2023;56(11):115501.
-
-\bibitem{Andrea}
-Far\'ias OJ, Aguilar GH, Vald\'es-Hern\'andez A, Ribeiro PHS, Davidovich L,
-  Walborn SP.
-\newblock Observation of the emergence of multipartite entanglement between a
-  bipartite system and its environment.
-\newblock Phys Rev Lett. 2012;109(15):150403.
-
-\bibitem{Andrea_AD}
-Aguilar GH, Vald\'es-Hern\'andez A, Davidovich L, Walborn SP, Souto~Ribeiro PH.
-\newblock Experimental entanglement redistribution under decoherence channels.
-\newblock Phys Rev Lett. 2014;113(24):240501.
-
-\bibitem{Barreiro}
-Barreiro J, Müller M, Schindler P, Nigg D, Monz T, Chwalla M, et~al.
-\newblock An open-system quantum simulator with trapped ions.
-\newblock Nature. 2011;470(7335):486--491.
-
-\bibitem{Marsden}
-Head-Marsden K, Krastanov S, Mazziotti D, Narang P.
-\newblock Capturing non-Markovian dynamics on near-term quantum computers.
-\newblock Phys Rev Res. 2021;3:013182.
-
-\bibitem{chuangbook}
-Nielsen MA, Chuang IL.
-\newblock Quantum computation and quantum information: 10th anniversary
-  edition.
-\newblock 10th ed. New York: Cambridge University Press; 2011.
-
-\bibitem{geometry}
-Bengtsson I, {\. Z}yczkowski K.
-\newblock Geometry of quantum states: an introduction to quantum entanglement.
-\newblock 1st ed. Cambridge: Cambridge University Press; 2006.
-
-\bibitem{Zbigniew}
-Puchała Z, Łukasz Rudnicki, {\. Z}yczkowski K.
-\newblock Pauli semigroups and unistochastic quantum channels.
-\newblock Phys Lett A. 2019;383(20):2376--2381.
-
-\bibitem{Davalos}
-Davalos D, Ziman M, Pineda C.
-\newblock Divisibility of qubit channels and dynamical maps.
-\newblock Quantum. 2019;3:144.
-
-\bibitem{Flammia}
-Steven F, Joel W.
-\newblock Efficient estimation of Pauli channels.
-\newblock ACM. 2020;1(3):1--32.
-
-\bibitem{cerezo}
-Cerezo M, Arrasmith A, Babbush R, Benjamin SC, Endo S, Fujii K, et~al.
-\newblock Variational quantum algorithms.
-\newblock Nat Rev Phys. 2020;3(9):625--644.
-
-\bibitem{Benedetti}
-Benedetti M, Lloyd E, Sack S, Fiorentini M.
-\newblock Parameterized quantum circuits as machine learning models.
-\newblock Quantum Sci Technol. 2019;4(4):043001.
-
-\bibitem{Rasmussen}
-Rasmussen S, Loft N, Bækkegaard T, Kues M, Zinner N.
-\newblock Reducing the amount of single-qubit rotations in VQE and related
-  algorithms.
-\newblock Adv Quantum Technol. 2020;3:2000063.
-
-\bibitem{Rieffel}
-Rieffel E, Polak W.
-\newblock Quantum computing: a gentle introduction.
-\newblock 1st ed. Massachusetts: The MIT Press; 2011.
-
-\bibitem{zimansbook}
-Heinosaari T, Ziman M.
-\newblock {The Mathematical Language of Quantum Theory: From Uncertainty to
-  Entanglement}.
-\newblock 2nd ed. Cambridge: Cambridge University Press; 2012.
-
-\bibitem{cirac}
-Wolf MM, Cirac JI.
-\newblock Dividing quantum channels.
-\newblock Comm Math Phys. 2008;279(1):147--168.
-
-\bibitem{choi}
-Choi MD.
-\newblock Completely positive linear maps on complex matrices.
-\newblock Linear Algebra Appl. 1975;10(3):285--290.
-
-\bibitem{jamil}
-Jamiołkowski A.
-\newblock Linear transformations which preserve trace and positive
-  semidefiniteness of operators.
-\newblock Rep Math Phys. 1972;3(4):275--278.
-
-\bibitem{Marinescu}
-Marinescu D, Marinescu G.
-\newblock Classical and Quantum Information.
-\newblock 1st ed. Oxford: Elsevier; 2012.
-
-\bibitem{Terhal}
-Terhal BM.
-\newblock Quantum error correction for quantum memories.
-\newblock Rev Mod Phys. 2015;87(2):307--346.
-
-\bibitem{Qiskit}
-{Qiskit contributors}. Qiskit: An Open-source Framework for Quantum Computing;
-  2023.
-
-\bibitem{Chuang:1996}
-Chuang IL, Nielsen MA.
-\newblock {Prescription for experimental determination of the dynamics of a
-  quantum black box}.
-\newblock J Mod Opt. 1997;44:2455--2467.
-
-\bibitem{wildebook}
-Wilde M.
-\newblock From classical to quantum Shannon theory.
-\newblock 2nd ed. Cambridge: Cambridge University Press; 2019.
-
-\bibitem{Watrous}
-Watrous J.
-\newblock Simpler semidefinite programs for completely bounded norms.
-\newblock Theor Comput Sci. 2013;19(8):1--19.
-
-\bibitem{Benenti}
-Benenti G, Strini G.
-\newblock Computing the distance between quantum channels: usefulness of the
-  Fano representation.
-\newblock J Phys B At Mol Opt Phys. 2010;43(21):215508.
-
-\bibitem{Andrea_4qb}
-Aguilar GH, Far\'ias OJ, Vald\'es-Hern\'andez A, Souto~Ribeiro PH,
-  Davidovich L, Walborn SP.
-\newblock Flow of quantum correlations from a two-qubit system to its
-  environment.
-\newblock Phys Rev A. 2014;89(2):022339.
-
-\end{thebibliography}
-
-% }}}
-\appendix
 \end{document}

### 2023-09-06 Tareas por hacer.tex
Tareas

--- 2023-07-01 Template/main.tex
@@
 \begin{document}
-% Titulo, afiliacion, abstract  {{{
-\vspace*{0.2in}
 
-\begin{flushleft}
-{\Large
-\textbf\newline{Quantum simulation of Pauli channels and dynamical maps: algorithm and implementation } % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Tomás Basile\textsuperscript{1,2\Yinyang},
-Carlos Pineda\textsuperscript{2*\Yinyang},
-\\
-\bigskip
-\textbf{1} Facultad de Ciencias. Universidad Nacional Autónoma de México, Ciudad de México 01000, Mexico
-\\
-\textbf{2} Instituto de Física, Universidad Nacional Autónoma de México, Ciudad de México 01000, México
-\\
-\bigskip
+\section{Simulación de cosas de dos qubits}
 
-% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
-% 
-% Remove or comment out the author notes below if they aren't used.
-%
-% Primary Equal Contribution Note
-\Yinyang These authors contributed equally to this work.
+En general, un canal de dos qubits va a requerir 4 qubits de ancilla. El circuito para hacerlo es una de las figuras del artículo y es una generalización sencilla del de un qubit.\\
 
-% Additional Equal Contribution Note
-% Also use this double-dagger symbol for special authorship notes, such as senior authorship.
-% \ddag These authors also contributed equally to this work.
+Algunos posibles canales a simular son por ejemplo:
+\begin{itemize}
+\item $\varepsilon(\rho) = p \rho + (1-p) \sigma_z \otimes \sigma_z \rho \sigma_z \otimes \sigma_z $.
+\item $\varepsilon(\rho) = p_1 \rho + p_2 \sigma_z \otimes I \rho \sigma_z \otimes I + p_3 I \otimes \sigma_z \rho I \otimes \sigma_3 $.
+\end{itemize}
+Como el primer canal solo involucra 2 de los 16 operadores de Pauli, en realidad sólo requiere un qubit de ancilla. El segundo canal requiere 2 qubits de ancilla. \\
 
-% Current address notes
-% \textcurrency Current Address: Dept/Program/Center, Institution Name, City, State, Country % change symbol to "\textcurrency a" if more than one current address note
-% \textcurrency b Insert second current address 
-% \textcurrency c Insert third current address
+Entonces, los dos son fáciles de implementar en las compus cuánticas.
 
-% Deceased author note
-% \dag Deceased
+\section{Ver cómo suben los datos otros artículos similares de Plos One}
 
-% Group/Consortium Author Note
-% \textpilcrow Membership list can be found in the Acknowledgments section.
+Por lo que encontré, muchos de los artículos no tenían datos abiertos al público.
+De los pocos que sí, casi todos subían un link a un repositorio de github que  contiene el código que hayan usado y quizá documentos con los resultados de dicho código.
 
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* carlospgmat03@gmail.com
+\section{Revisar la motivación que ponen otras simulaciones cuánticas}
 
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-% \cpnote{Revisar}
-Pauli channels are fundamental in the context of quantum computing as they
-model the simplest kind of noise in quantum devices.  We propose a quantum
-algorithm for simulating
-Pauli channels 
-and extend it to encompass Pauli dynamical maps 
-(parametrized Pauli channels).
-A parametrized quantum circuit is employed to accommodate for dynamical maps. 
-We also establish the mathematical conditions for an
-$N$-qubit transformation to be achievable using a parametrized circuit where
-only one single-qubit operation depends on the parameter. 
-The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
-for the case of one qubit, and the fidelity of this implementation is reported. 
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-%\section*{Author summary}
+\section{Revisar si se puede generalizar a qdits o a qué se refieren con lo de más de 2 dimensiones?}
 
-\linenumbers
+\section{La definicion de circuito cuantico}
 
-% Use "Eq" instead of "Equation" for equation citations.
-% }}}
-\section{Introduction} % {{{
-
-Since their inception, quantum computers were proposed as powerful tools for
-the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
-quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
-practical~\cite{breuer2007theory} interest, there has been efforts towards the
-simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
-and specifically for quantum channels~\cite{Xin,Wei,Zanetti}.
-
-Such systems have been simulated because of their many applications, 
-such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
-studying dissipative processes~\cite{Barreiro}
-and modeling non-Markovian dynamics~\cite{Marsden}.
-Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
-and withing them, the simplest class of channels that produce decoherence are
-Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
-effective models for the noise affecting quantum devices~\cite{Flammia}.
-
-To represent the algorithms implemented in quantum computers, either to
-simulate a physical system or for some other purpose, one often uses a quantum
-circuit~\cite{chuangbook}.  In this work, we shall also work with parametrized
-quantum circuits, that is,  quantum circuits in which some of the operations
-depend on variable parameters~\cite{cerezo}.  These circuits play an important
-part in applications such as quantum machine learning~\cite{Benedetti} and
-describing general quantum transformations dependent on parameters. Substantial
-research has been devoted to enhancing the efficiency of these
-circuits~\cite{Rasmussen}.
-
-We start by providing the definition of quantum channels, the general framework
-used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
-Our first objective is to present a quantum algorithm capable of simulating
-Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
-for a Pauli Channel}, where we also demonstrate its implementation using IBM's
-quantum computers for the particular case of single-qubit Pauli channels. 
-Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
-dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
-channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
-study parametrized quantum channels, aiming to adapt the algorithm developed
-for channels to dynamical maps.  Furthermore, we contribute to the body of work
-related to parametrized quantum circuits by establishing a theorem,
-which  sets the mathematical conditions for the transformations
-that can be done using a parametrized circuit with the condition that only a
-controlled single-qubit
-operation in the circuit may depend on the parameter.  Finally, in
-section \ref{sec: 1PR circuit for a Pauli map}, we conclude about the Pauli
-dynamical maps that fulfill the conditions of theorem \ref{theorem2}.
-
-% }}}
-\section{Pauli channels and dynamical maps}  \label{sec: Pauli Channels} % {{{
-
-% Intro  {{{
-
-In this section  we introduce the concept of quantum channels, focusing on a
-specific type called Pauli channels.  Furthermore, we define Pauli dynamical
-maps, which are curves of Pauli channels parametrized by a variable.
-% }}}
-\subsection{Quantum channels} \label{subsec: Quantum Channels} % {{{
-
-In quantum mechanics, a closed system's state is represented by a vector in a
-Hilbert space $\mathcal{H}$.  The state's evolution is unitary and given by
-Schrodinger's equation~\cite{Rieffel}.  However, in real-world situations,
-quantum systems are usually open, which means that they interact with their
-environment~\cite{breuer2007theory}.  For instance, the system's state may become
-entangled with the environment, leading to a loss of information about the
-system's state over time.
-
-To describe open systems, instead of state vectors, we use matrices $\rho$ that
-act on $\mathcal{H}$.  These matrices are called density matrices, and they
-include information about the system's interaction with its environment.  For a
-density matrix $\rho$ to be physically valid, it must satisfy two conditions:
-$\tr(\rho) = 1$ and it must be positive semi-definite, which is denoted as
-$\rho \geq 0$~\cite{chuangbook}.
-
-Knowing this, we can now define quantum channels.  Quantum channels are
-operators $\mathcal{E}$ that can describe the evolution of open quantum
-systems, such that $\rho \rightarrow \mathcal{E}(\rho)$.  Quantum channels are
-the most general linear operations that a quantum system can undergo
-independently of its past~\cite{zimansbook,cirac}.  These channels are
-constructed based on three fundamental properties: linearity, trace
-preservation, and complete positivity.
-
-Linearity ensures that a quantum channel $\mathcal{E}$ maps any ensemble of
-density matrices into the corresponding ensemble of their evolution.  The trace
-preserving property is given by $\tr (\mathcal{E}[\rho]) = \tr (\rho) = 1$ and
-guarantees that the quantum channel does not change the condition that
-$\tr(\rho) = 1$.  Finally, the channel should also preserve the condition $\rho
-\geq 0$, and a map that does this is called a positive map.  However,
-positivity of $\mathcal{E}$ is not enough, and we actually require the more
-restrictive condition of complete positivity.  Complete positivity means that
-$\mathcal{E} \otimes \mathbb{I}_n$ is positive for any positive integer $n$
-(where $\mathbb{I}_n$ is the $n\times n$ identity matrix).  This ensures that
-even if the principal system is entangled with another system, applying
-$\mathcal{E}$ to the principal system while doing nothing to the other one
-still results in  a positive semidefinite state for the principal
-system~\cite{chuangbook}.
-
-Given a quantum channel $\mathcal{E}$, the condition of trace preservation is
-straightforward to verify but complete positivity is not as simple.  To test
-complete positivity of a quantum channel, Jamiołkowski and
-Choi~\cite{choi,jamil} developed a simple algorithm that exploits the
-isomorphism between a channel $\mathcal{E}$ and the state $\mathcal{D} =
-(\mathbb{I} \otimes \mathcal{E}) [|\Omega \rangle \langle  \Omega|]$, where
-$|\Omega\rangle = 1/\text{dim}(\mathcal{H}) \sum_{i}^{\text{dim}(\mathcal{H})}
-|i \rangle |i \rangle$ is a maximally entangled state between the original
-system and an ancilla.  Remarkably, the map $\mathcal{E}$ is completely
-positive if and only if $\mathcal{D}$ (also known as the Choi or dynamical
-matrix of $\mathcal{E}$) is positive semidefinite.
-
-% }}}
-\subsection{Pauli channels}  \label{subsec: Pauli Channels} % {{{
-
-We have discussed the main features of quantum channels and 
-now we turn our attention to a specific 
-type of channels for $N$-qubit systems called Pauli channels.
-First we will define these channels for single-qubit systems,
-whose most general density matrix can be written as~\cite{chuangbook}:
-\begin{equation}
-\label{eq: Density Matrix}
-\rho = \dfrac{1}{2} \sum_{\alpha=0}^{3} r_{\alpha} \sigma_{\alpha},
-\end{equation}
-with $\sigma_0 = \mathbb{I}$, and $\sigma_{1,2,3}$ the usual Pauli matrices.
-The condition $\tr(\rho) = 1$ requires that $r_0 = 1$ while $\rho \geq 0$ 
-implies that the remaining $r_{1,2,3}$ form
-a vector $\vec{r}= (r_1,r_2,r_3)$ inside a unit sphere known as the Bloch sphere~\cite{Marinescu}.
-That is, every possible density matrix for a one-qubit
-system is uniquely associated with a point in a unit sphere.
-
-Given a one-qubit system described by $\rho$, 
-a Pauli channel is defined as an operation that with probability $k_{\gamma}$
-applies the Pauli matrix $\sigma_{\gamma}$ to
-the system, for $\gamma = 0,1,2,3$~\cite{geometry}.
-Mathematically, the Pauli channel is written in the following way:
-\begin{eqnarray}
-\label{eq: Pauli channel 1 qbit}
-\mathcal{E}(\rho) = \sum_{\gamma=0}^3 k_{\gamma} \sigma_{\gamma} \rho \sigma_{\gamma},
-\end{eqnarray} 
-where the probabilities $k_{\gamma}$ of applying $\sigma_{\gamma}$
-are non-negative real numbers such that 
-$\sum_{\gamma} k_{\gamma} = 1$ (these conditions also ensure that the channel is 
-trace preserving and completely positive).
-
-Pauli channels are some of the 
-most fundamental noise models in quantum information science~\cite{Terhal}. 
-Some notable examples of Pauli channels are the following:
-\begin{itemize}
-\item \textbf{Bit Flip Channel:} This is a channel that with probability $1-p$ leaves the qubit as it is 
-and with probability $p$ applies the $\sigma_1$ matrix 
-(which flips the basis states $|0\rangle$ and $|1\rangle$ of the qubit), and
-so it is given by:
-\begin{align*}
-\mathcal{E}(\rho) = (1-p) \rho + p \sigma_1 \rho \sigma_1.
-\end{align*}
-Analogous channels exist using $\sigma_3$ (called the bit flip channel,
-which has a probability $p$ of adding a relative phase $\pi$ to the state) or 
-using $\sigma_2$ (called the phase flip channel, 
-which has a probability $p$ of 
-flipping the base states and also add a relative phase $\pi$).
-\item \textbf{Depolarizing channel:} 
-This channel has a probability $1-p$
-of doing nothing to the qubit and a probability $p$ of converting it into the maximally mixed state $\dfrac{1}{2} \mathbb{I}$
-and it can be written as:
-\begin{equation}
-\mathcal{E}(\rho) = (1-p)\rho + p \dfrac{1}{2} \mathbb{I} = \left(1 - \dfrac{3p}{4} \right) \sigma + \dfrac{p}{4} \sigma_1 \rho \sigma_1 + \dfrac{p}{4} \sigma_2 \rho \sigma_2+ \dfrac{p}{4} \sigma_3 \rho \sigma_3.
-\end{equation} 
-\end{itemize}
-
-We can also see how an arbitrary Pauli channel acts on an arbitrary  
-density matrix.
-To do it, we substitute \eref{eq: Density Matrix} 
-in \eref{eq: Pauli channel 1 qbit}:
-\begin{equation}
-\mathcal{E}(\rho) = \dfrac{1}{2}\sum_{\gamma,\alpha=0}^3 k_{\gamma} r_{\alpha} \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}.
-\end{equation}
-This can be simplified by using the following property of Pauli matrices:
-\begin{equation}
-\label{eq: propiedad-pauli}
-\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A_{\alpha,\gamma} = \begin{pmatrix}
-1 & 1 & 1 & 1\\
-1 & 1 & -1 &-1 \\
-1 & -1 & 1 & -1 \\
-1 & -1 & -1 & 1
-\end{pmatrix},
-\end{equation}
-which leads to
-\begin{equation}
-\label{eq: rho-transformada}
-\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
-\end{equation}
-\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix}
-but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
-This gives us another way of understanding Pauli channels
-as operations that take each component $r_{\alpha}$
-of the density matrix and multiplies them
-by $\sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}$, 
-that is:
-\begin{equation}
-\label{eq: multipliers}
-r_{\alpha}  \xrightarrow[\text{Channel}]{\text{Pauli}}  \tau_{\alpha} r_{\alpha} ,\;\; \tau_{\alpha} := \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma}.
-\end{equation}
-Notice that $\tau_0 = 1$, which is a consequence of $\sum_{\gamma}k_{\gamma}=1$
-and ensures that after the channel, the resulting density matrix still has trace one. 
-Furthermore, reverting the definition of $\tau_{\alpha}$ by using that $A^{-1} = \dfrac{1}{4} A$, 
-we get that $k_{\gamma} = \dfrac{1}{4} \sum_{\alpha} A_{\alpha,\gamma} \tau_{\alpha}$.
-Then, using that $k_{\gamma} \geq 0$
-we get the following conditions on the multipliers $\tau_{\alpha}$:
-\begin{eqnarray}
-\label{eq: conditions-tetrahedron}
-&1+\tau_i -\tau_j - \tau_k \geq 0,  \;\;\; \text{for $i,j,k$ different numbers in $\{1,2,3\}$}, \\
-&1+\tau_1 + \tau_2 + \tau_3 \geq 0.
-\end{eqnarray}
-
-These conditions imply that $(\tau_1,\tau_2,\tau_3)$
-has to be inside a tetrahedron with
-vertices $(1,1,1), (1,-1,-1), (-1,1,-1)$ and $(-1,-1,1)$. 
-Therefore, the $\tau_{1,2,3}$ are numbers between 
-$-1$ and $1$, which means that the components
-$r_{\alpha}$ of the density matrix are always 
-attenuated and possibly sign flipped.
-
-Having defined the one qubit case,  we can now generalize to $N$ qubits.
-In order to do it, we need to introduce the so-called \textit{Pauli strings}, defined as
-\begin{eqnarray}
-\label{eq: Pauli string}
-\sigma_{\vec{\alpha}} = \sigma_{\alpha_1} \otimes \sigma_{\alpha_2}\otimes \cdots \otimes \sigma_{\alpha_N},
-\end{eqnarray}
-where $\vec{\alpha}$ denotes a multi-index $(\alpha_1, \cdots, \alpha_N)$
- and $\alpha_i \in \{0,1,2,3\}$. 
-These operators form an orthogonal basis in the space of operators acting on $N$ qubits. 
- Similarly to the single-qubit case, the density matrix $\rho$ 
-of a system of $N$ qubits can be written using Pauli strings as:
-\begin{equation}
-\label{eq:  Density matrix Nqbit}
-\rho = \dfrac{1}{2^N} \sum_{\vec{\alpha}} r_{\vec{\alpha}} \sigma_{\vec{\alpha}}.
-\end{equation}
-Then, just as before, we define a Pauli channel as a transformation that applies 
-the operator $\sigma_{\vec{\gamma}}$ to $\rho$ with probability $k_{\vec{\gamma}}$
-and is therefore described mathematically by:
-\begin{equation}
-\label{eq: pauli channel N-qubit}
-\mathcal{E}(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}} \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
-\end{equation}
-where just as before, $k_{\vec{\gamma}}$ are non-negative real numbers such 
-that $\sum_{\vec{\gamma}} k_{\vec{\gamma}}=1$.
-
-As in the one qubit case, Pauli channels for $N$ qubits 
-attenuate the components $r_{\vec{\alpha}}$ of the density matrix.
-This can be seen by substituting \eref{eq:  Density matrix Nqbit} in \eref{eq: pauli channel N-qubit}
-and using the property of \eref{eq: propiedad-pauli}:
-\begin{align*}
-\mathcal{E}(\rho) &= \dfrac{1}{2^N} \sum_{\vec{\gamma},\vec{\alpha}} k_{\vec{\gamma}} r_{\vec{\alpha}} \sigma_{\vec{\gamma}} \sigma_{\vec{\alpha}} \sigma_{\vec{\gamma}} \\
-& = \dfrac{1}{2^N} \sum_{\vec{\alpha}} \left( \sum_{\vec{\gamma}} {(A^{\otimes^N})}_{\vec{\alpha},\vec{\gamma}} \; k_{\vec{\gamma}} \right) r_{\vec{\alpha}} \sigma_{\vec{\alpha}},
-\end{align*}
-which means that applying the Pauli channel multiplies the 
-components $r_{\vec{\alpha}}$ by $\tau_{\vec{\alpha}} := \sum_{\vec{\gamma}} {(A^{\otimes^N})}_{\vec{\alpha},\vec{\gamma}} k_{\vec{\gamma}}$.
-% }}}
-\subsection{Pauli dynamical maps} % {{{
-\label{subsec: Pauli Dynamical Maps}
-
-As seen in the last section, Pauli channels and in 
-general quantum channels are discrete maps
-that transform a density matrix $\rho$ into $\mathcal{E}(\rho)$.
-However, we could also define a continuous set of 
-channels $\varepsilon_p$ with $p$ a real parameter.
-
-For the special case of Pauli channels, we define 
-a Pauli dynamical map as a continuous parametrized 
-curve drawn inside the set of Pauli channels and starting at the identity channel. 
-Therefore, a Pauli dynamical map can be written as
-\begin{eqnarray}
-\label{eq: Pauli dynamical map}
-\mathcal{E}_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
-\end{eqnarray}
-where $p$ is a parameter in an interval $[a,b]$ 
-and $\mathcal{E}_p$ is a Pauli channel for every $p$, 
-with $\mathcal{E}_a$ being the identity channel.
-
-% }}}
-% }}}
-\section{Circuit for a Pauli channel} % {{{
-\label{sec: Circuit for a Pauli Channel}
-% Intro {{{
-
-In this section we propose a quantum circuit that simulates $N$-qubit Pauli
-channels.  Moreover, we implement the circuit for $N=1$ on a quantum computer
-and analyze the results using the diamond norm.
-We find that close to the depolarizing channel, the general circuit simulator 
-can implement such channels with the highest fidelity. 
-% produce the highest 
-% }}} 
-\subsection{Description of the circuit for a Pauli channel} %{{{
-\label{subsec: Description of the circuit}
-
-To design the circuit that implements \eref{eq: pauli channel N-qubit}, we construct a state that 
-includes the probabilities $k_{\gamma}$ on the ancilla qubits and subsequently
-apply controlled Pauli operations on the main qubits.  The circuit that does
-this is presented in \fref{Fig1}.
-
-\begin{figure}[!h] % {{{
-\centering
-%\includegraphics{images/circuito_general.pdf}
-\caption{{\bf Circuit for an $N$-qubit
-Pauli channel.}
-The circuit creates the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}}|\vec{\gamma}\rangle$ 
-on the $2N$ ancilla qubits denoted by $\tilde{q}$.}
-\label{Fig1}
-\end{figure} % }}}
-
-The first part of the circuit involves the creation of the state
-\begin{eqnarray}
-\label{eq: state}
-\text{Ancilla state =} 
-\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma} \rangle
-\end{eqnarray}
-on the ancilla qubits, where $b_{\vec{\gamma}}$ are numbers such that $
-{|b_{\vec{\gamma}}|}^2 = k_{\vec{\gamma}}$ and
-the $2N$-qubit state $|\vec{\gamma}\rangle$ is defined as $|\gamma_1\rangle
-\cdots |\gamma_N\rangle$.
-When measured in the computational basis, the state given in \eref{eq: state}
-collapses to $|\vec{\gamma}\rangle$ with a 
-probability ${|b_{\vec{\gamma}}|}^2 = k_{\vec\gamma}$. 
-The circuit in \fref{Fig1} uses this fact
-to apply $\sigma_{\vec{\gamma}}$ on the main qubits
-with a probability $k_{\vec\gamma}$ by using controlled operations 
-conditioned on the state of the system being $|\vec{\gamma}\rangle$,
-just as the Pauli channel is supposed to do.
-
-%}}}
-\subsection{Simulation for one-qubit Pauli channels} % {{{
-\label{subsec: Simulation for one-qubit Pauli channels}
-
-For the particular case of a Pauli channel on one qubit, the circuit that
-simulates it can be constructed as in \fref{Fig2},
-which is a special case of \fref{Fig1}
-but with all details  explicitly shown.
-In said figure, the ancilla state
-of \eref{eq: state} can be taken to be
-$\sqrt{k_{00}} |00\rangle + \sqrt{k_{01}} |01\rangle + \sqrt{k_{10}} 
-|10\rangle + \sqrt{k_{11}}|11\rangle$
-and it is created on the ancilla qubits with the help of three rotations of angles
-defined by the following equations:
-\begin{align}
-\label{eq:angle}
-\cos\left(\dfrac{\theta_0}{2} \right) &= \sqrt{k_{00} + k_{01}},\nonumber \\
-\tan\left( \dfrac{\theta_1 + \theta_2}{2} \right) &= \sqrt{k_{01}/k_{00}},  \\
-\tan\left( \dfrac{\theta_2 - \theta_1}{2} \right) &= \sqrt{k_{11}/k_{10}}.  \nonumber
-\end{align}
-
-\begin{figure}[!h] % {{{
-\centering
-%\includegraphics{images/circuito_unqubit.pdf}
-\caption{
-{\bf One-qubit Pauli channel circuit.} Circuit for a one-qubit Pauli channel,
-which is a particular case of \fref{Fig1}.  Here we have two
-ancilla qubits and we use three rotations
-of angles given by \eref{eq:angle} to create the Ancilla State of
-of \eref{eq: state} for the two ancilla qubits.
-}
-\label{Fig2} 
-\end{figure} % }}}
-
-% We took a sample of one-qubit Pauli channels and
-% used the ibmq-lima quantum computer that IBM has available~\cite{Qiskit}
-% to simulate them. For each of these channels, we used quantum process
-% tomography~\cite{Qiskit, Chuang:1996} to obtain the 
-% operator $\xi_I$ corresponding to the implementation of the
-% circuit.  Then, we compared this operator with the ideal 
-% channel $\xi_T$  we
-% wanted to implement.
-
-We took a sample of one-qubit Pauli channels
-and evaluated their implementation on IBM's
-ibmq-lima quantum computer~\cite{Qiskit},
-as shown in \fref{Fig3}. 
-For each of the channels sampled, we used 
-quantum process tomography~\cite{Qiskit, Chuang:1996} to obtain the 
-operator $\xi_I$ corresponding to the implementation of the
-circuit in the quantum computer. 
-Then, we compared $\xi_I$ with the theoretical 
-operator $\xi_T$ of the Pauli channel we wanted to implement.
-To see how close the operators $\xi_I$ and 
-$\xi_T$ are, we shall use the
-diamond distance~\cite{wildebook}, which is defined by
-\begin{equation}
-||\xi_I - \xi_T ||_{\diamond}  = \max_{\rho} || (\xi_I \otimes I) \rho - (\xi_T \otimes I) \rho ||_1,
-\end{equation}
-with $I$ the identity map,
-$|| \cdot ||_1$ the trace norm and the maximization
-done over all density matrices $\rho$.
-The calculation of this norm is done using the semi-definite program from reference \cite{Watrous}.
-When the two channels are the same,
-the diamond distance has a value of $0$, while in the case that the channels
-are completely distinguishable, the distance reaches its maximum value of $2$~\cite{Benenti}.
-For the analysis done in \fref{Fig3}, we define a sort of ``diamond fidelity'' as: 
-\begin{equation}
-f = 1 - \dfrac{1}{2} ||\varepsilon_I - \varepsilon_T ||_{\diamond},
-\label{eq:diamond-fid}
-\end{equation}
-which ranges from $0$, when the channels have a maximum distance, to  $1$,
-when they are exactly equal.
-
-\begin{figure}[!h] % {{{
-\centering
-\caption{{\bf Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
-for a sample of Pauli channels in the tetrahedron.}  Notice that channels close
-to the center of the tetrahedron have high fidelities, while those close to the
-borders do not.  Moreover, we show the results for cuts of the tetrahedron at
-different values of $\tau_3$.}
-\label{Fig3}
-\end{figure} % }}}
-
-Finally, using the representation of Pauli channels in a tetrahedron as in
-\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
-fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
-see that channels close to the completely depolarizing channel (that is close
-to the center of the tetrahedron) have a high $f$, while those close to unitary
-channels have much lower $f$.  This is reasonable because quantum computers are
-prone to errors that depolarize qubits, which isn't very problematic when
-trying to simulate depolarization but it is when simulating unitary processes.
-Moreover, the algorithm of \fref{Fig2} is not optimal for
-unitary channels (that is, the channels corresponding to the vertices of the
-tetrahedron).  These straightforward channels could be accomplished more
-efficiently by simply applying the corresponding Pauli operation directly.
-Nevertheless, due to its general design to accommodate any Pauli channel, the
-algorithm employs numerous quantum gates even in such scenarios.
-
-% }}}
-% }}}
-\section{One parameter circuits} % {{{
-\label{sec: 1PR Circuits}
-
-Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
-of \fref{Fig1}. However, there is one difference: 
-the state to be created on the ancilla qubits now 
-depends on a parameter $p$, and it is represented by the expression:
-\begin{eqnarray}
-\label{eq: parametrized state}
-\sum_{\vec{\gamma}} b_{\vec{\gamma}}(p) |\vec{\gamma}\rangle.
-\end{eqnarray}
-Thus, we temporarily shift our focus from Pauli
-channels and dynamical maps to the general problem of 
-creating a circuit to generate a curve of
-states like the one described in \eref{eq: parametrized state}.
-
-In general, producing this curve of states for $N$ qubits will require
-many rotations parametrized by $p$,
-such as the three rotations used for the ancilla
-qubits in \fref{Fig2}.
-However, it would be preferable to achieve the same effect using only one parametrized rotation. 
-This would allow us to interpret said rotation 
-as a knob that smoothly traverses the curve of states.
-Consequently, we are faced with the question of which curves of states, 
-such as the one described in \eref{eq: parametrized state}, 
-can be produced using just a single parametrized rotation. 
-To clarify this, we provide the following definition 
-for a circuit with one parametrized rotation.
-
-\begin{definition}{\textbf{1-Parameter Rotation Circuit:}}
-A 1-Parameter Rotation (1PR) circuit is a parametrized quantum
-circuit that includes only one gate dependent on a parameter $p$.
-Moreover, the parametrized gate is a one-qubit rotation about any axis,
-whether controlled or not.
-\end{definition}
-
-Based on this definition, we aim to determine which curves of 
-states can be generated using 1PR circuits. 
-To accomplish this, we begin by proving that all 1PR circuits have 
-the form depicted in \fref{Fig4},
-where the parametrized rotation is around $\sigma_3$ and
-is applied to the last qubit.
-
-\begin{figure}[!h] % {{{
-\centering
-%\includegraphics{images/OPR-circuit.pdf}
-\caption{\textbf{General form of a 1PR circuit}.
-Any 1PR circuit can be transformed into this form,
-where the rotation on the last qubit
-can be controlled or not by any of the other qubits.
-$A$ and $B$
-are $N$-qubit gates that do not depend on the parameter $p$ and
-$s= s(p)$ is a function of the parameter.
-}
-\label{Fig4}
-\end{figure} % }}}
-
-\begin{theorem}
-An $N-$qubit 1PR circuit can always be transformed 
-into the form shown in \fref{Fig4}.
-\end{theorem}
-\textbf{Proof:} 
-First, we observe that according to the
-definition, a 1PR circuit always consists of an operation $B$ followed 
-by the parametrized rotation and then another operation $A$, 
-where $A$ and $B$ are not parametrized.
-
-Next, we note that it is not necessary to consider rotations about an arbitrary axis,
-as a rotation about any axis $\hat{n}$ parameterized by $p$
-can be transformed into a rotation about $\sigma_3$ without introducing 
-gates that depend on $p$. To see this, consider the rotation $R_{\hat{n}}(2s)$, where $2s$ 
-is a function of $p$ (the factor of 2 is for convenience later on) 
-and $\hat{n} = (n_1,n_2,n_3)$ represents the rotation axis. 
-We can express $\hat{n}$ as $(\sin \theta \cos \phi, \sin \theta \sin \phi, \cos \theta)$, 
-where $\theta$ and $\phi$ are fixed angles dependent on $\hat{n}$. 
-The rotation can then be rewritten as follows:
-\begin{eqnarray}
-R_{\hat{n}}(2s) = R_{\sigma_3}(\phi) R_{\sigma_2}(\theta) R_{\sigma_3}(2s) R_{\sigma_2}(-\theta) R_{\sigma_3}(-\phi).
-\end{eqnarray}
-Since the angles $\theta$ and $\phi$ do not depend on the parameter $p$,
-any 1PR circuit can be transformed into a circuit where the parametrized
- rotation is around $\sigma_3$ instead of an arbitrary axis. 
-Moreover, without loss of generality, we can choose the last qubit as the
-target qubit for the rotation, since if it weren't, we could use
-swap gates to move the rotation
-to the first qubit without adding gates
-that depend on $p$.
-
-Therefore, a 1PR circuit can be transformed such
-that the rotation is around $\sigma_3$ and is applied to the last qubit 
-(possibly controlled by other qubits), 
-resulting in the form depicted in \fref{Fig4}. 
-$\blacksquare$ \\
-$\;$\\
-
-With the aid of this theorem, we can now determine the curves
-of states of $N$ qubits that can be generated using a 1PR circuit. 
-This result is stated in the following theorem.
-
-\begin{theorem}
-\label{theorem2}
-Consider a 1PR circuit of $N$ qubits parametrized by $p$
-and denote by $U$ the operator it implements on this system. 
-Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
-we have that:
-\begin{align*}
-U|j\rangle = e^{is(p)} |a^j\rangle + e^{-is(p)} |b^j\rangle + |c^j\rangle
-\end{align*}
-with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
-c^j|c^j \rangle = 1$.
-\end{theorem}
-\textbf{Proof:} 
-We can conclude from theorem 1 that $U=ARB$,
-where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
-applied to the last qubit and controlled by some of the other ones.
-
-First, applying $B$ to $|j\rangle$ results in $B|j\rangle = B_{0,j} |0\rangle + B_{1,j} |1 \rangle + \cdots + B_{2^n-1,j}|2^n-1\rangle$,
-with $B_{i,j}$ the entries of matrix $B$.
-This can be rewritten by separating last qubit from the other $N-1$:
-\begin{equation}
-B|j\rangle = \sum_{k=0}^{2^{N-1}-1} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right).
-\end{equation}
-After the operator $B$, the circuit applies the  controlled rotation $R$.
-To simplify the analysis, we separate the states of
-the first $N-1$ qubits into those that fulfill the control conditions of the rotation
-(which we denote as the set $\mathcal{C}$)
-and those that do not, and write it as
-\begin{align}
-B|j\rangle = 
-   \sum_{k \in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle 
-                                     + B_{2k+1,j} |k \rangle |1\rangle  \right) 
-   + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  
-                                      + B_{2k+1,j} |k \rangle |1\rangle  \right).
-\end{align}
-
-Then, the rotation $R$ will only affect the states on the first sum (since they fulfill the control conditions)
-and not the others. Therefore,  
-remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is(p)}$ to $|0\rangle$
-and a phase $e^{is(p)}$ to $|1\rangle$, we have that,
-% \begin{small}
-% \begin{eqnarray}
-% &e^{-is} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1 \rangle 
-% + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle |0\rangle + B_{2k+1} |k\rangle |j \rangle \right)\\
-% & \qquad = e^{-is} \vec{b'}_j + e^{is} \vec{a'}_j + \vec{c'}_j,
-% \end{eqnarray}
-% \end{small}
-% test
-\begin{align}
-RB|j\rangle& = e^{-is(p)} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is(p)} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
-+ \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
-& = e^{-is(p)} |\tilde{b}^{j}\rangle + e^{is(p)} |\tilde{a}^j\rangle + |\tilde{c}^j\rangle,
-\end{align}
-where we defined
-\begin{align*}
-|\tilde{a}^j \rangle &= \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle,\\
-|\tilde{b}^j\rangle &= \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle,\\
-|\tilde{c}^j\rangle &= \sum_{k \not\in \mathcal{C}}\left( B_{2k,j} |k\rangle|0\rangle+ B_{2k+1,j} |k \rangle |1\rangle  \right).
-\end{align*}
-These states are clearly orthogonal because they are each linear combinations of different 
-orthogonal states of the computational basis. 
-Moreover, they satisfy  $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle c^j| c^j\rangle = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
-which is unitary.
-
-Finally, after having applied the rotation, the circuit applies gate $A$, 
-so that the result is given by:
-\begin{eqnarray}
-U|j\rangle = ARB|j\rangle = e^{-is(p)} A |\tilde{a}^j\rangle + e^{is(p)} A |\tilde{b}^j\rangle + A |\tilde{c}^j\rangle = e^{-is(p)} |a^j\rangle + e^{is(p)} |b^j\rangle + |c^j\rangle,
-\end{eqnarray}
-where $|a^j\rangle = A |\tilde{a}^j\rangle, |b^j\rangle = A |\tilde{b}^j\rangle, |c^j\rangle = A |\tilde{c}^j\rangle$ are still orthogonal
-states that satisfy $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$ because $A$ is unitary. $\blacksquare$  \\
- $\;$ \\
-
-This theorem implies that when starting from the state $|0\rangle$ 
-or any other initial state, the only possible curves of states that can be 
-created using a 1PR circuit are of the following form:
-\begin{equation}
-|\eta(p)\rangle = |c\rangle + e^{is(p)}|a\rangle + e^{-is(p)} |b\rangle,
-\label{eq:curve-states}
-\end{equation}
-with conditions defined by the equations: 
-\begin{equation}
-\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1,  \quad
-\langle a |b\rangle =
-\langle a |c\rangle =
-\langle b |c\rangle = 0.
-\label{eq:conditions-vecs}
-\end{equation}
-
-Moreover, it is possible to construct a 1PR circuit to generate any given curve of 
-states described by \eref{eq:curve-states}. 
-One approach to achieve this is by utilizing the circuit 
-depicted in \fref{Fig4}, 
-with the parametrized rotation $R$ applied to the last qubit controlled by all the 
-other qubits. The operators $A$ and $B$ can be defined as follows:
-\begin{align*}
-&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \\
-&A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
-\end{align*}
-The remaining part of the operators $A$ and $B$ can be defined
-in any arbitrary manner as long as they are unitary.
-By starting from the initial state $|0\rangle$ and 
-applying the circuit shown in \fref{Fig4}, straightforward calculations 
-lead us to obtain the resulting curve of states described in \eref{eq:curve-states}.
-
-To see it, we can rewrite the expression of $B|0\rangle$ by 
-separating the first $N-1$ qubits from the last one:
-$$B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.$$
-Since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$. As a result, we obtain:
-
-$$
-RB|0\rangle =\sqrt{\langle a | a \rangle} e^{is(p)} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} e^{-is(p)} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.
-$$
-
-Finally, applying the defined operator $A$ to this state yields the desired result.
-
-\section{1PR circuit for a Pauli map} % {{{
-\label{sec: 1PR circuit for a Pauli map}
-
-We can now use the previous results to conclude directly which Pauli dynamical maps
-can be implemented with a 1PR circuit.
-For this, the curve of states of \eref{eq: parametrized state} 
-has to be constructed with only one parametrized rotation,
-so it has to satisfy the conditions of theorem \ref{theorem2}.
-Therefore, this implies that the map
-\begin{eqnarray}
-\varepsilon_p(\rho) = \sum_{\vec{\gamma}} k_{\vec{\gamma}}(p) \sigma_{\vec{\gamma}} \rho \sigma_{\vec{\gamma}},
-\end{eqnarray}
-can be implemented  if there are numbers $\beta_{\vec{\gamma}}(p)$ such that $|\beta_{\vec{\gamma}}(p)|^2 = k_{\vec{\gamma}}(p)$ and
-\begin{eqnarray}
-\label{eq:vec}
-\sum_{\vec{\gamma}} \beta_{\vec{\gamma}}(p) |\vec{\gamma}\rangle = |c\rangle +  e^{is(p)} |a\rangle + e^{-is(p)}|b\rangle,
-\end{eqnarray}
-where $|a\rangle,|b\rangle,|c\rangle$ fulfill
-the conditions of \eref{eq:conditions-vecs}.
-
-For the particular case of one qubit, we can show some examples of Pauli
-dynamical maps implementable with a 1PR circuit, which are plotted in
-\fref{Fig5}. 
-The examples we show include some of the most common maps: the bit flip, phase flip, bit-phase flip and depolarizing.
-However, we also include the parabolic dynamical map,
-defined in \eref{eq:parab} and shown in \fref{Fig5}.
-This map traces a parabola inside the tetrahedron connecting two of its vertices
-and it describes a frontier in the tetrahedron between Pauli channels
-that are reachable by Lindbladian dynamics and those that are not~\cite{Davalos}.
-
-\begin{figure}[!h] % {{{
-%\captionsetup[subfigure]{justification=centering}
-\centering
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-%  \includegraphics[width=.9\linewidth]{images/curvas.png}
-%   \caption{}
-%  \label{Fig51}
-%\end{subfigure}%
-%\begin{subfigure}{.45\textwidth}
-%  \centering
-%  \includegraphics[width=.9\linewidth]{images/curvas-azar.png}
-%  \caption{}
-%  \label{Fig5-2}
-%\end{subfigure}
-\caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
-The curves painted in these tetrahedrons
-represent Pauli dynamical maps that can be implemented with 1PR circuits.
-(a) shows the dynamical maps mentioned in the main 
-text, which are: depolarizing (purple), bit flip (blue),
-phase flip (green), bit-phase flip (red)
-and parabolic (orange).
-(b) shows dynamical maps selected at random that can be implemented with 1PR 
-circuits.}
-\label{Fig5}
-\end{figure} % }}}
-
-\begin{itemize}
-\item \textbf{Depolarizing:} This dynamical map is given by
-\begin{align*}
-\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
-\end{align*}
-with $p \in [0,1]$. 
-Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
-qubits is such that ${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 =
-{|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.  Then, taking the $\beta_j$ to be
-real, the curve of states can be 
-\begin{align*}
-|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
-\end{align*}
-This state can be rewritten as:
-\begin{align*}
-|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle 
-      - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
-& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle 
-      + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
-\end{align*}
-with $\sin s = \sqrt{3p/4}$.
-We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
-1PR circuit.
-
-\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
-\begin{eqnarray}
-\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3,
-\label{eq:parab}
-\end{eqnarray}
-with $p \in [-1,1]$. 
-If we take the $\beta_j$ to be real,
-the curve of states needed on the ancilla qubits can be:
-\begin{eqnarray}
-|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
-\end{eqnarray}
-This can be rewritten as
-\begin{align*}
-|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
-& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
-\end{align*}
-with $\sin s = p$, so that
-this map fulfills the conditions of  \eref{eq:conditions-vecs}.
-
-\item \textbf{Bit flip map:} 
-This dynamical map is defined as
-\begin{align*}
-\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
-\end{align*}
-for $p \in [0,1]$. 
-In particular, if we take the $\beta_j$ to be real,
-we need to create the curve of states:
-\begin{align*}
-|\beta(p)\rangle = \sqrt{1-p} |00\rangle +\sqrt{p} |01\rangle.
-\end{align*}
-This can be rewritten as
-\begin{align*}
-|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |00\rangle - \dfrac{i}{2} |01\rangle \right) + e^{-is} \left( \frac{1}{2} |00\rangle + \frac{i}{2} |01\rangle \right),
-\end{align*}
-with $\sin s= \sqrt{p}$.
-Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
-and it can be created with a 1PR circuit.
-Note that in this case we actually only need one ancilla qubit
-since the state $|\beta(p)\rangle$ is only two dimensional.
-
-The exact same thing can be done
-for the phase flip and bit phase flip dynamical maps by
-changing $\sigma_1$ to
-$\sigma_3$ and $\sigma_2$ respectively.
-For example, the bit phase flip map was implemented in \cite{Andrea, Andrea_4qb} 
-using an optical arrangement, and  it was indeed done 
-by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate).
-
-\end{itemize}
-
-Furthermore, we can construct other examples of 
-Pauli dynamical maps such that they
-can be implemented with a 1PR circuit.
-To do it, we only need to choose the three states $|a\rangle$, $|b\rangle$, $|c\rangle$
-that satisfy the conditions of  \eref{eq:conditions-vecs}.
-For example, this can be done systematically for the case of curves of states of two qubits
-(that is, for Pauli dynamical maps of one qubit)
-with the following procedure:
-\begin{itemize}
-\item[1.] We first choose the norms $|a|$, $|b|$, $|c|$
-such that $\langle a| a\rangle + \langle b| b\rangle + \langle c| c\rangle = 1$. 
-This can be done by selecting two angles
-$\mu \in [0, \pi/2]$, $\nu \in [0,\pi/2]$ and defining:
-\begin{align*}
-|a| = \sin \nu \cos \mu, \; |b| = \sin \nu \sin \mu , \; |c| = \cos \nu.
-\end{align*}
-\item[2.] We define $|a'\rangle = |a| |0\rangle$, $|b'\rangle = |b| |1\rangle$, $|c'\rangle = |c| |2\rangle$.
-\item[3.] 
-Finally, we choose a unitary matrix $V$ with the condition that its first
-row is equal to $e^{i\theta} (|a|,|b|,|c|,0)$
-with $\theta$ a uniform random phase.
-That way, we can define $|a\rangle = V |a'\rangle$, $|b\rangle = V |b'\rangle$, $|c\rangle = V |c'\rangle$
-and since $V$ is unitary, these unprimed vectors will fulfill the conditions of
-\eref{eq:conditions-vecs}.
-Furthermore, the form of the first row ensures that the dynamical map begins at the identity,
-since it implies that when $s=0$, the 
-state created in \eref{eq:vec}
-is
-$|a\rangle + |b\rangle + |c\rangle = e^{i \theta} |0\rangle$,
-which  corresponds with applying the identity channel.
-
-Such a matrix $V$ can be randomly constructed by first finding three vectors 
-$\vec{w}_1 , \vec{w}_2, \vec{w}_3$ orthogonal to
-the first row using the Gram-Schmidt process.  Then selecting random complex
-numbers $r_1, r_2, r_3$ such that $|r_1|^2 + |r_2|^2 + |r_3|^2 = 1$ and defining
-the second row of $V$ to be $r_1 \vec{w}_1 + r_2 \vec{w}_2 + r_3 \vec{w}_3$.
-Once the first two rows are chosen, use Gram-Schmidt to find two vectors
-$\vec{v}_1, \vec{v}_2$ orthogonal to 
-them and similarly define the third row as $q_1 \vec{v}_1+ q_2 \vec{v}_2$
-with $|q_1|^2 + |q_2|^2$ and $q_1,q_2$
-selected at random. 
-Finally, there is only one choice for the fourth row so that it is 
-orthonormal to the first three
-and a random phase can be given to it.
-\end{itemize}
-
-Following this procedure for random
-angles and unitary matrices $V$, 
-we plot four Pauli dynamical maps  selected at random
-that can be implemented with a 1PR circuit in \fref{Fig5}.
-
-% }}}
-\section{Conclusion} % {{{
-
-In this work, we found a quantum algorithm for 
-simulating Pauli channels in $N$-qubit systems and
-generalized it to Pauli dynamical maps
-by using parametrized quantum circuits.
-Furthermore, we implemented single-qubit Pauli channels
-on one of IBM's quantum computers
-and obtained their fidelities. 
-Finally, when working with Pauli dynamical maps,
-we searched for a way of simplifying the parametrized circuit
-by requiring that only one single-qubit rotation depends on the parameter.
-In theorem \ref{theorem2} we found the general mathematical conditions for 
-this, applicable to any parametrized circuit.
-
-Therefore, this work presents yet another example of the current
-exploration into simulating open quantum
-systems in quantum computers,
-and we observe the big effect that the error of quantum computers have
-on these simulations.
-On the other hand, the result
-of theorem \ref{theorem2}
-shows what can be done with the condition of using only one
-parametrized rotation and
-can be applied to any quantum algorithm that requires parametrized circuits,
-such as those used for quantum machine learning.
-
-% }}}
-%\section{Supporting information} % {{{
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-% \paragraph*{S1 Fig.}
-% \label{S1_Fig}
-% {\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
-% 
-% \paragraph*{S2 Fig.}
-% \label{S2_Fig}
-% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-% 
-% \paragraph*{S1 File.}
-% \label{S1_File}
-% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-% 
-% \paragraph*{S1 Video.}
-% \label{S1_Video}
-% {\bf Lorem ipsum.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-% 
-% \paragraph*{S1 Appendix.}
-% \label{S1_Appendix}
-% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-% 
-% \paragraph*{S1 Table.}
-% \label{S1_Table}
-% {\bf Lorem ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-% }}}
-\section{Acknowledgments} % {{{
-Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.
-
-% Either type in your references using
-% \begin{thebibliography}{}
-% \bibitem{}
-% Text
-% \end{thebibliography}
-%
-% or
-%
-% Compile your BiBTeX database using our plos2015.bst
-% style file and paste the contents of your .bbl file
-% here. See http://journals.plos.org/plosone/s/latex for 
-% step-by-step instructions.
-
-\begin{thebibliography}{10}
-
-\bibitem{feynman1982simulating}
-Feynman RP.
-\newblock Simulating physics with computers.
-\newblock Int J Theor Phys. 1982;21(6/7):467--488.
-
-\bibitem{Zur91}
-Zurek WH.
-\newblock Decoherence and the transition from quantum to classical.
-\newblock Phys Today. 1991;44(10):36--44.
-
-\bibitem{RevModPhys.76.1267}
-Schlosshauer M.
-\newblock Decoherence, the measurement problem, and interpretations of quantum
-  mechanics.
-\newblock Rev Mod Phys. 2005;76(4):1267--1305.
-
-\bibitem{breuer2007theory}
-Breuer HP, Petruccione F.
-\newblock The theory of open quantum systems.
-\newblock 1st ed. New York: Oxford University Press; 2002.
-
-\bibitem{Garcia}
-García-Pérez G, Rossi M, Maniscalco S.
-\newblock IBM Q Experience as a versatile experimental testbed for simulating
-  open quantum systems.
-\newblock npj Quantum Inf. 2020;6(1):1--11.
-
-\bibitem{Wang}
-Wang H, Ashhab S, Nori F.
-\newblock Quantum algorithm for simulating the dynamics of an open quantum
-  system.
-\newblock Phys Rev A. 2011;83(6):062317.
-
-\bibitem{Weimer}
-Weimer H, Kshetrimayum A, Or\'us R.
-\newblock Simulation methods for open quantum many-body systems.
-\newblock Rev Mod Phys. 2021;93(1):015008.
-
-\bibitem{Xin}
-Xin T, Wei SJ, Pedernales JS, Solano E, Long GL.
-\newblock Quantum simulation of quantum channels in nuclear magnetic resonance.
-\newblock Phys Rev A. 2017;96(6):062303.
-
-\bibitem{Wei}
-Wei S, Xin T, Long G.
-\newblock Efficient universal quantum channel simulation in IBM's cloud quantum
-  computer.
-\newblock Sci China Phys Mech Astron. 2018;61(7):70311.
-
-\bibitem{Zanetti}
-Zanetti M, Pinto D, Basso M, Maziero J.
-\newblock Simulating noisy quantum channels via quantum state preparation
-  algorithms.
-\newblock Phys B At Mol Opt Phys. 2023;56(11):115501.
-
-\bibitem{Andrea}
-Far\'ias OJ, Aguilar GH, Vald\'es-Hern\'andez A, Ribeiro PHS, Davidovich L,
-  Walborn SP.
-\newblock Observation of the emergence of multipartite entanglement between a
-  bipartite system and its environment.
-\newblock Phys Rev Lett. 2012;109(15):150403.
-
-\bibitem{Andrea_AD}
-Aguilar GH, Vald\'es-Hern\'andez A, Davidovich L, Walborn SP, Souto~Ribeiro PH.
-\newblock Experimental entanglement redistribution under decoherence channels.
-\newblock Phys Rev Lett. 2014;113(24):240501.
-
-\bibitem{Barreiro}
-Barreiro J, Müller M, Schindler P, Nigg D, Monz T, Chwalla M, et~al.
-\newblock An open-system quantum simulator with trapped ions.
-\newblock Nature. 2011;470(7335):486--491.
-
-\bibitem{Marsden}
-Head-Marsden K, Krastanov S, Mazziotti D, Narang P.
-\newblock Capturing non-Markovian dynamics on near-term quantum computers.
-\newblock Phys Rev Res. 2021;3:013182.
-
-\bibitem{chuangbook}
-Nielsen MA, Chuang IL.
-\newblock Quantum computation and quantum information: 10th anniversary
-  edition.
-\newblock 10th ed. New York: Cambridge University Press; 2011.
-
-\bibitem{geometry}
-Bengtsson I, {\. Z}yczkowski K.
-\newblock Geometry of quantum states: an introduction to quantum entanglement.
-\newblock 1st ed. Cambridge: Cambridge University Press; 2006.
-
-\bibitem{Zbigniew}
-Puchała Z, Łukasz Rudnicki, {\. Z}yczkowski K.
-\newblock Pauli semigroups and unistochastic quantum channels.
-\newblock Phys Lett A. 2019;383(20):2376--2381.
-
-\bibitem{Davalos}
-Davalos D, Ziman M, Pineda C.
-\newblock Divisibility of qubit channels and dynamical maps.
-\newblock Quantum. 2019;3:144.
-
-\bibitem{Flammia}
-Steven F, Joel W.
-\newblock Efficient estimation of Pauli channels.
-\newblock ACM. 2020;1(3):1--32.
-
-\bibitem{cerezo}
-Cerezo M, Arrasmith A, Babbush R, Benjamin SC, Endo S, Fujii K, et~al.
-\newblock Variational quantum algorithms.
-\newblock Nat Rev Phys. 2020;3(9):625--644.
-
-\bibitem{Benedetti}
-Benedetti M, Lloyd E, Sack S, Fiorentini M.
-\newblock Parameterized quantum circuits as machine learning models.
-\newblock Quantum Sci Technol. 2019;4(4):043001.
-
-\bibitem{Rasmussen}
-Rasmussen S, Loft N, Bækkegaard T, Kues M, Zinner N.
-\newblock Reducing the amount of single-qubit rotations in VQE and related
-  algorithms.
-\newblock Adv Quantum Technol. 2020;3:2000063.
-
-\bibitem{Rieffel}
-Rieffel E, Polak W.
-\newblock Quantum computing: a gentle introduction.
-\newblock 1st ed. Massachusetts: The MIT Press; 2011.
-
-\bibitem{zimansbook}
-Heinosaari T, Ziman M.
-\newblock {The Mathematical Language of Quantum Theory: From Uncertainty to
-  Entanglement}.
-\newblock 2nd ed. Cambridge: Cambridge University Press; 2012.
-
-\bibitem{cirac}
-Wolf MM, Cirac JI.
-\newblock Dividing quantum channels.
-\newblock Comm Math Phys. 2008;279(1):147--168.
-
-\bibitem{choi}
-Choi MD.
-\newblock Completely positive linear maps on complex matrices.
-\newblock Linear Algebra Appl. 1975;10(3):285--290.
-
-\bibitem{jamil}
-Jamiołkowski A.
-\newblock Linear transformations which preserve trace and positive
-  semidefiniteness of operators.
-\newblock Rep Math Phys. 1972;3(4):275--278.
-
-\bibitem{Marinescu}
-Marinescu D, Marinescu G.
-\newblock Classical and Quantum Information.
-\newblock 1st ed. Oxford: Elsevier; 2012.
-
-\bibitem{Terhal}
-Terhal BM.
-\newblock Quantum error correction for quantum memories.
-\newblock Rev Mod Phys. 2015;87(2):307--346.
-
-\bibitem{Qiskit}
-{Qiskit contributors}. Qiskit: An Open-source Framework for Quantum Computing;
-  2023.
-
-\bibitem{Chuang:1996}
-Chuang IL, Nielsen MA.
-\newblock {Prescription for experimental determination of the dynamics of a
-  quantum black box}.
-\newblock J Mod Opt. 1997;44:2455--2467.
-
-\bibitem{wildebook}
-Wilde M.
-\newblock From classical to quantum Shannon theory.
-\newblock 2nd ed. Cambridge: Cambridge University Press; 2019.
-
-\bibitem{Watrous}
-Watrous J.
-\newblock Simpler semidefinite programs for completely bounded norms.
-\newblock Theor Comput Sci. 2013;19(8):1--19.
-
-\bibitem{Benenti}
-Benenti G, Strini G.
-\newblock Computing the distance between quantum channels: usefulness of the
-  Fano representation.
-\newblock J Phys B At Mol Opt Phys. 2010;43(21):215508.
-
-\bibitem{Andrea_4qb}
-Aguilar GH, Far\'ias OJ, Vald\'es-Hern\'andez A, Souto~Ribeiro PH,
-  Davidovich L, Walborn SP.
-\newblock Flow of quantum correlations from a two-qubit system to its
-  environment.
-\newblock Phys Rev A. 2014;89(2):022339.
-
-\end{thebibliography}
-
-% }}}
-\appendix
 \end{document}

### 2023-09-09 Tareas por hacer.tex
Algunos cambios

@@
 \begin{itemize}
-\item $\varepsilon(\rho) = p \rho + (1-p) \sigma_z \otimes \sigma_z \rho \sigma_z \otimes \sigma_z $.
-\item $\varepsilon(\rho) = p_1 \rho + p_2 \sigma_z \otimes I \rho \sigma_z \otimes I + p_3 I \otimes \sigma_z \rho I \otimes \sigma_3 $.
+\item $\varepsilon(\rho) = k \rho + (1-k) (\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z) $.
+\item $\varepsilon(\rho) = (1-k_1-k_2) \rho + k_1 (\sigma_z \otimes I) \rho (\sigma_z \otimes I) + k_2 (I \otimes \sigma_z) \rho (I \otimes \sigma_3)$.
 \end{itemize}
@@
 Entonces, los dos son fáciles de implementar en las compus cuánticas. 
+Por ejemplo, el segundo canal se puede hacer con el siguiente circuito:
 
+\begin{figure}[h!]
+\begin{quantikz}
+\lstick{$q_0$} & \qw  & \gate{\sigma_3} & \qw & \qw  \\
+\lstick{$q_1$} & \qw & \qw & \gate{\sigma_3}  & \qw  \\
+\lstick{$\tilde{q}_0$} & \gate[wires=2][3cm]{\quad\quad \text{Crear el estado de dos qubits}\quad\quad} & \octrl{-2} & \ctrl{-1}  & \qw \\
+\lstick{$\tilde{q}_1$} & \gateinput{$\;\;\;\;\;\;\; \sqrt{1-k_1-k_2} |0 \rangle |0 \rangle + \sqrt{k_1} |0 \rangle |1 \rangle + \sqrt{k_2} |1 \rangle |0 \rangle $} & \ctrl{-3} & \octrl{-2} & \qw
+\end{quantikz}
+\end{figure}
+
+Por ejemplo, para unos cuantos puntos dentro de las opciones de $k_1, k_2$ para el segundo canal, se obtienen las siguientes fidelidades:
+
+\begin{figure}[h!]
+\begin{center}
+\includegraphics[width=0.5\textwidth]{images/2qbit.png}\\
+\caption{Fidelidades para distintas elecciones de $k_1, k_2$ para el segundo canal mostrado arriba.  Al parecer las fidelidades no cambian mucho. }
+\end{center}
+\end{figure}
+
+\newpage
 \section{Ver cómo suben los datos otros artículos similares de Plos One}
@@
 Por lo que encontré, muchos de los artículos no tenían datos abiertos al público.
-De los pocos que sí, casi todos subían un link a un repositorio de github que  contiene el código que hayan usado y quizá documentos con los resultados de dicho código.
+De los pocos que sí, casi todos subían un link a un repositorio de github que  contiene el código que hayan usado y quizá documentos con los resultados de dicho código.\\
+
+Puse lo que pienso que se podría subir en la carpeta "Codigo/Para_subir" en el repositorio.
 
@@
 
-\section{Revisar si se puede generalizar a qdits o a qué se refieren con lo de más de 2 dimensiones?}
+Algunos artículos que encontré y lo que ponen:
+
+\begin{itemize}
+\item \textbf{Efficient universal quantum channel simulation in IBM's cloud quantum computer (Shi-Jie Wei, Tao Xin, Gui-Lu long) Science China:}\\
+
+Quantum simulation can efficiently simulate the dynamics of diverse systems
+[1, 6-10] in condensed matter [11, 12], quantum chemistry
+[13], and high-energy physics [14-16], which are intractable
+by classical computers. Moreover, every practical quantum
+system is open system because of the inevitable coupling to
+the environment. Thus, quantum simulation of open system
+is an equally important and more general subject to explore.
+However, open system quantum simulation is still in the
+early stages of development [17-23] and remains largely unexplored. The quantum simulation of open systems promises
+powerful applications in a class of physical problems, such as
+preparing various special state [24-28], thermalizing in spinboson systems and complex many fermion-boson systems
+[29, 30], and studying nonequilibrium dynamics [31]. \\
+
+\item \textbf{Testing quantum computers with the protocl of quantum state matching (Adrian Ortega, Orsolya Kalman) Physica Scripta} \\
+
+The fields of Quantum Computation and Quantum Information have received a huge boost in the last years with
+the advent of ‘public’ quantum computation. Current devices can be accessed remotely, opening the possibility
+for the larger public to carry out experiments and to test them by running programs. Quantum computers(qcs)
+can be based on several different physical systems such as superconducting qubits[1–3], trapped ions[4],
+photonic devices[5] and neutral atoms[6]. Given all these possibilities, questions, such as computational
+efficiency, error correction capability, stability and computational power start to become important matters for
+future applications.\\
+
+\item \textbf{Experimental quantum channel simulation (He Lu et al)}: \\
+
+Quantum simulation [1–3] is the most promising near-term
+application of quantum computing due to the resource requirements for imitating some classically intractable systems
+being significantly less onerous that for other applications
+such as factorization. Experimental quantum simulation on
+closed systems is well studied using photons [4], atoms [5]
+and trapped ions [6]. Quantum simulation of open-system
+dynamics also has variety of applications, such as dissipative quantum phase transitions [7] and dissipative quantumstate engineering [8], thermalization [9], quantum noise generators [10], non-Markovian dynamics [11], and non-unitary
+quantum computing [12].
+
+\item  \textbf{Optimizing Parametrized Quantum Circuits
+with Free-Axis Single-Qubit Gates (Hiroshi Watanabe)}:\\
+
+Parametrized quantum circuit (PQC) is one of the most essential components of hybrid quantum-classical
+algorithms on near-term quantum devices [1–3]. \\
+
+The design of PQC is critical in variational quantum algorithms. Oversimplified PQC cannot express
+the optimal quantum state even if it could be implemented on noisy quantum devices. On the other
+hand, a PQC designed with a deep circuit for high expressibility cannot be implemented on currently available noisy quantum devices.\\
+
+\item \textbf{Simulating noisy quantum channels via quantum state preparation algorithms (Marcelo Zanetti et al):} \\
+
+En este artículo hacen un algoritmo para simular canales cuánticos generales y lo demuestran en las computadoras de IBM. Sin embargo, no hablan mucho de motivación.
+
+\item \textbf{Single-qubit rotations in parametrized quantum circuits (S. E. Rasmussen, Loft)}:\\
+
+En éste ven cómo optimizar algoritmos cuánticos parametrizados reduciendo la cantidad de rotaciones de un qubit.
+
+\item \textbf{Experimental Implementation of Quantum Walks on
+IBM Quantum Computers (F. Acasiete et al.)}
+
+\item \textbf{Experimental Demonstration of Force Driven Quantum Harmonic Oscillator in IBM
+Quantum Computer (Alakesh Baishya et al.)} \\
+
+Quantum simulation is one of the tremendously growing areas in the field of quantum computation which
+has significant goals and opportunities1
+. From the
+past decades, this powerful area has been applied to
+variety of scientific disciplines, e.g., physics2–6, quantum chemistry7,8, quantum biology9,10, and computer
+science11 to name a few. Several time-dependent mass
+harmonic oscillators including the most famous socalled Caldirola-Kanai oscillator12,13 have been extensively studied over the past years14–17. IBM quantum
+experience, has played a considerable role from the recent years, the platform using which a number of research
+works have been performed in the field of quantum simulation. These include observation of Uhlmann phase19
+,
+chemical isomerization reaction20, simulation of far-fromequilibrium dynamics21, Ising model simulation22, quantum multi-particle tunneling23, quantum scrambling24
+,
+and simulation of Klein-Gordon equation25 to name a
+few. Other sub-disciplines such as developing quantum
+algorithms26–33, testing of quantum information theoretical tasks34–38, quantum cryptography39–42, quantum error correction43–46, quantum applications47–52 have also
+been explored.
+
+\item  \textbf{Quantum amplitude estimation algorithms on IBM quantum
+devices (Pooja Rao et al)}
+
+\item  \textbf{Classical simulation of intermediate-size quantum circuits (Jianxin Chen et al.)}
+
+Classically simulating quantum systems is a relatively old problem [1]. However, only recently have nascent
+quantum computers become competitive in simulating general quantum circuits. Recent announcements of larger
+systems with reasonable target fidelities [2, 3] are pushing the boundary of what classical simulations can handle.
+With this push, a variety of techniques have been invented in order to keep up with newer quantum processors
+[4–11]. Unfortunately, this race is one that us classical beings cannot win in the long-term, but there are many good
+reasons to try. \\
+
+\item \textbf{Quantum circuit simulation of superchannels (Kai Wang and Dong-Sheng Wang)} \\
+
+In modern quantum physics, the control and engineering of complex quantum dynamics is essential. In
+recent years, quantum computing has become a powerful paradigm to achieve this. With the standard
+quantum circuit model, the field of digital quantum simulation is expected to be powerful to realize and
+study quantum dynamics
+
+\end{itemize}
 
@@
 
+En ningún lugar se define bien qué es un circuito cuántico. Por ejemplo, en wikipedia lo definen así:
+
+In quantum information theory, a quantum circuit is a model for quantum computation, similar to classical circuits, in which a computation is a sequence of quantum gates, measurements, initializations of qubits to known values, and possibly other actions.
+
 \end{document}

### 2023-09-09 main.tex
Comentarios editor

@@
 \FXRegisterAuthor{tb}{ttb}{\color{green}TB}
+\FXRegisterAuthor{ed}{eed}{\color{red}ED}
 
@@
 
+% Citar a estos manes de alguna manera y pedir que nos citen;
+% https://mail.google.com/mail/u/0/#inbox/FMfcgzGtwgbtTGtlXkBtrCGQRxjRZrph
+
 Since their inception, quantum computers were proposed as powerful tools for
@@
 Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
-and withing them, the simplest class of channels that produce decoherence are
+and within them, the simplest class of channels that produce decoherence are
 Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
@@
 research has been devoted to enhancing the efficiency of these
-circuits~\cite{Rasmussen}.
+circuits~\cite{Rasmussen}.  \\
+
+\ednote{I fail to see the point here - the logic of the paper is: 
+1."open quantum systems can be modeled through a class of channels representing he various types of decoherence.
+2.
+Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible.
+3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them. \\
+What I am missing is what do we learn by doing it which can't be learned by actually performing the Pauli channel onto a quantum system?
+For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial.
+Why would I need to decompose (not even effectively for any channel) the Pauli channels to match a gate based description?
+Which class of problems can we simulate that cannot be simulated otherwise?
+Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)\\
+Intuitively, it seems incredibly harder resource wise to create the sum $b|gamma\rangle$ superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.}
 
@@
 which  sets the mathematical conditions for the transformations
-that can be done using a parametrized circuit with the condition that only a
+that can be done using a parametrized circuit with the restriction that only a
 controlled single-qubit
 rotation in the circuit may depend on the parameter.  Finally, in
-section \ref{sec: 1PR circuit for a Pauli map}, we conclude about the Pauli
+section \ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
 dynamical maps that fulfill the conditions of theorem \ref{theorem2}.
@@
 This can be simplified by using the following property of Pauli matrices:
+\ednote{Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.}
+
+\tbnote{Una posible forma de escribirlo  (que no es con lo de Levi Civita, pero es que con lo de Levi Civita creo que quedaría muy complicado)}
+{\color{green}
+\begin{equation*}
+\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   (-1)^{(1-\delta_{0\gamma}) (1-\delta_{\alpha 0}) (1-\delta_{\alpha \gamma })} \sigma_{\alpha}
+\end{equation*}
+}
+
 \begin{equation}
 \label{eq: propiedad-pauli}
-\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A_{\alpha,\gamma} = \begin{pmatrix}
+\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A = \begin{pmatrix}
 1 & 1 & 1 & 1\\
@@
 \end{equation}
-\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix}
+\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix} \ednote{eq 2} \tbnote{No, sí es la eq 1}
 but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
@@
 In this section we propose a quantum circuit that simulates $N$-qubit Pauli
-channels.  Moreover, we implement the circuit for $N=1$ on a quantum computer
+channels.
+\ednote{At this point I am missing a proper defiition of a "quantum circuit" consistent with the mathematical formalism.
+The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.}  Moreover, we implement the circuit for $N=1$ on a quantum computer
 and analyze the results using the diamond norm.
@@
 \centering
-\includegraphics{images/circuito_general.pdf}
+\includegraphics{circuito_general.pdf}
 \caption{{\bf Circuit for an $N$-qubit
@@
 \centering
-\includegraphics{images/circuito_unqubit.pdf}
+\includegraphics{circuito_unqubit.pdf}
 \caption{
@@
 \centering
-\includegraphics{images/fig-tetra.pdf}
+\includegraphics{fig-tetra.pdf}
 \caption{{\bf Results of the diamond fidelities as defined in \eref{eq:diamond-fid}
@@
 to the center of the tetrahedron) have a high $f$, while those close to unitary
-channels have much lower $f$.  This is reasonable because quantum computers are
+channels have much lower $f$.
+\ednote{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise.
+}  This is reasonable because quantum computers are
 prone to errors that depolarize qubits, which isn't very problematic when
@@
 Moreover, the algorithm of \fref{Fig2} is not optimal for
-unitary channels (that is, the channels corresponding to the vertices of the
+unitary channels \ednote{why?} (that is, the channels corresponding to the vertices of the
 tetrahedron).  These straightforward channels could be accomplished more
 efficiently by simply applying the corresponding Pauli operation directly.
+\ednote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
 Nevertheless, due to its general design to accommodate any Pauli channel, the
-algorithm employs numerous quantum gates even in such scenarios.
+algorithm employs numerous quantum gates even in such scenarios. \ednote{but this is a severe disadvantage, that begs the question: what is the advantage?}
 
@@
 \end{definition}
+\ednote{This definition is vague - given the vagueness of the term "quantum circuit".
+ Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit.}
 
@@
 \centering
-\includegraphics{images/OPR-circuit.pdf}
+\includegraphics{OPR-circuit.pdf}
 \caption{\textbf{General form of a 1PR circuit}.
@@
 Moreover, without loss of generality, we can choose the last qubit as the
-target qubit for the rotation, since if it weren't, we could use
+target qubit for the rotation, since if it is not, we could use
 swap gates to move the rotation
@@
 \end{align*}
-with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
+with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states \ednote{normal} and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
 c^j|c^j \rangle = 1$.
 \end{theorem}
-\textbf{Proof:} 
+\textbf{Proof:}  \ednote{again, this is not a conclusion from theorem 1.
+This is literally Definition 1.
+Also, use the proper notation here - make A and B operators living on an dim N Hilbert state, and R explixitly dependent on s and operating on qubit N.
+Then the matrix representation of the operators is a $2^n \times 2^n$ matrix which is applied to the state j....
+The explanation in words in not sufficient.}
 We can conclude from theorem 1 that $U=ARB$,
@@
 with $B_{i,j}$ the entries of matrix $B$.
-This can be rewritten by separating last qubit from the other $N-1$:
+This can be rewritten by separating the last qubit from the other $N-1$:
 \begin{equation}
@@
 and not the others. Therefore,  
-remembering that a $\sigma_3$ rotation acts by adding a phase $e^{-is(p)}$ to $|0\rangle$
+remembering that a $R_{\sigma_3}(s(p))$ rotation acts by adding a phase $e^{-is(p)}$ to $|0\rangle$
 and a phase $e^{is(p)}$ to $|1\rangle$, we have that,
@@
 \begin{align*}
-|\tilde{a}^j \rangle &= \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|0\rangle,\\
+|\tilde{a}^j \rangle &= \sum_{k \in \mathcal{C}} B_{2k,j}|k\rangle|1\rangle,\\
 |\tilde{b}^j\rangle &= \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |0 \rangle,\\
@@
 Moreover, they satisfy  $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle c^j| c^j\rangle = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
-which is unitary.
+which is unitary. \ednote{true only if the initial j states are normalised, but they were undefined.}
 
@@
 with the parametrized rotation $R$ applied to the last qubit controlled by all the 
-other qubits. The operators $A$ and $B$ can be defined as follows:
+other qubits. The operators $A$ and $B$ can be defined as follows: \ednote{How can it make sense to define A and B applied respectively to the last 3 and the first qubit?}
 \begin{align*}
@@
 \end{align*}
+\ednote{Please, at least give an example of this semiarbitrary construction of A and B.}
 The remaining part of the operators $A$ and $B$ can be defined
 in any arbitrary manner as long as they are unitary.
+\ednote{I don't understand what operatively is happening here.
+Select the state 0, apply B, apply s, apply A and then "straight forward calculations" lead to what?}
 By starting from the initial state $|0\rangle$ and 
@@
 
-To see it, we can rewrite the expression of $B|0\rangle$ by 
+To see it, \ednote{to see what?} we can rewrite the expression of $B|0\rangle$ by 
 separating the first $N-1$ qubits from the last one:
 $$B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.$$
-Since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$. As a result, we obtain:
+Since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$.
+As a result, we obtain: \ednote{so this is just the proof that the proposed operative definition of A and B is properly normalised, right?}
 
@@
 
-Finally, applying the defined operator $A$ to this state yields the desired result.
+Finally, applying the defined operator $A$ to this state yields the desired result. \ednote{which is??}
 
@@
 \centering
-\includegraphics{images/fig-curves.pdf}
+\includegraphics{fig-curves.pdf}
 \caption{{\bf Some Pauli dynamical maps that can be implemented with a 1PR circuit.}
@@
 \end{align*}
+\ednote{to be consistent with the previous formalism, the states should be 0,1,2,3}
 with $\sin s = \sqrt{3p/4}$.
@@
 using an optical arrangement, and  it was indeed done 
-by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate).
+by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate). \ednote{there is literally one parameter in one qubit, of course it depends on one parameter...
+ how can this be a result?}
 
@@
 that can be implemented with a 1PR circuit in \fref{Fig5}.
+\ednote{This is interesting, instead of giving only some random examples, I would actually explore more in details the zoology of this class of dynamical maps - if lucky, you would find class of interesting problems that can be simulated effectively in an experimental setup by just accessing one parameter (as the authors say, just with one set of waveplates, for example), }
 
@@
 \section{Conclusion} % {{{
+
+\ednote{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit.
+I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so..
+what is the applicability of the theorem for higher dimensions?}
 
@@
 generalized it to Pauli dynamical maps
-by using parametrized quantum circuits.
+by using parametrized quantum circuits \ednote{imprecise}.
 Furthermore, we implemented single-qubit Pauli channels
@@
 Finally, when working with Pauli dynamical maps,
-we searched for a way of simplifying the parametrized circuit
+we searched for a way of simplifying the parametrized circuit \ednote{This reasoning I miss, simplifying for achieving what goal? }
 by requiring that only one single-qubit rotation depends on the parameter.
@@
 and we observe the big effect that the error of quantum computers have
-on these simulations.
+on these simulations. \ednote{There is no quantification of this, it´s not even the focus of the paper}
 On the other hand, the result
@@
 can be applied to any quantum algorithm that requires parametrized circuits,
-such as those used for quantum machine learning.
+such as those used for quantum machine learning. \ednote{citation required here}
 
@@
 %\section{Supporting information} % {{{
-
-% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
-% \paragraph*{S1 Fig.}
-% \label{S1_Fig}
-% {\bf Bold the title sentence.} Add descriptive text after the title of the item (optional).
 %
+%
+%% Include only the SI item label in the paragraph heading. Use the \nameref{label} command to cite SI items in the text.
+%\paragraph*{S1 Code.}
+% \label{S1_code}
+% {\bf Simulation of Pauli Channels.} Python code for the simulation of Pauli channels on IBM's quantum computers.
+%% 
 % \paragraph*{S2 Fig.}

### 2023-09-10 Tareas por hacer.tex
.

@@
 
-Puse lo que pienso que se podría subir en la carpeta "Codigo/Para_subir" en el repositorio.
+Puse lo que pienso que se podría subir en la carpeta "Codigo/Para-subir" en el repositorio.
 
+\newpage
 \section{Revisar la motivación que ponen otras simulaciones cuánticas}
 
-Algunos artículos que encontré y lo que ponen:
+Algunos artículos que encontré y lo que ponen.
+
+Identifico los siguientes temas:
+\begin{itemize}
+\item[1.] {\color{green} La simulación de sistemas cuánticos es un tema poco explorado y que vale la pena estudiar para entender más de sistemas cuánticos abiertos.}
+\item[2.] {\color{blue}  Hacemos la simulación no necesariamente por algo útil, sino que para aprovechar que hay computadoras cuánticas.}
+\item[3.] {\color{orange} Porque la simulación cuántica es una de las aplicaciones más prometedoras de la computación cuántica (y una de las aplicaciones que se pensaron inicialmente)}
+\end{itemize}
+
+Aquí están los artículos:
 
@@
 system is open system because of the inevitable coupling to
-the environment. Thus, quantum simulation of open system
+the environment. {\color{green} Thus, quantum simulation of open system
 is an equally important and more general subject to explore.
@@
 preparing various special state [24-28], thermalizing in spinboson systems and complex many fermion-boson systems
-[29, 30], and studying nonequilibrium dynamics [31]. \\
+[29, 30], and studying nonequilibrium dynamics [31].} \\
 
@@
 The fields of Quantum Computation and Quantum Information have received a huge boost in the last years with
-the advent of ‘public’ quantum computation. Current devices can be accessed remotely, opening the possibility
-for the larger public to carry out experiments and to test them by running programs. Quantum computers(qcs)
+the advent of ‘public’ quantum computation.
+{\color{blue} Current devices can be accessed remotely, opening the possibility
+for the larger public to carry out experiments and to test them by running programs.} Quantum computers(qcs)
 can be based on several different physical systems such as superconducting qubits[1–3], trapped ions[4],
@@
 
-Quantum simulation [1–3] is the most promising near-term
+{ \color{blue} Quantum simulation [1–3] is the most promising near-term
 application of quantum computing due to the resource requirements for imitating some classically intractable systems
 being significantly less onerous that for other applications
-such as factorization. Experimental quantum simulation on
+such as factorization.} Experimental quantum simulation on
 closed systems is well studied using photons [4], atoms [5]
@@
 
-\item  \textbf{Optimizing Parametrized Quantum Circuits
-with Free-Axis Single-Qubit Gates (Hiroshi Watanabe)}:\\
+\item \textbf{Quantum Simulation of quantum channels in nuclear magnetic resonance.(Tao Xin, Shi-Jie Wei, Julen S. Pedernales, Enrique Solano and Gui-Lu Long) Physical Review A: }\\
 
-Parametrized quantum circuit (PQC) is one of the most essential components of hybrid quantum-classical
-algorithms on near-term quantum devices [1–3]. \\
+\textbf{En éste artículo hacen algo muy parecido a lo nuestro, pues hacen un algoritmo para simular canales cuánticos. Además, lo usan para Amplitude damping, Phase damping y depolarizing.}\\
 
-The design of PQC is critical in variational quantum algorithms. Oversimplified PQC cannot express
-the optimal quantum state even if it could be implemented on noisy quantum devices. On the other
-hand, a PQC designed with a deep circuit for high expressibility cannot be implemented on currently available noisy quantum devices.\\
+In the last decades, significant progress has been achieved in
+the isolation and coherent control of quantum systems, allowing for the observation of their unitary dynamics [1–7].
+{\color{orange} Such a
+degree of controllability has resulted in the implementation of
+quantum machines composed of a growing number of qubits,
+which have been used for key tests of quantum simulations
+and quantum computers. As envisioned by Feynman [8],
+large-scale quantum simulators would open the door to the
+analysis of new quantum physical phenomena and to the
+study of various models that are nowadays intractable with
+classical computers.}
+{\color{green} In opposition to quantum simulators of
+closed quantum systems, the simulation of open quantum
+systems, which has also been the subject of some research
+both from a theoretical [9–17] and an experimental [18–20]
+point of view, has been comparatively less explored. } In this
+sense, both from a theoretical and an experimental perspective,
+simulating open quantum systems pose relevant challenges.
+For example, understanding how quantum systems interact
+with their environment could potentially shed light on the
+physics of photosynthetic processes or transport phenomena
+in general [21,22], which in turn could help us design more
+efficient light-harvesting devices [23–25]. It could also help
+us understand dissipation and thermalization processes, or
+the nature of phase transitions. In the same manner, topics
+related to the foundations of quantum physics, such as the measurement process or the quantum-to-classical transition [26],
+would greatly benefit from a deeper physical understanding of
+open quantum systems. \\
 
@@
 
-En este artículo hacen un algoritmo para simular canales cuánticos generales y lo demuestran en las computadoras de IBM. Sin embargo, no hablan mucho de motivación.
-
-\item \textbf{Single-qubit rotations in parametrized quantum circuits (S. E. Rasmussen, Loft)}:\\
-
-En éste ven cómo optimizar algoritmos cuánticos parametrizados reduciendo la cantidad de rotaciones de un qubit.
-
-\item \textbf{Experimental Implementation of Quantum Walks on
-IBM Quantum Computers (F. Acasiete et al.)}
+En este artículo hacen un algoritmo para simular canales cuánticos generales y lo demuestran en las computadoras de IBM. Sin embargo, no hablan mucho de motivación. \\
 
@@
 Quantum simulation is one of the tremendously growing areas in the field of quantum computation which
-has significant goals and opportunities1
-. From the
+has significant goals and opportunities. From the
 past decades, this powerful area has been applied to
@@
 experience, has played a considerable role from the recent years, the platform using which a number of research
-works have been performed in the field of quantum simulation. These include observation of Uhlmann phase19
-,
-chemical isomerization reaction20, simulation of far-fromequilibrium dynamics21, Ising model simulation22, quantum multi-particle tunneling23, quantum scrambling24
-,
-and simulation of Klein-Gordon equation25 to name a
+works have been performed in the field of quantum simulation.
+These include observation of Uhlmann phase19, chemical isomerization reaction20, simulation of far-fromequilibrium dynamics21, Ising model simulation22, quantum multi-particle tunneling23, quantum scrambling24, and simulation of Klein-Gordon equation25 to name a
 few. Other sub-disciplines such as developing quantum
@@
 
+\item \textbf{Algunos otros art\'iculos que hacen alguna simulaci\'on cu\'antica:}
+
+\begin{itemize}
+\item \textbf{Experimental Implementation of Quantum Walks on
+IBM Quantum Computers (F. Acasiete et al.)}
+
 \item  \textbf{Quantum amplitude estimation algorithms on IBM quantum
@@
 
-\item  \textbf{Classical simulation of intermediate-size quantum circuits (Jianxin Chen et al.)}
+\item \textbf{Quantum circuit simulation of superchannels (Kai Wang and Dong-Sheng Wang)} \\
+\end{itemize}
 
-Classically simulating quantum systems is a relatively old problem [1]. However, only recently have nascent
-quantum computers become competitive in simulating general quantum circuits. Recent announcements of larger
-systems with reasonable target fidelities [2, 3] are pushing the boundary of what classical simulations can handle.
-With this push, a variety of techniques have been invented in order to keep up with newer quantum processors
-[4–11]. Unfortunately, this race is one that us classical beings cannot win in the long-term, but there are many good
-reasons to try. \\
+\item \textbf{Ahora art\'iculos que hacen algo de circuitos cu\'anticos parametrizados y que hablan de optimizar este tipo de circuitos.}
 
-\item \textbf{Quantum circuit simulation of superchannels (Kai Wang and Dong-Sheng Wang)} \\
+\begin{itemize}
+\item  \textbf{Optimizing Parametrized Quantum Circuits
+with Free-Axis Single-Qubit Gates (Hiroshi Watanabe)}:\\
 
-In modern quantum physics, the control and engineering of complex quantum dynamics is essential. In
-recent years, quantum computing has become a powerful paradigm to achieve this. With the standard
-quantum circuit model, the field of digital quantum simulation is expected to be powerful to realize and
-study quantum dynamics
+Parametrized quantum circuit (PQC) is one of the most essential components of hybrid quantum-classical
+algorithms on near-term quantum devices [1–3]. 
+The design of PQC is critical in variational quantum algorithms. Oversimplified PQC cannot express
+the optimal quantum state even if it could be implemented on noisy quantum devices. On the other
+hand, a PQC designed with a deep circuit for high expressibility cannot be implemented on currently available noisy quantum devices.\\
+
+\item  \textbf{Single-qubit rotations in parametrized quantum circuits (S.E. Rasmussen, Loft)}:
+
+En este art\'iculo ven c\'omo optimizar algoritmos cu\'anticos parametrizados reduciendo la cantidad de rotaciones de un qubit.
 
@@
 
+\end{itemize}
+
+\newpage
 \section{La definicion de circuito cuantico}
@@
 
+En el Chuang y otros libros, generalmente van entrando de poco en poco y nunca es algo que definan tal cual.
+
+\newpage
+\section{Los comentarios}
+Los puse también en el documento main, en donde he contestado algunos.
+
+\begin{enumerate}
+\item I fail to see the point here - the logic of the paper is: 
+1.
+"open quantum systems can be modeled through a class of channels representing he various types of decoherence." 2.
+"Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible."
+3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them.
+
+What I am missing is what do we learn by doing it which cant be learned by actually performing the Pauli channel onto a quantum system?
+For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial.
+Why would I need to decompose (not even effectively for any channel) the pauli channels to match a gate based description?
+Which class of problems can we simulate that cannot be simulated otherwise?
+Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)
+
+Intuitively, it seems incredibly harder resource wise to create the sum b|gamma> superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.
+
+\item Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.
+
+\item At this point I am missing a proper defiition of a "quantum circuit" consistent with the mathematical formalism.
+The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.
+
+\item So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise.
+
+\item I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron. \\
+
+El statement es: These straightforward channels could be accomplished more efficiently by
+simply applying the corresponding Pauli operation directly. \\
+
+\item but this is a severe disadvantage, that begs the question: what is the advantage? \\
+
+\item This definition is vague - given the vagueness of the term "quantum circuit".
+ Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit.
+
+\item again, this is not a conclusion from theorem 1.
+This is literally Definition 1.
+Also, use the proper notation here - make A and B operators living on an dim N Hilbert state, and R explixitly dependent on s and operating on qubit N.
+Then the matrix representation of the operators is a $2^n\times 2^n$ matrix which is applied to the state j....
+
+The explanation in words in not sufficient.
+
+\item true only if the initial j states are normalised, but they were undefined.
+
+\item How can it make sense to define A and B applied respectively to the last 3 and the first qubit?
+
+\item  Please, at least give an example of this semiarbitrary construction of A and B.
+
+\item I don't understand what operatively is happening here. Select the state 0, apply B, apply s, apply A and then "straight forward calculations" lead to what?
+
+\item so this is just the proof that the proposed operative definition of A and B is properly normalised, right?
+
+\item there is literally one parameter in one qubit, of course it depends on one parameter...
+ how can this be a result?
+
+ \item This is interesting, instead of giving only some random examples, I would actually explore more in details the zoology of this class of dynamical maps - if lucky, you would find class of interesting problems that can be simulated effectively in an experimental setup by just accessing one parameter (as the authors say, just with one set of waveplates, for example),
+
+ \item I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit.
+I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so..
+what is the applicability of the theorem for higher dimensions?
+
+ \item Imprcise (using parametrized quantum
+circuits.)
+
+ \item This reasoning I miss, simplifying for achieving what goal?
+
+ \item There is no quantification of this, it´s not even the focus of the paper
+
+ \item citation required here
+\end{enumerate}
+
 \end{document}

### 2023-09-10 main.tex
.

@@
 
-\tbnote{Una posible forma de escribirlo  (que no es con lo de Levi Civita, pero es que con lo de Levi Civita creo que quedaría muy complicado)}
+\tbnote{Una posible forma de escribirlo  (que no es con lo de Levi Civita, pero es que con lo de Levi Civita creo que quedaría muy complicado):}
 {\color{green}
 \begin{equation*}
-\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   (-1)^{(1-\delta_{0\gamma}) (1-\delta_{\alpha 0}) (1-\delta_{\alpha \gamma })} \sigma_{\alpha}
+\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\;\; \text{with} \; A_{\alpha, \gamma} = (-1)^{(1-\delta_{0\gamma}) (1-\delta_{\alpha 0}) (1-\delta_{\alpha \gamma })} \sigma_{\alpha}
 \end{equation*}

### 2023-09-16 Tareas por hacer.tex
Algunos cambios mas

@@
 \begin{itemize}
+\item \textbf{Quantum Simulation of Open Quantum Systems Using Density-Matrix Purification (Anthony W. Schlimgen et al.) PRL
+} \\
+
+With the increased
+use of quantum algorithms for unitary-gate-based quantum
+computers, techniques for casting non-unitary operations into
+unitary forms have become increasingly important.
+
+\item  \textbf{Quantum Simulation of Open Quantum Systems Using a Unitary Decomposition of Operators (Anthony W. Schlimgen, et al.) PRL:}
+
+The time evolution of an electronic state is
+critical to predicting many important physical phenomena
+including exciton transport [1], molecular conductivity [2],
+chemical catalysis [3], quantum phase transitions [4, 5], and
+magnetization [6]. Often these processes involve non-trivial
+interactions with a large environment, requiring the definition and treatment of open quantum systems [7–15]. Recent
+research has considered the simulation of open quantum systems on quantum devices [16–20].
+
 \item \textbf{Efficient universal quantum channel simulation in IBM's cloud quantum computer (Shi-Jie Wei, Tao Xin, Gui-Lu long) Science China:}\\

### 2023-09-17 cover_letter_plos.tex
these confounded tests drive me nuts
Contestando mas comentarios / simulacion mapas dinamicos

@@
 \usepackage[utf8]{inputenc}
+\usepackage{hyperref}
+
 % \date{17 de Octubre de 2018}
@@
 
+All relevant data and codes to replicate the results can be found in the following
+public repository \href{https://github.com/tbasile/Quantum-simulation-of-Pauli-Channels.git}{https://github.com/tbasile/Quantum-simulation-of-Pauli-Channels.git}.
+
 We declare the manuscript’s originality and exclusivity for publication. In
@@
 manuscript. In the event that our manuscript is chosen for review, we kindly
-suggest Dr. Fabio Sciarrino as a suitable reviewer, given his background and
+suggest Dr. Fabio Sciarrino as a suitable editor, given his background and
 expertise to evaluate our findings. We have no objections to any other
@@
 of this manuscript. Furthermore, the named authors have no conflicts of
-interest to disclose.
-
-% Thank you for considering our work.
-% On behalf of all authors
+interest to disclose. Both authors received support from projects CONAHCyT 
+(Consejo Nacional de Humanidades, Ciencias y Tecnologías
+\href{https://dgapa.unam.mx/index.php/impulso-a-la-investigacion/papiit}{https://dgapa.unam.mx/index.php/impulso-a-la-investigacion/papiit}) 285754, 
+and UNAM-PAPIIT  (Universidad Nacional Autónoma de México - Programa de Apoyo a 
+Proyectos de Investigación e Innovación Tecnológica \href{https://conahcyt.mx/}{https://conahcyt.mx/}) IG101421.
+The funders had no role in study design, data collection and analysis, 
+decision to publish, or preparation of the manuscript.
 

### 2023-09-17 main.tex
Algunos cambios mas
Contestando mas comentarios / simulacion mapas dinamicos

--- 2023-09-09 main.tex
@@
 \FXRegisterAuthor{tb}{ttb}{\color{green}TB}
-\FXRegisterAuthor{ed}{eed}{\color{red}ED}
+\FXRegisterAuthor{rev}{rrv}{\color{red}REV}
 
@@
 \bigskip
-\textbf{1} Facultad de Ciencias. Universidad Nacional Autónoma de México, Ciudad de México 01000, Mexico
+\textbf{1} Facultad de Ciencias. Universidad Nacional Autónoma de México, Ciudad de México, Mexico
 \\
-\textbf{2} Instituto de Física, Universidad Nacional Autónoma de México, Ciudad de México 01000, México
+\textbf{2} Instituto de Física, Universidad Nacional Autónoma de México, Ciudad de México, México
 \\
@@
 
-\ednote{I fail to see the point here - the logic of the paper is: 
+\revnote{I fail to see the point here - the logic of the paper is: 
 1."open quantum systems can be modeled through a class of channels representing he various types of decoherence.
@@
 Intuitively, it seems incredibly harder resource wise to create the sum $b|gamma\rangle$ superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.}
+
+\tbnote{Entiendo que su punto es que los canales de Pauli se podrían hacer de una forma
+similar pero en lugar de usar los qubits de ancilla para crear las probabilidades, crearlas
+de otra forma que sea mejor y que entonces no tiene mucho sentido el artículo.  \\
+La verdad no sé bien cómo contestar a este comentario. \\
+Una forma podría ser haciendo más énfasis en lo de circuitos 1PR
+y que lo de canales de Pauli sea como un ejemplo particular de cómo se puede usar eso. Claro que eso significaría cambiar demasiado el artículo
+ (hasta habría que cambiar el título ) y no sé si eso sea factible. Quizá se puede hacer
+ más énfasis en lo de 1PR sin cambiar taaanto el orden del artículo\\
+Igual la verdad que estoy perdido con qué contestar a este artículo}
 
@@
 This can be simplified by using the following property of Pauli matrices:
-\ednote{Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.}
-
-\tbnote{Una posible forma de escribirlo  (que no es con lo de Levi Civita, pero es que con lo de Levi Civita creo que quedaría muy complicado)}
+\revnote{Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.}
+
+\tbnote{Siguiendo la relaci\'on de conmutaci\'on, resulta que las Levi Civitas desaparecen y quedan s\'olo deltas de Dirac:}
 {\color{green}
 \begin{equation*}
-\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   (-1)^{(1-\delta_{0\gamma}) (1-\delta_{\alpha 0}) (1-\delta_{\alpha \gamma })} \sigma_{\alpha}
+\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\;\; \text{with} \; A_{\alpha, \gamma} = (2\delta_{ij}-1)(2\delta_{i0}-1)(2\delta_{j0}-1)
 \end{equation*}
@@
 \end{equation}
-\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix} \ednote{eq 2} \tbnote{No, sí es la eq 1}
+\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix} \revnote{eq 2} \tbnote{No, sí es la eq 1}
 but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
@@
 channels.
-\ednote{At this point I am missing a proper defiition of a "quantum circuit" consistent with the mathematical formalism.
-The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.}  Moreover, we implement the circuit for $N=1$ on a quantum computer
+\revnote{At this point I am missing a proper definition of a "quantum circuit" consistent with the mathematical formalism.
+The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \tbnote{Agregué algo abajo}
+ Moreover, we implement the circuit for $N=1$ on a quantum computer
 and analyze the results using the diamond norm.
 We find that close to the depolarizing channel, the general circuit simulator 
-can implement such channels with the highest fidelity. 
+can implement such channels with the highest fidelity.  \\
+
+{\color{green} A quantum circuit is a model for representing computation on a quantum system. 
+This computation may include preparing the initial state of the system, applying unitary operations and measuring the whole system or parts of it~\cite{Rieffel}.
+
+Here, our systems always consist of some number $N$ of qubits.
+The qubits can be divided into the ones to which we will apply the quantum channel, or ``principal qubits'' and the ones that help us complete said operation, or ``ancilla qubits''.
+The circuit implements a unitary operator $U$ and then some or all of the qubits are measured.
+}
+
 % produce the highest 
@@
 to the center of the tetrahedron) have a high $f$, while those close to unitary
-channels have much lower $f$.
-\ednote{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise.
-}  This is reasonable because quantum computers are
+channels have much lower $f$. \revnote{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise. } 
+\tbnote{La respuesta a esto puede incluir lo siguiente: 
+It works better for depolarizing channels, yes, but still has considerably big zone with high fidelity.}
+ This is reasonable because quantum computers are
 prone to errors that depolarize qubits, which isn't very problematic when
@@
 Moreover, the algorithm of \fref{Fig2} is not optimal for
-unitary channels \ednote{why?} (that is, the channels corresponding to the vertices of the
+unitary channels \revnote{why?} (that is, the channels corresponding to the vertices of the
 tetrahedron).  These straightforward channels could be accomplished more
 efficiently by simply applying the corresponding Pauli operation directly.
-\ednote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
+\revnote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
+\tbnote{Este comentario se conecta con lo del 
+primer comentario, que no sé bien cómo contestar.}
 Nevertheless, due to its general design to accommodate any Pauli channel, the
-algorithm employs numerous quantum gates even in such scenarios. \ednote{but this is a severe disadvantage, that begs the question: what is the advantage?}
+algorithm employs numerous quantum gates even in such scenarios. \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
+\tbnote{As I see it, an advantage is that only one circuit arrengment is needed for any channel. We don't have to change
+the circuit to implement different channels, only need to change parameters.
+This allows us to consider parametrized circuits and then explore what happens when
+we constrain to only one parametrized operation.}
 
@@
 \end{definition}
-\ednote{This definition is vague - given the vagueness of the term "quantum circuit".
+\revnote{This definition is vague - given the vagueness of the term "quantum circuit".
  Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit.}
+ \tbnote{Agregar lo siguiente a la definición:}
+
+{\color{green}
+Therefore, a 1PR circuit implements a unitary operator $U(p)$ on some number $N$ of qubits,
+such that $U$ depends on the parameter $p$ only locally on one specific qubit.
+}
 
@@
 definition, a 1PR circuit always consists of an operation $B$ followed 
-by the parametrized rotation and then another operation $A$, 
+by the parametrized rotation on a specific qubit and then another operation $A$, 
 where $A$ and $B$ are not parametrized.
@@
 Consider a 1PR circuit of $N$ qubits parametrized by $p$
-and denote by $U$ the operator it implements on this system. 
+and denote by $U(p)$ the operator it implements on this system. 
 Then, for every $j \in \{0, 1, \cdots, 2^N-1\}$, 
 we have that:
-\begin{align*}
-U|j\rangle = e^{is(p)} |a^j\rangle + e^{-is(p)} |b^j\rangle + |c^j\rangle
-\end{align*}
-with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states \ednote{normal} and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
-c^j|c^j \rangle = 1$.
+\begin{align}
+U(p)|j\rangle = e^{is(p)} |a^j\rangle + e^{-is(p)} |b^j\rangle + |c^j\rangle
+\label{eq:uj}
+\end{align}
+with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states \revnote{normal} \tbnote{Aquí no estoy seguro, sí sería normal el término correcto?} and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
+c^j|c^j \rangle = 1$. Here $|j\rangle$ represents the N-qubit base states in the computational basis.
 \end{theorem}
-\textbf{Proof:}  \ednote{again, this is not a conclusion from theorem 1.
+\textbf{Proof:}  \revnote{again, this is not a conclusion from theorem 1.
 This is literally Definition 1.
@@
 Then the matrix representation of the operators is a $2^n \times 2^n$ matrix which is applied to the state j....
-The explanation in words in not sufficient.}
+The explanation in words in not sufficient.} \tbnote{Cambié la siguiente oración por el párrafo en verde}
 We can conclude from theorem 1 that $U=ARB$,
@@
 applied to the last qubit and controlled by some of the other ones.
+
+{\color{green} As before, from the definition of a 1PR, we know that $U(p)$ can be decomposed as $ARB$, where 
+$A,B$ are unitary operators acting on the $N$-qubit system
+and $R$ is a rotation applied to one qubit.
+From theorem 1, we conclude that $R$ can be taken in general as a $\sigma_3$ rotation of angle $2s(p)$ applied to the last qubit and controlled by some of the other ones. 
+To prove the result, we will apply $U(p)$ to $|j\rangle$ by first applying $B$,
+then $R_{\sigma_3}(2s(p))$ and finally $A$, with
+the goal of getting to \eref{eq:uj}. }
 
@@
 \end{equation}
-After the operator $B$, the circuit applies the  controlled rotation $R$.
+After the operator $B$, the circuit applies the  controlled rotation $R_{\sigma_3}(2s(p))$.
 To simplify the analysis, we separate the states of
@@
 and not the others. Therefore,  
-remembering that a $R_{\sigma_3}(s(p))$ rotation acts by adding a phase $e^{-is(p)}$ to $|0\rangle$
+using that a $R_{\sigma_3}(2s(p))$ rotation acts by adding a phase $e^{-is(p)}$ to $|0\rangle$
 and a phase $e^{is(p)}$ to $|1\rangle$, we have that,
@@
 % test
+\begin{small}
 \begin{align}
-RB|j\rangle& = e^{-is(p)} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is(p)} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
+R_{\sigma_3}(2s(p))B|j\rangle& = e^{-is(p)} \sum_{k \in \mathcal{C}} B_{2k,j} |k\rangle |0\rangle + e^{is(p)} \sum_{k \in \mathcal{C}} B_{2k+1,j} |k\rangle |1\rangle 
 + \sum_{k \not\in \mathcal{C}} \left( B_{2k,j} |k\rangle|0\rangle  + B_{2k+1,j} |k \rangle |1\rangle  \right) \nonumber \\
@@
 \end{align}
+\end{small}
 where we defined
@@
 Moreover, they satisfy  $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle c^j| c^j\rangle = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
-which is unitary. \ednote{true only if the initial j states are normalised, but they were undefined.}
+which is unitary. \revnote{true only if the initial j states are normalised, but they were undefined.} 
+\tbnote{Agregué una línea en el enunciado del teorema sobre que los $|j \rangle$ son 
+la base computacional del sistema de N qubits.}
 
@@
 so that the result is given by:
-\begin{eqnarray}
-U|j\rangle = ARB|j\rangle = e^{-is(p)} A |\tilde{a}^j\rangle + e^{is(p)} A |\tilde{b}^j\rangle + A |\tilde{c}^j\rangle = e^{-is(p)} |a^j\rangle + e^{is(p)} |b^j\rangle + |c^j\rangle,
-\end{eqnarray}
+\begin{eqnarray*}
+U|j\rangle = AR_{\sigma_3}(2s(p)) B|j\rangle = e^{-is(p)} A |\tilde{a}^j\rangle + e^{is(p)} A |\tilde{b}^j\rangle + A |\tilde{c}^j\rangle = e^{-is(p)} |a^j\rangle + e^{is(p)} |b^j\rangle + |c^j\rangle,
+\end{eqnarray*}
 where $|a^j\rangle = A |\tilde{a}^j\rangle, |b^j\rangle = A |\tilde{b}^j\rangle, |c^j\rangle = A |\tilde{c}^j\rangle$ are still orthogonal
@@
 with the parametrized rotation $R$ applied to the last qubit controlled by all the 
-other qubits. The operators $A$ and $B$ can be defined as follows: \ednote{How can it make sense to define A and B applied respectively to the last 3 and the first qubit?}
-\begin{align*}
-&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \\
+other qubits. There is some freedom when defining
+the operators $A$ and $B$, we only need
+to make sure that: \revnote{How can it make sense to define A and B applied respectively to the last 3 and the first qubit?} 
+\tbnote{Reescribí la oración anterior para no decir que es una definición,
+sino que queda algo de libertad (aunque igual lo decía después de la ecuación}
+\begin{align}
+&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \nonumber \\
 &A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
-\end{align*}
-\ednote{Please, at least give an example of this semiarbitrary construction of A and B.}
+\label{eq:BA}
+\end{align}
+\revnote{Please, at least give an example of this semiarbitrary construction of A and B.}
+\tbnote{Hay ejemplos en los ejemplos de abajo.}
 The remaining part of the operators $A$ and $B$ can be defined
 in any arbitrary manner as long as they are unitary. 
-\ednote{I don't understand what operatively is happening here.
-Select the state 0, apply B, apply s, apply A and then "straight forward calculations" lead to what?}
-By starting from the initial state $|0\rangle$ and 
-applying the circuit shown in \fref{Fig4}, straightforward calculations 
-lead us to obtain the resulting curve of states described in \eref{eq:curve-states}.
-
-To see it, \ednote{to see what?} we can rewrite the expression of $B|0\rangle$ by 
+Then, by following the calculations of applying 
+$A R_{\sigma_3}(2s(p)) B$ to $|0\rangle$,
+it can be shown that the curve of states created is that described in \eref{eq:curve-states}.
+\revnote{I don't understand what operatively is happening here. Select the state 0, apply B, apply s, apply A and then "straight forward calculations" lead to what?}
+\tbnote{Reescrib\'i la oraci\'on anterior de forma que creo que se entiende mejor.}
+
+To see that $A R_{\sigma_3}(s(p)) B |0\rangle$ in fact creates
+the curve of states described in \eref{eq:curve-states}, \revnote{to see what?} \tbnote{Ya cambié la oración anterior} we can rewrite the expression of $B|0\rangle$ by 
 separating the first $N-1$ qubits from the last one:
 $$B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.$$
-Since the parametrized rotation $R$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$.
-As a result, we obtain: \ednote{so this is just the proof that the proposed operative definition of A and B is properly normalised, right?}
+Since the parametrized rotation $R_{\sigma_3}(2s(p))$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$.
+As a result, we obtain: \revnote{so this is just the proof that the proposed operative definition of A and B is properly normalised, right?} \tbnote{No entiendo la pregunta, pero creo que la respuesta es no}
 
 $$
-RB|0\rangle =\sqrt{\langle a | a \rangle} e^{is(p)} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} e^{-is(p)} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.
+R_{\sigma_3}(2s(p))B|0\rangle =\sqrt{\langle a | a \rangle} e^{is(p)} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} e^{-is(p)} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.
 $$
 
-Finally, applying the defined operator $A$ to this state yields the desired result. \ednote{which is??}
+Finally, applying the  operator $A$ to this state yields the desired result: \revnote{which is??} \tbnote{Ya lo puse abajo}
+\begin{align*}
+AR_{\sigma_3}(2s(p))B = |c\rangle + e^{is(p)} |a\rangle + e^{-is(p)} |b\rangle.
+\end{align*}
+Therefore proving that any curve of states as that in \eref{eq:curve-states} 
+can be constructed by the circuit in  \fref{Fig4} with the parametrized rotation 
+controlled by all the other qubits 
+by correctly choosing matrices $A$ and $B$.
 
@@
 \begin{align*}
-|\beta(p) \rangle = \sqrt{1-3p/4} |00\rangle + \sqrt{p/4} |01\rangle + \sqrt{p/4} |10 \rangle  + \sqrt{p/4} |11\rangle.
+|\beta(p) \rangle = \sqrt{1-3p/4} |0\rangle + \sqrt{p/4} |1\rangle + \sqrt{p/4} |2 \rangle  + \sqrt{p/4} |3\rangle.
 \end{align*}
@@
 \begin{align*}
-|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |00\rangle - \dfrac{i}{2\sqrt{3}} |01\rangle 
-      - \dfrac{i}{2\sqrt{3}} |10 \rangle - \dfrac{i}{2\sqrt{3}} |11\rangle \right) \\
-& + e^{-is} \left( \dfrac{1}{2} |00\rangle + \dfrac{i}{2\sqrt{3}} |01\rangle 
-      + \dfrac{i}{2\sqrt{3}} |10\rangle + \dfrac{i}{2\sqrt{3}} |11 \rangle \right),
-\end{align*}
-\ednote{to be consistent with the previous formalism, the states should be 0,1,2,3}
+|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |0\rangle - \dfrac{i}{2\sqrt{3}} |1\rangle 
+      - \dfrac{i}{2\sqrt{3}} |2 \rangle - \dfrac{i}{2\sqrt{3}} |3\rangle \right) \\
+& + e^{-is} \left( \dfrac{1}{2} |0\rangle + \dfrac{i}{2\sqrt{3}} |1\rangle 
+      + \dfrac{i}{2\sqrt{3}} |2\rangle + \dfrac{i}{2\sqrt{3}} |3 \rangle \right) \\
+\equiv & e^{is} |a\rangle + e^{-is} |b\rangle
+\end{align*}
+\revnote{to be consistent with the previous formalism, the states should be 0,1,2,3} \tbnote{Done.}
 with $\sin s = \sqrt{3p/4}$.
@@
 1PR circuit.
+Explicitly, following the discussion after theorem \ref{theorem2},
+we know that this curve of states can be constructed by 
+the circuit of \fref{FigS2q}.
+
+\begin{figure} % {{{
+\centering
+\includegraphics{images/estado-2-qbits.pdf}
+\caption{
+{\bf 1PR Circuit for one qubit curve of states.} This is a 1PR circuit for creating a curve of states that satisfies
+the conditions of theorem \ref{theorem2}. 
+given the curve of states, operations $A$ and $B$ can be defined as in \eref{eq:BA}.
+}
+\label{FigS2q} 
+\end{figure} % }}}
+
+Now, defining $A$ and $B$ as in  \eref{eq:BA} for the particular
+vectors $|a\rangle, |b\rangle, |c \rangle$ of this dynamical map, we have that
+\begin{align*}
+A = \begin{pmatrix}
+0 & 0 & 1/\sqrt{2} & 1/\sqrt{2} \\
+1/\sqrt{6} & -1/\sqrt{2} & i /\sqrt{6} & -i /\sqrt{6} \\
+1/\sqrt{6}  & 1/\sqrt{2} & i/\sqrt{6} & -i/\sqrt{6} \\
+-\sqrt{2/3} & 0 & i/\sqrt{6} & -i/\sqrt{6}
+\end{pmatrix} \; , \; B = \begin{pmatrix}
+0 & 0 & 0& 1 \\
+0 & 0 & 1 & 0 \\
+1/\sqrt{2} & -1/\sqrt{2} & 0 & 0 \\
+1/\sqrt{2} & 1/\sqrt{2} & 0 & 0 
+\end{pmatrix}
+\end{align*}
+where the first column of $A$ and the
+last three of $B$ can be chosen arbitrarily as long as the resultant matrices are unitary. 
+We ran this circuit in IBM's quantum computer ibmq-lima for $25$ different values of $p$ between $0$ and $1$,
+and $20$ repetitions for each value of $p$.
+The diamond fidelity was calculated in each case and is shown in \fref{fid}.
 
@@
 \begin{eqnarray}
-\epsilon(\rho) = \dfrac{1}{4} {(1-p)}^2  \rho + \dfrac{1}{4} (1-p^2) \sigma_1 \rho \sigma_1 + \dfrac{1}{4} (1-p^2) \sigma_2 \rho \sigma_2 + \dfrac{1}{4} {(1+p)}^2 \sigma_3 \rho \sigma_3,
+\epsilon(\rho) =  {(1-p)}^2  \rho + (p-p^2) \sigma_1 \rho \sigma_1 + (p-p^2) \sigma_2 \rho \sigma_2 + p^2 \sigma_3 \rho \sigma_3,
 \label{eq:parab}
 \end{eqnarray}
-with $p \in [-1,1]$. 
+with $p \in [0,1]$. 
 If we take the $\beta_j$ to be real,
@@
 \begin{eqnarray}
-|\beta(p)\rangle = \dfrac{1}{2} (1-p) |00\rangle + \dfrac{1}{2} \sqrt{1-p^2} |01\rangle +  \dfrac{1}{2} \sqrt{1-p^2} |10\rangle +  \dfrac{1}{2}(1+p) |11\rangle.
+|\beta(p)\rangle =  (1-p) |0\rangle + \sqrt{p-p^2} |1\rangle +  \sqrt{p-p^2} |2\rangle + p |3\rangle.
 \end{eqnarray}
@@
 \begin{align*}
-|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|00\rangle + \dfrac{1}{2} |11\rangle \right) + e^{is} \left( \dfrac{i}{4}|00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle - \dfrac{i}{4} |11\rangle \right) \\
-& + e^{-is}  \left( \dfrac{-i}{4} |00\rangle + \dfrac{1}{4} |01\rangle + \dfrac{1}{4} |10\rangle + \dfrac{i}{4} |11\rangle \right),
-\end{align*}
-with $\sin s = p$, so that
-this map fulfills the conditions of  \eref{eq:conditions-vecs}.
+|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|0\rangle + \dfrac{1}{2} |3\rangle \right) + e^{is} \left( \dfrac{i}{4}|0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle - \dfrac{i}{4} |3\rangle \right) \\
+& + e^{-is}  \left( \dfrac{-i}{4} |0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle + \dfrac{i}{4} |3\rangle \right) \\
+& := |c\rangle + e^{is} |a\rangle + e^{-is} |b\rangle,
+\end{align*}
+with $\sin s = 2p-1$, so that
+this curve fulfills the conditions of  \eref{eq:conditions-vecs}.
+This  means that it can be created with the
+1PR circuit of figure \fref{FigS2q}. In this
+case, matrices $A$ and $B$ can be taken to be:
+\begin{align*}
+A = \begin{pmatrix}
+0 & 1/\sqrt{2} & -i/2 & i/2 \\
+-1/\sqrt{2} & 0 & 1/2 & 1/2 \\
+1/\sqrt{2} & 0 & 1/2 & 1/2 \\
+0 & 1/\sqrt{2} & i/2 & -i/2
+\end{pmatrix} \\
+B = \begin{pmatrix}
+0 & 1 &0 &0 \\
+1/\sqrt{2} & 0 & 0 &-1/\sqrt{2} \\
+1/2 & 0 & 1/\sqrt{2} & 1/2 \\
+1/2 & 0 & - 1/\sqrt{2} & 1/2
+\end{pmatrix},
+\end{align*}
+where again, the first column of $A$ and the last three of $B$ can be chosen arbitrarily. 
+As before, we ran this circuit for $25$ values of $p$ between $0$ and $1$, with $20$ repetitions for each,
+obtaining as a result the fidelities shown in \fref{FigS2q}.
 
@@
 \begin{align*}
-|\beta(p)\rangle = \sqrt{1-p} |00\rangle +\sqrt{p} |01\rangle.
+|\beta(p)\rangle = \sqrt{1-p} |0\rangle +\sqrt{p} |1\rangle.
 \end{align*}
@@
 \begin{align*}
-|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |00\rangle - \dfrac{i}{2} |01\rangle \right) + e^{-is} \left( \frac{1}{2} |00\rangle + \frac{i}{2} |01\rangle \right),
+|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |0\rangle - \dfrac{i}{2} |1\rangle \right) + e^{-is} \left( \frac{1}{2} |0\rangle + \frac{i}{2} |1\rangle \right),
 \end{align*}
@@
 and it can be created with a 1PR circuit.
-Note that in this case we actually only need one ancilla qubit
-since the state $|\beta(p)\rangle$ is only two dimensional.
+Matrices $A$ and $B$ can be obtained as for the other
+dynamical maps and the we ran the resulting circuit in ibmq-lima with the same
+specifications as for the other examples
+and the results are shown in \fref{FigS2q}.
+%Note that in this case we actually only need one ancilla qubit
+%since the state $|\beta(p)\rangle$ is only two dimensional.
 
@@
 using an optical arrangement, and  it was indeed done 
-by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate). \ednote{there is literally one parameter in one qubit, of course it depends on one parameter...
+by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate). \revnote{there is literally one parameter in one qubit, of course it depends on one parameter...
  how can this be a result?}
-
+\tbnote{Aquí la verdad no entiendo del todo qué intenta decir.
+El resultado es que en ese paper sólo hubo que variar un parámetro
+para hacer el bit phase flip, que coincde con lo que nosotros 
+probamos sobre qué canales se pueden hacer con una rotación parametrizada (pues bit phase flip es uno de esos). }
 \end{itemize}
+
+\begin{figure} % {{{
+\centering
+\includegraphics[width=0.60\textwidth]{images/dynamic-fidelitites.png}
+\caption{
+{\bf Fidelitis for dynamical maps.} Results of the fidelities obtained when simulating the three dynamical maps considered (depolarizing, parabolic and bit flip). 
+The implementation was done on IBM's ibmq-lima quantum computer.
+We can see that just as in \fref{Fig3}, fidelities are high for points close to the depolarizing channel 
+($p=1$ for depolarizing map, $p=1/2$ for parabolic map) and lower for points close
+to unitary channels ($p=0$ for all maps and $p=1$ for parabolic and bit flip).
+Furthermore, we can see that the fidelities are comparable to those of \fref{Fig3}, so that using the 1PR circuit
+doesn't considerably affect fidelity.}
+\label{FigS2q} 
+\end{figure} % }}}
 
@@
 that can be implemented with a 1PR circuit in \fref{Fig5}.
-\ednote{This is interesting, instead of giving only some random examples, I would actually explore more in details the zoology of this class of dynamical maps - if lucky, you would find class of interesting problems that can be simulated effectively in an experimental setup by just accessing one parameter (as the authors say, just with one set of waveplates, for example), }
+\revnote{This is interesting, instead of giving only some random examples, I would actually explore more in details the zoology of this class of dynamical maps - if lucky, you would find class of interesting problems that can be simulated effectively in an experimental setup by just accessing one parameter (as the authors say, just with one set of waveplates, for example), }
+\tbnote{Los mapas que ya mencionamos más a profundidad (depolarizing, phase damping, etc.) son esos ejemplos creo yo.
+Pues son ejemplos de mapas útiles o conocidos (por lo menos el depolarizing y los bit flip, phase flip, bit phase flip) y que
+probamos que se pueden hacer con una rotación parametrizada.}
 
@@
 
-\ednote{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit.
+\revnote{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit.
 I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so..
@@
 generalized it to Pauli dynamical maps
-by using parametrized quantum circuits \ednote{imprecise}.
+by using parametrized quantum circuits \revnote{imprecise}.
 Furthermore, we implemented single-qubit Pauli channels
@@
 Finally, when working with Pauli dynamical maps,
-we searched for a way of simplifying the parametrized circuit \ednote{This reasoning I miss, simplifying for achieving what goal? }
+we searched for a way of simplifying the parametrized circuit \revnote{This reasoning I miss, simplifying for achieving what goal? }
 by requiring that only one single-qubit rotation depends on the parameter.
@@
 and we observe the big effect that the error of quantum computers have
-on these simulations. \ednote{There is no quantification of this, it´s not even the focus of the paper}
+on these simulations. \revnote{There is no quantification of this, it´s not even the focus of the paper}
 On the other hand, the result
@@
 can be applied to any quantum algorithm that requires parametrized circuits,
-such as those used for quantum machine learning. \ednote{citation required here}
+such as those used for quantum machine learning. \revnote{citation required here}
 
@@
 
-\section{Acknowledgments} % {{{
-Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.
+%
+%\section{Acknowledgments} % {{{
+%Support by projects CONACyT 285754, and UNAM-PAPIIT IG101421 is acknowledged.
 

### 2023-09-19 main.tex
2qbits

@@
 we constrain to only one parametrized operation.}
+
+{\color{green}
+\subsection{Two-qubit Pauli channels}
+\tbnote{Voy a agregar toda esta sección sobre el circuito para dos qubits}
+
+For the case of a two-qubit Pauli channel,
+the circuit of \fref{Fig1} would have two principal
+qubits and $2N$ ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
+However, the number of ancilla qubits can be reduced for Pauli 
+channels in which not all two-qubit Pauli matrices are applied to
+the system. For example, consider the following two-qubit dephasing channel:
+\begin{align}
+\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  (\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  (\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
+\label{2qbit-c}
+\end{align}
+where $p \in [0,1]$ is a parameter that defines the channel. 
+Since this channel has $4$ Pauli operations, 
+only $2$ ancilla qubits will be necessary, and it can be implemented
+using the circuit of \fref{2qbit}a).
+
+\begin{figure} % {{{
+\centering
+\includegraphics{images/qbit-im.pdf}
+\caption{{\bf Circuit for 2-qubit dephasing channel.}  Circuit implementation for the 2-qubit dephasing channel of \eref{2qbit-c}.
+The state on the two ancilla qubits can be constructed just as it was done for \fref{Fig2}.
+}
+\label{2qbit}
+\end{figure} % }}}
+
+Just as for the one-qubit Pauli channels, this 
+channel was implemented on IBM's ibmq-lima  quantum computer and we obtained the Choi 
+matrix by doing quantum process tomography on
+the two principal qubits. Then, we calculated the diamond fidelity for different values of $p$ and
+obtained the results shown in \fref{2qbit}b).
+
+}
 
@@
 
+{\color{green}
 \begin{figure} % {{{
@@
 doesn't considerably affect fidelity.}
-\label{FigS2q} 
+\label{fid} 
 \end{figure} % }}}
+}
 

### 2023-09-20 main.tex
Cambios menores

@@
 The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \tbnote{Agregué algo abajo}
+
+{\color{green} A quantum circuit is a model for representing computation on a quantum system. 
+This computation may include preparing the initial state of the system, applying unitary operations and measuring the whole system or parts of it~\cite{Rieffel}.
+
+Our systems always consists of some number of qubits,
+that can be divided into the ones to which we will apply the quantum channel,
+ or ``principal qubits'' and the ones that help us complete said operation, or ``ancilla qubits''.
+The circuit implements a unitary operator $U$ on the 
+system consisting of all the qubits 
+and then the principal qubits are measured.
+}
+
  Moreover, we implement the circuit for $N=1$ on a quantum computer
@@
 can implement such channels with the highest fidelity.  \\
-
-{\color{green} A quantum circuit is a model for representing computation on a quantum system. 
-This computation may include preparing the initial state of the system, applying unitary operations and measuring the whole system or parts of it~\cite{Rieffel}.
-
-Here, our systems always consist of some number $N$ of qubits.
-The qubits can be divided into the ones to which we will apply the quantum channel, or ``principal qubits'' and the ones that help us complete said operation, or ``ancilla qubits''.
-The circuit implements a unitary operator $U$ and then some or all of the qubits are measured.
-}
 
@@
 This allows us to consider parametrized circuits and then explore what happens when
-we constrain to only one parametrized operation.}
+we constrain to only one parametrized operation.}\\
+\tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
+{\color{green} This disadvantage comes from the fact
+that the circuit is  fully general and applicable to any Pauli channel, but that means that sometimes
+it is not the most straightforward algorithm to simulate a Pauli channel.
+However, the main advantage is that if we want 
+to simulate many Pauli channels (for example,
+for simulating a Pauli dynamical map as we will see later),
+we only have to change a couple of angles in the circuit and
+not completely reconstruct it. 
+And as we will see, sometimes only changing
+one angle in the circuit will be enough.}
 
 {\color{green}
-\subsection{Two-qubit Pauli channels}
+\subsection{Simulation of a two-qubit Pauli channel}
 \tbnote{Voy a agregar toda esta sección sobre el circuito para dos qubits}
@@
 the circuit of \fref{Fig1} would have two principal
-qubits and $2N$ ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
+qubits and four ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
 However, the number of ancilla qubits can be reduced for Pauli 
@@
 \begin{align}
-\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  (\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  (\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
+\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  \dfrac{p}{3}(\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  \dfrac{p}{3}(\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
 \label{2qbit-c}
@@
 matrix by doing quantum process tomography on
-the two principal qubits. Then, we calculated the diamond fidelity for different values of $p$ and
+the principal qubits. Then, we calculated the diamond fidelity for different values of $p$ and
 obtained the results shown in \fref{2qbit}b).
@@
 and $R$ is a rotation applied to one qubit.
-From theorem 1, we conclude that $R$ can be taken in general as a $\sigma_3$ rotation of angle $2s(p)$ applied to the last qubit and controlled by some of the other ones. 
-To prove the result, we will apply $U(p)$ to $|j\rangle$ by first applying $B$,
+From theorem 1, we conclude that $R$ can be taken in general as a $\sigma_3$
+rotation of angle $2s(p)$ applied to the last qubit and controlled by some of the other ones.
+Given  this, to prove the result of this theorem,
+we will apply $U(p)$ to $|j\rangle$ by first applying $B$,
 then $R_{\sigma_3}(2s(p))$ and finally $A$, with
@@
 \tbnote{Reescribí la oración anterior para no decir que es una definición,
-sino que queda algo de libertad (aunque igual lo decía después de la ecuación}
+sino que queda algo de libertad (aunque igual lo decía después de la ecuación)}
 \begin{align}
@@
 To see that $A R_{\sigma_3}(s(p)) B |0\rangle$ in fact creates
-the curve of states described in \eref{eq:curve-states}, \revnote{to see what?} \tbnote{Ya cambié la oración anterior} we can rewrite the expression of $B|0\rangle$ by 
+the curve of states described in \eref{eq:curve-states}, \revnote{to see what?} \tbnote{Ya cambié la oración anterior, pero siento que queda redundante.
+Creo que como estaba antes ``to see it'', era suficiente.} we can rewrite the expression of $B|0\rangle$ by
 separating the first $N-1$ qubits from the last one:
@@
       + \dfrac{i}{2\sqrt{3}} |2\rangle + \dfrac{i}{2\sqrt{3}} |3 \rangle \right) \\
-\equiv & e^{is} |a\rangle + e^{-is} |b\rangle
+\equiv &\; e^{is} |a\rangle + e^{-is} |b\rangle
 \end{align*}
@@
 
-Now, defining $A$ and $B$ as in  \eref{eq:BA} for the particular
+The circuit requires defining $A$ and $B$ as in  \eref{eq:BA}, and for the particular
 vectors $|a\rangle, |b\rangle, |c \rangle$ of this dynamical map, we have that
@@
 -\sqrt{2/3} & 0 & i/\sqrt{6} & -i/\sqrt{6}
-\end{pmatrix} \; , \; B = \begin{pmatrix}
+\end{pmatrix} , \; B = \begin{pmatrix}
 0 & 0 & 0& 1 \\
@@
 1/\sqrt{2} & 1/\sqrt{2} & 0 & 0 
-\end{pmatrix}
+\end{pmatrix},
 \end{align*}
-where the first column of $A$ and the
+where, as mentioned before, the first column of $A$ and the
 last three of $B$ can be chosen arbitrarily as long as the resultant matrices are unitary. 
 We ran this circuit in IBM's quantum computer ibmq-lima for $25$ different values of $p$ between $0$ and $1$,
-and $20$ repetitions for each value of $p$.
+with $20$ repetitions for each value of $p$.
 The diamond fidelity was calculated in each case and is shown in \fref{fid}.
@@
 & + e^{-is}  \left( \dfrac{-i}{4} |0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle + \dfrac{i}{4} |3\rangle \right) \\
-& := |c\rangle + e^{is} |a\rangle + e^{-is} |b\rangle,
+\equiv & \; |c\rangle + e^{is} |a\rangle + e^{-is} |b\rangle,
 \end{align*}
@@
 0 & 1/\sqrt{2} & i/2 & -i/2
-\end{pmatrix} \\
+\end{pmatrix},
 B = \begin{pmatrix}
@@
 As before, we ran this circuit for $25$ values of $p$ between $0$ and $1$, with $20$ repetitions for each,
-obtaining as a result the fidelities shown in \fref{FigS2q}.
+obtaining as a result the fidelities shown in \fref{fid}.
 
@@
 Matrices $A$ and $B$ can be obtained as for the other
-dynamical maps and the we ran the resulting circuit in ibmq-lima with the same
-specifications as for the other examples
-and the results are shown in \fref{FigS2q}.
+dynamical maps and we ran the resulting circuit in ibmq-lima with the same
+specifications as for the other examples,
+with the results are shown in \fref{fid}.
 %Note that in this case we actually only need one ancilla qubit
@@
 The implementation was done on IBM's ibmq-lima quantum computer.
-We can see that just as in \fref{Fig3}, fidelities are high for points close to the depolarizing channel 
-($p=1$ for depolarizing map, $p=1/2$ for parabolic map) and lower for points close
-to unitary channels ($p=0$ for all maps and $p=1$ for parabolic and bit flip).
 Furthermore, we can see that the fidelities are comparable to those of \fref{Fig3}, so that using the 1PR circuit
@@
 }
+
+From the results of \fref{fid}, we can see that just as in figure 
+\fref{Fig3}, fidelities are high for points close to the depolarizing channel 
+($p=1$ for depolarizing map, $p=1/2$ for parabolic map) and lower for points close
+to unitary channels ($p=0$ for all maps and $p=1$ for parabolic and bit flip).
+Furthermore, we can see that the actual values of the fidelities are comparable
+to those of \fref{Fig3}, which means that
+using the 1PR circuit as opposed to 
+implementing each channel with \fref{Fig2}
+does not considerably affect fidelity.
 

### 2023-09-20 main.tex
Update main.tex

@@
 La verdad no sé bien cómo contestar a este comentario. \\
-Una forma podría ser haciendo más énfasis en lo de circuitos 1PR
-y que lo de canales de Pauli sea como un ejemplo particular de cómo se puede usar eso. Claro que eso significaría cambiar demasiado el artículo
- (hasta habría que cambiar el título ) y no sé si eso sea factible. Quizá se puede hacer
- más énfasis en lo de 1PR sin cambiar taaanto el orden del artículo\\
-Igual la verdad que estoy perdido con qué contestar a este artículo}
+Una forma podria ser cambiar un poco el enfoque. 
+Hacer que el objetivo principal sea
+simular un mapa dinámico (en lugar de simular canales de Pauli asi nada mas)  y estudiar como entra el parámetro en juego. 
+Podemos decir que aunque en general se ha hecho mucha simulación cuántica, 
+no se le ha dado mucho enfoque a operaciones parametrizadas.\\
+Luego, decir que para simular mapas parametrizados de Pauli,
+necesitamos empezar con un algortimo para canales y que funcione para cualquier canal de Pauli.
+Al ser tan general, no es perfecto, pues varios canales se podrian hacer más fácil, 
+pero lo bueno es que es un mismo algorigmo para todos, lo que 
+nos va a permitir usarlo para canales parametrizados, ya que entonces sólo habrá que
+mover un parámetro, en vez de cambiar todo el algoritmo para pasar de un canal a otro.\\
+Luego, generalizamos el circuito para ahora sí hacerlo en mapas dinámicos y vemos qué onda con lo de 
+poder reducir el número de parámetros, con lo que
+llegamos al teorema de los circuitos 1PR y etc.
+También corremos el circuito en compus cuánticas,
+lo que ayuda a ver que haber modificado el circuito para que tenga un sólo parámetro
+(hacer lo de meter las matrices A y B), no afectó mucho la fidelidad.
+Observar cómo se afecta o no la fidelidad al hacer eso puede ser una motivación de
+haber usado compus cuanticas. \\
+Al final, también recalcar que el resutlado sobre 1PR es más
+general que solo canales de Pauli y puede ser útil
+para cualquier curcuito parametrizado.}
 

### 2023-09-27 main.tex
Revision

@@
 llegamos al teorema de los circuitos 1PR y etc.
-También corremos el circuito en compus cuánticas,
+También corremos el circuito en computadoras cuánticas,
 lo que ayuda a ver que haber modificado el circuito para que tenga un sólo parámetro

### 2023-09-27 main.tex
fig 4 y 8

@@
 \caption{
-{\bf Fidelitis for dynamical maps.} Results of the fidelities obtained when simulating the three dynamical maps considered (depolarizing, parabolic and bit flip). 
+{\bf Fidelities for dynamical maps.} Results of the fidelities obtained when simulating the three dynamical maps considered (depolarizing, parabolic and bit flip). 
 The implementation was done on IBM's ibmq-lima quantum computer.

### 2023-10-10 main.tex
Update main.tex

@@
 % }}}
+
+\tbnote{Propuesta haciendo unos cambios de enfoque que menciono en la intro:}\\
+$\;$ \\
+
+{\color{green}
+Pauli channels are fundamental in the context of quantum computing as they
+model the simplest kind of noise in quantum devices, and
+Pauli dynamical maps are parametrized Pauli channels,
+which can model a continuous transformation of a quantum device.
+In this article, we propose a quantum
+algorithm for simulating
+Pauli dynamical maps
+by using a parametrized quantum circuit.
+We also establish the mathematical conditions for an
+$N$-qubit transformation to be achievable using a parametrized circuit where
+only one single-qubit operation depends on the parameter. 
+The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
+for the case of one qubit, and the fidelity of this implementation is reported. 
+}
 \section{Introduction} % {{{
@@
 circuits~\cite{Rasmussen}.  \\
-
-\revnote{I fail to see the point here - the logic of the paper is: 
-1."open quantum systems can be modeled through a class of channels representing he various types of decoherence.
-2.
-Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible.
-3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them. \\
-What I am missing is what do we learn by doing it which can't be learned by actually performing the Pauli channel onto a quantum system?
-For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial.
-Why would I need to decompose (not even effectively for any channel) the Pauli channels to match a gate based description?
-Which class of problems can we simulate that cannot be simulated otherwise?
-Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)\\
-Intuitively, it seems incredibly harder resource wise to create the sum $b|gamma\rangle$ superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.}
-
-\tbnote{Entiendo que su punto es que los canales de Pauli se podrían hacer de una forma
-similar pero en lugar de usar los qubits de ancilla para crear las probabilidades, crearlas
-de otra forma que sea mejor y que entonces no tiene mucho sentido el artículo.  \\
-La verdad no sé bien cómo contestar a este comentario. \\
-Una forma podria ser cambiar un poco el enfoque. 
-Hacer que el objetivo principal sea
-simular un mapa dinámico (en lugar de simular canales de Pauli asi nada mas)  y estudiar como entra el parámetro en juego. 
-Podemos decir que aunque en general se ha hecho mucha simulación cuántica, 
-no se le ha dado mucho enfoque a operaciones parametrizadas.\\
-Luego, decir que para simular mapas parametrizados de Pauli,
-necesitamos empezar con un algortimo para canales y que funcione para cualquier canal de Pauli.
-Al ser tan general, no es perfecto, pues varios canales se podrian hacer más fácil, 
-pero lo bueno es que es un mismo algorigmo para todos, lo que 
-nos va a permitir usarlo para canales parametrizados, ya que entonces sólo habrá que
-mover un parámetro, en vez de cambiar todo el algoritmo para pasar de un canal a otro.\\
-Luego, generalizamos el circuito para ahora sí hacerlo en mapas dinámicos y vemos qué onda con lo de 
-poder reducir el número de parámetros, con lo que
-llegamos al teorema de los circuitos 1PR y etc.
-También corremos el circuito en computadoras cuánticas,
-lo que ayuda a ver que haber modificado el circuito para que tenga un sólo parámetro
-(hacer lo de meter las matrices A y B), no afectó mucho la fidelidad.
-Observar cómo se afecta o no la fidelidad al hacer eso puede ser una motivación de
-haber usado compus cuanticas. \\
-Al final, también recalcar que el resutlado sobre 1PR es más
-general que solo canales de Pauli y puede ser útil
-para cualquier curcuito parametrizado.}
 
@@
 dynamical maps that fulfill the conditions of theorem \ref{theorem2}.
+
+\revnote{I fail to see the point here - the logic of the paper is: 
+1."open quantum systems can be modeled through a class of channels representing he various types of decoherence.
+2.
+Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible.
+3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them. \\
+What I am missing is what do we learn by doing it which can't be learned by actually performing the Pauli channel onto a quantum system?
+For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial.
+Why would I need to decompose (not even effectively for any channel) the Pauli channels to match a gate based description?
+Which class of problems can we simulate that cannot be simulated otherwise?
+Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)\\
+Intuitively, it seems incredibly harder resource wise to create the sum $b|gamma\rangle$ superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.}
+
+\tbnote{Entiendo que su punto es que los canales de Pauli se podrían hacer de una forma
+similar pero en lugar de usar los qubits de ancilla para crear las probabilidades, crearlas
+de otra forma que sea mejor y que entonces no tiene mucho sentido el artículo.  \\
+La verdad no sé bien cómo contestar a este comentario. \\
+Una forma podria ser cambiar un poco el enfoque. 
+Hacer que el objetivo principal sea
+simular un mapa dinámico (en lugar de simular canales de Pauli asi nada mas)  y estudiar como entra el parámetro en juego. 
+Luego, decir que para simular mapas parametrizados de Pauli,
+necesitamos empezar con un algortimo para canales y que funcione para cualquier canal de Pauli.
+Al ser tan general, no es perfecto, pues varios canales se podrian hacer más fácil, 
+pero lo bueno es que es un mismo algorigmo para todos, lo que 
+nos va a permitir usarlo para canales parametrizados, ya que entonces sólo habrá que
+mover un parámetro, en vez de cambiar todo el algoritmo para pasar de un canal a otro.\\
+Luego, generalizamos el circuito para ahora sí hacerlo en mapas dinámicos y vemos qué onda con lo de 
+poder reducir el número de parámetros, con lo que
+llegamos al teorema de los circuitos 1PR y etc.
+También corremos el circuito en computadoras cuánticas,
+lo que ayuda a ver que haber modificado el circuito para que tenga un sólo parámetro
+(hacer lo de meter las matrices A y B), no afectó mucho la fidelidad.
+Observar cómo se afecta o no la fidelidad al hacer eso puede ser una motivación de
+haber usado compus cuanticas. \\
+Al final, también recalcar que el resutlado sobre 1PR es más
+general que solo canales de Pauli y puede ser útil
+para cualquier curcuito parametrizado.} \\
+$\;$ \\
+Ahora sí la nueva propuesta de la intro (los primeros dos párrafos son iguales): \\
+$\;$ \\
+{\color{green}
+
+Since their inception, quantum computers were proposed as powerful tools for
+the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
+quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
+practical~\cite{breuer2007theory} interest, there has been efforts towards the
+simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
+and specifically for quantum channels~\cite{Xin,Wei,Zanetti}.
+Such quantum algorithms can be represented using what is known as a quantum
+circuit~\cite{chuangbook}, which we will study in section \ref{sec: Circuit for a Pauli Channel}.
+
+Such systems have been simulated because of their many applications, 
+such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
+studying dissipative processes~\cite{Barreiro}
+and modeling non-Markovian dynamics~\cite{Marsden}.
+Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
+and within them, the simplest class of channels that produce decoherence are
+Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
+effective models for the noise affecting quantum devices~\cite{Flammia}.
+
+To represent the algorithms implemented in quantum computers, either to
+simulate a physical system or for some other purpose, one often uses a quantum
+circuit~\cite{chuangbook}.
+
+However, in this article, our main goal is not to implement Pauli channels, but to study and implement Pauli dynamical maps, which are continuous parametrized curves of Pauli channels. 
+These maps can be used to model continuous change of a qubit instead of only discrete jumps.
+Implementing these maps will lead us to study  quantum algorithms with free parameters, 
+something that is common in areas such as quantum machine learning~\cite{Benedetti}.
+This can be done using parametrized quantum circuits, which consist of quantum circuits in which one or more operations depend on a free parameter. \\
+
+Our study of such circuits for the use of simulating Pauli dynamical maps will lead 
+us to theorem 2, in which we find general condition for any parametrized
+transformation (for example, a Pauli dynamical map) to be achievable on a quantum circuit 
+with only one single-qubit rotation dependent on the parameter.
+Said parameter is in some sense a knob that we can control to continuously perform the transformation by
+only having to move one number. \\
+
+We start the article by providing the definition of quantum channels, the general framework
+used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
+Then, since our main objective is to obtain a parametrized circuit for Pauli dynamical maps, we will first need a 
+circuit that can implement any Pauli channel by only changing some parameters
+in the quantum gates and without changing the design of the circuit itself.
+Therefore, in section\ref{sec: Circuit
+for a Pauli Channel} we present such a circuit
+and we also show its implementation using IBM's quantum computers for the particular case of single-qubit Pauli channels and some two-qubit ones.
+In section \ref{sec: 1PR Circuits}, we adapt the algorithm to dynamical maps.
+Then we aim to simplify the algorithm so that it only contains one parametrized single-qubit rotation, 
+and in the process we contribute to the work in parametrized quantum circuits by establishing   in
+\ref{theorem2} which general quantum transformations
+can be implemented this way.
+Finally, in
+section \ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
+dynamical maps that fulfill the conditions of theorem \ref{theorem2}. 
+}
 
@@
 \revnote{At this point I am missing a proper definition of a "quantum circuit" consistent with the mathematical formalism.
-The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \tbnote{Agregué algo abajo}
+The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \tbnote{Agregué algo abajo:}\\
 
@@
 and then the principal qubits are measured.
+
+We will create a general circuit that can implement any $N$-qubit Pauli channel
+by only changing some parameters and not changing the design of the circuit itself.
+This is done with the intent of converting it into a parametrized circuit for dynamical maps in the next section.
 }
@@
 And as we will see, sometimes only changing
-one angle in the circuit will be enough.}
+one angle in the circuit will be enough.}\\
+$\;$\\
+
+\tbnote{Sección que agregué:}\\
 
@@
 
-Just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
-of \fref{Fig1}. However, there is one difference: 
+{\color{green}
+Finally, we move to the main goal of this article, which is 
+simulating Pauli dynamical maps.
+This is pretty much already solved, since
+just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
+of \fref{Fig1}.} However, there is one difference: 
 the state to be created on the ancilla qubits now 
@@
 generalized it to Pauli dynamical maps
-by using parametrized quantum circuits \revnote{imprecise}.
+by using parametrized quantum circuits \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise}.
 Furthermore, we implemented single-qubit Pauli channels
@@
 can be applied to any quantum algorithm that requires parametrized circuits,
-such as those used for quantum machine learning. \revnote{citation required here}
+such as those used for quantum machine learning~\cite{Benedetti}.
 

### 2023-10-17 main.tex
increased loading time by a bit

@@
 % Use "Eq" instead of "Equation" for equation citations.
-% }}}
 
@@
 }
+% }}}
 \section{Introduction} % {{{
@@
 and specifically for quantum channels~\cite{Xin,Wei,Zanetti}.
+Such quantum algorithms can be represented using what is known as a quantum
+circuit~\cite{chuangbook}, which we will study in section \ref{sec: Circuit for a Pauli Channel}.
 
@@
 
-\revnote{I fail to see the point here - the logic of the paper is: 
-1."open quantum systems can be modeled through a class of channels representing he various types of decoherence.
-2.
-Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible.
-3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them. \\
-What I am missing is what do we learn by doing it which can't be learned by actually performing the Pauli channel onto a quantum system?
-For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial.
-Why would I need to decompose (not even effectively for any channel) the Pauli channels to match a gate based description?
-Which class of problems can we simulate that cannot be simulated otherwise?
-Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)\\
-Intuitively, it seems incredibly harder resource wise to create the sum $b|gamma\rangle$ superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.}
-
-\tbnote{Entiendo que su punto es que los canales de Pauli se podrían hacer de una forma
+\revnote{I fail to see the point here - the logic of the paper is: % {{{
+1."open quantum systems can be modeled through a class of channels representing
+he various types of decoherence. 2. Quantum circuits are a convenient
+gate-based formalism that is well understood and has an extensive body of work,
+and experimentally accessible.  3. We map (generalised) Pauli channels onto
+quantum circuits, as a way to simulate them. \\
+What I am missing is what do we learn by doing it which can't be learned by
+actually performing the Pauli channel onto a quantum system? For example,
+applying well controlled sx, sy, sz operations and their coherent parametric
+combination using a photonic polarisation or path encoding is experimentally
+trivial. Why would I need to decompose (not even effectively for any channel)
+the Pauli channels to match a gate based description? Which class of problems
+can we simulate that cannot be simulated otherwise? Is there any advantage (for
+example in speed up, resources like ancillas required, resistance to unwanted
+noise etc..?)\\
+Intuitively, it seems incredibly harder resource wise to create the sum
+$b|gamma\rangle$ superposition state needed for the ancilla, just for the sake
+of having it into a "quantum circuit" perspective.} % }}}
+\tbnote{Entiendo que su punto es que los canales de Pauli se podrían hacer de una forma % {{{
 similar pero en lugar de usar los qubits de ancilla para crear las probabilidades, crearlas
@@
 Hacer que el objetivo principal sea
-simular un mapa dinámico (en lugar de simular canales de Pauli asi nada mas)  y estudiar como entra el parámetro en juego. 
+simular un mapa dinámico (en lugar de simular canales de Pauli asi nada mas)  y
+estudiar como entra el parámetro en juego. 
 Luego, decir que para simular mapas parametrizados de Pauli,
@@
 general que solo canales de Pauli y puede ser útil
-para cualquier curcuito parametrizado.} \\
-$\;$ \\
+para cualquier curcuito parametrizado.} % }}}
+
 Ahora sí la nueva propuesta de la intro (los primeros dos párrafos son iguales): \\
@@
 {\color{green}
-
-Since their inception, quantum computers were proposed as powerful tools for
-the simulation of quantum systems~\cite{feynman1982simulating}.  Being open
-quantum systems of fundamental~\cite{Zur91,RevModPhys.76.1267} and
-practical~\cite{breuer2007theory} interest, there has been efforts towards the
-simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
-and specifically for quantum channels~\cite{Xin,Wei,Zanetti}.
-Such quantum algorithms can be represented using what is known as a quantum
-circuit~\cite{chuangbook}, which we will study in section \ref{sec: Circuit for a Pauli Channel}.
 

### 2023-10-19 main.tex
last minute fixes.

@@
 
+*****************************************************************
+*****************************************************************
+*****************************************************************
 To represent the algorithms implemented in quantum computers, either to
@@
 
+To represent the algorithms implemented in quantum computers, either to
+simulate a physical system or for some other purpose, one often uses a quantum
+circuit~\cite{chuangbook}.
+
+However, in this article, our main goal is not to implement Pauli channels, but to study and implement Pauli dynamical maps, which are continuous parametrized curves of Pauli channels. 
+These maps can be used to model continuous change of a qubit instead of only discrete jumps.
+Implementing these maps will lead us to study  quantum algorithms with free parameters, 
+something that is common in areas such as quantum machine learning~\cite{Benedetti}.
+This can be done using parametrized quantum circuits, which consist of quantum circuits in which one or more operations depend on a free parameter. \\
+
+Our study of such circuits for the use of simulating Pauli dynamical maps will lead 
+us to theorem 2, in which we find general condition for any parametrized
+transformation (for example, a Pauli dynamical map) to be achievable on a quantum circuit 
+with only one single-qubit rotation dependent on the parameter.
+Said parameter is in some sense a knob that we can control to continuously perform the transformation by
+only having to move one number. \\
+
+*****************************************************************
+*****************************************************************
+*****************************************************************
 We start by providing the definition of quantum channels, the general framework
@@
 
-Such systems have been simulated because of their many applications, 
-such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
-studying dissipative processes~\cite{Barreiro}
-and modeling non-Markovian dynamics~\cite{Marsden}.
-Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
-and within them, the simplest class of channels that produce decoherence are
-Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
-effective models for the noise affecting quantum devices~\cite{Flammia}.
-
-To represent the algorithms implemented in quantum computers, either to
-simulate a physical system or for some other purpose, one often uses a quantum
-circuit~\cite{chuangbook}.
-
-However, in this article, our main goal is not to implement Pauli channels, but to study and implement Pauli dynamical maps, which are continuous parametrized curves of Pauli channels. 
-These maps can be used to model continuous change of a qubit instead of only discrete jumps.
-Implementing these maps will lead us to study  quantum algorithms with free parameters, 
-something that is common in areas such as quantum machine learning~\cite{Benedetti}.
-This can be done using parametrized quantum circuits, which consist of quantum circuits in which one or more operations depend on a free parameter. \\
-
-Our study of such circuits for the use of simulating Pauli dynamical maps will lead 
-us to theorem 2, in which we find general condition for any parametrized
-transformation (for example, a Pauli dynamical map) to be achievable on a quantum circuit 
-with only one single-qubit rotation dependent on the parameter.
-Said parameter is in some sense a knob that we can control to continuously perform the transformation by
-only having to move one number. \\
-
 We start the article by providing the definition of quantum channels, the general framework

### 2023-10-19 main.tex
Improvements

--- 2023-10-17 main.tex
@@
 % line numbers
-\usepackage[right]{lineno}
+\usepackage[mathlines]{lineno}  \linenumbers \setlength\linenumbersep{3pt}
 
@@
 research has been devoted to enhancing the efficiency of these
-circuits~\cite{Rasmussen}.  \\
-
+circuits~\cite{Rasmussen}.
+
+\cpnote{Iteara de nuevo Tomas:
+However, in this article, our main goal is not to implement Pauli channels, but to study and implement Pauli dynamical maps, which are continuous parametrized curves of Pauli channels. 
+These maps can be used to model continuous change of a qubit instead of only discrete jumps.
+Implementing these maps will lead us to study  quantum algorithms with free parameters, 
+something that is common in areas such as quantum machine learning~\cite{Benedetti}.
+This can be done using parametrized quantum circuits, which consist of quantum
+circuits in which one or more operations depend on a free parameter. }
+
+\cpnote{Porfa mete esto en el parrafo donde va la estructura:
+Our study of such circuits for the use of simulating Pauli dynamical maps will
+lead us to theorem 2, in which we find general condition for any parametrized
+transformation (for example, a Pauli dynamical map) to be achievable on a
+quantum circuit with only one single-qubit rotation dependent on the parameter.
+Said parameter is in some sense a knob that we can control to continuously
+perform the transformation by only having to move one number. }
+
+\cpnote{dejar solo un parrafo de estructura}
 We start by providing the definition of quantum channels, the general framework
@@
 for channels to dynamical maps.  Furthermore, we contribute to the body of work
-related to parametrized quantum circuits by establishing a theorem,
-which  sets the mathematical conditions for the transformations
-that can be done using a parametrized circuit with the restriction that only a
-controlled single-qubit
-rotation in the circuit may depend on the parameter.  Finally, in
-section \ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
+related to parametrized quantum circuits by establishing a theorem, which  sets
+the mathematical conditions for the transformations that can be done using a
+parametrized circuit with the restriction that only a controlled single-qubit
+rotation in the circuit may depend on the parameter.  Finally, in section
+\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
+dynamical maps that fulfill the conditions of theorem \ref{theorem2}.
+
+We start the article by providing the definition of quantum channels, the
+general framework used here, and multi-qubit Pauli channels in section
+\ref{sec: Pauli Channels}.  Then, since our main objective is to obtain a
+parametrized circuit for Pauli dynamical maps, we will first need a circuit
+that can implement any Pauli channel by only changing some parameters in the
+quantum gates and without changing the design of the circuit itself.
+Therefore, in section\ref{sec: Circuit for a Pauli Channel} we present such a
+circuit and we also show its implementation using IBM's quantum computers for
+the particular case of single-qubit Pauli channels and some two-qubit ones.  In
+section \ref{sec: 1PR Circuits}, we adapt the algorithm to dynamical maps.
+Then we aim to simplify the algorithm so that it only contains one parametrized
+single-qubit rotation, and in the process we contribute to the work in
+parametrized quantum circuits by establishing   in \ref{theorem2} which general
+quantum transformations can be implemented this way.  Finally, in section
+\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
 dynamical maps that fulfill the conditions of theorem \ref{theorem2}.
@@
 of having it into a "quantum circuit" perspective.} % }}}
-\tbnote{Entiendo que su punto es que los canales de Pauli se podrían hacer de una forma % {{{
-similar pero en lugar de usar los qubits de ancilla para crear las probabilidades, crearlas
-de otra forma que sea mejor y que entonces no tiene mucho sentido el artículo.  \\
-La verdad no sé bien cómo contestar a este comentario. \\
-Una forma podria ser cambiar un poco el enfoque. 
-Hacer que el objetivo principal sea
-simular un mapa dinámico (en lugar de simular canales de Pauli asi nada mas)  y
-estudiar como entra el parámetro en juego. 
-Luego, decir que para simular mapas parametrizados de Pauli,
-necesitamos empezar con un algortimo para canales y que funcione para cualquier canal de Pauli.
-Al ser tan general, no es perfecto, pues varios canales se podrian hacer más fácil, 
-pero lo bueno es que es un mismo algorigmo para todos, lo que 
-nos va a permitir usarlo para canales parametrizados, ya que entonces sólo habrá que
-mover un parámetro, en vez de cambiar todo el algoritmo para pasar de un canal a otro.\\
-Luego, generalizamos el circuito para ahora sí hacerlo en mapas dinámicos y vemos qué onda con lo de 
-poder reducir el número de parámetros, con lo que
-llegamos al teorema de los circuitos 1PR y etc.
-También corremos el circuito en computadoras cuánticas,
-lo que ayuda a ver que haber modificado el circuito para que tenga un sólo parámetro
-(hacer lo de meter las matrices A y B), no afectó mucho la fidelidad.
-Observar cómo se afecta o no la fidelidad al hacer eso puede ser una motivación de
-haber usado compus cuanticas. \\
-Al final, también recalcar que el resutlado sobre 1PR es más
-general que solo canales de Pauli y puede ser útil
-para cualquier curcuito parametrizado.} % }}}
-
-Ahora sí la nueva propuesta de la intro (los primeros dos párrafos son iguales): \\
-$\;$ \\
-{\color{green}
-
-Such systems have been simulated because of their many applications, 
-such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
-studying dissipative processes~\cite{Barreiro}
-and modeling non-Markovian dynamics~\cite{Marsden}.
-Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
-and within them, the simplest class of channels that produce decoherence are
-Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
-effective models for the noise affecting quantum devices~\cite{Flammia}.
-
-To represent the algorithms implemented in quantum computers, either to
-simulate a physical system or for some other purpose, one often uses a quantum
-circuit~\cite{chuangbook}.
-
-However, in this article, our main goal is not to implement Pauli channels, but to study and implement Pauli dynamical maps, which are continuous parametrized curves of Pauli channels. 
-These maps can be used to model continuous change of a qubit instead of only discrete jumps.
-Implementing these maps will lead us to study  quantum algorithms with free parameters, 
-something that is common in areas such as quantum machine learning~\cite{Benedetti}.
-This can be done using parametrized quantum circuits, which consist of quantum circuits in which one or more operations depend on a free parameter. \\
-
-Our study of such circuits for the use of simulating Pauli dynamical maps will lead 
-us to theorem 2, in which we find general condition for any parametrized
-transformation (for example, a Pauli dynamical map) to be achievable on a quantum circuit 
-with only one single-qubit rotation dependent on the parameter.
-Said parameter is in some sense a knob that we can control to continuously perform the transformation by
-only having to move one number. \\
-
-We start the article by providing the definition of quantum channels, the general framework
-used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
-Then, since our main objective is to obtain a parametrized circuit for Pauli dynamical maps, we will first need a 
-circuit that can implement any Pauli channel by only changing some parameters
-in the quantum gates and without changing the design of the circuit itself.
-Therefore, in section\ref{sec: Circuit
-for a Pauli Channel} we present such a circuit
-and we also show its implementation using IBM's quantum computers for the particular case of single-qubit Pauli channels and some two-qubit ones.
-In section \ref{sec: 1PR Circuits}, we adapt the algorithm to dynamical maps.
-Then we aim to simplify the algorithm so that it only contains one parametrized single-qubit rotation, 
-and in the process we contribute to the work in parametrized quantum circuits by establishing   in
-\ref{theorem2} which general quantum transformations
-can be implemented this way.
-Finally, in
-section \ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
-dynamical maps that fulfill the conditions of theorem \ref{theorem2}. 
-}
 
@@
 \mathcal{E}(\rho) = \dfrac{1}{2}\sum_{\gamma,\alpha=0}^3 k_{\gamma} r_{\alpha} \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}.
+\label{eq:Edepol}
 \end{equation}
-This can be simplified by using the following property of Pauli matrices:
-\revnote{Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.}
-
-\tbnote{Siguiendo la relaci\'on de conmutaci\'on, resulta que las Levi Civitas desaparecen y quedan s\'olo deltas de Dirac:}
-{\color{green}
-\begin{equation*}
-\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\;\; \text{with} \; A_{\alpha, \gamma} = (2\delta_{ij}-1)(2\delta_{i0}-1)(2\delta_{j0}-1)
-\end{equation*}
-}
-
+This can be simplified noting that 
 \begin{equation}
-\label{eq: propiedad-pauli}
 \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A = \begin{pmatrix}
@@
 \end{equation}
-which leads to
+which was obtained following the 
+commutation relation of Pauli matrices $[\sigma_\alpha,\sigma_\beta] = 2 i
+\epsilon_{\alpha \beta \gamma} \sigma_\gamma$ and $\epsilon_{\alpha \beta \gamma} \sigma_\gamma$ is 
+the Levi-Civita tensor. Then, \eref{eq:Edepol} takes the form
+% 
+% 
+% 
+% 
+% This can be simplified by using the following property of Pauli matrices:
+% \revnote{Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.}
+% 
+% 
+% \tbnote{Siguiendo la relaci\'on de conmutaci\'on, resulta que las Levi Civitas desaparecen y quedan s\'olo deltas de Dirac:}
+% {\color{green}
+% \begin{equation*}
+% \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\;\; \text{with} \; A_{\alpha, \gamma} = (2\delta_{ij}-1)(2\delta_{i0}-1)(2\delta_{j0}-1)
+% \end{equation*}
+% }
+% 
+% 
+% \begin{equation}
+% \label{eq: propiedad-pauli}
+% \sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma} = A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\; \text{with} \; A = \begin{pmatrix}
+% 1 & 1 & 1 & 1\\
+% 1 & 1 & -1 &-1 \\
+% 1 & -1 & 1 & -1 \\
+% 1 & -1 & -1 & 1
+% \end{pmatrix},
+% \end{equation}
+% which leads to
 \begin{equation}
@@
 
+\revnote{At this point I am missing a proper definition of a "quantum circuit"
+consistent with the mathematical formalism. The authors start from the very
+basic regarding Pauli channels, but give for granted the quantum circuit
+formalism.}
+
 In this section we propose a quantum circuit that simulates $N$-qubit Pauli
 channels. 
-\revnote{At this point I am missing a proper definition of a "quantum circuit" consistent with the mathematical formalism.
-The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \tbnote{Agregué algo abajo:}\\
-
-{\color{green} A quantum circuit is a model for representing computation on a quantum system. 
+A quantum circuit is a model for representing computation on a quantum system. 
 This computation may include preparing the initial state of the system, applying unitary operations and measuring the whole system or parts of it~\cite{Rieffel}.
-
-Our systems always consists of some number of qubits,
-that can be divided into the ones to which we will apply the quantum channel,
- or ``principal qubits'' and the ones that help us complete said operation, or ``ancilla qubits''.
-The circuit implements a unitary operator $U$ on the 
-system consisting of all the qubits 
-and then the principal qubits are measured.
-
-We will create a general circuit that can implement any $N$-qubit Pauli channel
-by only changing some parameters and not changing the design of the circuit itself.
-This is done with the intent of converting it into a parametrized circuit for dynamical maps in the next section.
-}
-
+Our systems always consists of some number of qubits, that can be divided into
+the ones to which we will apply the quantum channel, or ``main qubits''
+and the ones that help us complete said operation, or ``ancilla qubits''.
+The circuit implements a unitary operator $U$ on the system consisting of all
+the qubits and then the effect on the main qubits is measured. 
 Moreover, we implement the circuit for $N=1$ on a quantum computer
@@
 We find that close to the depolarizing channel, the general circuit simulator 
-can implement such channels with the highest fidelity.  \\
+can implement such channels with the highest fidelity.
 
@@
 
-{\color{green}
-Finally, we move to the main goal of this article, which is 
-simulating Pauli dynamical maps.
+% {\color{green}
+% Finally, we move to the main goal of this article, which is 
+% simulating Pauli dynamical maps.
+% 
+Finally, we consider the simulation of 
+Pauli dynamical maps.
+% 
 This is pretty much already solved, since
 just as Pauli channels, Pauli dynamical maps can be implemented using the circuit
-of \fref{Fig1}.} However, there is one difference: 
+of \fref{Fig1}. However, there is one difference: 
 the state to be created on the ancilla qubits now 

### 2023-10-19 main.tex
.

@@
 (where $\mathbb{I}_n$ is the $n\times n$ identity matrix).  This ensures that
-even if the principal system is entangled with another system, applying
-$\mathcal{E}$ to the principal system while doing nothing to the other one
-still results in  a positive semidefinite state for the principal
+even if the main system is entangled with another system, applying
+$\mathcal{E}$ to the main system while doing nothing to the other one
+still results in  a positive semidefinite state for the main
 system~\cite{chuangbook}.
@@
 commutation relation of Pauli matrices $[\sigma_\alpha,\sigma_\beta] = 2 i
-\epsilon_{\alpha \beta \gamma} \sigma_\gamma$ and $\epsilon_{\alpha \beta \gamma} \sigma_\gamma$ is 
+\epsilon_{\alpha \beta \gamma} \sigma_\gamma$ and $\epsilon_{\alpha \beta \gamma}$ is 
 the Levi-Civita tensor. Then, \eref{eq:Edepol} takes the form
@@
 \end{equation}
-\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix} \revnote{eq 2} \tbnote{No, sí es la eq 1}
+\eref{eq: rho-transformada} once again has the form of \eref{eq: Density Matrix}
 but with components $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.
@@
 
-\revnote{At this point I am missing a proper definition of a "quantum circuit"
-consistent with the mathematical formalism. The authors start from the very
-basic regarding Pauli channels, but give for granted the quantum circuit
-formalism.}
-
 In this section we propose a quantum circuit that simulates $N$-qubit Pauli
@@
 Our systems always consists of some number of qubits, that can be divided into
-the ones to which we will apply the quantum channel, or ``main qubits''
-and the ones that help us complete said operation, or ``ancilla qubits''.
+the ones to which we will apply the quantum channel, or main qubits
+and the ones that help us complete said operation, or ancilla qubits.
 The circuit implements a unitary operator $U$ on the system consisting of all
@@
 channels have much lower $f$. \revnote{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise. } 
-\tbnote{La respuesta a esto puede incluir lo siguiente: 
-It works better for depolarizing channels, yes, but still has considerably big zone with high fidelity.}
+\tbnote{Contestar en la carta que funciona hasta cierto punto para todos los canales propuestos
+y que se cuantifica qué tan bien funciona o no usando la fidelidad}
  This is reasonable because quantum computers are
@@
 Moreover, the algorithm of \fref{Fig2} is not optimal for
-unitary channels \revnote{why?} (that is, the channels corresponding to the vertices of the
+unitary channels \revnote{why?} \tbnote{Replantear lo que es} (that is, the channels corresponding to the vertices of the
 tetrahedron).  These straightforward channels could be accomplished more
-efficiently by simply applying the corresponding Pauli operation directly.
+efficiently by simply applying the corresponding Pauli operator directly.
 \revnote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
@@
 For the case of a two-qubit Pauli channel,
-the circuit of \fref{Fig1} would have two principal
+the circuit of \fref{Fig1} would have two main
 qubits and four ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
@@
 matrix by doing quantum process tomography on
-the principal qubits. Then, we calculated the diamond fidelity for different values of $p$ and
+the main qubits. Then, we calculated the diamond fidelity for different values of $p$ and
 obtained the results shown in \fref{2qbit}b).

### 2023-10-19 main.tex
.

@@
 rotation of angle $2s(p)$ applied to the last qubit and controlled by some of the other ones.
-Given  this, to prove the result of this theorem,
+To prove this theorem,
 we will apply $U(p)$ to $|j\rangle$ by first applying $B$,

### 2023-10-21 Response to Reviewers.tex
Algunos cambios

\documentclass[10pt,letterpaper]{article} % {{{
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
\usepackage{amsmath,amssymb}
% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% textcomp cpackage and marvosym package for additional characters
\usepackage{textcomp,marvosym}
\usepackage{subcaption}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage[nopatch=eqnum]{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}
\usepackage{caption}
\captionsetup[figure]{labelfont={bf},labelformat={default},labelsep=period,name={Fig}}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}
\renewcommand{\succ}{\textrm{succ}}

\newcommand{\fref}[1]{Fig~\ref{#1}}
\newcommand{\eref}[1]{Eq~(\ref{#1})}
% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}

\usepackage[english]{babel}
\usepackage{graphicx,helvet}
\usepackage{color}
\usepackage{url}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
% \usepackage[inline]{showlabels}
\usepackage{bbm,bm}
\usepackage{soul}
\usepackage{amsfonts}

\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{quantikz}

\usepackage[draft,inline,nomargin]{fixme} \fxsetup{theme=color}
\FXRegisterAuthor{cp}{acp}{\color{blue}CP}
\FXRegisterAuthor{tb}{ttb}{\color{green}TB}

%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}
\DeclareMathOperator{\tr}{tr}
\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}

%% END MACROS SECTION

% }}}
\begin{document}

\section{Response to Editor:}

We are re-submitting our paper ``Quantum simulation of Pauli channels and dynamical maps: algorithm and implementation''. 
We believe that the revised version of our paper addresses all
concerns by the referees in detail and is suitable for publication.

\section*{Reviewers' General Comments}

\textbf{Reviewer 1:} \\

\textbf{
The paper presents two results: 1. A way to simulate
parametric Pauli Channels using a gate-based formalism, useful for
quantum computation, and 2. An investigation on the class of
parametric Pauli Channels that can be parametrised by acting only on
one qubit via one parameter.
The full detailed comments on the paper are attached in the pdf file.
My general comments are the following:
\begin{itemize}
\item[1.]The two aforementioned results are disjointed and completely
lacking in motivation. The entire logic of the paper is obscure, and
seemingly lacks any ground for the results to be useful in any way.
\item[2.] The simulation on the IBM quantum computer is irrelevant, and does
not prove neither the validity of the decomposition (as it fails for
most of the range of operations) nor it is quantifiying any relevant
parameter (noise for example). Data from those experimental runs and
complete methodology for calculating the diamond norm is also missing.
\item[3.] The claims are vague, and the mathematical formalism is vague, with
strong abuse of notation and non-strict definitions and theorems.
There are also many spelling mistakes and refuses, even in the
formulas.
\item[4.] The analysis on the 1-parametrisation is lacking a discussion on
what happens at higher than 2 dimensions.
\end{itemize}
For the aformenetioned reasons, I cannot reccomend this paper for
publication. I suggest the following three course of actions:
\begin{itemize}
\item[1.] Separate the two main results.
\item[2.]Improve the tightness of the mathematical formalism.
\item[3.]  Find an application of the generalised Pauli Channels that can be
effectively simulated with the methodology.
\end{itemize}
}

\textbf{Reviewer 2:} \\
\textbf{The authors introduced some quantum circuits to implement the action
of arbitrary Pauli channels using fixed-state ancilla qubits, and
certain single-parameter Pauli dynamical channels using
one-parameter-rotation circuits consisting of one parametrized
single-qubit rotation and two unparametrized multiqubit unitary
operations. They showed that the latter class of dynamical channels
implementable is related to the one-parameter ancilla-state curves
allowable for such circuits. This is understandable since only a
single-parameter controlled rotation is used for the circuit, which
does not offer sufficient flexibility to realize all single-parameter
Pauli dynamical channels from my understanding.}

\textbf{While the implementations appear to be mathematically sound, there
appears to be a lack of comparisons between the actual channel
implemented and the target channel. There is only one Fig. 3 that
shows the diamond fidelities for homogenously-chosen single-qubit
unparametrized Pauli target channels within the tetrahedron region.
This is a nice plot that reveals the realistic errors coming from the
IBM quantum cloud, namely that the single-qubit Pauli channels
corresponding to the central part, which I presume are the
depolarizing channels, have the highest diamond fidelity.}

\textbf{
Besides this plot, the authors however did not show the performance of
their algorithms for larger number of qubits, and there are no
performance plots for dynamical Pauli-channel implementations. For a
further evaluation as to whether the algorithms are scientifically
practical, at least a plot on two-qubit Pauli channels and one on
two-qubit dynamical Pauli channels. My take is that because the
unitary operators A and B are too sophisticated for hardware
implementations, since they are even more complicated than single
controlled unitary operators, the fidelity could be very strongly
peaked around the zero of the pseudo Bloch-vector space for multiqubit
systems. If the overall system is too large even for simulating
two-qubit channels (due to the ancillas), then classical numerical
simulations are sufficient.}

\textbf{
In any case, after supplying the performance plots, I believe that the
algorithms and performance plots shall supply a fair presentation on
the scientific soundness of this work.}

\section{Comments throughout the text}

\begin{enumerate}
\item \textbf{I fail to see the point here, the logic of the paper is: 
1. ``open quantum systems can be modeled through a class of channels representing he various types of decoherence.'' 2. ``Quantum circuits are a convenient gate-based formalism that is well understood and has an extensive body of work, and experimentally accessible.''
3. We map (generalised) Pauli channels onto quantum circuits, as a way to simulate them.}

\textbf{What I am missing is what do we learn by doing it which cant be learned by actually performing the Pauli channel onto a quantum system? For example, applying well controlled sx, sy, sz operations and their coherent parametric combination using a photonic polarisation or path encoding is experimentally trivial. Why would I need to decompose (not even effectively for any channel) the pauli channels to match a gate based description? Which class of problems can we simulate that cannot be simulated otherwise? Is there any advantage (for example in speed up, resources like ancillas required, resistance to unwanted noise etc..?)}

\textbf{Intuitively, it seems incredibly harder resource wise to create the sum b|gamma> superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.}\\

\item \textbf{ Really confusing notation, I suggest use the much more well known relation using the Levi-Civita tensor.}\\

A sentence was added to the text mentioning how we get to the equation by starting with the relation $[\sigma_\alpha,\sigma_\beta] = 2 i
\epsilon_{\alpha \beta \gamma} \sigma_\gamma$.
After using this equation on $\sigma_{\alpha} \sigma_{\gamma} \sigma_{\alpha}$, the Levi-Civita are summed out and we are left with:
\begin{equation*}
\sigma_{\gamma} \sigma_{\alpha} \sigma_{\gamma}  =   A_{\alpha,\gamma} \sigma_{\alpha}, \;\;\;\;\;\; \text{with} \; A_{\alpha, \gamma} = (2\delta_{\alpha \gamma}-1)(2\delta_{\alpha 0}-1)(2\delta_{\gamma 0}-1)
\end{equation*}
We believe that writing matrix $A$ explicitly is more simple than this expression.

\item \textbf{Eq 2} \\

The correct equation is indeed equation 1, since we are referring to the fact that 
\begin{equation}
\label{eq: rho-transformada}
\mathcal{E}(\rho) = \dfrac{1}{2} \sum_{\alpha} \left(\sum_{\gamma} A_{\alpha, \gamma} k_{\gamma} \right) r_{\alpha} \sigma_{\alpha}.
\end{equation}
has the form of $\dfrac{1}{2} \sum_{\alpha} r_{\alpha} \sigma_{\alpha}$, only with the
$r_{\alpha}$ replaced by $\left( \sum_{\gamma} A_{\alpha,\gamma} k_{\gamma} \right) r_{\alpha}$.

\item \textbf{ At this point I am missing a proper defiition of a "quantum circuit" consistent with the mathematical formalism. The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \\

We added a few lines at the beginning of section 3 defining the concept of quantum circuit.
We  mention that quantum circuits are a representation of computation on quantum systems, which applies a unitary operator $U$ on it.

\item  \textbf{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise.}\\

The algorithm works to some extent for all Pauli channels, and how well
it does or does not work is quantified by the fidelity.
Indeed, the result we got is that it works much better for channels that are depolarizing
and works less well as we get closer to unitary channels.

\item \textbf{Why?}\\
We rephrased the sentence to make the point more clear
and explained that as a consequence of the circuit being usable in general for any Pauli channel,
it implements unitary channels in a very roundabout way.

\item \textbf{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.} \\

\item \textbf{but this is a severe disadvantage, that begs the question: what is the advantage?} \\

The advantages are that it is a straightforward, concrete and general way
of simulating Pauli channels.
Being general gives the possibility to later use it for Pauli dynamical maps by only needing to vary a few parameters.

\item \textbf{This definition is vague - given the vagueness of the term "quantum circuit".
 Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit. } \\

We added a sentence explaining that to make it more concrete.

\item \textbf{Normal}\\

They are only orthogonal, since their individual norms are not equal to $1$.

\item \textbf{Again, this is not a conclusion from theorem 1. This is literally Definition 1. Also, use the proper notation here - make A and B operators living on an dim N Hilbert state, and R explixitly dependent on s and operating on qubit N. Then the matrix representation of the operators is a $2^n\times 2^n$ matrix which is applied to the state j. The explanation in words in not sufficient.} \\

We rephrased the first paragraph of the proof to make it more clear when we use the result of theorem 1. 
Basically, we first use definition 1 to say that the circuit has the form $ARB$,
and then the result of theorem $1$
to conclude that $R$ is actually a $\sigma_3$ rotation
of angle $2s$ applied to the last qubit.\\

\item \textbf{true only if the initial j states are normalised, but they were undefined.}\\

We added the definition of $|j\rangle$  at the end of the theorem statement.\\

\item \textbf{How can it make sense to define A and B applied respectively to the last 3 and the first qubit?}\\

We changed the phrasing to make it more clear that $A$ and $B$ 
are restricted to act in a particular way on the last 3 and first qubit respectively.
Besides from that, the remaining parts of the operators $A$ and $B$ can be chosen arbitrarily, 
with the only restriction that the resulting matrices are unitary. \\

\item  \textbf{Please, at least give an example of this semiarbitrary construction of A and B.}\\

We added examples of these matrices for three particular dynamical maps in the next section. \\

\item \textbf{I don't understand what operatively is happening here. Select the state 0, apply B, apply $R_s$, apply A and then "straight forward calculations" lead to what?} \\

We rephrased this part to make it clearer. The idea is that we are searching for the matrices $A$ and $B$ such
that for given vectors $|a\rangle, |b\rangle, |c\rangle$, the circuit creates
the state $e^{is(p)} |a \rangle + e^{-is(p)} |b \rangle + |c\rangle$.
In this part, we show that with the matrices $A$ and $B$ we constructed,
we indeed create said state.
That way, given any curve of states that can be done with a 1PR circuit
according to theorem 2, here we show how
to actually create said circuit (that is, which matrices $A$, $B$ to select).\\

\item \textbf{To see what?} \\

As said before, to see that the selection of matrices $A$, $B$ creates 
the curve of states we wanted.
This part of the text has been rewritten to make it clearer.\\

\item \textbf{so this is just the proof that the proposed operative definition of A and B is properly normalised, right?} \\

This is an intermediate step, but as said in the previous questions, 
we are proving that the selection of $A$ and $B$ for given vectors $|a\rangle, |b\rangle, |c\rangle$ 
indeed works to create the state
$e^{is(p)} |a \rangle + e^{-is(p)} |b \rangle + |c\rangle$.\\

\item \textbf{To be consistent with the previous formalism, the states should be 0,1,2,3}\\

We made the change.\\

\item \textbf{there is literally one parameter in one qubit, of course it depends on one parameter...
 how can this be a result?} \\

The result is that they needed  to move just one parameter to implement 
many Pauli channels in the bit flip maps.
For other maps, they may need to move more than one parameter to 
implement all the channels in the map. 
However, just as we showed that the bit flip map can be done with a 1PR circuit,
they implemented the map using one parameter.\\

 \item  \textbf{This is interesting, instead of giving only some random examples, I would actually explore more in details the zoology of this class of dynamical maps - if lucky, you would find class of interesting problems that can be simulated effectively in an experimental setup by just accessing one parameter (as the authors say, just with one set of waveplates, for example)} \\

Some of the examples given (depolarizing, bit flip, phase flip, bit-phase flip) are very well known 
Pauli maps.
We also included random examples with the purpose of seeing how some general maps that 
can be implemented with a 1PR circuit look like.

 \item  \textbf{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit. I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so.. what is the applicability of the theorem for higher dimensions?} \\

 We added a couple of sentences talking about that.

 \item \textbf{Imprcise} \\

 We

 \item This reasoning I miss, simplifying for achieving what goal?

 \item There is no quantification of this, it´s not even the focus of the paper

 \item citation required here
\end{enumerate}

\end{document}

### 2023-10-21 main.tex
Algunos cambios

@@
 
-\tbnote{Propuesta haciendo unos cambios de enfoque que menciono en la intro:}\\
-$\;$ \\
-
-{\color{green}
-Pauli channels are fundamental in the context of quantum computing as they
-model the simplest kind of noise in quantum devices, and
-Pauli dynamical maps are parametrized Pauli channels,
-which can model a continuous transformation of a quantum device.
-In this article, we propose a quantum
-algorithm for simulating
-Pauli dynamical maps
-by using a parametrized quantum circuit.
-We also establish the mathematical conditions for an
-$N$-qubit transformation to be achievable using a parametrized circuit where
-only one single-qubit operation depends on the parameter. 
-The implementation of the proposed circuit is demonstrated using IBM's quantum computers 
-for the case of one qubit, and the fidelity of this implementation is reported. 
-}
 % }}}
@@
 simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
-and specifically for quantum channels~\cite{Xin,Wei,Zanetti}.
+and specifically for quantum channels~\cite{Xin,Wei,Zanetti}, 
+which can be used to study and model decoherence.
 Such quantum algorithms can be represented using what is known as a quantum
@@
 
-To represent the algorithms implemented in quantum computers, either to
-simulate a physical system or for some other purpose, one often uses a quantum
-circuit~\cite{chuangbook}.  In this work, we shall also work with parametrized
-quantum circuits, that is,  quantum circuits in which some of the operations
-depend on variable parameters~\cite{cerezo}.  These circuits play an important
-part in applications such as quantum machine learning~\cite{Benedetti} and
-describing general quantum transformations dependent on parameters. Substantial
-research has been devoted to enhancing the efficiency of these
-circuits~\cite{Rasmussen}.
-
 \cpnote{Iteara de nuevo Tomas:
@@
 
-\cpnote{dejar solo un parrafo de estructura}
+\tbnote{
+Continuing with this previous work done to simulate quantum processes, in this article we 
+propose a quantum algorithm for simulating Pauli channels
+and implement it on one of IBM's quantum computers.
+The algorithm proposed is straightforward and can be used for any Pauli channel by only changing a couple of 
+parameters in the operations it performs. 
+To represent the algorithm, we use a quantum circuit, which is a common
+way of representing algorithms intended for quantum computers.~\cite{chuangbook}.  }
+
+\tbnote{ Furthermore, we will also simulate Pauli dynamical maps, which are continuous parametrized curves of Pauli channels.
+These maps can be used to model a continuous change of a qubit instead of only discrete jumps. 
+The generality of the algorithm proposed for Pauli channels will be very useful in this part, since then
+using for dynamical maps will come very naturally.
+Implementing these maps will lead us to study quantum algorithms  with free parameters, 
+something that is common in areas such as quantum machine learning~\cite{Benedetti}.
+This can be done using parametrized quantum circuits, which consist of quantum
+circuits in which one or more operations depend on a free parameter. }
+
+\cpnote{dejar solo un parrafo de estructura:} 
+\tbnote{Aqui está:}
+
 We start by providing the definition of quantum channels, the general framework
 used here, and multi-qubit Pauli channels in section \ref{sec: Pauli Channels}.
-Our first objective is to present a quantum algorithm capable of simulating
+Our first objective is to present a general and straightforward quantum algorithm capable of simulating
 Pauli channels on quantum computers; we do this in section \ref{sec: Circuit
 for a Pauli Channel}, where we also demonstrate its implementation using IBM's
-quantum computers for the particular case of single-qubit Pauli channels.
+quantum computers for some single and two-qubit Pauli channels.
 Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
@@
 
-We start the article by providing the definition of quantum channels, the
-general framework used here, and multi-qubit Pauli channels in section
-\ref{sec: Pauli Channels}.  Then, since our main objective is to obtain a
-parametrized circuit for Pauli dynamical maps, we will first need a circuit
-that can implement any Pauli channel by only changing some parameters in the
-quantum gates and without changing the design of the circuit itself.
-Therefore, in section\ref{sec: Circuit for a Pauli Channel} we present such a
-circuit and we also show its implementation using IBM's quantum computers for
-the particular case of single-qubit Pauli channels and some two-qubit ones.  In
-section \ref{sec: 1PR Circuits}, we adapt the algorithm to dynamical maps.
-Then we aim to simplify the algorithm so that it only contains one parametrized
-single-qubit rotation, and in the process we contribute to the work in
-parametrized quantum circuits by establishing   in \ref{theorem2} which general
-quantum transformations can be implemented this way.  Finally, in section
-\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
-dynamical maps that fulfill the conditions of theorem \ref{theorem2}.
+%
+%We start the article by providing the definition of quantum channels, the
+%general framework used here, and multi-qubit Pauli channels in section
+%\ref{sec: Pauli Channels}.  Then, since our main objective is to obtain a
+%parametrized circuit for Pauli dynamical maps, we will first need a circuit
+%that can implement any Pauli channel by only changing some parameters in the
+%quantum gates and without changing the design of the circuit itself.
+%Therefore, in section\ref{sec: Circuit for a Pauli Channel} we present such a
+%circuit and we also show its implementation using IBM's quantum computers for
+%the particular case of single-qubit Pauli channels and some two-qubit ones.  In
+%section \ref{sec: 1PR Circuits}, we adapt the algorithm to dynamical maps.
+%Then we aim to simplify the algorithm so that it only contains one parametrized
+%single-qubit rotation, and in the process we contribute to the work in
+%parametrized quantum circuits by establishing   in \ref{theorem2} which general
+%quantum transformations can be implemented this way.  Finally, in section
+%\ref{sec: 1PR circuit for a Pauli map}, we conclude analyzing the Pauli
+%dynamical maps that fulfill the conditions of theorem \ref{theorem2}.
 
@@
 \end{pmatrix},
+\label{eq: propiedad-pauli}
 \end{equation}
@@
 Moreover, the algorithm of \fref{Fig2} is not optimal for
-unitary channels \revnote{why?} \tbnote{Replantear lo que es} (that is, the channels corresponding to the vertices of the
-tetrahedron).  These straightforward channels could be accomplished more
+unitary channels (that is, the channels corresponding to the vertices of the
+tetrahedron). \revnote{why?} \tbnote{Replantear, decir que cerca de los vertices del tetraedro teneos una fidelidad
+baja segun la imagen, por lo que podemos ver que los unitarios
+tienen una fid baja.} 
+\tbnote{Moreover, as can be seen in \fref{Fig3}, the algorithm of \fref{Fig2} is not optimal for 
+channels in the edges of the tetrahedron, which corresponds to unitary channels. }
+ These simple channels could be accomplished more
 efficiently by simply applying the corresponding Pauli operator directly.
@@
 algorithm employs numerous quantum gates even in such scenarios. \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
-\tbnote{As I see it, an advantage is that only one circuit arrengment is needed for any channel. We don't have to change
-the circuit to implement different channels, only need to change parameters.
-This allows us to consider parametrized circuits and then explore what happens when
-we constrain to only one parametrized operation.}\\
 \tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
 {\color{green} This disadvantage comes from the fact
-that the circuit is  fully general and applicable to any Pauli channel, but that means that sometimes
+that the circuit is applicable to any Pauli channel, which that means that sometimes
 it is not the most straightforward algorithm to simulate a Pauli channel.
-However, the main advantage is that if we want 
+However, the main advantages are that the algorithm is simple, and if we want 
 to simulate many Pauli channels (for example,
 for simulating a Pauli dynamical map as we will see later),
-we only have to change a couple of angles in the circuit and
-not completely reconstruct it. 
+we only have to change a couple of angles in the circuit to move between 
+different Pauli channels and not completely reconstruct the circuit. 
 And as we will see, sometimes only changing
@@
 \subsection{Simulation of a two-qubit Pauli channel}
-\tbnote{Voy a agregar toda esta sección sobre el circuito para dos qubits}
 
@@
 qubits and four ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
-However, the number of ancilla qubits can be reduced for Pauli 
-channels in which not all two-qubit Pauli matrices are applied to
-the system. For example, consider the following two-qubit dephasing channel:
+However, since the quantum computer ibmq-lima we used does not have that many qubits,
+we will simulate a Pauli channel that does not apply all two-qubit Pauli matrices to the system.
+For example, consider the following two-qubit dephasing channel:
 \begin{align}
@@
 only $2$ ancilla qubits will be necessary, and it can be implemented
-using the circuit of \fref{2qbit}a).
+using the circuit of \fref{2qbit}b.
 
@@
 the main qubits. Then, we calculated the diamond fidelity for different values of $p$ and
-obtained the results shown in \fref{2qbit}b).
-
+obtained the results shown in \fref{2qbit}a. 
+As can be seen in the figure, the fidelity doesn't vary much as we change the value of $p$,
+and it stays at a value of around $0.75$, 
+and it is biggest around $p=0$, corresponding to the identity channel.
 }
@@
 \end{align}
-with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states \revnote{normal} \tbnote{Aquí no estoy seguro, sí sería normal el término correcto?} and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
-c^j|c^j \rangle = 1$. Here $|j\rangle$ represents the N-qubit base states in the computational basis.
+with $s(p)$ some function of $p$,  $|a^j\rangle ,|b^j\rangle, |c^j\rangle$ orthogonal states 
+and $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle
+c^j|c^j \rangle = 1$. Here $|j\rangle$ represents an element of the N-qubit  computational basis.
 \end{theorem}
@@
 
-{\color{green} As before, from the definition of a 1PR, we know that $U(p)$ can be decomposed as $ARB$, where 
+{\color{green} As before, from the definition of a 1PR circuit, we know that $U(p)$ can be decomposed as $ARB$, where 
 $A,B$ are unitary operators acting on the $N$-qubit system
@@
 Moreover, they satisfy  $\langle a^j| a^j\rangle + \langle b^j| b^j\rangle + \langle c^j| c^j\rangle = 1$ because this quantity is the squared norm of the $j$th column of $B$, 
-which is unitary. \revnote{true only if the initial j states are normalised, but they were undefined.} 
-\tbnote{Agregué una línea en el enunciado del teorema sobre que los $|j \rangle$ son 
-la base computacional del sistema de N qubits.}
+which is unitary.
 
@@
 with the parametrized rotation $R$ applied to the last qubit controlled by all the 
-other qubits. There is some freedom when defining
+other qubits. There is some freedom when choosing
 the operators $A$ and $B$, we only need
-to make sure that: \revnote{How can it make sense to define A and B applied respectively to the last 3 and the first qubit?} 
-\tbnote{Reescribí la oración anterior para no decir que es una definición,
-sino que queda algo de libertad (aunque igual lo decía después de la ecuación)}
+to make sure that:
 \begin{align}
@@
 \end{align}
-\revnote{Please, at least give an example of this semiarbitrary construction of A and B.}
-\tbnote{Hay ejemplos en los ejemplos de abajo.}
-The remaining part of the operators $A$ and $B$ can be defined
+The remaining part of the operators $A$ and $B$ can be chosen
 in any arbitrary manner as long as they are unitary. 
-Then, by following the calculations of applying 
-$A R_{\sigma_3}(2s(p)) B$ to $|0\rangle$,
-it can be shown that the curve of states created is that described in \eref{eq:curve-states}.
-\revnote{I don't understand what operatively is happening here. Select the state 0, apply B, apply s, apply A and then "straight forward calculations" lead to what?}
-\tbnote{Reescrib\'i la oraci\'on anterior de forma que creo que se entiende mejor.}
+Examples of these matrices are shown for particular dynamical maps in the next section.
+%Then, by following the calculations of applying 
+%$A R_{\sigma_3}(2s(p)) B$ to $|0\rangle$,
+%it can be shown that the curve of states created is that described in \eref{eq:curve-states}.
 
 To see that $A R_{\sigma_3}(s(p)) B |0\rangle$ in fact creates
-the curve of states described in \eref{eq:curve-states}, \revnote{to see what?} \tbnote{Ya cambié la oración anterior, pero siento que queda redundante.
-Creo que como estaba antes ``to see it'', era suficiente.} we can rewrite the expression of $B|0\rangle$ by
+the curve of states described in \eref{eq:curve-states}, we can rewrite the expression of $B|0\rangle$ by 
 separating the first $N-1$ qubits from the last one:
 $$B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.$$
-Since the parametrized rotation $R_{\sigma_3}(2s(p))$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$.
-As a result, we obtain: \revnote{so this is just the proof that the proposed operative definition of A and B is properly normalised, right?} \tbnote{No entiendo la pregunta, pero creo que la respuesta es no}
+Since the parametrized rotation $R_{\sigma_3}(2s(p))$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$. As a result, we obtain:
 
@@
 
-Finally, applying the  operator $A$ to this state yields the desired result: \revnote{which is??} \tbnote{Ya lo puse abajo}
+Finally, applying the  operator $A$ to this state yields: 
 \begin{align*}
@@
 \end{align*}
-Therefore proving that any curve of states as that in \eref{eq:curve-states} 
+With this, we prove that any curve of states as that in \eref{eq:curve-states} 
 can be constructed by the circuit in  \fref{Fig4} with the parametrized rotation 
@@
 \item \textbf{Depolarizing:} This dynamical map is given by
-\begin{align*}
+\begin{align}
 \varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
-\end{align*}
+\label{eq:depo}
+\end{align}
 with $p \in [0,1]$. 
@@
 \end{align*}
-\revnote{to be consistent with the previous formalism, the states should be 0,1,2,3} \tbnote{Done.}
 with $\sin s = \sqrt{3p/4}$.
@@
 probamos sobre qué canales se pueden hacer con una rotación parametrizada (pues bit phase flip es uno de esos). }
+
+\tbnote{Buscar alguna forma fácil de probar que no todos los mapas tienen la forma de 1PR} 
 \end{itemize}
@@
 
+\tbnote{Añadir un parrafito al final que lo visualizamos sólo para una dimensión,
+pero que para más dimensiones creemos que los mapas representativos se podrán hacer así. 
+Sería interesante verlo en el futuro.}
+
 In this work, we found a quantum algorithm for 
@@
 generalized it to Pauli dynamical maps
-by using parametrized quantum circuits \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise}.
+by using parametrized quantum circuits \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise. Responder que 
+esperamos que ya con los cambios hechos esté más claro}.
 Furthermore, we implemented single-qubit Pauli channels
@@
 and obtained their fidelities.
-Finally, when working with Pauli dynamical maps,
-we searched for a way of simplifying the parametrized circuit \revnote{This reasoning I miss, simplifying for achieving what goal? }
-by requiring that only one single-qubit rotation depends on the parameter.
+
+Then, when working with Pauli dynamical maps,
+we searched for a way of minimizing the amount of 
+parametric operations in the circuit 
+by requiring that only one single-qubit rotation depends on the parameter. \revnote{This reasoning I miss, simplifying for achieving what goal? } 
+\tbnote{Le di una reescritura a esa frase.}
 In theorem \ref{theorem2} we found the general mathematical conditions for 
 this, applicable to any parametrized circuit.
+\tbnote{Given this condition, we considered the space of Pauli maps that are possible to parametrize with one parameter, and 
+gave some explicit examples for a system of one qubit. 
+We expect that as the number of qubits gets bigger, the space of such maps becomes a smaller 
+part of the whole space of Pauli dynamical maps. 
+However, some paradigmatic maps as the dephasing one we studied for 2 qubits will still be
+possible to do with a 1PR circuit (for this case, this can be seen by
+noticing that said dephasing channel in \eref{2qbit-c} has the same form as the depolarizing channel of \eref{eq:depo}, which we proved
+to be possible to implement with a 1PR circuit).}
 
@@
 systems in quantum computers,
-and we observe the big effect that the error of quantum computers have
-on these simulations. \revnote{There is no quantification of this, it´s not even the focus of the paper}
+and we observe the effect that the error of a quantum computer have
+on these simulations, quantified by the fidelity. \revnote{There is no quantification of this, it´s not even the focus of the paper} \tbnote{ya cambié la oración}
 On the other hand, the result

### 2023-10-21 Response to Reviewers.tex
.

@@
 
- We
+ \item \textbf{This reasoning I miss, simplifying for achieving what goal? }
 
- \item This reasoning I miss, simplifying for achieving what goal?
+ \item\textbf{ There is no quantification of this, it´s not even the focus of the paper.}
 
- \item There is no quantification of this, it´s not even the focus of the paper
-
- \item citation required here
+ \item \textbf{Citation required here.}
+ I placed a citation.
 \end{enumerate}

### 2023-10-21 main.tex
Articulo

@@
 \subsection{Simulation of a two-qubit Pauli channel}
-
+\label{2qbit}
 For the case of a two-qubit Pauli channel,
@@
 
-\tbnote{Añadir un parrafito al final que lo visualizamos sólo para una dimensión,
-pero que para más dimensiones creemos que los mapas representativos se podrán hacer así. 
-Sería interesante verlo en el futuro.}
+\tbnote{Añadí el párrafo en verde hablando de eso.}
 
@@
 generalized it to Pauli dynamical maps
-by using parametrized quantum circuits \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise. Responder que 
-esperamos que ya con los cambios hechos esté más claro}.
+by using parametrized quantum circuits \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise.}.
 Furthermore, we implemented single-qubit Pauli channels
@@
 gave some explicit examples for a system of one qubit. 
-We expect that as the number of qubits gets bigger, the space of such maps becomes a smaller 
-part of the whole space of Pauli dynamical maps. 
-However, some paradigmatic maps as the dephasing one we studied for 2 qubits will still be
+As the number of qubits gets bigger, the degrees of freedom for choosing a Pauli dynamical map also gets bigger,
+so we would expect that the space of maps that can be done with only 
+one parameter
+becomes a smaller part of the whole space of Pauli dynamical maps.
+However, some paradigmatic maps as the dephasing one we studied for 2 qubits in section \ref{2qbit} will still be
 possible to do with a 1PR circuit (for this case, this can be seen by
@@
 
-Therefore, this work presents yet another example of the current
+In conclusion, this work presents yet another example of the current
 exploration into simulating open quantum

### 2023-10-22 Response to Reviewers.tex
Articulo
Comentarios

@@
 
-\section{Response to Editor:}
+\section*{Response to Editor:}
 
@@
 
+We thank the first reviewer for the time spent carefully 
+reviewing the manuscript, and the opinions regarding it.
+We have made major changes in the manuscript following your comments and recommendations. 
+Some of the general changes we made are explained in the following list
+and then we respond to more specific comments
+throughout the text.
+\begin{itemize}
+\item We rewrote big parts of the introduction to make more clear the logic of the paper. 
+We begin the paper by presenting the theory of Pauli channels, 
+and then present the first result, which is the algorithm for simulating them on a quantum computer.
+With that algorithm in mind, we seek to generalize it to Pauli dynamical maps, 
+so as to include continuous transformations of the 
+N-qubit system. This goal leads us to
+focus on parametrized quantum circuits and then to consider
+what can be done with only moving one parameter.
+\item We added the data and code from the IBM quantum computer simulations
+to a Github repository.
+\item We improved the tightness of the formulation by adding
+a more mathematical definition of 1PR circuits and
+rephrasing the proof of theorem 2 to make it more clear. 
+\item In section 5 of the paper we expanded on the examples for Pauli dynamical maps
+that can be implemented with a 1PR circuit.
+These Pauli dynamical maps are well-known and we prove here
+that they can be done with only moving one parameter in the circuit.
+Furthermore, we also implemented these dynamical circuits on IBM's using a 1PR circuit.
+
+\end{itemize}
+
 \textbf{Reviewer 2:} \\
@@
 algorithms and performance plots shall supply a fair presentation on
-the scientific soundness of this work.}
+the scientific soundness of this work.} \\
 
-\section{Comments throughout the text}
+We thank the second reviewer for the detailed analysis
+of our manuscript and the comments made. 
+Following the recommendations, we 
+added section 3.3 in which we simulate a two qubit Pauli dynamical map 
+and show that the fidelities are still reasonably high. 
+Furthermore, we also supplied plots of the simulation of the
+three Pauli dynamical maps studied in section 5. 
+For each of these simulations, we used the proposed 1PR circuit and plotted the fidelities for
+different channels along the dynamical map.
+
+\section*{Comments throughout the text}
+
+Here we present the comments made by the reviewers throughout the text 
+and respond to each of them individually.
+The comments are written in bold and our response in regular font.
 
@@
 
-\textbf{Intuitively, it seems incredibly harder resource wise to create the sum b|gamma> superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.}\\
+\textbf{Intuitively, it seems incredibly harder resource wise to create the sum b|gamma> superposition state needed for the ancilla, just for the sake of having it into a "quantum circuit" perspective.
+}\\
+
+We rewrote parts of the introduction to make the objective of the manuscript more clear. 
+First of all, one of the principal objectives of quantum computers nowadays
+is to use them for simulation of quantum processes,
+and out of all quantum processes, decoherence is one of the most important and prevalent.
+That is why we chose to simulate Pauli channels, which are one of the
+simplest descriptions of decoherence. 
+Important characteristics about the algorithm proposed for Pauli channels
+are its simplicity and generality.
+We choose to represent the channel using a gate-based formalism because
+of it being one of the most common and general ways of
+representing quantum algorithms.
+
+Furthermore, the simplicity and generality of the circuit proposed allows us to
+naturally generalize it to Pauli dynamical maps by just
+adding movable parameters to the circuit.
+Finally, we show the general result of what parametrized quantum operations can be done 
+moving only one parameter, which experimentally could translate
+to having to adapt only one setting of an experiment
+to simulate a quantum operation.
 
@@
 \epsilon_{\alpha \beta \gamma} \sigma_\gamma$.
-After using this equation on $\sigma_{\alpha} \sigma_{\gamma} \sigma_{\alpha}$, the Levi-Civita are summed out and we are left with:
+After using this equation on $\sigma_{\alpha} \sigma_{\gamma} \sigma_{\alpha}$, the Levi-Civita tensors are summed out and we are left with:
 \begin{equation*}
@@
 \end{equation*}
-We believe that writing matrix $A$ explicitly is more simple than this expression.
+We believe that writing matrix $A$ explicitly is simpler than this expression.
 
@@
 
-\item \textbf{ At this point I am missing a proper defiition of a "quantum circuit" consistent with the mathematical formalism.
+\item \textbf{At this point I am missing a proper defiition of a "quantum circuit" consistent with the mathematical formalism.
 The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \\
@@
 We added a few lines at the beginning of section 3 defining the concept of quantum circuit.
-We  mention that quantum circuits are a representation of computation on quantum systems, which applies a unitary operator $U$ on it.
+We  mention that quantum circuits are a representation of computation on quantum systems, which applies a unitary operator $U$.
 
@@
 Indeed, the result we got is that it works much better for channels that are depolarizing
-and works less well as we get closer to unitary channels.
+and less well as we get closer to unitary channels.
 
@@
 
-\item \textbf{but this is a severe disadvantage, that begs the question: what is the advantage?} \\
+\item \textbf{But this is a severe disadvantage, that begs the question: what is the advantage?} \\
 
@@
 of simulating Pauli channels.
-Being general gives the possibility to later use it for Pauli dynamical maps by only needing to vary a few parameters.
+Being general gives the possibility to later use it for Pauli dynamical maps by only needing to vary the parameters
+and not the design of the circuit in general.
 
@@
 and then the result of theorem $1$
-to conclude that $R$ is actually a $\sigma_3$ rotation
+to conclude that $R$ is in particular a $\sigma_3$ rotation
 of angle $2s$ applied to the last qubit.\\
 
-\item \textbf{true only if the initial j states are normalised, but they were undefined.}\\
+\item \textbf{True only if the initial j states are normalised, but they were undefined.}\\
 
@@
 
-We added examples of these matrices for three particular dynamical maps in the next section. \\
+We added examples of these matrices for the three particular dynamical maps shown in the next section. \\
 
@@
 
-\item \textbf{so this is just the proof that the proposed operative definition of A and B is properly normalised, right?} \\
+\item \textbf{So this is just the proof that the proposed operative definition of A and B is properly normalised, right?} \\
 
@@
 
-\item \textbf{there is literally one parameter in one qubit, of course it depends on one parameter...
+\item \textbf{There is literally one parameter in one qubit, of course it depends on one parameter...
  how can this be a result?} \\
@@
 The result is that they needed  to move just one parameter to implement 
-many Pauli channels in the bit flip maps.
+many Pauli channels of the bit flip map.
 For other maps, they may need to move more than one parameter to 
@@
 
- We added a couple of sentences talking about that.
+We added a paragraph in the conclusion talking about that.
+There we argue that for bigger systems, the space of dynamical maps
+that can be implemented with a 1PR circuit
+is a smaller part of the whole space of dynamical maps.
+However, some of the most paradigmatic maps will still be implementable this way.
 
- \item \textbf{Imprcise} \\
+\item \textbf{Imprecise} \\
 
- \item \textbf{This reasoning I miss, simplifying for achieving what goal? }
+We have rephrased parts of the conclusion to make it more clear.
 
- \item\textbf{ There is no quantification of this, it´s not even the focus of the paper.}
+\item \textbf{This reasoning I miss, simplifying for achieving what goal? } \\
+
+We rephrased the conclusion to make it more clear. We wanted to reduce the number of parametrized gates
+so as to have only one parameter that works as a kind of knob to move around in the channels forming
+a dynamical map.
+
+\item\textbf{ There is no quantification of this, it´s not even the focus of the paper.}  \\
+
+We have a quantification of the fidelity of the implementation of different Pauli channel and dynamical maps.
+ Even though it is indeed not the focus of the paper, we believe it
+ is an important enough part of it as to mention it again in the conclusion.
 
 \item \textbf{Citation required here.}
- I placed a citation.
+We added a citation.
 \end{enumerate}

### 2023-11-08 main.tex
fix bug, for realz

@@
 
-Such systems have been simulated because of their many applications, 
-such as studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
-studying dissipative processes~\cite{Barreiro}
-and modeling non-Markovian dynamics~\cite{Marsden}.
-Among quantum systems, the simplest case is that of a qubit~\cite{chuangbook},
-and within them, the simplest class of channels that produce decoherence are
-Pauli channels~\cite{geometry,Zbigniew,Davalos}. Indeed, they serve as
-effective models for the noise affecting quantum devices~\cite{Flammia}.
-
-\cpnote{Iteara de nuevo Tomas:
-However, in this article, our main goal is not to implement Pauli channels, but to study and implement Pauli dynamical maps, which are continuous parametrized curves of Pauli channels. 
-These maps can be used to model continuous change of a qubit instead of only discrete jumps.
-Implementing these maps will lead us to study  quantum algorithms with free parameters, 
-something that is common in areas such as quantum machine learning~\cite{Benedetti}.
-This can be done using parametrized quantum circuits, which consist of quantum
-circuits in which one or more operations depend on a free parameter. }
-
-\cpnote{Porfa mete esto en el parrafo donde va la estructura:
-Our study of such circuits for the use of simulating Pauli dynamical maps will
-lead us to theorem 2, in which we find general condition for any parametrized
-transformation (for example, a Pauli dynamical map) to be achievable on a
-quantum circuit with only one single-qubit rotation dependent on the parameter.
-Said parameter is in some sense a knob that we can control to continuously
-perform the transformation by only having to move one number. }
-
-\tbnote{
-Continuing with this previous work done to simulate quantum processes, in this article we 
-propose a quantum algorithm for simulating Pauli channels
-and implement it on one of IBM's quantum computers.
-The algorithm proposed is straightforward and can be used for any Pauli channel by only changing a couple of 
-parameters in the operations it performs. 
-To represent the algorithm, we use a quantum circuit, which is a common
-way of representing algorithms intended for quantum computers.~\cite{chuangbook}.  }
-
-\tbnote{ Furthermore, we will also simulate Pauli dynamical maps, which are continuous parametrized curves of Pauli channels.
-These maps can be used to model a continuous change of a qubit instead of only discrete jumps. 
-The generality of the algorithm proposed for Pauli channels will be very useful in this part, since then
-using for dynamical maps will come very naturally.
-Implementing these maps will lead us to study quantum algorithms  with free parameters, 
-something that is common in areas such as quantum machine learning~\cite{Benedetti}.
-This can be done using parametrized quantum circuits, which consist of quantum
-circuits in which one or more operations depend on a free parameter. }
-
-\cpnote{dejar solo un parrafo de estructura:} 
-\tbnote{Aqui está:}
+Such systems have been simulated because of their many applications, such as
+studying the emergence of multipartite entanglement~\cite{Andrea,Andrea_AD},
+studying dissipative processes~\cite{Barreiro} and modeling non-Markovian
+dynamics~\cite{Marsden}.  Among quantum systems, the simplest case is that of a
+qubit~\cite{chuangbook}, and within them, the simplest class of channels that
+produce decoherence are Pauli channels~\cite{geometry,Zbigniew,Davalos}.
+Indeed, they serve as effective models for the noise affecting quantum
+devices~\cite{Flammia}.
+
+In this article we propose a quantum algorithm for simulating Pauli channels
+and implement it on one of IBM's quantum computers.  The algorithm proposed is
+straightforward and can be used for any Pauli channel by only changing a couple
+of parameters in the operations it performs.  To represent the algorithm, we
+use a quantum circuit, which is a common way of representing algorithms
+intended for quantum computers.~\cite{chuangbook}.  Furthermore, we will also
+simulate Pauli dynamical maps, which are continuous parametrized curves of
+Pauli channels.  These maps can be used to model a continuous change of a qubit
+instead of only discrete jumps.  The generality of the algorithm proposed for
+Pauli channels will be very useful in this part, since then using for dynamical
+maps will come very naturally.  Implementing these maps will lead us to study
+quantum algorithms  with free parameters, something that is common in areas
+such as quantum machine learning~\cite{Benedetti}.  This can be done using
+parametrized quantum circuits, which consist of quantum circuits in which one
+or more operations depend on a free parameter.
 
@@
 for a Pauli Channel}, where we also demonstrate its implementation using IBM's
-quantum computers for some single and two-qubit Pauli channels.
-Expanding beyond discrete Pauli channels, we introduce the concept of Pauli
+quantum computers for several single and two-qubit Pauli channels.
+Expanding beyond Pauli channels, we introduce the concept of Pauli
 dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
@@
 study parametrized quantum channels, aiming to adapt the algorithm developed
-for channels to dynamical maps.  Furthermore, we contribute to the body of work
+for channels to dynamical maps\cpnote{Me parece que las dos frases anteriores 
+dicen casi lo mismo. Poner una sola frase}.  Furthermore, we contribute to the body of work
 related to parametrized quantum circuits by establishing a theorem, which  sets
@@
 
-\revnote{I fail to see the point here - the logic of the paper is: % {{{
-1."open quantum systems can be modeled through a class of channels representing
-he various types of decoherence. 2. Quantum circuits are a convenient
-gate-based formalism that is well understood and has an extensive body of work,
-and experimentally accessible.  3. We map (generalised) Pauli channels onto
-quantum circuits, as a way to simulate them. \\
-What I am missing is what do we learn by doing it which can't be learned by
-actually performing the Pauli channel onto a quantum system? For example,
-applying well controlled sx, sy, sz operations and their coherent parametric
-combination using a photonic polarisation or path encoding is experimentally
-trivial. Why would I need to decompose (not even effectively for any channel)
-the Pauli channels to match a gate based description? Which class of problems
-can we simulate that cannot be simulated otherwise? Is there any advantage (for
-example in speed up, resources like ancillas required, resistance to unwanted
-noise etc..?)\\
-Intuitively, it seems incredibly harder resource wise to create the sum
-$b|gamma\rangle$ superposition state needed for the ancilla, just for the sake
-of having it into a "quantum circuit" perspective.} % }}}
+% \revnote{I fail to see the point here - the logic of the paper is: % {{{
+% 1."open quantum systems can be modeled through a class of channels representing
+% he various types of decoherence. 2. Quantum circuits are a convenient
+% gate-based formalism that is well understood and has an extensive body of work,
+% and experimentally accessible.  3. We map (generalised) Pauli channels onto
+% quantum circuits, as a way to simulate them. \\
+% What I am missing is what do we learn by doing it which can't be learned by
+% actually performing the Pauli channel onto a quantum system? For example,
+% applying well controlled sx, sy, sz operations and their coherent parametric
+% combination using a photonic polarisation or path encoding is experimentally
+% trivial. Why would I need to decompose (not even effectively for any channel)
+% the Pauli channels to match a gate based description? Which class of problems
+% can we simulate that cannot be simulated otherwise? Is there any advantage (for
+% example in speed up, resources like ancillas required, resistance to unwanted
+% noise etc..?)\\
+% Intuitively, it seems incredibly harder resource wise to create the sum
+% $b|gamma\rangle$ superposition state needed for the ancilla, just for the sake
+% of having it into a "quantum circuit" perspective.} % }}}
 
@@
 to the center of the tetrahedron) have a high $f$, while those close to unitary
-channels have much lower $f$. \revnote{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise. } 
-\tbnote{Contestar en la carta que funciona hasta cierto punto para todos los canales propuestos
-y que se cuantifica qué tan bien funciona o no usando la fidelidad}
+channels have much lower $f$. 
+% \revnote{So another way to see this is that the simulation through the
+% proposed decomposition works only for depolarising channels, and fails
+% otherwise. } 
+% \tbnote{Contestar en la carta que funciona hasta cierto punto para todos los
+% canales propuestos y que se cuantifica qué tan bien funciona o no usando la
+% fidelidad}
 This is reasonable because quantum computers are
@@
 trying to simulate depolarization but it is when simulating unitary processes.
-Moreover, the algorithm of \fref{Fig2} is not optimal for
-unitary channels (that is, the channels corresponding to the vertices of the
-tetrahedron). \revnote{why?} \tbnote{Replantear, decir que cerca de los vertices del tetraedro teneos una fidelidad
-baja segun la imagen, por lo que podemos ver que los unitarios
-tienen una fid baja.} 
-\tbnote{Moreover, as can be seen in \fref{Fig3}, the algorithm of \fref{Fig2} is not optimal for 
-channels in the edges of the tetrahedron, which corresponds to unitary channels. }
+% Moreover, the algorithm of \fref{Fig2} is not optimal for
+% unitary channels (that is, the channels corresponding to the vertices of the
+% tetrahedron). \revnote{why?} \tbnote{Replantear, decir que cerca de los vertices del tetraedro teneos una fidelidad
+% baja segun la imagen, por lo que podemos ver que los unitarios
+% tienen una fid baja.} 
+% \tbnote{
+Moreover, as can be seen in \fref{Fig3}, the algorithm of \fref{Fig2} is not optimal for 
+channels in the edges of the tetrahedron, which corresponds to unitary channels. 
+% }
  These simple channels could be accomplished more
@@
 % }}}
-
 %

### 2023-11-16 main.tex
and so the crazy refactoring process sees the sunlight after some months in the dark!

@@
 % }
- These simple channels could be accomplished more
-efficiently by simply applying the corresponding Pauli operator directly.
-\revnote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
-\tbnote{Este comentario se conecta con lo del 
-primer comentario, que no sé bien cómo contestar.}
-Nevertheless, due to its general design to accommodate any Pauli channel, the
-algorithm employs numerous quantum gates even in such scenarios. \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
-\tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
-{\color{green} This disadvantage comes from the fact
-that the circuit is applicable to any Pauli channel, which that means that sometimes
-it is not the most straightforward algorithm to simulate a Pauli channel.
-However, the main advantages are that the algorithm is simple, and if we want 
-to simulate many Pauli channels (for example,
-for simulating a Pauli dynamical map as we will see later),
-we only have to change a couple of angles in the circuit to move between 
-different Pauli channels and not completely reconstruct the circuit. 
-And as we will see, sometimes only changing
-one angle in the circuit will be enough.}\\
-$\;$\\
-
-\tbnote{Sección que agregué:}\\
-
-{\color{green}
-\subsection{Simulation of a two-qubit Pauli channel}
-\label{2qbit}
-For the case of a two-qubit Pauli channel,
-the circuit of \fref{Fig1} would have two main
-qubits and four ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
-However, since the quantum computer ibmq-lima we used does not have that many qubits,
-we will simulate a Pauli channel that does not apply all two-qubit Pauli matrices to the system.
+These channels could be accomplished more
+efficiently by simply applying the corresponding unitary operator directly. 
+% \revnote{I wholeheartedly agree with this statement, and I would go so far as
+% to claim that this is true in general, even at the center of the tethraedron.}
+% \tbnote{Este comentario se conecta con lo del 
+% primer comentario, que no sé bien cómo contestar.}
+% Nevertheless, due to its general design to accommodate any Pauli channel, the
+% algorithm employs numerous quantum gates even in such scenarios. 
+In this case we would be trading generality for fidelity. 
+% \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
+% \tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
+The main advantage of the algorithm is that we can simulate with a unitary 
+circuit
+% simple, and if we want 
+% to 
+any Pauli channel, 
+% (for example,
+% for simulating a Pauli dynamical map as we will see later),
+only varying a couple of angles in the circuit.
+%  to move between 
+% different Pauli channels and not completely reconstruct the circuit. 
+In fact, as we will see, sometimes only changing one angle in the circuit will
+be enough to simulate many non-unitary dynamical maps of physical interest. 
+\cpnote{Revisa estas ultimas frases. Reformule lo que pusiste.}
+
+% {\color{green} This disadvantage comes from the fact
+% that the circuit is applicable to any Pauli channel, which that means that sometimes
+% it is not the most straightforward algorithm to simulate a Pauli channel.
+% However, the main advantages are that the algorithm is simple, and if we want 
+% to simulate many Pauli channels (for example,
+% for simulating a Pauli dynamical map as we will see later),
+% we only have to change a couple of angles in the circuit to move between 
+% different Pauli channels and not completely reconstruct the circuit. 
+% And as we will see, sometimes only changing
+% one angle in the circuit will be enough.}\\
+% $\;$\\
+% 
+% \tbnote{Sección que agregué:}\\
+% }}}
+\subsection{Simulation of a two-qubit Pauli channel} \label{2qbit} % {{{
+% {\color{green}
+For the general case of a two-qubit Pauli channel,
+the circuit of \fref{Fig1} requires two main
+qubits and four ancilla qubits.
+% , on which it would be necessary to create the state $\sum_{\vec{\gamma}}
+% b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
+However, the quantum computer which we are using has only \cpnote{cuantos qubits 
+tiene esa compu?}.
+does not have that many qubits,
+We can still simulate a two qubit Pauli channel that does not apply all 
+two-qubit Pauli matrices to the system\cpnote{that applies at most tantos operaciones 
+de Pauli}.
 For example, consider the following two-qubit dephasing channel:
@@
 where $p \in [0,1]$ is a parameter that defines the channel. 
-Since this channel has $4$ Pauli operations, 
-only $2$ ancilla qubits will be necessary, and it can be implemented
+Since this channel has four Pauli operations, 
+only $2$ ancilla qubits will be necessary, and thus it can be implemented
 using the circuit of \fref{2qbit}b.
@@
 \includegraphics{images/qbit-im.pdf}
-\caption{{\bf Circuit for 2-qubit dephasing channel.}  Circuit implementation for the 2-qubit dephasing channel of \eref{2qbit-c}.
-The state on the two ancilla qubits can be constructed just as it was done for \fref{Fig2}.
-}
+\caption{{\bf Circuit for 2-qubit dephasing channel.}  Circuit implementation
+for the 2-qubit dephasing channel of \eref{2qbit-c}. The state on the two
+ancilla qubits can be constructed just as it was done for \fref{Fig2}.
+\cpnote{Este caption no está copleto. Falta describir la a y luego la b. De hecho 
+dado que primero proponemos el circuito y luego vemos la fidelidad, propngo 
+poenr el circuito arriba y la fidelidad abajo. TAbien describir ambas cosas. } }
 \label{2qbit}
@@
 Just as for the one-qubit Pauli channels, this 
-channel was implemented on IBM's ibmq-lima  quantum computer and we obtained the Choi 
+channel was implemented on IBM's ibmq-lima  quantum computer. We obtained the Choi 
 matrix by doing quantum process tomography on
@@
 obtained the results shown in \fref{2qbit}a. 
-As can be seen in the figure, the fidelity doesn't vary much as we change the value of $p$,
-and it stays at a value of around $0.75$, 
-and it is biggest around $p=0$, corresponding to the identity channel.
-}
+As can be seen in the figure, the fidelity doesn't vary much as we change the value of $p$.
+It stays at a value of around $0.75$, and it is biggest around $p=0$,
+corresponding to the identity channel\cpnote{Una descripcion mas precisa de
+estos valores por favor.}
+% }
 
@@
 \end{definition}
-\revnote{This definition is vague - given the vagueness of the term "quantum circuit".
- Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit.}
- \tbnote{Agregar lo siguiente a la definición:}
-
-{\color{green}
+% \revnote{This definition is vague - given the vagueness of the term "quantum circuit".
+%  Here what you are defining is just a unitary operation acting on a N-qubit Hilbert space, that is parameter dependent only locally on one specific qubit.}
+%  \tbnote{Agregar lo siguiente a la definición:} 
+%  
 Therefore, a 1PR circuit implements a unitary operator $U(p)$ on some number $N$ of qubits,
 such that $U$ depends on the parameter $p$ only locally on one specific qubit.
-}
 
@@
 \end{theorem}
-\textbf{Proof:}  \revnote{again, this is not a conclusion from theorem 1.
-This is literally Definition 1.
-Also, use the proper notation here - make A and B operators living on an dim N Hilbert state, and R explixitly dependent on s and operating on qubit N.
-Then the matrix representation of the operators is a $2^n \times 2^n$ matrix which is applied to the state j....
-The explanation in words in not sufficient.} \tbnote{Cambié la siguiente oración por el párrafo en verde}
-We can conclude from theorem 1 that $U=ARB$,
-where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
-applied to the last qubit and controlled by some of the other ones.
-
-{\color{green} As before, from the definition of a 1PR circuit, we know that $U(p)$ can be decomposed as $ARB$, where 
-$A,B$ are unitary operators acting on the $N$-qubit system
-and $R$ is a rotation applied to one qubit.
-From theorem 1, we conclude that $R$ can be taken in general as a $\sigma_3$
-rotation of angle $2s(p)$ applied to the last qubit and controlled by some of the other ones.
-To prove this theorem,
-we will apply $U(p)$ to $|j\rangle$ by first applying $B$,
-then $R_{\sigma_3}(2s(p))$ and finally $A$, with
-the goal of getting to \eref{eq:uj}. }
+\textbf{Proof:}  
+% \revnote{again, this is not a conclusion from theorem 1. This is literally
+% Definition 1. Also, use the proper notation here - make A and B operators
+% living on an dim N Hilbert state, and R explixitly dependent on s and operating
+% on qubit N. Then the matrix representation of the operators is a $2^n \times
+% 2^n$ matrix which is applied to the state j.... The explanation in words in not
+% sufficient.} \tbnote{Cambié la siguiente oración por el párrafo en verde}
+% We can conclude from theorem 1 that $U=ARB$,
+% where $A$ and $B$ are unitary matrices and $R$ is a $\sigma_3$ rotation of angle $2s$
+% applied to the last qubit and controlled by some of the other ones. 
+% {\color{green} 
+As before, from the definition of a 1PR circuit, we know that $U(p)$ can be
+decomposed as $ARB$, where $A,B$ are unitary operators acting on the $N$-qubit
+system and $R$ is a rotation applied to one qubit.  From theorem 1, we conclude
+that $R$ can be taken in general as a $\sigma_3$ rotation of angle $2s(p)$
+applied to the last qubit and controlled by some of the other ones.  To prove
+this theorem, we will apply $U(p)$ to $|j\rangle$ by first applying $B$, then
+$R_{\sigma_3}(2s(p))$ and finally $A$, with the goal of getting to
+\eref{eq:uj}. 
+% }
 
@@
 so that the result is given by:
-\begin{eqnarray*}
-U|j\rangle = AR_{\sigma_3}(2s(p)) B|j\rangle = e^{-is(p)} A |\tilde{a}^j\rangle + e^{is(p)} A |\tilde{b}^j\rangle + A |\tilde{c}^j\rangle = e^{-is(p)} |a^j\rangle + e^{is(p)} |b^j\rangle + |c^j\rangle,
-\end{eqnarray*}
+% \begin{eqnarray*}
+\begin{align}
+U|j\rangle &= AR_{\sigma_3}(2s(p)) B|j\rangle \nonumber \\
+           &= e^{-is(p)} A |\tilde{a}^j\rangle + e^{is(p)} A |\tilde{b}^j\rangle 
+              + A |\tilde{c}^j\rangle \nonumber \\
+           &= e^{-is(p)} |a^j\rangle + e^{is(p)} |b^j\rangle + |c^j\rangle,
+\end{align}
+% \end{eqnarray*}
 where $|a^j\rangle = A |\tilde{a}^j\rangle, |b^j\rangle = A |\tilde{b}^j\rangle, |c^j\rangle = A |\tilde{c}^j\rangle$ are still orthogonal
@@
 using an optical arrangement, and  it was indeed done 
-by varying only one angle that depends on the parameter $p$ (the angle of a half waveplate). \revnote{there is literally one parameter in one qubit, of course it depends on one parameter...
- how can this be a result?}
-\tbnote{Aquí la verdad no entiendo del todo qué intenta decir.
-El resultado es que en ese paper sólo hubo que variar un parámetro
-para hacer el bit phase flip, que coincde con lo que nosotros 
-probamos sobre qué canales se pueden hacer con una rotación parametrizada (pues bit phase flip es uno de esos). }
+by varying only one angle that depends on the parameter $p$ (the angle of a
+half waveplate). 
+% \revnote{there is literally one parameter in one qubit, of
+% course it depends on one parameter...
+%  how can this be a result?}
+% \tbnote{Aquí la verdad no entiendo del todo qué intenta decir.
+% El resultado es que en ese paper sólo hubo que variar un parámetro
+% para hacer el bit phase flip, que coincde con lo que nosotros 
+% probamos sobre qué canales se pueden hacer con una rotación parametrizada (pues bit phase flip es uno de esos). }
 
@@
 that can be implemented with a 1PR circuit in \fref{Fig5}. 
-\revnote{This is interesting, instead of giving only some random examples, I would actually explore more in details the zoology of this class of dynamical maps - if lucky, you would find class of interesting problems that can be simulated effectively in an experimental setup by just accessing one parameter (as the authors say, just with one set of waveplates, for example), }
-\tbnote{Los mapas que ya mencionamos más a profundidad (depolarizing, phase damping, etc.) son esos ejemplos creo yo.
-Pues son ejemplos de mapas útiles o conocidos (por lo menos el depolarizing y los bit flip, phase flip, bit phase flip) y que
-probamos que se pueden hacer con una rotación parametrizada.}
+% \revnote{This is
+% interesting, instead of giving only some random examples, I would actually
+% explore more in details the zoology of this class of dynamical maps - if lucky,
+% you would find class of interesting problems that can be simulated effectively
+% in an experimental setup by just accessing one parameter (as the authors say,
+% just with one set of waveplates, for example), }
+% \tbnote{Los mapas que ya mencionamos más a profundidad (depolarizing, phase damping, etc.) son esos ejemplos creo yo.
+% Pues son ejemplos de mapas útiles o conocidos (por lo menos el depolarizing y los bit flip, phase flip, bit phase flip) y que
+% probamos que se pueden hacer con una rotación parametrizada.}
 
@@
 
-\revnote{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit.
+% \revnote{I feel that there needs to be a treatment of what happens, at least qualitatively at higher than two dimension, as one of the selling point is the generality of the formalism for N qubit.
 I expect, however, that the higher the dimension, the less rich is the space that can be parametrised by only one parameter, so..
 what is the applicability of the theorem for higher dimensions?}
-
-\tbnote{Añadí el párrafo en verde hablando de eso.}
-
+% 
+% \tbnote{Añadí el párrafo en verde hablando de eso.}
+% 
 In this work, we found a quantum algorithm for 
@@
 generalized it to Pauli dynamical maps
-by using parametrized quantum circuits \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise.}.
+by using parametrized quantum circuits.
+%  \revnote{imprecise} \tbnote{No sé exactamente qué es imprecise.}.
 Furthermore, we implemented single-qubit Pauli channels
@@
 parametric operations in the circuit 
-by requiring that only one single-qubit rotation depends on the parameter. \revnote{This reasoning I miss, simplifying for achieving what goal? } 
-\tbnote{Le di una reescritura a esa frase.}
+by requiring that only one single-qubit rotation depends on the parameter. 
+% \revnote{This reasoning I miss, simplifying for achieving what goal? } 
+% \tbnote{Le di una reescritura a esa frase.}
 In theorem \ref{theorem2} we found the general mathematical conditions for 
 this, applicable to any parametrized circuit.
-\tbnote{Given this condition, we considered the space of Pauli maps that are possible to parametrize with one parameter, and 
-gave some explicit examples for a system of one qubit. 
-As the number of qubits gets bigger, the degrees of freedom for choosing a Pauli dynamical map also gets bigger,
-so we would expect that the space of maps that can be done with only 
-one parameter
-becomes a smaller part of the whole space of Pauli dynamical maps.
-However, some paradigmatic maps as the dephasing one we studied for 2 qubits in section \ref{2qbit} will still be
-possible to do with a 1PR circuit (for this case, this can be seen by
-noticing that said dephasing channel in \eref{2qbit-c} has the same form as the depolarizing channel of \eref{eq:depo}, which we proved
-to be possible to implement with a 1PR circuit).}
+\tbnote{Given this condition, we considered the space of Pauli maps that are
+possible to parametrize with one parameter, and gave some explicit examples for
+a system of one qubit.  As the number of qubits gets bigger, the degrees of
+freedom for choosing a Pauli dynamical map also gets bigger, so we would expect
+that the space of maps that can be done with only one parameter
+becomes a relatively smaller part of the whole space of Pauli dynamical maps.
+However, some paradigmatic maps as the dephasing one we studied for 2 qubits in
+section \ref{2qbit} will still be possible to do with a 1PR circuit (for this
+case, this can be seen by noticing that said dephasing channel in
+\eref{2qbit-c} has the same form as the depolarizing channel of \eref{eq:depo},
+which we proved to be possible to implement with a 1PR circuit).}
+\cpnote{Reescribe lo anterior sin hacer referencias a ecuaciones o secciones.}
 
@@
 and we observe the effect that the error of a quantum computer have
-on these simulations, quantified by the fidelity. \revnote{There is no quantification of this, it´s not even the focus of the paper} \tbnote{ya cambié la oración}
+on these simulations, quantified by the fidelity. 
+% \revnote{There is no quantification of this, it´s not even the focus of the paper} \tbnote{ya cambié la oración}
 On the other hand, the result

### 2023-11-17 main.tex
Derp

@@
 \section*{Abstract}
-% \cpnote{Revisar}
 Pauli channels are fundamental in the context of quantum computing as they
@@
 dynamical maps, defined as a continuous parametrization of multi-qubit Pauli
-channels.  Therefore, in section \ref{sec: 1PR Circuits} we shift our focus to
-study parametrized quantum channels, aiming to adapt the algorithm developed
-for channels to dynamical maps\cpnote{Me parece que las dos frases anteriores 
-dicen casi lo mismo. Poner una sola frase}.  Furthermore, we contribute to the body of work
+channels. In fact, in order  to implement them, we study parametrized quantum
+circuits in chapter \ref{sec: 1PR Circuits}. Furthermore, we contribute to the body of work
 related to parametrized quantum circuits by establishing a theorem, which  sets
@@
 be enough to simulate many non-unitary dynamical maps of physical interest.
-\cpnote{Revisa estas ultimas frases. Reformule lo que pusiste.}
 
@@
 % }}}
-\subsection{Simulation of a two-qubit Pauli channel} \label{2qbit} % {{{
+\subsection{Simulation of a two-qubit Pauli channel} \label{2qbit-s} % {{{
 % {\color{green}
@@
 % b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
-However, the quantum computer which we are using has only \cpnote{cuantos qubits 
-tiene esa compu?}.
-does not have that many qubits,
-We can still simulate a two qubit Pauli channel that does not apply all 
-two-qubit Pauli matrices to the system\cpnote{that applies at most tantos operaciones 
-de Pauli}.
+However, the quantum computer which we are using has only 5 qubits.
+We could still simulate a two qubit Pauli channel that applies at most $8$ Pauli operations,
+instead of 16 which would be the most general case,
+using the three ancilla qubits. 
 For example, consider the following two-qubit dephasing channel:
@@
 \caption{{\bf Circuit for 2-qubit dephasing channel.}  Circuit implementation
-for the 2-qubit dephasing channel of \eref{2qbit-c}. The state on the two
+for the 2-qubit dephasing channel of \eref{2qbit-c} and fidelity results of its implementation using ibmq-lima.
+ The circuit is shown in figure a), where the  state on the two
 ancilla qubits can be constructed just as it was done for \fref{Fig2}. 
-\cpnote{Este caption no está copleto. Falta describir la a y luego la b. De hecho 
-dado que primero proponemos el circuito y luego vemos la fidelidad, propngo 
-poenr el circuito arriba y la fidelidad abajo. TAbien describir ambas cosas. } }
+In figure b) we show the results of fidelities after implementing
+this circuit on ibmq-lima for $25$ values of $p$ between $0$ and $1$, 
+each of which is simulated $10$ times.
+}
 \label{2qbit}
@@
 As can be seen in the figure, the fidelity doesn't vary much as we change the value of $p$.
-It stays at a value of around $0.75$, and it is biggest around $p=0$,
-corresponding to the identity channel\cpnote{Una descripcion mas precisa de
-estos valores por favor.}
-% }
+The average fidelity over all values of $p$ is $0.758$ and it is biggest when $p=0$,
+corresponding to the identity channel, where it reaches a fidelity of $0.874$.
 
@@
 
-\tbnote{Buscar alguna forma fácil de probar que no todos los mapas tienen la forma de 1PR} 
 \end{itemize}
@@
 this, applicable to any parametrized circuit.
-\tbnote{Given this condition, we considered the space of Pauli maps that are
+Given this condition, we considered the space of Pauli maps that are
 possible to parametrize with one parameter, and gave some explicit examples for
@@
 becomes a relatively smaller part of the whole space of Pauli dynamical maps.
-However, some paradigmatic maps as the dephasing one we studied for 2 qubits in
-section \ref{2qbit} will still be possible to do with a 1PR circuit (for this
-case, this can be seen by noticing that said dephasing channel in
-\eref{2qbit-c} has the same form as the depolarizing channel of \eref{eq:depo},
-which we proved to be possible to implement with a 1PR circuit).}
-\cpnote{Reescribe lo anterior sin hacer referencias a ecuaciones o secciones.}
+However, some paradigmatic maps as the dephasing one we studied for 2 qubits will still be possible to do with a 1PR circuit (for this
+case, this can be seen by noticing that said dephasing channel
+has the same form as the depolarizing channel for one qubit,
+which we proved to be possible to implement with a 1PR circuit).
 

### 2023-11-17 Response to Reviewers.tex
Cambios-carta

@@
 We thank the first reviewer for the time spent carefully 
-reviewing the manuscript, and the opinions regarding it.
+assessing the manuscript, and the opinions given.
 We have made major changes in the manuscript following your comments and recommendations. 
@@
 \begin{itemize}
-\item We rewrote big parts of the introduction to make more clear the logic of the paper. 
+\item We rewrote big parts of the introduction to make clearer the logic and motivation of the paper. 
 We begin the paper by presenting the theory of Pauli channels, 
-and then present the first result, which is the algorithm for simulating them on a quantum computer.
+and then show the first result, which is the algorithm for simulating them on a quantum computer,
+which we try out for systems of one and two qubits.
 With that algorithm in mind, we seek to generalize it to Pauli dynamical maps, 
@@
 \item We added the data and code from the IBM quantum computer simulations
-to a Github repository.
-\item We improved the tightness of the formulation by adding
+to a Github repository: \href{https://github.com/tbasile/Quantum-simulation-of-Pauli-Channels.git}{https://github.com/tbasile/Quantum-simulation-of-Pauli-Channels.git}
+\item We improved the tightness of the mathematical formulation by adding
 a more mathematical definition of 1PR circuits and
-rephrasing the proof of theorem 2 to make it more clear. 
-\item In section 5 of the paper we expanded on the examples for Pauli dynamical maps
+rephrasing the proof of theorem 2 to make it clearer. 
+The specific changes are discussed below as responses to the comments made by the reviewer throughout the text.
+\item In section 5 of the paper we expanded the explanations on the examples for Pauli dynamical maps
 that can be implemented with a 1PR circuit.
 These Pauli dynamical maps are well-known and we prove here
-that they can be done with only moving one parameter in the circuit.
-Furthermore, we also implemented these dynamical circuits on IBM's using a 1PR circuit.
+that they can be done with only moving one parameter in the circuit. We also added explicitly the matrices $A$ and $B$ that can
+be used to simulate them with a 1PR circuit.
+Furthermore, we included Fig. 8, where
+we show the results of implementing these dynamical circuits on IBM's computer using a 1PR circuit.
 
@@
 algorithms and performance plots shall supply a fair presentation on
-the scientific soundness of this work.} \\
+the scientific soundness of this work.} \\$\;$\\
 
@@
 added section 3.3 in which we simulate a two qubit Pauli dynamical map 
-and show that the fidelities are still reasonably high. 
-Furthermore, we also supplied plots of the simulation of the
-three Pauli dynamical maps studied in section 5. 
-For each of these simulations, we used the proposed 1PR circuit and plotted the fidelities for
+and in Fig. 4 show that the fidelities are still reasonably high.
+
+Regarding the 1PR circuits, we added explicitly the matrices $A$ and $B$
+to the examples of dynamical maps and
+simulated them on IBM's quantum computer
+using the dynamical Pauli channel implementation.
+For each of these simulations, we used the proposed 1PR circuit and plotted  in Fig. 8 the fidelities for
 different channels along the dynamical map.
+
+Finally, we included a paragraph in the conclusion discussing what happens on higher dimensions and arguing that paradigmatic
+channels such as the two qubit dephasing channel of section 3.3 will still have a 
+1PR circuit implementation.
 
@@
 
-We rewrote parts of the introduction to make the objective of the manuscript more clear. 
+We rewrote parts of the introduction to make the objective of the manuscript clearer. 
 First of all, one of the principal objectives of quantum computers nowadays
@@
 are its simplicity and generality.
-We choose to represent the channel using a gate-based formalism because
+We chose to represent the channel using a gate-based formalism because
 of it being one of the most common and general ways of
@@
 to having to adapt only one setting of an experiment
-to simulate a quantum operation.
+to simulate the quantum operation.
 
@@
 \item \textbf{Why?}\\
-We rephrased the sentence to make the point more clear
+We rephrased the sentence to make the point clearer
 and explained that as a consequence of the circuit being usable in general for any Pauli channel,
 it implements unitary channels in a very roundabout way.
-
-\item \textbf{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.} \\
 
@@
 Being general gives the possibility to later use it for Pauli dynamical maps by only needing to vary the parameters
-and not the design of the circuit in general.
+and not the design of the circuit itself.
 
@@
 They are only orthogonal, since their individual norms are not equal to $1$. 
+After restructuring the proof of theorem 2, this is now clearer.
 
@@
 
-We rephrased the first paragraph of the proof to make it more clear when we use the result of theorem 1. 
+We rephrased the first paragraph of the proof to make it easier to see when we use the result of theorem 1. 
 Basically, we first use definition 1 to say that the circuit has the form $ARB$,
@@
 
-We changed the phrasing to make it more clear that $A$ and $B$ 
+We changed the phrasing to make it clearer that $A$ and $B$ 
 are restricted to act in a particular way on the last 3 and first qubit respectively.
@@
 
-We added examples of these matrices for the three particular dynamical maps shown in the next section. \\
+We added examples of these matrices for the particular dynamical maps shown in section 5. \\
 
@@
 
-We have rephrased parts of the conclusion to make it more clear.
+We have rephrased parts of the conclusion to make it clearer.
 
@@
 
-We rephrased the conclusion to make it more clear. We wanted to reduce the number of parametrized gates
+We rephrased the conclusion to make it clearer. We wanted to reduce the number of parametrized gates
 so as to have only one parameter that works as a kind of knob to move around in the channels forming

### 2023-11-17 main.tex
Cambios-carta

@@
 simulation of the evolution of open quantum systems~\cite{Garcia, Wang,Weimer}
-and specifically for quantum channels~\cite{Xin,Wei,Zanetti}, 
+and specifically for quantum channels~\cite{He-Lu,Xin,Wei,Zanetti}, 
 which can be used to study and model decoherence.
